### 2025-02-17 paper.tex
Initial paper

\documentclass[twoside,11pt]{article}

\usepackage{blindtext}

% Any additional packages needed should be included after jmlr2e.
% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

% Available options for package jmlr2e are:
%
%   - abbrvbib : use abbrvnat for the bibliography style
%   - nohyperref : do not load the hyperref package
%   - preprint : remove JMLR specific information from the template,
%         useful for example for posting to preprint servers.
%
% Example of using the package with custom options:
%
% \usepackage[abbrvbib, preprint]{jmlr2e}

\usepackage{jmlr2e}
\usepackage{amsmath}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}

\usepackage{lastpage}
\jmlrheading{23}{2022}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}

% Short headings should be running head and authors last names

\ShortHeadings{Sample JMLR Paper}{One and Two}
\firstpageno{1}

\begin{document}

\title{Comparison of canonical polychotomous coupling methods with the method of Wu-Lin-Weng}

\author{\name Ondrej Šuch \email ondrejs@savbb.sk \\
       \addr Matematický ústav SAV\\
       Ďumbierska 1\\
       Banská Bystrica, 974 01, Slovakia
       \AND
       \name Peter Novotný \email two@cs.berkeley.edu \\
       \addr Division of Computer Science\\
       University of California\\
       Berkeley, CA 94720-1776, USA}

\editor{My editor}

\maketitle

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
\blindtext
\end{abstract}

\begin{keywords}
  keyword one, keyword two, keyword three
\end{keywords}

\section{Introduction}

%\blindmathpaper

Multi-class classification is considered to be a more challenging problem than binary classification.  A natural approach to multi-class classification is to reduce it to a series of binary classification problems and deduce the multi-class decision by aggregating decisions for the binary problems.

One popular method belonging to  this paradigm uses probabilistic modelling for one-vs-one series of binary problems. Notably, it is used as the basis for multi-class classification models using support vector machines (SVM) in LIBSVM library. However one can use the approach more generally,  because it can be applied to any probabilistic binary classification method.

A key step in probabilistic one-vs-one modelling is the aggregation of results of individual binary classifiers - so-called \emph{coupling method}. The most commonly used coupling method is that proposed by Wu-Lin-Weng. As noted in \cite{dohau}, the method is (one of) non-canonical decisions used in multi-class SVM modelling. The goal of this paper is to compare its behavior with canonical methods.

\section{Theoretical basis of coupling methods}

Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$. Let us denote the $r_{ij}(x)$ the output of Bayes (binary) classifier for $x$ in $X$ yielding the probability $p(x \in C_i \mid x\in C_i \cup C_j )$. Then we have
$$
r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
$$
Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_ij$ for all pairs $i\not= j$. A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
$$
\hat{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt}
$$

Clearly, the equations in \eqref{eq:bt} can be transformed to a system of linear equations. One should note that 
\begin{itemize}
\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
\end{itemize}

Here is a citation \cite{chow:68}.

% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references

\acks{All acknowledgements go at the end of the paper before appendices and references.
Moreover, you are required to declare funding (financial activities supporting the
submitted work) and competing interests (related financial activities outside the submitted work).
More information about this disclosure can be found on the JMLR website.}

% Manual newpage inserted to improve layout of sample file - not
% needed in general before appendices/bibliography.

\newpage

\appendix
\section{}
\label{app:theorem}

% Note: in this sample, the section number is hard-coded in. Following
% proper LaTeX conventions, it should properly be coded as a reference:

%In this appendix we prove the following theorem from
%Section~\ref{sec:textree-generalization}:

In this appendix we prove the following theorem from
Section~6.2:

\noindent
{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
respective empirical mutual information values based on the sample
$\dataset$. Then
\[
	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
\]
with equality only if $u$ is identically 0.} \hfill\BlackBox

\section{}

\noindent
{\bf Proof}. We use the notation:
\[
P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
\]
These values represent the (empirical) probabilities of $v$
taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\

{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}

\vskip 0.2in
\bibliography{sample}

\end{document}

### 2025-02-19 glm1.R
Added framework to keep information about binary classifiers

@@ -9,17 +9,27 @@ files <- c( "dna",
             "usps", 
             "waveform")
 
+my_pmap <- function(l, f = rbind.data.frame) {
+    stopifnot(is.list(l))
+    stopifnot(is.list(l[[1]]))
+    lapply (1:length(l[[1]]), function(i) {
+        ml <- lapply(1:length(l), function(j) l[[j]][[i]])
+        do.call(f, ml)
+    })
+}
+
 glm1 <- function(files = files, workers = 12) {
     plan(multicore, workers = workers)
 
     map (files, function(file) {
         map (c(300, 800), function(n) {
             future_map (0:19, ~ {
-                dfs <- read_wlw(n, dataset = file, .)
+                print(.)
+                dfs <- read_wlws(n, dataset = file, .)
                 model_glm1(dfs)
-            }) |> future_map_dfr(~ . )
-        }) |> list_rbind()
-    }) |> list_rbind()
+            }) |> my_pmap()
+        }) |> my_pmap()
+    }) |> my_pmap()
 }
 
 e <- new.env(parent = emptyenv()) 
@@ -45,6 +55,12 @@ model_glm1 <- function(dfs, alpha = 0) {
 
     min_lambda <- Inf
     max_lambda <- -Inf
+
+    binary = data.frame(i = vector("integer", 0),
+                        j = vector("integer", 0),
+                        lambda = vector("numeric", 0)
+                        )
+                        
     for (i in 1:(K-1)) {
         for (j in (i+1):K) {
             df_ij <- filter(df, class_id %in% c(i,j))
@@ -61,7 +77,7 @@ model_glm1 <- function(dfs, alpha = 0) {
 
             y <- as.matrix(cbind(v2, v1))
             # y <- as.numeric(df$class_id == i) * (1 - 1/ nrow(df)) + 0.5 /nrow(df)
-            cv1  <- cv.glmnet(x, y, family = binomial(), alpha = alpha)
+            cv1  <- cv.glmnet(x, y, family = binomial(), alpha = alpha, standardize = F)
             lambda <- cv1$lambda.min
             if (lambda == min(cv1$lambda)) {
                 print(sprintf("lower too large %d %d", i, j))
@@ -70,13 +86,15 @@ model_glm1 <- function(dfs, alpha = 0) {
                 print(sprintf("upper too small %d %d", i, j))
             }
             print(lambda)
[…]

### 2025-02-19 glm1.R
Added computation of binary precision

@@ -56,9 +56,13 @@ model_glm1 <- function(dfs, alpha = 0) {
     min_lambda <- Inf
     max_lambda <- -Inf
 
-    binary = data.frame(i = vector("integer", 0),
+    binary = data.frame(n = vector("integer", 0),
+                        i = vector("integer", 0),
                         j = vector("integer", 0),
-                        lambda = vector("numeric", 0)
+                        lambda = vector("numeric", 0),
+                        lambda_min = vector("numeric", 0),
+                        lambda_max = vector("numeric", 0),
+                        bacc = vector("numeric", 0)
                         )
                         
     for (i in 1:(K-1)) {
@@ -91,7 +95,19 @@ model_glm1 <- function(dfs, alpha = 0) {
             yt <- as.matrix(select(dft, -class_id))
             r[i,j, ] = predict(model, yt, type = "link")
 
-            binary[nrow(binary) + 1, ] <- data.frame(i = i, j = j, lambda = lambda)
+            dfb_ij <- filter(dft, class_id %in% c(i,j))
+            xb <- as.matrix(select(dfb_ij, -class_id))
+            bacc <- mean((dfb_ij$class_id == i)==  (predict(model, xb, type = "link")> 0.5))
+
+
+            binary[nrow(binary) + 1, ] <- data.frame(
+                n = n, 
+                i = i, 
+                j = j, 
+                lambda = lambda, 
+                lambda_min = min(cv1$lambda),
+                lambda_max = max(cv1$lambda), 
+                bacc = bacc)
         } # end loop j
     } # end loop i 
     multi = map (ls(e), function(m) {

### 2025-02-19 glm1.R
Added computation of ECE

@@ -1,5 +1,6 @@
 source("msvm.R")
 library(glmnet)
+library(CalibratR)
 
 files <- c( "dna", 
             "letter", 
@@ -62,7 +63,8 @@ model_glm1 <- function(dfs, alpha = 0) {
                         lambda = vector("numeric", 0),
                         lambda_min = vector("numeric", 0),
                         lambda_max = vector("numeric", 0),
-                        bacc = vector("numeric", 0)
+                        bacc = vector("numeric", 0),
+                        ece = vector("numeric", 0)
                         )
                         
     for (i in 1:(K-1)) {
@@ -97,7 +99,8 @@ model_glm1 <- function(dfs, alpha = 0) {
 
             dfb_ij <- filter(dft, class_id %in% c(i,j))
             xb <- as.matrix(select(dfb_ij, -class_id))
-            bacc <- mean((dfb_ij$class_id == i)==  (predict(model, xb, type = "link")> 0.5))
+            bacc <- mean((dfb_ij$class_id == i)==  (predict(model, xb, type = "link")> 0))
+            ece <- getECE(dfb_ij$class_id == i, predict(model, xb, type = "response"))
 
 
             binary[nrow(binary) + 1, ] <- data.frame(
@@ -107,7 +110,8 @@ model_glm1 <- function(dfs, alpha = 0) {
                 lambda = lambda, 
                 lambda_min = min(cv1$lambda),
                 lambda_max = max(cv1$lambda), 
-                bacc = bacc)
+                bacc = bacc, 
+                ece = ece)
         } # end loop j
     } # end loop i 
     multi = map (ls(e), function(m) {

### 2025-02-23 glm1.R
Added experimental evlauation of trees for triples

@@ -45,10 +45,46 @@ glm1 <- function(files = files, workers = 12) {
     }) |> my_pmap()
 }
 
+
+omit1 <- function(M_logits, idx) {
+    inverse_logit <- function(x) {
+          return(1 / (1 + exp(-x)))
+    }
+    M <- matrix(0, nrow = 3, ncol = 3)
+
+    for (i in 1:3) {
+        for (j in 1:3) {
+            if (i != j)
+                M[i,j] = exp(M_logits[i,j])
+        }
+    }
+
+    p1 <- 1 
+    if (idx != 3) {
+        p2 <- p1 * M[2, 1] 
+    } 
+    if (idx != 2) {
+        p3 <- p1 * M[3, 1] 
+    } else {
+        p3 <- p2 * M[3, 1] 
+    }
+
+    if (idx == 3) {
+        p2 <- p3 * M[2, 3] 
+    }
+    p <- c(p1, p2, p3)
+    p / (sum(p))
+}
+
 e <- new.env(parent = emptyenv()) 
 e[["wlw2"]] = wu2_ld
 e[["normal"]] = normal_ld
 e[["radial"]] = stratified_ld
+
+e3 <- new.env(parent = emptyenv())
+e3[["omit1"]] = function(x) omit1(x, 1)
+e3[["omit2"]] = function(x) omit1(x, 2)
+e3[["omit3"]] = function(x) omit1(x, 3)
 
 
 model_binary <- function(dfs, alpha = 0) {
@@ -155,6 +191,20 @@ model_triple <- function(dfs, alpha  = 0) {
                 map (ls(e), function(m) {
                     p <- sapply(1:N, function(k) {
                         fn <- e[[m]]
+                        vecp <- fn(r[,,k])
+                        which.max(vecp)
+                    })
+                    t2 <- truth[truth %in% triple]
+                    q <- sapply(1:length(t2), function(k) {
+                        which(t2[k] == triple) 
+                    })
+                    res[nrow(res) + 1,] <<- list(i = i, j = j , k = k, 
+                          method = m, 
+                          acc = mean(p == q))
+                })
+                map (ls(e3), function(m) {
+                    p <- sapply(1:N, function(k) {
+                        fn <- e3[[m]]
                         vecp <- fn(r[,,k])
                         which.max(vecp)
                     })

### 2025-02-26 paper.tex
Stated desirata - needs polishing

@@
 The most commonly used coupling method is that proposed by Wu-Lin-Weng.
-As noted in \cite{dohau}, the method is (one of) non-canonical decisions used in multi-class SVM modelling.
+As noted in \cite{dohau}, the method is one of several non-canonical decisions used in multi-class SVM modelling.
 The goal of this paper is to compare its behavior with canonical methods.
@@
 \section{Theoretical basis of coupling methods}
+
+Many different coupling methods have been proposed
+
+\subsection{Bradley-Terry equations}
 
@@
 A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
-$$
+\begin{equation}
 \hat{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt}
-$$
+\end{equation}
 
@@
 \end{itemize}
+
+\subsection{Desiderata on coupling method}
+
+Let us outline what kind of conditions may be desirable in a coupling method.
+
+%\begin{itemize}
+%\item a coupling method should should always provide a unique solution, at least when all $r_{ij}>0$,
+%\item Bradley-Terry consistency,
+%\item canonicity,
+%\item symmetry,
+%\item Bayes covariance,
+%
+%\item good accuracy on benchmark tasks,
+%\item lack of parameters, or at least having a small number of parameters,
+%\item Hinton's minimality,
+%\item simplicity of computation.
+%\end{itemize}
+
+\emph{Unique solution} refers to the fact that the procedure to compute a multi-class probabilistic prediction always converges to a unique solution.
+One way to satisfy this condition would be that it amounts to a linear system of equations in $K$ variables, and the matrix of the system would be invertible.
+Another example would be when the procedure amounts to finding the minimum of a strongly convex function.
+
+\emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
+The requirement states that shouldwe apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
+satisfies \eqref{eq:bt}.
+
+\emph{Canonicity} refers to requirement that the method should be in a natural way unique.
+Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
+Therefore OLS  is a \emph{canonical} way to build a regression model.
+Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
+
+\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on predictions.
+The action of a permutation $\sigma$ extends to the action on pairwise matrix by
+\begin{equation}
+	\hat r^\sigma_{i,j} = \hat r_{\sigma(i), \sigma(j)}
+\end{equation}
+
+\emph{Bayes covariance} is a notion introduced in work \cite{BarredaSuch}.
+It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
+Any Bayes classifier changes its prediction when the priors change.
+The change happens according to Bayes theorem.
+
+\emph{Good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
+This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform.
+However a good coupling method should perform robustly across a variety of datasets.
+A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
+At the time he was submitting his paper describingLDA he had confirmed usefulness of his method not only on the famous iris dataset, but also on two other collaborations with archaeologists.
+
+\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtained unbiased estimates of the parameters of the coupling method.
+This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters.
+This is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
+
+\emph{Simplicity of computation}  may refer to the computational requirement for inference.
+With the dramatic increase of edge computing devices, such as smartphones, a simple, fast, energy-efficient algorithm may be preferable to a better performing one which would require more computational resources.
+
+Let us finally describe \emph{Hinton's minimality}.
+Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction.
+Suppose we are classifying objects from CIFAR-10 dataset.
+If the true class is  a ``dog'', why should we care what is the output of the classifier distinguishing ``airplanes'' from ``ships''?
+The binary classifier is trained only on airplanes and ships, and has never seen a dog.
+One may thus prefer a classifier which somehow suppresses noisy output of classifiers.
+
+The first that the five conditions have a clear mathematical definition, whereas the rest are not exact.
+For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.
+
+\subsection{Linear kernel}
+
+%\begin{tabular}
+\input{glm1-multi.tex}
+%\end{tabular}
 

### 2025-02-27 paper.tex
New version of table

@@
 
+\usepackage{amsmath, amsthm, amssymb}
 \usepackage{jmlr2e}
-\usepackage{amsmath}
+
+\newtheorem{prop}{Proposition}
 
@@
 $$
-Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_ij$ for all pairs $i\not= j$.
+
+The system of equations is called Bradley--Terry equations.
+The equations in \eqref{eq:bt}  can be transformed to a system of linear equations.
+The theoretical basis for one-vs-one classification framework is provided by the following result.
+
+\begin{prop}
+Suppose $p_i(x) >0$ so that all $r_{ij}(x)$ are defined. The system of linear equations \eqref{eq:bt}  has a unique solution which is the multi-class Bayes classifier.
+\end{prop}
+\begin{proof}
+TODO	
+\end{proof}
+
+Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$.
 A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
@@
 
-Clearly, the equations in \eqref{eq:bt} can be transformed to a system of linear equations. One should note that 
+ One should note that 
 \begin{itemize}
@@
 A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
-At the time he was submitting his paper describingLDA he had confirmed usefulness of his method not only on the famous iris dataset, but also on two other collaborations with archaeologists.
+At the time he was submitting his paper describing LDA he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
 
@@
 The binary classifier is trained only on airplanes and ships, and has never seen a dog.
-One may thus prefer a classifier which somehow suppresses noisy output of classifiers.
+One may thus prefer a classifier which somehow suppresses noisy output of (seemingly) irrelevant classifiers.
 

### 2025-03-01 data.qmd
Investigation into separability of Wu-Lin-Weng's benchmark datasets

---
title: "Dataset properties"
author: "Ondrej Such"
date: "2025-03-01"
format: html
---

## Number of classes

First, let us retrieve the number of classes for each dataset 
```{r number of classes}
source("glm1.R")
library(purrr)
library(knitr)

df <- map(files, function(f) {
# df <- map("dna", function(f) {
    dfs <- read_wlws(800, f, 0)  
    data.frame(dataset = f, K = max(dfs$train$class_id))
}) |> list_rbind()

e = new.env(parent= emptyenv())
for (i in 1:nrow(df)) {
    e[[df$dataset[i] ]] = df$K[i]
}

kable(df)
```

Now we check for linear separation of classes

```{r separation}
library(CVXR)

df_sep <- map(1:nrow(df), function(r) {
    map(0:19, function(run) {
        dfs <- read_wlws(800, df$dataset[r], run)
        dft <- dfs$train
        X <- as.matrix(dplyr::select(dft, -class_id))
        K <- df$K[r]

        w <- Variable(ncol(dft) - 1, cols = 1)
        b <- Variable(1)

        tot <- 0 
        for (i in 1:(K-1)) {
            for (j in (i+1):K) {
                X1 <- X[dft$class_id == i,]
                X2 <- X[dft$class_id == j,]
                objective <- Minimize(sum_squares(w))
                constraints <- list (X1 %*% w + b <= -1,
                                     X2 %*% w + b >= 1)
                problem  <- Problem(objective, 
                        constraints = constraints)
                result <- solve(problem, "ECOS")
                if(result$status == "optimal") {
                    tot <- tot + 1
                }
            }
        }
#        stopifnot(F)
        data.frame(dataset = df$dataset[r], K = K, tot = tot)
    }) |> list_rbind()
}) |> list_rbind()

kable(df_sep |> group_by(dataset, K ) |> summarize(mean(tot)))

```

### 2025-03-11 data.qmd
Start work on LDA

@@
 
-df <- map(files, function(f) {
+df <- map(files[1], function(f) {
 # df <- map("dna", function(f) {
@@
 df_sep <- map(1:nrow(df), function(r) {
+# df_sep <- map(1:1, function(r) {
     map(0:19, function(run) {
+        print(sprintf("%s %d", df$dataset[r], run))
         dfs <- read_wlws(800, df$dataset[r], run)
@@
                     tot <- tot + 1
+                } else {
+                    stopifnot(result$status == "infeasible")
                 }
@@
 }) |> list_rbind()
+```
 
-kable(df_sep |> group_by(dataset, K ) |> summarize(mean(tot)))
+Now we output the summary statistics to a table
 
+```{r output)
+library(xtable)
+
+df_sep_sum <- df_sep |> group_by(dataset, K ) |> summarize(mean(tot * 2 / (K * (K-1))))
+
+sink("data-tbl.tex")
+print(xtable(df_sep_sum, label = "tab:sep-sum", digits = 2,
+    caption = "Average number of binary subproblems that are separable for a given dataset"), include.rownames = FALSE)
+sink()
 ```

### 2025-03-11 lda.R

@@ -1,0 +1,246 @@
+source("msvm.R")
+library(glmnet)
+library(CalibratR)
+library(MASS)
+
+files <- c( "dna", 
+            "letter", 
+            "mnist", 
+            "satimage", 
+            "segment", 
+            "usps", 
+            "waveform")
+
+my_pmap <- function(l, f = rbind.data.frame) {
+    stopifnot(is.list(l))
+    stopifnot(is.list(l[[1]]))
+    r <- lapply (1:length(l[[1]]), function(i) {
+        ml <- lapply(1:length(l), function(j) l[[j]][[i]])
+        do.call(f, ml)
+    })
+    names(r) <- names(l[[1]])
+    r
+}
+
+save_glm1 <- function(... ) {
+    l <- glm1(...)
+    dir <- "data"
+    prefix <- sprintf("%s/glm1-", dir)
+    where <- sprintf("%s%s.csv", prefix, c("binary", "multi"))
+    print(where)
+    write_csv(l$binary, file = where[[1]])
+    write_csv(l$multi, file = where[[2]])
+}
+
+glm1 <- function(files = files, workers = 12) {
+    plan(multicore, workers = workers)
+
+    map (files, function(file) {
+        map (c(300, 800), function(n) {
+            future_map (0:19, ~ {
+                print(.)
+                dfs <- read_wlws(n, dataset = file, .)
+                model_glm1(dfs)
+            }) |> my_pmap()
+        }) |> my_pmap()
+    }) |> my_pmap()
+}
+
+
+omit1 <- function(M_logits, idx) {
+    inverse_logit <- function(x) {
+          return(1 / (1 + exp(-x)))
+    }
+    M <- matrix(0, nrow = 3, ncol = 3)
+
+    for (i in 1:3) {
+        for (j in 1:3) {
+            if (i != j)
+                M[i,j] = exp(M_logits[i,j])
+        }
+    }
+
+    p1 <- 1 
+    if (idx != 3) {
+        p2 <- p1 * M[2, 1] 
+    } 
+    if (idx != 2) {
+        p3 <- p1 * M[3, 1] 
+    } else {
+        p3 <- p2 * M[3, 1] 
+    }
+
+    if (idx == 3) {
+        p2 <- p3 * M[2, 3] 
+    }
+    p <- c(p1, p2, p3)
+    p / (sum(p))
+}
+
[…]

### 2025-03-11 decode.cpp
Analysis of triplets for LDA method

@@ -12,6 +12,10 @@
 using namespace Rcpp;
 using namespace Eigen;
 
+static int max_iter = 1000;
+static int max_used = 0;
+
+
 template <typename D> class Decoder {
 
     // static int last_k;
@@ -190,7 +194,15 @@ NumericVector Decoder<D>::stratified(NumericMatrix logits, bool verbose)
        iter++;
        p2 = p4;
        delta = delta1;
-    } while(1);
+    } while(iter < max_iter);
+    
+    if (iter > max_used) {
+        max_used = iter;
+    }
+
+    if (iter == max_iter) {
+        warning("stratified() : Maximum number of iterations reached without convergence");
+    }
 
     if (verbose) {
         std::cout << iter << " extra iterations" << std::endl;
@@ -308,4 +320,24 @@ NumericVector wu2_d(NumericMatrix logits, bool verbose = false) {
 //
 NumericVector wu2_ld(NumericMatrix logits, bool verbose = false) {
     return Decoder<long double>::wu2(logits, verbose);
+}
+
+// [[Rcpp::export]]
+//
+int set_max_iter(int new_iter) {
+    int old_iter = max_iter;
+    max_iter = new_iter;
+    return old_iter;
+}
+
+// [[Rcpp::export]]
+//
+int get_max_iter() {
+    return max_iter;
+}
+
+// [[Rcpp::export]]
+//
+int get_max_used() {
+    return max_used;
 }

### 2025-03-11 lda.R

@@ -1,7 +1,7 @@
 source("msvm.R")
 library(glmnet)
 library(CalibratR)
-library(MASS)
+suppressPackageStartupMessages(library(MASS))
 
 files <- c( "dna", 
             "letter", 
@@ -46,8 +46,46 @@ glm1 <- function(files = files, workers = 12) {
     }) |> my_pmap()
 }
 
-
 omit1 <- function(M_logits, idx) {
+    M <- M_logits
+
+    if (idx != 1) {
+        perm <- if (idx == 2) c(2,1,3) else c(3,2,1)
+        M <- M[perm, perm]
+    }
+
+        if (M[1,2] >= 0) {
+            # p1 >= p2
+        if (M[1,3] >=0) {
+            # p1 is the largets
+            p <- c(1, exp(M[2,1]), exp(M[3,1]))
+        } else {
+            # p3 is the largest
+            p <- c(exp(M[1,3]), exp(M[1,3] + M[2,1]), 1)
+        }
+    } else {
+        # p2 >= p1
+        if (M[1,3] >= 0) {
+            # p2 is the largest
+            p <- c(exp(M[1,2]), 1, exp(M[1,2] + M[3,1]))
+        } else {
+            # p3 is larger than p1, but unsure yet what is the largest
+            if (M[1,3] + M[2,1] >= 0) {
+                # p2 is the largest
+                p <- c(exp(M[1,2]), 1, exp(M[1,2] + M[3,1]))
+            } else {
+                # p3 is the largest
+                p <- c(exp(M[1,3]), exp(M[1,3] + M[2,1]), 1)
+            }
+        }
+    }
+    stopifnot(max(p) <= 1)
+    r <- p / sum(p)
+    if (idx != 1) r[perm] else r
+}
+
+
+omit2 <- function(M_logits, idx) {
     inverse_logit <- function(x) {
           return(1 / (1 + exp(-x)))
     }
@@ -67,14 +105,22 @@ omit1 <- function(M_logits, idx) {
     if (idx != 2) {
         p3 <- p1 * M[3, 1] 
     } else {
-        p3 <- p2 * M[3, 1] 
+        p3 <- p2 * M[3, 2] 
     }
 
     if (idx == 3) {
         p2 <- p3 * M[2, 3] 
     }
     p <- c(p1, p2, p3)
-    p / (sum(p))
+    res <- p / (sum(p))
+    if (sum(is.na(res) > 0)) {
+            print(M_logits)
+            print(idx)
[…]

### 2025-03-11 decode.cpp
Minor tweaks to decoding

@@ -14,6 +14,7 @@ using namespace Eigen;
 
 static int max_iter = 1000;
 static int max_used = 0;
+static NumericMatrix max_matrix;
 
 
 template <typename D> class Decoder {
@@ -180,9 +181,11 @@ NumericVector Decoder<D>::stratified(NumericMatrix logits, bool verbose)
     Eigen::Matrix<D, Dynamic, 1> p2 = p1 / p1.sum();
 
     D delta1, delta = (Q * p2 - p2).squaredNorm();
+    delta1 = delta;
     int iter = 0;
 
     do {
+       delta = delta1;
        Eigen::Matrix<D, Dynamic, 1> p3 = Q * p2;
        Eigen::Matrix<D, Dynamic, 1> p4 = p3 / p3.sum();
        delta1 = (Q * p4 - p4).squaredNorm();
@@ -193,7 +196,6 @@ NumericVector Decoder<D>::stratified(NumericMatrix logits, bool verbose)
        }
        iter++;
        p2 = p4;
-       delta = delta1;
     } while(iter < max_iter);
     
     if (iter > max_used) {
@@ -201,7 +203,9 @@ NumericVector Decoder<D>::stratified(NumericMatrix logits, bool verbose)
     }
 
     if (iter == max_iter) {
-        warning("stratified() : Maximum number of iterations reached without convergence");
+        warning("stratified() : Maximum number of iterations reached without convergence \n delta =%lg\n delta1= %lg\n",
+        delta, delta1);
+        max_matrix = logits;
     }
 
     if (verbose) {
@@ -327,6 +331,7 @@ NumericVector wu2_ld(NumericMatrix logits, bool verbose = false) {
 int set_max_iter(int new_iter) {
     int old_iter = max_iter;
     max_iter = new_iter;
+    max_used = 0;
     return old_iter;
 }
 
@@ -340,4 +345,10 @@ int get_max_iter() {
 //
 int get_max_used() {
     return max_used;
+}
+
+// [[Rcpp::export]]
+//
+NumericMatrix get_max_matrix() {
+    return max_matrix;
 }

### 2025-03-11 msvm.R
Suppress startup messages

@@ -1,8 +1,8 @@
 library(e1071)
-library(dplyr)
+suppressPackageStartupMessages(library(dplyr))
 library(Rcpp)
 library(ParBayesianOptimization)
-library(furrr)
+suppressPackageStartupMessages(library(furrr))
 library(future)
 library(magrittr)
 library(readr)

### 2025-03-12 lda.R
Added code to compute individual LDA multiclass predictions

@@ -1,5 +1,5 @@
 source("msvm.R")
-library(glmnet)
+# library(glmnet)
 library(CalibratR)
 suppressPackageStartupMessages(library(MASS))
 
@@ -134,7 +134,7 @@ e3[["omit13"]] = function(x) omit1(x, 2)
 e3[["omit12"]] = function(x) omit1(x, 3)
 
 # Function to identify columns constant within groups
-remove_constant_within_groups <- function(data, group_col) {
+remove_constant_within_groups <- function(data, group_col, tol = 0) {
   # Extract the grouping variable
   groups <- data[[group_col]]
   # Get numeric predictors (exclude the group column)
@@ -143,8 +143,10 @@ remove_constant_within_groups <- function(data, group_col) {
   # Check each column for constancy within groups
   constant_cols <- sapply(predictors, function(col) {
   # Split column by group and check if variance is 0 (or near 0) in any group
+  # by_group <- tapply(col, groups, function(x) var(x, na.rm = TRUE))
+  # any(by_group == 0 | is.na(by_group))  # NA variance occurs if all values are identical
   by_group <- tapply(col, groups, function(x) var(x, na.rm = TRUE))
-  any(by_group == 0 | is.na(by_group))  # NA variance occurs if all values are identical
+  sum(by_group <= tol)
                                 })
   # Return names of non-constant columns
   names(predictors)[!constant_cols]
@@ -162,19 +164,35 @@ lda_binary <- function(dfs, subclasses = 1:max(dfs$train$class_id)) {
     res1 <- map(1:nrow(pairs), function (r) {
         i <- pairs$i[r]
         j <- pairs$j[r]
+        print(c(i,j))
 
         df_ij <- filter(df, class_id %in% c(i,j))
         df_ij$class_id = factor(df_ij$class_id)
 
         # Identify non-constant columns
         group_col <- "class_id"
-        non_constant_cols <- remove_constant_within_groups(df_ij, group_col)
+        tol <- 0
+        model <- NULL
 
-        # Subset the data to keep only non-constant columns + group column
-        cleaned_data <- df_ij[, c(group_col, non_constant_cols)]
+        while (is.null(model)) {
+            non_constant_cols <- remove_constant_within_groups(df_ij, group_col, tol)
+
[…]

### 2025-03-12 msvm.R

@@ -6,7 +6,7 @@ suppressPackageStartupMessages(library(furrr))
 library(future)
 library(magrittr)
 library(readr)
-library(purrr)
+suppressPackageStartupMessages(library(purrr))
 
 sourceCpp("decode.cpp")
 

### 2025-03-13 decode.cpp
Fix to conform to Wu-Lin-Weng paper; fix computation of logistic function; debugging output

@@ -49,8 +49,15 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
         for (int j = 0; j < k; j++) {
             if (i == j)
                 r(i, j) = 0;
-            else
-                r(i, j) = 1 / (1 + _exp(-logits(i, j)));
+            else {
+                D x = logits(i,j);
+                if (x >= 0) {
+                    r(i, j) = 1 / (1 + _exp(-x));
+                } else {
+                    r(i,j) = _exp(x) / (1 + _exp(x));
+                }
+
+            }
         }
     }
     // std::cout << r << std::endl;
@@ -58,9 +65,14 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
     for (int i = 0; i < k; i++) {
         for (int j = 0; j < k; j++) {
             if (i == j) {
-                D s = 0;
+                D s = 0; // Kahan summation
+                D c = 0;
                 for (int m = 0; m < k; m++) {
-                    s += r(m, i) * r(m, i);
+                    D y = r(m, i) * r(m, i) - c;
+                    D t = s + y;
+                    c = (t - s) - y;
+                    s = t;
+                    // s += r(m, i) * r(m, i);
                 }
                 Q(i,j) = s;
                 Q1(i,j) = s;
@@ -82,16 +94,29 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
     v(k, 0) = 1;
     Eigen::Matrix<D, Dynamic, 1> p1 = 
         Q1.colPivHouseholderQr().solve(v);
+ 
+    p1 = p1.cwiseAbs(); // replaces negative entries by their absolute values
+    p1 = p1 / p1.sum();
     // Eigen::Matrix<D, Dynamic, 1> p2 = p1 / p1.sum();
     D delta1, delta = (Q1 * p1 - v).squaredNorm();
     int iter = 0;
 
     do {
+        int c;
+        if ( (c = (p1.head(k).array() < 0).count()) > 0) {
+            std::cout << "matrix has " << c ;
+            std::cout << " negative entries in iter " ;
+            std::cout << iter << std::endl;
+            if (c > 0) {
+                std::cout << p1.head(k)  << std::endl;
+            }
+
+        }
         Eigen::Matrix<D, Dynamic, 1> p2(k, 1); 
[…]

### 2025-03-15 decode.cpp
Fixed negative entries

@@ -15,6 +15,7 @@ using namespace Eigen;
 static int max_iter = 1000;
 static int max_used = 0;
 static NumericMatrix max_matrix;
+static NumericMatrix A,b, vecx;
 
 
 template <typename D> class Decoder {
@@ -94,25 +95,34 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
     v(k, 0) = 1;
     Eigen::Matrix<D, Dynamic, 1> p1 = 
         Q1.colPivHouseholderQr().solve(v);
+
+    if ( ((p1.head(k).array() < 0).count()) > 0) {
+        A = NumericMatrix(Q1.rows(), Q1.cols(), Q1.data());
+        b = NumericMatrix(v.rows(), v.cols(), v.data());
+    }
  
-    p1 = p1.cwiseAbs(); // replaces negative entries by their absolute values
-    p1 = p1 / p1.sum();
+    // std::cout << p1 << std::endl;
+    // std::cout << "----------------" << std::endl;
     // Eigen::Matrix<D, Dynamic, 1> p2 = p1 / p1.sum();
     D delta1, delta = (Q1 * p1 - v).squaredNorm();
     int iter = 0;
 
     do {
-        int c;
-        if ( (c = (p1.head(k).array() < 0).count()) > 0) {
-            std::cout << "matrix has " << c ;
-            std::cout << " negative entries in iter " ;
-            std::cout << iter << std::endl;
-            if (c > 0) {
-                std::cout << p1.head(k)  << std::endl;
+        bool changed = false;
+        for (int i = 0; i < k; i++) {
+            if (p1[i] < 0) {
+                if (p1[i] < -1e-9) {
+                    Rcpp::stop("Unexpectedly negative probability component");
+                }
+                p1[i] = 0;
+                changed = true;
             }
+        }
+        if (changed) {
 
         }
-        Eigen::Matrix<D, Dynamic, 1> p2(k, 1); 
+        Eigen::Matrix<D, Dynamic, 1> p2(k, 1);
+        p2 = p1.head(k); 
         Eigen::Matrix<D, Dynamic, 1> p3(k + 1, 1); 
         for (int t = 0; t < k; t++) {
             Eigen::Matrix<D, Dynamic, 1> p = p1.head(k);
@@ -130,7 +140,12 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
                 c = (t - s) - y;
[…]

### 2025-03-15 quarto/data.qmd
Quarto documents

--- 2025-03-11 data.qmd
@@
 date: "2025-03-01"
-format: html
+format: pdf
 ---
@@
 
-df <- map(files[1], function(f) {
+df <- map(files, function(f) {
 # df <- map("dna", function(f) {
@@
                 } else {
-                    stopifnot(result$status == "infeasible")
+                    if(result$status != "infeasible") {
+                        print(result$status)
+                    }
                 }
@@
 
-```{r output)
+```{r output}
 library(xtable)
+library(knitr)
 
@@
 
-sink("data-tbl.tex")
-print(xtable(df_sep_sum, label = "tab:sep-sum", digits = 2,
-    caption = "Average number of binary subproblems that are separable for a given dataset"), include.rownames = FALSE)
-sink()
+#sink("data-tbl.tex")
+(kable(df_sep_sum, label = "tab:sep-sum", digits = 2,
+    caption = "Average number of binary subproblems that are separable for a given dataset"))
+#sink()
 ```

### 2025-03-15 quarto/lda.qmd
Quarto documents

---
title: " LDA example"
author: "Ondrej Such"
date: "2025-03-11"
format: pdf
---

## Number of classes

First, let us read the data files
```{r read data files for mnist}
source("lda.R")
dfs <- read_wlws(800, "mnist", 2)
```

Now let us compute result of coupling methods for all triplets of classes
```{r triplets}
r <- lda_triples(dfs)
```

Now we display interesting cases

```{r display interesting cases}
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(knitr))
df <- r |> 
    pivot_wider(names_from = "method", values_from = "acc") |> 
    filter(wlw2 > normal + 0.15) |> 
    mutate(imp =  wlw2 - pmax(omit12, omit23, omit13)) |> 
    arrange(desc(imp))

kable(df, digits = 3)
```

### 2025-03-15 lda.R
Add id's, and identify the predictoin based on the coupling method

@@ -266,7 +266,11 @@ lda_pred3 <- function(dfs, i, j, k) {
             fn(r[,,k])
         }) |> t()
         colnames(p) <- c("p1", "p2", "p3")
-        data.frame(p[idx,], truth = q, method = m, original = truth[idx])
+        pred <- apply(p[idx,],1, which.max)
+        data.frame(p[idx,], 
+                    id = 1:sum(idx), orig_id = (1:N)[idx], 
+                    truth = q, pred = pred, method = m, 
+                    orig_truth = truth[idx])
     }) |>  list_rbind()
     # print(dim(df1))
     # df2 <- map (ls(e3), function(m) {

### 2025-03-15 separation.R
Allow make to automate computation of separability

@@ -1,0 +1,37 @@
+library(CVXR)
+source("msvm.R")
+source("lda.R")
+
+check_sep <- function(f = "dna") {
+    print(sprintf("%s ", f ))
+    map(0:19, function(run) {
+        dfs <- read_wlws(800, f , run)
+        dft <- dfs$train
+        X <- as.matrix(dplyr::select(dft, -class_id))
+        K <- max(dft$class_id)
+
+        w <- Variable(ncol(dft) - 1, cols = 1)
+        b <- Variable(1)
+
+        df <- map (1:(K-1), function(i) {
+            map ((i+1):K, function(j) {
+                X1 <- X[dft$class_id == i,]
+                X2 <- X[dft$class_id == j,]
+                objective <- Minimize(sum_squares(w))
+                constraints <- list (X1 %*% w + b <= -1,
+                                     X2 %*% w + b >= 1)
+                problem  <- Problem(objective, 
+                        constraints = constraints)
+                solvers <- c("ECOS")
+                map (solvers, function(solver) {
+                    result <- solve(problem, solver)
+                    data.frame(i = i, j = j, status = result$status, solver = solver)
+                }) |> list_rbind()
+            }) |> list_rbind()
+        }) |>  list_rbind()
+        df$dataset = f
+        df$K = K
+        df
+    }) |> list_rbind()
+}
+

### 2025-03-15 lda.R
Add function to compute whole dataset accuracies

@@ -164,7 +164,7 @@ lda_binary <- function(dfs, subclasses = 1:max(dfs$train$class_id)) {
     res1 <- map(1:nrow(pairs), function (r) {
         i <- pairs$i[r]
         j <- pairs$j[r]
-        print(c(i,j))
+        # print(c(i,j))
 
         df_ij <- filter(df, class_id %in% c(i,j))
         df_ij$class_id = factor(df_ij$class_id)
@@ -186,11 +186,10 @@ lda_binary <- function(dfs, subclasses = 1:max(dfs$train$class_id)) {
                                 data = cleaned_data), 
             error = function(e) {
                 tol <<- if (tol == 0) 1e-8 else 2 * tol
-                print
                 return(NULL)
             }, 
             finally = if (tol > 0) print(sprintf("Tol increased to %g for %d %d", tol, i,j)))
-            print(is.null(m1))
+            # print(is.null(m1))
             model <- m1
         }
         dft <- dfs$test[, c(group_col, non_constant_cols)]
@@ -351,26 +350,38 @@ lda_multi <- function(dfs) {
     r <- v$r
     N <- nrow(dft)
     K <- max(dft$class_id)
-    dataset <- dfs$dataset
     run = dfs$run
     n = dfs$n
 
-    print("binary done")
+    # print("binary done")
     multi = map (ls(e), function(m) {
-        print(m)
+        # print(m)
         p <- sapply(1:N, function(k) {
                 fn <- e[[m]]
                 vecp <- fn(r[,,k])
                 which.max(vecp)
                 })
-        data.frame(n = n, K = K, method = m, dataset = dataset, run = run,  correct = sum(p == dft$class_id))
+        data.frame(n = n, K = K, method = m, correct = sum(p == dft$class_id))
     } )|> list_rbind()
     # Now, let's do Hinton's oracle
     mr <- sapply(1:N, function(i) 
         sum(r[dft$class_id[i],,i] > 0))
     # print(mr)
     multi <- rbind(multi,
-        data.frame(n = n, K = K, method = "oracle", dataset = dataset, run = run, correct = sum(mr == K-1)))
-        
+        data.frame(n = n, K = K, method = "oracle", correct = sum(mr == K-1)))
+
+    multi$dataset = dfs$dataset
+    multi$run = run
     list(multi = multi, binary = v$binary)
+}
+
+write_multi <- function(runs = 20, workers = 11) {
[…]

### 2025-03-15 decode.cpp
Fixes to NaN results

@@ -6,6 +6,7 @@
 #include <assert.h>
 #include <iostream>
 #include <stdio.h>
+#include <cmath> 
 // #include "../../Rcpp11/inst/include/Rcpp/Array.h"
 
 
@@ -87,6 +88,7 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
         Q1(i, k) = 1;
     }
     Q1(k, k) = 0;
+    // std::cout << "Q1 \n" << Q1 << std::endl;
 
     Eigen::Matrix<D, Dynamic, 1> v(k + 1, 1);
     for ( int i = 0; i < k; i++) {
@@ -109,6 +111,7 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
 
     do {
         bool changed = false;
+        // std::cout << "p1 \n" << p1 << std::endl;;
         for (int i = 0; i < k; i++) {
             if (p1[i] < 0) {
                 if (p1[i] < -1e-9) {
@@ -141,11 +144,15 @@ NumericVector Decoder<D>::wu2(NumericMatrix logits, bool verbose)
                 s = t;
             }
             D newVal = s / Q(t,t);
+            if (std::isnan(newVal)) {
+                p3 = p1;
+                break; // We divide by zero
+            }
             assert(newVal > -1e-9);
             if (newVal < -1e-9) {
                 Rcpp::stop("newVal too small");
             }
-            p2(t, 0) = s >=0 ? newVal : 0 ;
+            p2(t, 0) = newVal >=0 ? newVal : 0 ;
             // Eigen::Matrix<D, Dynamic, 1> p4 = p3 / p3.sum();
             p3(k, 0) = -newb;
             D sum = p2.sum();
@@ -206,23 +213,45 @@ NumericVector Decoder<D>::stratified(NumericMatrix logits, bool verbose)
 
     for (int i = 0; i < k; i++) {
         D s = 0;
-        for (int j = 0; j < k; j++) {
-            if (j != i) {
-                s = s + _exp(logits(j, i));
+        D maxVal = logits(0, i);
+        int idxVal = 0;
+        for (int j = 1; j < k; j++) {
+            if (maxVal < logits(j,i))  {
+                maxVal = logits(j,i) ;
+                idxVal = j;
             }
         }
-        D pmain = 1 / ( 1 + s);
+
[…]

### 2025-03-16 lda.R
Implement crossevaluatin of stacking ensemble

@@ -2,6 +2,8 @@ source("msvm.R")
 # library(glmnet)
 library(CalibratR)
 suppressPackageStartupMessages(library(MASS))
+library(dplyr)
+suppressPackageStartupMessages(library(tidyr))
 
 files <- c( "dna", 
             "letter", 
@@ -10,6 +12,31 @@ files <- c( "dna",
             "segment", 
             "usps", 
             "waveform")
+
+make_folds <- function(grp, f = 5) {
+    gs <- unique(grp)
+    K <- length(gs)
+    res <- vector("integer", length(grp))
+    for (g in gs) {
+        N <- sum(grp == g)
+        N5 <- N %/% f
+        ubds <- N5 * seq(1, f)
+        R5 <- N %% f
+        v <- as.integer(rep(0, f))
+        if (R5 > 0) {
+            pos <- sample(1:f, size = R5, replace = F)
+            v[pos] <- 1
+        }
+        cumv <- cumsum(v)
+        cubds <- ubds + cumv
+        idx <- grp == g
+        perm <- sample(1:N, replace = F, size = N)  - 1
+        folds <- sapply(perm, function(x) sum(x >= cubds)) + 1
+        res[idx] <- folds
+    }
+    res
+}
+
 
 my_pmap <- function(l, f = rbind.data.frame) {
     stopifnot(is.list(l))
@@ -60,7 +87,7 @@ omit1 <- function(M_logits, idx) {
             # p1 is the largets
             p <- c(1, exp(M[2,1]), exp(M[3,1]))
         } else {
-            # p3 is the largest
+# p3 is the largest
             p <- c(exp(M[1,3]), exp(M[1,3] + M[2,1]), 1)
         }
     } else {
@@ -304,9 +331,16 @@ lda_triples <- function(dfs) {
                 r <- v$r[triple, triple, truth %in% triple]
                 N <- dim(r)[3]
                 map (ls(e), function(m) {
-                    p <- sapply(1:N, function(k) {
+                    p <- sapply(1:N, function(s) {
                         fn <- e[[m]]
-                        vecp <- fn(r[,,k])
+                        vecp <- fn(r[,,s])
+                        if (sum(is.na(vecp)) > 0) {
+                            print(sprintf("Triple %d %d %d is bad for %s", 
+                                            i, j, k, m))
+                            print(r[,,s])
+                            print(vecp)
[…]

### 2025-03-16 lda.R
Added more flexibility to stack model creation - now can select which Bayes covariant methods to use

@@ -436,7 +436,7 @@ write_triples <- function(runs = 20, workers = 11) {
     write.csv(df, file = "data/triples.csv", row.names = F, quote = F)
 }
 
-try_stack <- function(dfs, i, j, k, n = 200, f = 5, div = 10) {
+try_stack <- function(dfs, i, j, k, n = 200, f = 5, div = 10, predictors = 1:4) {
     pred <- lda_pred3(dfs, i, j, k)
     truth <- pred$truth[pred$method =="normal"]
     folds <- make_folds(truth)
@@ -444,37 +444,59 @@ try_stack <- function(dfs, i, j, k, n = 200, f = 5, div = 10) {
     q2 <- as.matrix(filter(pred, method =="omit12") |> dplyr::select(1:3))
     q3 <- as.matrix(filter(pred, method =="omit13") |> dplyr::select(1:3))
     q4 <- as.matrix(filter(pred, method =="omit23") |> dplyr::select(1:3))
+    ql <- list(q1, q2, q3, q4)[predictors]
+    names <- list("normal", "omit12", "omit13", "omit23")[predictors]
+    qL <- length(ql)
+    print(qL)
 
     W <- sapply( 1:n,  function(i) { 
-                    s <- sample(0:div , 3, replace = T) |> sort()
+                    s <- sample(0:div , qL - 1, replace = T) |> 
+                            sort()
+                    if (qL == 2)
+                        c(s[1], div - s[1]) / div
+                    else 
+                        c(s[1], 
+                        sapply(1:(qL - 2), function(i) (s[i + 1] - s[i])),
+                        (div - s[qL - 1])) / div
+                    })  |> t()
 
-                    c(s[1] / div, 
-                            (s[2] - s[1]) / div, 
-                            (s[3] - s[2]) / div,
-                            (div - s[3]) / div) }) |> t()
-    colnames(W) <- c("w1", "w2", "w3", "w4")
+                    # c(s[1] / div, 
+                            # (s[2] - s[1]) / div, 
+                            # (s[3] - s[2]) / div,
+                            # (div - s[3]) / div) }) |> t()
+    colnames(W) <- sprintf("w_%s", names)
     wp <- sapply(1:n, function(i) {
-            p <- W[i,1] * q1 + W[i,2] * q2 + W[i,3] * q3 + W[i,4] * q4
[…]

### 2025-03-17 lda.R
Added PCA preprocessing step

@@ -203,14 +203,23 @@ lda_binary <- function(dfs, subclasses = 1:max(dfs$train$class_id)) {
 
         while (is.null(model)) {
             non_constant_cols <- remove_constant_within_groups(df_ij, group_col, tol)
-
             # Subset the data to keep only non-constant columns + group column
-            cleaned_data <- df_ij[, c(group_col, non_constant_cols)]
-
+            cleaned_data <- df_ij[, non_constant_cols]
+            pca <- prcomp(cleaned_data, 
+                                        tol = 0.001, 
+                                        scale. = F,
+                                        center = F)
+            newd <- as.data.frame(predict(pca, cleaned_data))
+            # print(head(newd))
+            # print(class(newd))
+            newd$class_id = df_ij$class_id
+            # print(dim(newd))
+            # print(head(newd))
+            # stopifnot(F)
 
             m1 <- NULL
             m1 <- tryCatch(lda(class_id == i ~ ., 
-                                data = cleaned_data), 
+                                data = newd), 
             error = function(e) {
                 tol <<- if (tol == 0) 1e-8 else 2 * tol
                 return(NULL)
@@ -219,7 +228,9 @@ lda_binary <- function(dfs, subclasses = 1:max(dfs$train$class_id)) {
             # print(is.null(m1))
             model <- m1
         }
-        dft <- dfs$test[, c(group_col, non_constant_cols)]
+        dft <- predict(pca, dfs$test[, non_constant_cols]) |> as.data.frame()
+        dft$class_id = dfs$test$class_id
+        
         pred <- predict(model, dft)
         dfb_ij <- filter(dft, class_id %in% c(i,j))
         pred_ij <- predict(model, dfb_ij)
@@ -228,12 +239,12 @@ lda_binary <- function(dfs, subclasses = 1:max(dfs$train$class_id)) {
         ece <- getECE(dfb_ij$class_id == i, pred_ij$posterior[,2])
         pr = predict(model, dft )
         prp <- pr$posterior
-        n1 <- sum(cleaned_data$class_id == i)
-        n2 <- sum(cleaned_data$class_id == j)
-        m1 <- mean(predict(model, cleaned_data)$x[cleaned_data$class_id == i])
[…]

### 2025-03-17 lda.R
Added code to sample for the point with highest Brier score for an ensemble of Bayes covariant methods

@@ -288,7 +288,7 @@ lda_binary <- function(dfs, subclasses = 1:max(dfs$train$class_id)) {
 lda_pred3 <- function(dfs, i, j, k) {
     triple <- c(i,j,k)
     v <- lda_binary(dfs, subclasses = triple)
-    K <- max(v$binary$j)
+    K <- max(dfs$train$class_id)
     truth <- dfs$test$class_id
     r <- v$r
     idx <- truth %in% triple
@@ -326,7 +326,8 @@ lda_pred3 <- function(dfs, i, j, k) {
 
 lda_triples <- function(dfs) {
     v <- lda_binary(dfs)
-    K <- max(v$binary$j)
+    K <- max(dfs$train$class_id)
+    print(K)
 
     res <- data.frame(
             i = vector("integer", 0),
@@ -419,7 +420,7 @@ lda_multi <- function(dfs) {
 
     multi$dataset = dfs$dataset
     multi$run = run
-    list(multi = multi, binary = v$binary)
+    list(multi = multi, binary = v$summary)
 }
 
 write_multi <- function(runs = 20, workers = 11) {
@@ -449,36 +450,35 @@ write_triples <- function(runs = 20, workers = 11) {
     write.csv(df, file = "data/triples.csv", row.names = F, quote = F)
 }
 
-try_stack <- function(dfs, i, j, k, n = 200, f = 5, div = 10, predictors = 1:4) {
+gen_W <- function(n = 200, div = 10, qL = 4) {
+  sapply( 1:n,  function(i) { 
+    s <- sample(0:div , qL - 1, replace = T) |> 
+            sort()
+    if (qL == 2)
+        c(s[1], div - s[1]) / div
+    else 
+        c(s[1], 
+        sapply(1:(qL - 2), function(i) (s[i + 1] - s[i])),
+        (div - s[qL - 1])) / div
+    })  |> t()
+}
+
+stack_acc <- function(dfs, i, j, k, W = gen_W(), f = 10, predictors = 1:4) {
+    stopifnot(ncol(W) == length(predictors))
     pred <- lda_pred3(dfs, i, j, k)
     truth <- pred$truth[pred$method =="normal"]
-    folds <- make_folds(truth)
-    q1 <- as.matrix(filter(pred, method =="normal") |> dplyr::select(1:3))
-    q2 <- as.matrix(filter(pred, method =="omit12") |> dplyr::select(1:3))
-    q3 <- as.matrix(filter(pred, method =="omit13") |> dplyr::select(1:3))
[…]

### 2025-03-25 paper.tex
Fix merging

@@
 Then we have
-$$
-r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
-$$
+\begin{equation}
+r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}. \label{eq:bt1}
+\end{equation}
 
 The system of equations is called Bradley--Terry equations.
-The equations in \eqref{eq:bt}  can be transformed to a system of linear equations.
+The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations.
 The theoretical basis for one-vs-one classification framework is provided by the following result.
@@
 \begin{prop}
-Suppose $p_i(x) >0$ so that all $r_{ij}(x)$ are defined. The system of linear equations \eqref{eq:bt}  has a unique solution which is the multi-class Bayes classifier.
+Suppose $p_i(x) >0$ so that all $r_{ij}(x)$ are defined. The system of linear equations \eqref{eq:bt1}  has a unique solution which is the multi-class Bayes classifier.
 \end{prop}
@@
 \begin{equation}
-	\hat{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt}
+	\hat{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
 \end{equation}
@@
 
-\subsection{Desiderata on coupling method}
+\subsection{Exact desiderata on coupling method}
 
@@
 \emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
-The requirement states that shouldwe apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
-satisfies \eqref{eq:bt}.
+The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
+satisfies \eqref{eq:bt1}.
 
@@
 The change happens according to Bayes theorem.
+
+\subsection{Inexact desiderata for coupling methods}
 
@@
 For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.
+
+\section{Examples of coupling methods}
+
+\subsection{Arboreal coupling methods}
+
+This coupling method ignores all but $K-1$ of the pairwise predictions.
+A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes 1 and 3.
+The two equations form \eqref{eq:bt2} together with the requirement that the prediction probabilities should sum to 1 yield the following system of equations
+\begin{equation}
+\begin{split}
+\frac{\hat p_1}{\hat p_2} &= \vec{r}_{12}\\
+\frac{\hat p_2}{\hat p_3} &= \vec{r}_{23}\\
+\hat p_1 + \hat p_2 + \hat p_3 &= 0
+\end{split}
+\end{equation}
+
+For $K=3$, there are three different arboreal coupling methods, which we shall call $omit12$, $omit13$, $omit23$.
+
+In order to obtain a regular system of equations for  larger values of $K$ , the resulting classifiers must form a tree within the complete graph on all classes.
+
+This method is non-canonical, because there is no natural way to choose a tree in a complete graph.
+
+\subsection{Hinton's oracle}
+
+This oracle method assumes it has the access to the ground truth $y = C_i$. It outputs probabilities by solving only the equations
+$$
+\frac{p_i}{p_j} = \vec{r}_{ij},\quad \textrm{for }i\not = j,
+$$
+together  with total sum equation
+$$
+\sum_{i=1}^K  \hat p_i = 1.
+$$
+
+It is thus an arboreal method where the underlying tree forms a star.
+This method is clearly the optimal one with respect to Hinton's minimality criterion.
+It is not a true classification method, because it ``peeks'' at the label.
+Its main utility is to provide a way to benchmark other methods with respect to Hinton's minimality.
+
+%\subsection{Radial coupling}
+%
+%This coupling method aims to convert Hinton's oracle to a practical method.
+Denote by $\hat{\boldsymbol{h}}_i$ the prediction of Hinton's oracle method, if the true class was $C_i$.
+These predictions will generally span the simplex $\sum_i \hat p_i = 1$.
+In that case the prediction $\boldsymbol{r}$ of the method  can be expressed as a linear combination of $\hat{\boldsymbol{h}}_i$.
+The radial coupling method requires that for  weights we could in fact use the components of $\boldsymbol{r}$ i.e.
+%\begin{equation}
+%	\boldsymbol{r} = \sum_{i=1}^K r_i \hat{\boldsymbol{h}}_i. \label{eq:radial}
+%\end{equation}
+%
+%The intuition behind \eqref{eq:radial} is that if some component of $\boldsymbol{r}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\boldsymbol{r}$ should be close to the prediction of Hinton's oracle $\hat{\boldsymbol{h}}_i$.
+
+\subsection{Normal coupling}
+
+\subsection{Wu-Lin-Weng's method}
 

### 2025-03-25 quarto/data.qmd
Fix merging

@@
 
-df <- map(files, function(f) {
-# df <- map("dna", function(f) {
+# df <- map(files[1], function(f) {
+df <- map("dna", function(f) {
     dfs <- read_wlws(800, f, 0)  
@@
                     }
+ #                 stopifnot(result$status == "infeasible")
+
                 }

### 2025-03-25 paper.tex
Added text about divergence based methods

@@
 
+\usepackage{multirow}
+\usepackage{makecell}
+\usepackage{booktabs}
+\usepackage{rotating}
+
 \newtheorem{prop}{Proposition}
@@
 \newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
+\DeclareMathOperator*{\divm}{div}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 
-Many different coupling methods have been proposed
+Suppose we have $K$ classes of objects, each distributed according to a probability distribution $p_i$, $i=1,\ldots, K$ on a feature space $X$.
+In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class.
+Given $x$ in $X$ we aim to find the probability that $x$ belongs to $i$-th class.
 
-\subsection{Bradley-Terry equations}
+An exact solution to this problem is provided by the Bayes classifier.
+To simplify the discussion we will assume that $p_i(x) > 0$ for all $x$ and $P_i = 0$ for all $i$.
+Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
+\begin{align}
+ p^\Pi_i = \frac{p_i(x) P_i}{\sum_{k=1}^K p_k(x)P_k}.
+\end{align}
+
+Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of classes.
+Assuming prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier predicts the probability of $i$-th class as
+
+\begin{align}
+	r_{ij}(x) = \frac{p_i(x) P_1}{p_i(x)P_1 + p_j(x)P_2}.
+\end{align}
+
+Knowledge of vector $\boldsymbol{p}^\Pi$ is essentially equivalent to knowing the function $r_{ij}(x)$. Indeed, if $p_{i}> 0$ for all $x$, then we have
+\begin{align}
+r_{ij}(x) = \frac{p_i^\Pi}{p_i^\Pi + p_j^\Pi}. \label{eq:bt1}
+\end{align}
+
+Conversely, it is easy to show that  the system of equations \label{eq:bt1} has a unique solution.
+
+\begin{prop} \label{prop:binary2multi}
+The system of linear equations \eqref{eq:bt1}  has a unique solution which is the multi-class Bayes classifier.
+\end{prop}
+\begin{proof}
+Indeed, we have 
+\begin{align*}
+\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
+\end{align*}
+\end{proof}
+
+\subsection{One-vs-one classification }
 
@@
 The theoretical basis for one-vs-one classification framework is provided by the following result.
-
-\begin{prop}
-Suppose $p_i(x) >0$ so that all $r_{ij}(x)$ are defined. The system of linear equations \eqref{eq:bt1}  has a unique solution which is the multi-class Bayes classifier.
-\end{prop}
-\begin{proof}
-TODO	
-\end{proof}
 
@@
 Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
-Therefore OLS  is a \emph{canonical} way to build a regression model.
+Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
 Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
@@
 A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
-At the time he was submitting his paper describing LDA he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
+At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
 
-\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtained unbiased estimates of the parameters of the coupling method.
+\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtain unbiased estimates of the parameters of the coupling method.
 This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters.
-This is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
+For example, this is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
 
@@
 Let us finally describe \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction.
+Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction \cite[p.~467]{hastie1998classification}.
 Suppose we are classifying objects from CIFAR-10 dataset.
@@
 
-\section{Examples of coupling methods}
+\section{Examples of coupling methods} \label{sec:coupling}
 
-\subsection{Arboreal coupling methods}
+There is a plethora of methods available for coupling. Let us describe four major categories.
 
-This coupling method ignores all but $K-1$ of the pairwise predictions.
+\subsection{Optimizing binary divergence}
+
+A multi-class estimate $\hat{\boldsymbol{p}}$ obtained by a coupling method implies via \eqref{eq:bt1} probability distributions on each pair of classes:
+\begin{align*}
+	\hat D_{ij}^\textrm{multi}= \biggl(\frac{\hat{p_i}}{\hat p_i + \hat p_j},\frac{\hat{p_j}}{\hat p_i + \hat p_j}\biggr)	
+\end{align*}
+On the other hand, binary classifiers provide another distribution for each pair of  classes, namely
+\begin{align*}
+\hat D_{ij}^\textrm{binary} = (\hat r_{ij}, \hat r_{ji}).
+\end{align*}
+
+A natural way to find  $\hat{\boldsymbol{p}}$ is thus to minimize a functional incorporating divergence measures between these distributions
+\begin{align*}
+\hat{\boldsymbol{p}} = \argmax_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
+\end{align*}
+
+A notable example which uses this principle is the coupling method introduced in \cite{hastie1998classification}. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
+\begin{align*}
+	\divm\nolimits_\textrm{KL} (\boldsymbol{p}, \boldsymbol{q})= \sum p_i \log (p_i/ q_i)
+\end{align*}
+
+Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
+In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score.
+
+For instance, a popular alternative is divergence arising from the quadratic  score (also called Brier score).  This divergence takes the form
+$$
+\divm\nolimits_\textrm{quad} (\boldsymbol{p}, \boldsymbol{q})= \sum (p_i - q_i)^2.
+$$
+Unlike Kullback-Leibler divergence, the penalty for incorrect prediction with arbitrarily low probability is bounded (by one).
+This quadratic score is the basis of the popular Wu-Lin-Weng's method \cite{wu2004probability}.
+
+Their method use an additional trick, which we term \emph{self-referentiality}.
+In the method of Hastie and Tibshirani, $w_{ij}$ are constants derived from observed class frequencies.
+However, we could use weights $w_{ij}$ that increase when the predicted probability of either class $i$ or $j$ is high.
+A reasonable choice would be for instance $w_{ij}= p_i + p_j$.
+In the case of quadratic score, it is more convenient to use weights $w_{ij} = (p_i + p_j)^2$ because then the resulting optimization problem is just minimization of a quadratic form
+\begin{align*}
+\hat{\boldsymbol{p}} = \argmin_{\boldsymbol{p}} \sum_{i,j} (r_{ij}p_j - r_{ji}p_i)^2.
+\end{align*}
+
+We note that the method is symmetric, but the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary. Thus we cannot view Wu-Lin-Weng's method as canonical.
+
+\subsection{Arboreal-based methods}
+
+Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns. This principle underlies arboreal coupling methods.
+
+An arboreal coupling method ignores all but $K-1$ of the pairwise predictions.
 A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes 1 and 3.
@@
 
-In order to obtain a regular system of equations for  larger values of $K$ , the resulting classifiers must form a tree within the complete graph on all classes.
+In order to obtain a regular system of equations for  larger values of $K$ , the resulting classifiers must represent a connected tree within the complete graph on all classes.
+Any arboreal method is non-canonical, because there is no natural way to choose a tree in a complete graph.
 
-This method is non-canonical, because there is no natural way to choose a tree in a complete graph.
+\subsection{Methods emphasizing Hinton's minimality}
 
-\subsection{Hinton's oracle}
-
-This oracle method assumes it has the access to the ground truth $y = C_i$. It outputs probabilities by solving only the equations
+A variant on arboreal methods is the following oracle method which we shall call Hinton's oracle.
+It  assumes it has the access to the ground truth $y = C_i$.
+It outputs probabilities by solving only the equations
 $$
@@
 
-It is thus an arboreal method where the underlying tree forms a star.
-This method is clearly the optimal one with respect to Hinton's minimality criterion.
-It is not a true classification method, because it ``peeks'' at the label.
+For any sample, its result is identical to the arboreal method where the underlying tree forms a star.
+This method is clearly the optimal one with respect to Hinton's minimality criterion, because it ignores the output of any classifier not trained on the true class.
+It is not a true classification method, however, because it ``peeks'' at the label.
 Its main utility is to provide a way to benchmark other methods with respect to Hinton's minimality.
 
-%\subsection{Radial coupling}
+In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
+Denote by $\hat{\boldsymbol{T}}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
+The predictions will generally span the simplex $\sum_i \hat p_i = 1$.
+In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $\hat{\boldsymbol{T}}_i$.
+Let us now define \emph{radial} coupling method.
+The  method requires that for  weights we could in fact use the components of $\boldsymbol{p}$ i.e.
+\begin{equation}
+	\hat {\boldsymbol{p}} = \sum_{i=1}^K p_i \hat{\boldsymbol{T}}_i. \label{eq:radial}
+\end{equation}
 %
-%This coupling method aims to convert Hinton's oracle to a practical method.
-Denote by $\hat{\boldsymbol{h}}_i$ the prediction of Hinton's oracle method, if the true class was $C_i$.
-These predictions will generally span the simplex $\sum_i \hat p_i = 1$.
-In that case the prediction $\boldsymbol{r}$ of the method  can be expressed as a linear combination of $\hat{\boldsymbol{h}}_i$.
-The radial coupling method requires that for  weights we could in fact use the components of $\boldsymbol{r}$ i.e.
-%\begin{equation}
-%	\boldsymbol{r} = \sum_{i=1}^K r_i \hat{\boldsymbol{h}}_i. \label{eq:radial}
-%\end{equation}
-%
-%The intuition behind \eqref{eq:radial} is that if some component of $\boldsymbol{r}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\boldsymbol{r}$ should be close to the prediction of Hinton's oracle $\hat{\boldsymbol{h}}_i$.
+The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by $\hat{\boldsymbol{T}}_i$.
 
@@
 
-\subsection{Wu-Lin-Weng's method}
+\subsection{Properties of coupling methods}
 
-\subsection{Linear kernel}
+The following table indicates which properties are enjoyed by each coupling method we described in this section.
+
+\begin{table}[!ht]
+\begin{tabular}{cm{2.5cm}cccm{1.5cm}m{1.5cm}}
+&property & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
+\hline 
+\multirow{4}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
+&uniqueness & yes & yes & yes & yes & yes \\
+&Bradley-Terry consistency & yes & yes & yes & yes & yes \\
+&canonicity & no & yes & yes & no & yes \\
+&symmetry & yes & yes & yes & no & yes \\
+\hline
+\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
+&Hinton's minimality & ?  & ++ & ?  & ? & +++ \\
+&lack of parameters & yes & yes & yes & yes & yes \\
+& amounts to a linear system & yes & yes & yes & yes & yes\\
+& linear system of special form & no & yes & yes & yes & yes \\
+& iterative method & yes & yes & no & not needed & not needed\\
+\hline
+\end{tabular}
+\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
+\label{tab:summaryCoupling}
+\end{table}
+
+%\subsection{Wu-Lin-Weng's method}
+
+%\subsection{Linear kernel}
 
 %\begin{tabular}
-\input{glm1-multi.tex}
+%\input{glm1-multi.tex}
 %\end{tabular}
@@
 \vskip 0.2in 
-\bibliography{sample}
+\bibliography{paper}
 

### 2025-03-25 paper.tex
Cleaned up Bayes classifier

@@
 \usepackage{rotating}
+\usepackage{tikz-cd}
 
 \newtheorem{prop}{Proposition}
+\newtheorem{thm}{Theorem}
 
@@
 
-\ShortHeadings{Sample JMLR Paper}{One and Two}
+\ShortHeadings{Probabilistic OVO}{Probabilistic OVO}
 \firstpageno{1}
@@
 
-\title{Comparison of canonical polychotomous coupling methods with the method of Wu-Lin-Weng}
+\title{On probabilistic one-vs-one classification}
 
@@
 
+\subsection{Bayes classifier}
+
 An exact solution to this problem is provided by the Bayes classifier.
-To simplify the discussion we will assume that $p_i(x) > 0$ for all $x$ and $P_i = 0$ for all $i$.
-Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
+To simplify the discussion we will assume that $p_i(x) > 0$ for all $x$ and $P_i > 0$ for all $i$.
+Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines.
+
+ The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
 \begin{align}
- p^\Pi_i = \frac{p_i(x) P_i}{\sum_{k=1}^K p_k(x)P_k}.
+ p^\Pi_i(x) = \frac{p_i(x) P_i}{\sum_{k=1}^K p_k(x)P_k}.
 \end{align}
@@
 \begin{align}
-	r_{ij}(x) = \frac{p_i(x) P_1}{p_i(x)P_1 + p_j(x)P_2}.
+	p_{ij}^\Pi(x) = \frac{p_i(x) P_1}{p_i(x)P_1 + p_j(x)P_2}.
 \end{align}
 
-Knowledge of vector $\boldsymbol{p}^\Pi$ is essentially equivalent to knowing the function $r_{ij}(x)$. Indeed, if $p_{i}> 0$ for all $x$, then we have
+Knowledge of vector $\boldsymbol{p}^\Pi$ is  equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed, if $p_{i}> 0$ for all $x$, then we have
 \begin{align}
-r_{ij}(x) = \frac{p_i^\Pi}{p_i^\Pi + p_j^\Pi}. \label{eq:bt1}
+p_{ij}^\Pi(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
 \end{align}
 
-Conversely, it is easy to show that  the system of equations \label{eq:bt1} has a unique solution.
+Conversely, it is easy to show that  the system of equations \eqref{eq:bt1} has a unique solution.
 
 \begin{prop} \label{prop:binary2multi}
-The system of linear equations \eqref{eq:bt1}  has a unique solution which is the multi-class Bayes classifier.
+The system of  equations \eqref{eq:bt1}  has a unique solution which is the multi-class Bayes classifier.
 \end{prop}
-\begin{proof}
-Indeed, we have 
-\begin{align*}
-\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
-\end{align*}
-\end{proof}
+%\begin{proof}
+%Indeed, we have 
+%\begin{align*}
+%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
+%\end{align*}
+%\end{proof}
 
@@
 
-Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$.
+In practice one does not have know true probability distributions and hence cannot construct Bayes classifier.
+However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}(x)$.
+The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$.
+One does it by finding approximate solution of the system of equations
+%\begin{align}
+%
+%\end{align}
+%
+%
+%Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$.
 Let us denote the $r_{ij}(x)$ the output of Bayes (binary) classifier for $x$ in $X$ yielding the probability $p(x \in C_i \mid x\in C_i \cup C_j )$.
 Then we have
+%\begin{equation}
+%r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
+%\end{equation}
+%
+%
+%The system of equations is called Bradley--Terry equations.
+The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations.
+The theoretical basis for one-vs-one classification framework is provided by the following result.
+%
+%
+%
+%Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$.
+A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
 \begin{equation}
-r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}. \label{eq:bt1}
+	{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
 \end{equation}
 
-The system of equations is called Bradley--Terry equations.
-The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations.
-The theoretical basis for one-vs-one classification framework is provided by the following result.
+% One should note that 
+%\begin{itemize}
+%\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
+%\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
+%\end{itemize}
 
-Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$.
-A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
-\begin{equation}
-	\hat{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
-\end{equation}
-
- One should note that 
-\begin{itemize}
-\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
-\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
-\end{itemize}
-
-\subsection{Exact desiderata on coupling method}
+Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
+The system is usually inconsistent and additional assumptions are needed.
+A method to solve Bradley-Terry equations is called a coupling method.
+Its input can be represented by a matrix with off-diagonal entries being $r_{ij}(x)$.
 
 Let us outline what kind of conditions may be desirable in a coupling method.
+In Section \ref{sec:des:exact} we will describe exact mathematical criteria, while in \ref{sec:des:inexact} we shall describe more flexible properties.
+
+\subsection{Exact desiderata on coupling method} \label{sec:des:exact}
 
@@
 
-\emph{Bayes covariance} is a notion introduced in work \cite{BarredaSuch}.
+\emph{Bayes covariance} is a notion introduced in  \cite{vsuch2016bayes}.
 It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
-Any Bayes classifier changes its prediction when the priors change.
-The change happens according to Bayes theorem.
+Any Bayes classifier, whether binary or multiclass changes its prediction when the priors change.
+Let us describe the process.
+Suppose we change priors from $\Pi = (P_1, \ldots, P_k)$ to $\Pi'= (P'_1, \ldots, P'_K)$.
+Then the prediction of Bayes classifiers changes from $\boldsymbol{p}^\Pi= (p_1, \ldots, p_K)$ to the vector
+\begin{align}
+\boldsymbol{p}^{\Pi'} \propto (p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}). \label{eq:changePrior}
+\end{align}
+
+When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
+If the results are identical, for all initial pairwise data $R$, then we say that the coupling method is Bayes covariant.
+Symbolically, let us denote by  $\pi$ the change of priors.
+Let $R^\pi$ be pairwise datum when we apply \eqref{eq:changePrior} to each binary classifier.
+For Bayes covariant method $V$ the following diagram commutes.
+
+\begin{figure}[!h]
+\centering
+\begin{tikzcd}
+	R \arrow[r, "\pi"] \arrow[d, "V"] & R^\pi \arrow[d, "V"] \\
+	V(R) \arrow[r, "\pi"] & V(R^\pi) = V(R)^\pi
+\end{tikzcd}
+\caption{Diagrammatical description of Bayes covariance for a coupling method $V$}
+\label{fig:bc}
+\end{figure}
 
 \subsection{Inexact desiderata for coupling methods}
+
+\label{sec:des:inexact}
 
@@
 \begin{align*}
-\hat{\boldsymbol{p}} = \argmax_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
+\hat{\boldsymbol{p}} = \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
 \end{align*}
@@
 Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
-In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score.
+In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score \cite{gneiting2007strictly}.
 
-For instance, a popular alternative is divergence arising from the quadratic  score (also called Brier score).  This divergence takes the form
+For instance, a popular alternative is divergence arising from the quadratic  score (also known as Brier score) \cite{gneiting2007strictly}. This divergence takes the form
 $$
@@
 
-\subsection{Arboreal-based methods}
+\subsection{Arboreal methods}
 
@@
 
-\subsection{Normal coupling}
+\subsection{Bayes covariant methods}
+
+There are many Bayes covariant methods.
+For instance any arboreal method is Bayes covariant.
+Given two Bayes covariant methods one can interpolate between them using their ``linear combination'' - an ensemble which is also Bayes covariant.
+Let us make it explicit.
+
+ Suppose real numbers $\alpha, \beta$ are given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
+\begin{align*}
+	\boldsymbol{B}(x) = (p_1, \ldots, p_K)\quad\textrm{and}\quad \boldsymbol{\tilde B}(x) = (\tilde p_1, \ldots, \tilde p_K)
+\end{align*}
+then the prediction of the ensemble $\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}$ is given by
+\begin{align*}
+	\bigl(\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}\bigr)(x)\propto (\,p_1^\alpha \tilde p_1^\beta, \ldots, p_K^\alpha \tilde p_K^\beta).
+\end{align*}
+
+As an example, consider the classification problem with three classes.
+We have three arboreal classifiers $\boldsymbol{T}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$ which correspond to star graphs centered respectively at classes $C_1, C_2, C_3$.
+The classifier
+\begin{align}
+\frac13 \boldsymbol{T}_1 \oplus \frac13 \boldsymbol{T}_2 \oplus \frac 13 \boldsymbol{T}_3 = \frac13 \boldsymbol{T}_1 \oplus \frac23 \biggl(\frac12 \boldsymbol{T}_2 \oplus \frac 12 \boldsymbol{T}_3
+\biggr), \label{eq:bc1}
+\end{align}
+is Bayes covariant \emph{and} symmetric. A key result proved in \cite{vsuch2016bayes} is that it is a unique such classifier for $K=3$.
+
+\begin{thm}
+	There exists a unique symmetric Bayes covariant coupling methods for $K=3$.
+\end{thm}
+
+Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{T}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$:
+\[
+\boldsymbol{E} = \frac13 \boldsymbol{T}_1(x) + \frac13 \boldsymbol{T}_2(x) + \frac 13 \boldsymbol{T}_3(x).
+\]
+Note that here we use the plus symbol to denote the vector addition of vectors representing $K$-class probability distributions.
+This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.
 
@@
 \begin{table}[!ht]
-\begin{tabular}{cm{2.5cm}cccm{1.5cm}m{1.5cm}}
-&property & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
+\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
+&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
 \hline 
-\multirow{4}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
-&uniqueness & yes & yes & yes & yes & yes \\
-&Bradley-Terry consistency & yes & yes & yes & yes & yes \\
-&canonicity & no & yes & yes & no & yes \\
-&symmetry & yes & yes & yes & no & yes \\
+\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
+&uniqueness &  yes & yes & yes & yes & yes & yes \\
+&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
+&canonicity & yes & no & yes & yes & no & yes \\
+&symmetry & yes & yes & yes & yes & no & yes \\
+& Bayes covariant & no & no & no & yes & yes & yes \\
 \hline
 \multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
-&Hinton's minimality & ?  & ++ & ?  & ? & +++ \\
-&lack of parameters & yes & yes & yes & yes & yes \\
-& amounts to a linear system & yes & yes & yes & yes & yes\\
-& linear system of special form & no & yes & yes & yes & yes \\
-& iterative method & yes & yes & no & not needed & not needed\\
+&Hinton's minimality & ? & ?  & ++ & ?  & ? & +++ \\
+&lack of parameters & yes & yes & yes & yes & yes & yes \\
+& amounts to a linear system & no & yes & yes & yes & yes & yes\\
+& linear system of special form & no & no & yes & yes & yes & yes \\
+& iterative method & yes & yes & yes & no & not needed & not needed\\
 \hline
@@
 \end{table}
+
+\section{Experimental results.}
 
@@
 
-Here is a citation \cite{chow:68}.
+%Here is a citation \cite{chow:68}.
 
@@
 \section{}
-\label{app:theorem}
+\label{app:explicit}
 
@@
 %Section~\ref{sec:textree-generalization}:
+
+In this appendix we provide explicit predictions of coupling methods used in the paper.
 

### 2025-03-26 paper.tex
Added references

@@
 \begin{prop} \label{prop:binary2multi}
-The system of  equations \eqref{eq:bt1}  has a unique solution which is the multi-class Bayes classifier.
+The system of  equations \eqref{eq:bt1} in unknowns $p_i^\Pi(x)$ has a unique solution which is the multi-class Bayes classifier.
 \end{prop}
@@
 Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
-In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score \cite{gneiting2007strictly}.
+In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score [\cite{gneiting2007strictly, buja2005loss}].
 
-For instance, a popular alternative is divergence arising from the quadratic  score (also known as Brier score) \cite{gneiting2007strictly}. This divergence takes the form
+For instance, a popular alternative is divergence arising from the quadratic  score [\cite{gneiting2007strictly}] (also known as Brier score [\cite{brier1950verification}]).
+This divergence takes the form
 $$
@@
 Unlike Kullback-Leibler divergence, the penalty for incorrect prediction with arbitrarily low probability is bounded (by one).
-This quadratic score is the basis of the popular Wu-Lin-Weng's method \cite{wu2004probability}.
+This quadratic score is the basis of the popular Wu-Lin-Weng's method [\cite{wu2004probability}].
 
@@
 
-We note that the method is symmetric, but the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary. Thus we cannot view Wu-Lin-Weng's method as canonical.
+We note that the method is symmetric.
+The choice of quadratic scoring rule can also be viewed as canonical in view of axiomatic characterization given in  [\cite{selten1998axiomatic}].
+However the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary.
+Thus we do not view Wu-Lin-Weng's method as canonical.
 

### 2025-04-02 paper.tex
Minor changes

@@
 \newtheorem{thm}{Theorem}
+\newtheorem{assumption}{Assumption}
 
@@
 \usepackage{lastpage}
-\jmlrheading{23}{2022}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
+\jmlrheading{23}{2025}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
 
@@
        \AND
-       \name Peter Novotný \email two@cs.berkeley.edu \\
-       \addr Division of Computer Science\\
-       University of California\\
-       Berkeley, CA 94720-1776, USA}
+       \name Peter Novotný \email peter.novotny@uniza.sk \\
+       \addr Fakulta informatiky a riadenia\\
+       Žilinská Univerzita v Žiline\\
+       Žilina, 010 26, Slovakia
+       \AND
+       \name Ali Haidar \email haidar@savbb.sk \\
+       \addr Matematický ústav SAV\\
+       Ďumbierska 1\\
+       Banská Bystrica, 974 01, Slovakia
+       }
 
@@
 
-An exact solution to this problem is provided by the Bayes classifier.
-To simplify the discussion we will assume that $p_i(x) > 0$ for all $x$ and $P_i > 0$ for all $i$.
-Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines.
+An exact solution to this problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.
+
+\begin{assumption} \label{ass:1}
+ For all $x$ in the feature space we have $p_i(x) > 0$.
+\end{assumption}
+Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.
 
@@
 \begin{align}
-	p_{ij}^\Pi(x) = \frac{p_i(x) P_1}{p_i(x)P_1 + p_j(x)P_2}.
+	p_{ij}^\Pi(x) = \frac{p_i(x) P_i}{p_i(x)P_i + p_j(x)P_j}.
 \end{align}
 
-Knowledge of vector $\boldsymbol{p}^\Pi$ is  equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed, if $p_{i}> 0$ for all $x$, then we have
+Knowledge of vector $\boldsymbol{p}^\Pi(x)$ is  equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
 \begin{align}
@@
 In practice one does not have know true probability distributions and hence cannot construct Bayes classifier.
-However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}(x)$.
+However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$.
 The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$.
-One does it by finding approximate solution of the system of equations
+One does it by finding an approximate solution of the system of equations
 %\begin{align}
@@
 A method to solve Bradley-Terry equations is called a coupling method.
-Its input can be represented by a matrix with off-diagonal entries being $r_{ij}(x)$.
+Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
+Schematically, classification using coupling method $\boldsymbol{C}$ proceeds as indicated in Figure \ref{fig:coupling}.
 
-Let us outline what kind of conditions may be desirable in a coupling method.
-In Section \ref{sec:des:exact} we will describe exact mathematical criteria, while in \ref{sec:des:inexact} we shall describe more flexible properties.
+\begin{figure}[!h]
+	\centering
+	\begin{tikzcd}[column sep=3cm]
+		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow{dr}[swap]{multi-class~ prediction} & \boldsymbol{R}(x) \arrow{d}{coupling}[swap]{V} \\
+		 & V(\boldsymbol{R}(x)) 
+	\end{tikzcd}
+	\caption{Multi-class classification using a coupling method ${V}$}
+	\label{fig:coupling}
+\end{figure}
 
 \subsection{Exact desiderata on coupling method} \label{sec:des:exact}
+
+Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
+this section
+ we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
 
@@
 
-\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on predictions.
-The action of a permutation $\sigma$ extends to the action on pairwise matrix by
+\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions.
+The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by
 \begin{equation}
-	\hat r^\sigma_{i,j} = \hat r_{\sigma(i), \sigma(j)}
+	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
 \end{equation}
+We say that a coupling method $V$ is \emph{symmetric} if 
+\begin{align}
+		V(\boldsymbol{R})^\sigma = V(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
+\end{align}
 
@@
 When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
-If the results are identical, for all initial pairwise data $R$, then we say that the coupling method is Bayes covariant.
+If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is Bayes covariant.
 Symbolically, let us denote by  $\pi$ the change of priors.
-Let $R^\pi$ be pairwise datum when we apply \eqref{eq:changePrior} to each binary classifier.
+Let $\boldsymbol{R}^\pi$ be pairwise datum when we apply \eqref{eq:changePrior} to each binary classifier.
 For Bayes covariant method $V$ the following diagram commutes.
@@
 \begin{tikzcd}
-	R \arrow[r, "\pi"] \arrow[d, "V"] & R^\pi \arrow[d, "V"] \\
-	V(R) \arrow[r, "\pi"] & V(R^\pi) = V(R)^\pi
+	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "V"] & \boldsymbol{R}^\pi \arrow[d, "V"] \\
+	V(\boldsymbol{R}) \arrow[r, "\pi"] & V(\boldsymbol{R}^\pi) = V(\boldsymbol{R})^\pi
 \end{tikzcd}
@@
 \label{sec:des:inexact}
+
+In this section we describe several concepts that lack strict mathematical delineation, but may still be important to consider.
 
@@
 
-Let us finally describe \emph{Hinton's minimality}.
+Let us finally mention \emph{Hinton's minimality}.
 Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction \cite[p.~467]{hastie1998classification}.
@@
 
-The first that the five conditions have a clear mathematical definition, whereas the rest are not exact.
+%The first that the five conditions have a clear mathematical definition, whereas the rest are not exact.
 For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.
@@
 
-There is a plethora of methods available for coupling. Let us describe four major categories.
+There is a plethora of methods available for coupling. Let us describe four major classes.
 
-\subsection{Optimizing binary divergence}
+\subsection{Methods aiming to minimize binary divergence}
 
@@
 
-Their method use an additional trick, which we term \emph{self-referentiality}.
+Their method uses an additional trick, which we term \emph{self-referentiality}.
 In the method of Hastie and Tibshirani, $w_{ij}$ are constants derived from observed class frequencies.
@@
 \begin{align*}
-\hat{\boldsymbol{p}} = \argmin_{\boldsymbol{p}} \sum_{i,j} (r_{ij}p_j - r_{ji}p_i)^2.
+\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{i,j} (r_{ij}p_j - r_{ji}p_i)^2.
 \end{align*}
@@
 \begin{equation}
-	\hat {\boldsymbol{p}} = \sum_{i=1}^K p_i \hat{\boldsymbol{T}}_i. \label{eq:radial}
+	\hat {\boldsymbol{p}} = \bigoplus_{i=1}^K p_i \hat{\boldsymbol{T}}_i. \label{eq:radial}
 \end{equation}
@@
 
-There are many Bayes covariant methods.
-For instance any arboreal method is Bayes covariant.
-Given two Bayes covariant methods one can interpolate between them using their ``linear combination'' - an ensemble which is also Bayes covariant.
-Let us make it explicit.
+There are many Bayes covariant methods. For instance any arboreal method is Bayes covariant.
 
- Suppose real numbers $\alpha, \beta$ are given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
+Given several Bayes covariant methods one can form  their ``linear combination'' - an ensemble which is also Bayes covariant. Let us make it explicit.
+
+ Suppose real numbers $\alpha_1, \alpha_L$ are real numbers and $\boldsymbol{C}_1, \ldots, \boldsymbol{C}_L$ are coupling methods. We define their linear combination by requiring that 
+ \begin{align*}
+ 	\bigl(\alpha_1 \boldsymbol{C}_1 \oplus \ldots \oplus \alpha_L \boldsymbol{C}_L\bigr)(x) \propto 
+ \end{align*}
+
+ given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
 \begin{align*}
@@
 \section{Experimental results.}
+
+We considered the following questions
+
+- are there Bayes covariant methods that match the performance of Wu-Lin-Weng's method ?
+- when priors change, is it better to apply Bayes update before or after coupling?
+- which coupling methods are best with respect to Hinton's minimality?
+
+\subsection{Datasets}
+
+\begin{figure}[!ht]
+	\includegraphics[width = 0.5\linewidth]{graph/dna-lda.pdf}
+	\includegraphics[width = 0.5\linewidth]{graph/waveform-lda.pdf}
+	\caption{Projections of three-class datasets using LDA Left: dna, right: waveform}
+\end{figure}
 

### 2025-04-02 lda.R
Implemented change of priors experiment for triples

@@ -75,13 +75,17 @@ glm1 <- function(files = files, workers = 12) {
 
 log_omit1 <- function(M_logits, idx) {
     M <- M_logits
+    stopifnot(nrow(M_logits) ==  3)
+    stopifnot(nrow(M_logits) ==  3)
+    stopifnot(idx >= 1)
+    stopifnot(idx <= 3)
 
     if (idx != 1) {
         perm <- if (idx == 2) c(2,1,3) else c(3,2,1)
         M <- M[perm, perm]
     }
 
-        if (M[1,2] >= 0) {
+    if (M[1,2] >= 0) {
             # p1 >= p2
         if (M[1,3] >=0) {
             # p1 is the largets
@@ -113,6 +117,17 @@ log_omit1 <- function(M_logits, idx) {
 omit1 <- function(M_logits, idx) {
     lp <- log_omit1(M_logits, idx)
     p <- exp(lp)
+    p / sum(p)
+}
+
+half1 <- function(M_logits, idx) {
+    s = rep(0, 3)
+    for (j in which(idx != c(1,2,3))) {
+        s = s +  log_omit1(M_logits, j)
+    }
+    s = s / 2
+    s <- s - max(s)
+    p <- exp(s)
     p / sum(p)
 }
 
@@ -165,6 +180,10 @@ e3 <- new.env(parent = emptyenv())
 e3[["omit23"]] = function(x) omit1(x, 1)
 e3[["omit13"]] = function(x) omit1(x, 2)
 e3[["omit12"]] = function(x) omit1(x, 3)
+e3[["half1"]] = function(x) half1(x, 1)
+e3[["half2"]] = function(x) half1(x, 2)
+e3[["half3"]] = function(x) half1(x, 3)
+
 
 log3 <- new.env(parent = emptyenv())
 log3[["omit23"]] = function(x) log_omit1(x, 1)
@@ -356,7 +375,7 @@ log_pred3 <- function(dfs, i, j, k) {
 lda_triples <- function(dfs) {
     v <- lda_binary(dfs)
     K <- max(dfs$train$class_id)
-    print(K)
+    # print(K)
 
     res <- data.frame(
             i = vector("integer", 0),
@@ -513,6 +532,28 @@ gen_W3 <- function(n = 1000, lbd = 0, ubd = 1) {
         nrow = n, ncol = 3)
 
 
+}
+
+# use triangular grid (same as gen_W2)
[…]

### 2025-04-03 lda.R
Added tuple evalution of prior change

@@ -801,7 +801,7 @@ bc_triple <- function(dfs, i, j, k, add = 2) {
                 correct2 <- weight * (pred == q)
                 acc2 <- sum(correct2) / sum(weight[idx])
                 # acc2 <- mean(pred == q)
-                data.frame(changed = n, factor = (1 + acc) , binary = acc2, multi = acc, method = m)
+                data.frame(changed = n, factor = (1 + add) , binary = acc2, multi = acc, method = m)
                 # data.frame(p[idx,], 
                         # id = 1:sum(idx), orig_id = (1:N)[idx], 
                         # truth = q, pred = pred, method = m, 
@@ -916,4 +916,62 @@ hinton <- function(dfs) {
     triple1 <- triple |> dplyr::select(-(1:3)) |> apply(2, mean) 
     multi  <- hinton_multi(dfs)$brier |> apply(2, mean) |> as.list() |> data.frame()
     list(triple = triple1, multi = multi)
+}
+
+bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
+    stopifnot(all(as.logical(sapply(ns, function(n) n %in% tuple))))
+    df1 <- dfs$train
+    df2 <- dfs$test
+    K <- max(dfs$train$class_id)
+
+    v <- lda_binary(dfs, subclasses = tuple)
+
+    truth <- dfs$test$class_id
+    r <- v$r
+    idx <- truth %in% tuple
+    dft <- dfs$test
+    N <- nrow(dft)
+    t2 <- truth[idx]
+    q <- sapply(1:length(t2), function(k) {
+            which(t2[k] == tuple) 
+        })
+
+    map(ns, function(n) {
+        print(n)
+        it <- which(n == tuple)     
+        
+        map (ls(e), function(m) {
+            fn <- e[[m]]
+            p <- sapply(1:N, function(k) {
+                fn(r[,,k])
+            }) |> t()
+
+            #w <- rep(1,3)
+            #w[which(n == triple)] = (1 + add)
+            # p <- w * p
+            wp <- p
+            wp[, it] = (1 + add) * wp[,it]
+            # also could use t(w * t(p))
+            predictions <- apply(wp, 1, which.max)
+            weight <- if_else (t2 == n, 1 + add, 1)
+            correct <- weight * (predictions[idx] == q)
+            acc <- sum(correct) / sum(weight[idx])
+
+            p2 <- sapply(1:N, function(k) {
+                r2 <- r[,,k]
+                for (s in 1:3) {
[…]

### 2025-04-06 lda.R
Count flips when priors change

@@ -534,6 +534,7 @@ gen_W3 <- function(n = 1000, lbd = 0, ubd = 1) {
 
 }
 
+
 # use triangular grid (same as gen_W2)
 # probably should remove in order not to confuse 
 #
@@ -950,12 +951,14 @@ bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
             #w[which(n == triple)] = (1 + add)
             # p <- w * p
             wp <- p
+            old_predictions <- apply(p, 1, which.max)
             wp[, it] = (1 + add) * wp[,it]
             # also could use t(w * t(p))
             predictions <- apply(wp, 1, which.max)
             weight <- if_else (t2 == n, 1 + add, 1)
             correct <- weight * (predictions[idx] == q)
             acc <- sum(correct) / sum(weight[idx])
+            flipped = mean(predictions[idx] != old_predictions[idx])
 
             p2 <- sapply(1:N, function(k) {
                 r2 <- r[,,k]
@@ -971,7 +974,7 @@ bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
             pred <- apply(p2[idx,],1, which.max)
             correct2 <- weight * (pred == q)
             acc2 <- sum(correct2) / sum(weight[idx])
-            data.frame(changed = n, factor = (1 + add) , binary = acc2, multi = acc, method = m)
+            data.frame(changed = n, factor = (1 + add) , binary = acc2, multi = acc, method = m, flipped = flipped)
         }) |>  list_rbind()
     }) |>  list_rbind()
 }

### 2025-04-06 paper.tex
Text for preliminary analysis

@@
 
-There is a plethora of methods available for coupling. Let us describe four major classes.
+There is a plethora of methods available for coupling. In this section we describe four major classes.
 
@@
 
-Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns. This principle underlies arboreal coupling methods.
+System of equations \eqref{eq:bt2} is overdetermined because there are $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.
+Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns.
+This principle underlies arboreal coupling methods.
 
@@
 	\begin{split}
-		\frac{\hat p_1}{\hat p_2} &= \vec{r}_{12}\\
-		\frac{\hat p_2}{\hat p_3} &= \vec{r}_{23}\\
-		\hat p_1 + \hat p_2 + \hat p_3 &= 0
+		\frac{\hat p_1}{\hat p_1 + \hat p_2} &= {r}_{12}\\
+		\frac{\hat p_2}{\hat p_2 + \hat p_3} &= {r}_{23}\\
+		\hat p_1 + \hat p_2 + \hat p_3 &= 1
 	\end{split}
+	\label{eq:arb1}
 \end{equation}
 
-For $K=3$, there are three different arboreal coupling methods, which we shall call $omit12$, $omit13$, $omit23$.
+For $K=3$, there are three different arboreal coupling methods, which we shall call $T_1$, $T_2$, $T_3$, where the system \eqref{eq:arb1} represents coupling method $T_2$.
 
@@
 A variant on arboreal methods is the following oracle method which we shall call Hinton's oracle.
-It  assumes it has the access to the ground truth $y = C_i$.
+It  assumes it has the access to the ground truth $y = C_t$.
 It outputs probabilities by solving only the equations
 $$
-\frac{p_i}{p_j} = \vec{r}_{ij},\quad \textrm{for }i\not = j,
+\frac{\hat p_t}{\hat p_t + \hat p_j} = {r}_{tj},\quad \textrm{for }j\not = t,
 $$
-together  with total sum equation
+together the  with total sum equation
 $$
@@
 In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
-Denote by $\hat{\boldsymbol{T}}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
-The predictions will generally span the simplex $\sum_i \hat p_i = 1$.
-In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $\hat{\boldsymbol{T}}_i$.
+Denote by ${T}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
+The predictions will generally span the vector space $R^K$.
+In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $T_i(x)$.
 Let us now define \emph{radial} coupling method.
-The  method requires that for  weights we could in fact use the components of $\boldsymbol{p}$ i.e.
+The  method requires that for the  weights we could in fact use the components of $\boldsymbol{p}$ i.e.
 \begin{equation}
-	\hat {\boldsymbol{p}} = \bigoplus_{i=1}^K p_i \hat{\boldsymbol{T}}_i. \label{eq:radial}
+	\begin{split}
+	\hat {\boldsymbol{p}} &= \hat p_1 T_1(x) + \ldots + \hat p_K T_K(x)\\
+	1 &= \hat p_1 + \ldots + \hat p_K
+	\end{split}
+	 \label{eq:radial}
 \end{equation}
 %
-The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by $\hat{\boldsymbol{T}}_i$.
+The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${{T}}_i$.
 
@@
 
-We considered the following questions
+It is natural to consider the following interrelated questions
 
-- are there Bayes covariant methods that match the performance of Wu-Lin-Weng's method ?
-- when priors change, is it better to apply Bayes update before or after coupling?
-- which coupling methods are best with respect to Hinton's minimality?
+\begin{itemize}
+\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
+\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
+\item[c)] If the answer to b) is negative, how serious is the impact of the lack of Bayes covariance in practice?
+\end{itemize}
+
+The following sections attempt to gather answers to these questions.
 
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width = 0.5\linewidth]{graph/dna-lda.pdf}
-	\includegraphics[width = 0.5\linewidth]{graph/waveform-lda.pdf}
-	\caption{Projections of three-class datasets using LDA Left: dna, right: waveform}
-\end{figure}
+It is natural to consider the benchmark datasets used in previous evaluation of coupling methods \cite{wu2004probability}.
+The authors considered altogether seven datasets with number of classes ranging from 3 to 26.
+For each dataset they extracted 40 pairs of training and testing datasets.
+Half of these were smaller (300 training samples and 500 testing samples) and the other half was larger (800 training samples and 1000 testing samples).
+In our experiments we use only the larger pairs.
+
+As a preliminary step we conducted analysis of linear separability of the datasets.
+We used ECOS solver in CVXR library to solve the underlying quadratic program.
+The results are reported in Table \ref{tab:sep}.
+
+\input{tab-sep.tex}
+
+We can infer that except for 'waveform' dataset, majority of binary problems are linearly separable.
+
+\subsection{Binary classifiers}
+
+We have opted to use LDA as a binary classification tool.
+Its appeal is that it is applicable even for linearly separable datasets, thus obviating additional crossvalidation step incurred by methods that use regularization (e.g.
+penalized logistic regression or SVM).
+It usually provides results close to logistic regression \cite{james2013introduction}.
+
+For preprocessing we first removed features that were constant across classes.
+Then we projected the data using PCA to the subspace for which corresponding singular values were at least $1/1000$.
+We used PCA without scaling or centering since the datasets' features were already normalized to interval $[-1,1]$.
+
+For training LDA we used MASS library in R.
+
+%\begin{figure}[!ht]
+%	\includegraphics[width = 0.5\linewidth]{graph/dna-lda.pdf}
+%	\includegraphics[width = 0.5\linewidth]{graph/waveform-lda.pdf}
+%	\caption{Projections of three-class datasets using LDA Left: dna, right: waveform}
+%\end{figure}
+
+\subsection{Experiment 1: Accuracy on benchmark datasets}
+
+The first experiment compares the performanc of three parameterless coupling methods
+\begin{itemize}
+\item method of Wu-Lin-Weng, which is widely used in software libraries, and thus can be viewed as an orthodox choice,
+\item normal coupling, which is a Bayes covariant method,
+\item radial coupling, which is not Bayes covariant.
+\end{itemize}
+
+Although previous evaluations of the latter two methods were done in \cite{vsuch2016bayes}, they used phonetic data for which ground truth may be imprecise.
+
+\input{tab-multi.tex}
+
+From Table \ref{tab:multi} we can clearly see that Wu-Lin-Weng's method has the best performance.
+On some datasets it trounces normal coupling method by a wide margin.
+The edge over radial method is smaller, with the exception of usps dataset where its accuracy is higher by remarkable 30\%.
+
+\subsection{Experiment 2: Accuracy of Bayes covariant methods with parameters}
 

### 2025-04-06 tab-exp2.R
Add code to generate tables

@@ -1,0 +1,16 @@
+library(tidyr)
+library(dplyr)
+library(xtable)
+
+
+
+df <- read.csv("data/exp2.csv")
+
+df1 <- df |> group_by(dataset) |> summarize(cv_acc = mean(cv_acc), wlw2 = mean(wlw2))
+# colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
+sink("tab-multi.tex")
+print(xtable(df1, label = "tab:exp2", digits = 2,
+             caption = "Comparison of combinations of trees and Wu-Lin-Weng's method"
+),  include.rownames = FALSE)
+sink()
+

### 2025-04-06 tab-multi.R

@@ -1,0 +1,15 @@
+library(tidyr)
+library(dplyr)
+library(xtable)
+
+df <- read.csv("data/multi.csv")
+
+df1 <- df |> group_by(dataset) |> summarize(normal = mean(normal)/1000, 
+                                            radial = mean(radial)/1000, 
+                                            wlw2 = mean(wlw2)/1000)
+colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
+sink("tab-multi.tex")
+print(xtable(df1, label = "tab:multi", digits = 2,
+             caption = "Comparison of accuracy for three parameterless coupling methods"
+),  include.rownames = FALSE)
+sink()

### 2025-04-06 tab-sep.R

@@ -1,0 +1,20 @@
+library(tidyr)
+library(dplyr)
+library(xtable)
+
+df <- read.csv("data/separation.csv")
+
+df1 <- df |> group_by(dataset, status, K) |> summarize(count = n() ) |>
+  mutate(pct = count / (10 * K * (K-1))) |>
+  pivot_wider(id_cols = c("dataset", "K"), 
+              names_from = "status", 
+              values_from = "pct", 
+              values_fill = 0) |>
+  mutate(separable = optimal) |>
+  select(dataset, K, separable)
+
+sink("tab-sep.tex")
+print(xtable(df1, label = "tab:sep", digits = 2,
+             caption = "The benchmark datasets with indication of the number of classes $K$ and percentage of binary problems deemed separable",
+),  include.rownames = FALSE)
+sink()

### 2025-04-06 paper.tex
More about the second experiment

@@
 
-\begin{thm}
+\begin{thm} \label{thm:K3}
 	There exists a unique symmetric Bayes covariant coupling methods for $K=3$.
@@
 
-\subsection{Experiment 1: Accuracy on benchmark datasets}
+\subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets}
 
@@
 \subsection{Experiment 2: Accuracy of Bayes covariant methods with parameters}
+
+In the previous experiment we established that the method of Wu-Lin-Weng provides leading performance. However in view of Theorem \ref{thm:K3} the method is not Bayes covariant.
+
+In this experiment we investigated whether we can (always) find  a Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method, if we allow it to have (a few) trainable parameters.
+Our experiment proceeds in five steps.
+
+First, we restrict our investigation to the case of three class datasets. This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask.
+
+As a second step, we consider whether the three arboreal methods $ \boldsymbol{S}_1,~ \boldsymbol{S}_2,~ \boldsymbol{S}_3$ (which do not have any parameters) could bridge the gap.
+The statistics are shown in Table \ref{tab:step2}.
+
+\input{tab-step2.tex}
+
+We can see that approximately half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
+Therefore we should extend search to Bayes covariant methods with trainable parameters.
+
+In the third step we define two parameter family of Bayes covariant coupling methods
+\begin{align}
+a_1 \boldsymbol{S}_1 + a_2 \boldsymbol{S}_2 + a_3 \boldsymbol{S}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1
+\end{align}
+Note that the parameter space of this family is not compact.
+In order to facilitate computations we opted to conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
+
+In order to reduce computational burden we selected 1000 three-class subproblems. The results are shown in Figure \ref{fig:par-bc}.
+
+\begin{figure}[!ht]
+\includegraphics{graph/exp2-summary.pdf}
+\caption{Results of grid search for parametric Bayes covariant methods matching performance of Wu-Lin-Weng's method}
+\label{fig:par-bc}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics{graph/exp2-detail.pdf}
+	\caption{Color map indicates the value of Brier score computed for an ensemble of coupling methods on the testing dataset.
+The vertices triangle indicate the arboreal coupling methods, and the black circle the location of the optimum.}
+\end{figure}
 

### 2025-04-06 tab-step2.R

@@ -1,0 +1,22 @@
+library(tidyr)
+library(dplyr)
+library(xtable)
+
+df <- read.csv("data/triples.csv")
+
+df1 <- df |> mutate(omit = pmax(omit12, omit13, omit23)) |> 
+            summarize(`normal >= WLW` = mean(normal >= wlw2),
+                      `omit >= WLW` = mean(omit >= wlw2),
+                      `WLW > max(normal, omit)` = mean(wlw2 > normal & wlw2 > omit)) |>
+      pivot_longer(everything(), names_to = 'outcome', values_to = "percentage")
+            
+                      
+                      
+                      
+           
+# colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
+sink("tab-step2.tex")
+print(xtable(df1, label = "tab:step2", digits = 2,
+             caption = "Comparison of Wu-Lin-Weng's method and  parameterless coupling methods on three class subset"
+),  include.rownames = FALSE)
+sink()

### 2025-04-07 paper.tex
Clean up notation for coupling methods

@@
 Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
-Schematically, classification using coupling method $\boldsymbol{C}$ proceeds as indicated in Figure \ref{fig:coupling}.
+Schematically, classification using coupling method $\boldsymbol{v}$ proceeds as indicated in Figure \ref{fig:coupling}.
 
@@
 	\begin{tikzcd}[column sep=3cm]
-		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow{dr}[swap]{multi-class~ prediction} & \boldsymbol{R}(x) \arrow{d}{coupling}[swap]{V} \\
-		 & V(\boldsymbol{R}(x)) 
+		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow{dr}[swap]{multi-class~ prediction} & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
+		\arrow{d}{coupling} \\
+		 & \boldsymbol{v}(\boldsymbol{R}(x)) 
 	\end{tikzcd}
-	\caption{Multi-class classification using a coupling method ${V}$}
+	\caption{Multi-class classification using a coupling method $\boldsymbol{v}$}
 	\label{fig:coupling}
@@
 \begin{align}
-		V(\boldsymbol{R})^\sigma = V(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
+		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
 \end{align}
@@
 Let $\boldsymbol{R}^\pi$ be pairwise datum when we apply \eqref{eq:changePrior} to each binary classifier.
-For Bayes covariant method $V$ the following diagram commutes.
+For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
 
@@
 \begin{tikzcd}
-	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "V"] & \boldsymbol{R}^\pi \arrow[d, "V"] \\
-	V(\boldsymbol{R}) \arrow[r, "\pi"] & V(\boldsymbol{R}^\pi) = V(\boldsymbol{R})^\pi
+	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
+	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
 \end{tikzcd}
-\caption{Diagrammatical description of Bayes covariance for a coupling method $V$}
+\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
 \label{fig:bc}
@@
 \begin{align*}
-\hat{\boldsymbol{p}} = \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
+\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
 \end{align*}
@@
 
-For $K=3$, there are three different arboreal coupling methods, which we shall call $T_1$, $T_2$, $T_3$, where the system \eqref{eq:arb1} represents coupling method $T_2$.
+For $K=3$, there are three different arboreal coupling methods, which we shall call $\boldsymbol{s}_1$, $\boldsymbol{s}_2$, $\boldsymbol{s}_3$, where the system \eqref{eq:arb1} represents the coupling method $\boldsymbol{s}_2$.
 
@@
 In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
-Denote by ${T}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
+Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
 The predictions will generally span the vector space $R^K$.
-In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $T_i(x)$.
+In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $\boldsymbol{s}_i(x)$.
 Let us now define \emph{radial} coupling method.
@@
 	\begin{split}
-	\hat {\boldsymbol{p}} &= \hat p_1 T_1(x) + \ldots + \hat p_K T_K(x)\\
+	\hat {\boldsymbol{p}} &= \hat p_1 \boldsymbol{s}_1(x) + \ldots + \hat p_K \boldsymbol{s}_K(x)\\
 	1 &= \hat p_1 + \ldots + \hat p_K
@@
 
-There are many Bayes covariant methods. For instance any arboreal method is Bayes covariant.
+There are many Bayes covariant methods. First examples are provided by arboreal coupling methods.
+
+\begin{prop}
+Any arboreal method is Bayes covariant.
+\end{prop}
 
@@
 
- Suppose real numbers $\alpha_1, \alpha_L$ are real numbers and $\boldsymbol{C}_1, \ldots, \boldsymbol{C}_L$ are coupling methods. We define their linear combination by requiring that 
+Suppose real numbers $\alpha_1, \alpha_L$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_L$ are coupling methods.
+We define their linear combination $\bigoplus_i a_i \boldsymbol{v}_i$ as the coupling method that for any $x$ yields the probability distribution on $L$ classes that satisfies
 \begin{align*}
- 	\bigl(\alpha_1 \boldsymbol{C}_1 \oplus \ldots \oplus \alpha_L \boldsymbol{C}_L\bigr)(x) \propto 
+ 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_L \boldsymbol{v}_L\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_L^{a_L}(x),
 \end{align*}
+where the symbol $\odot$ denotes componentwise multiplication. With this definition we have the following result.
 
- given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
-\begin{align*}
-	\boldsymbol{B}(x) = (p_1, \ldots, p_K)\quad\textrm{and}\quad \boldsymbol{\tilde B}(x) = (\tilde p_1, \ldots, \tilde p_K)
-\end{align*}
-then the prediction of the ensemble $\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}$ is given by
-\begin{align*}
-	\bigl(\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}\bigr)(x)\propto (\,p_1^\alpha \tilde p_1^\beta, \ldots, p_K^\alpha \tilde p_K^\beta).
-\end{align*}
+\begin{prop}
+Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_L$ are Bayes covariant. If $\sum a_i = 1$, then $\bigoplus_i a_i \boldsymbol{v}_i$ is also a Bayes covariant coupling method.
+\end{prop}
+
+% 
+% given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
+%\begin{align*}
+%	\boldsymbol{B}(x) = (p_1, \ldots, p_K)\quad\textrm{and}\quad \boldsymbol{\tilde B}(x) = (\tilde p_1, \ldots, \tilde p_K)
+%\end{align*}
+%then the prediction of the ensemble $\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}$ is given by
+%\begin{align*}
+%	\bigl(\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}\bigr)(x)\propto (\,p_1^\alpha \tilde p_1^\beta, \ldots, p_K^\alpha \tilde p_K^\beta).
+%\end{align*}
 
 As an example, consider the classification problem with three classes.
-We have three arboreal classifiers $\boldsymbol{T}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$ which correspond to star graphs centered respectively at classes $C_1, C_2, C_3$.
+We have three arboreal classifiers $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$ which correspond to star graphs centered respectively at classes $C_1, C_2, C_3$.
 The classifier
 \begin{align}
-\frac13 \boldsymbol{T}_1 \oplus \frac13 \boldsymbol{T}_2 \oplus \frac 13 \boldsymbol{T}_3 = \frac13 \boldsymbol{T}_1 \oplus \frac23 \biggl(\frac12 \boldsymbol{T}_2 \oplus \frac 12 \boldsymbol{T}_3
-\biggr), \label{eq:bc1}
+\frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:bc1}
 \end{align}
@@
 
-Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{T}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$:
+Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$:
 \[
-\boldsymbol{E} = \frac13 \boldsymbol{T}_1(x) + \frac13 \boldsymbol{T}_2(x) + \frac 13 \boldsymbol{T}_3(x).
+\boldsymbol{E} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
 \]
@@
 
-It is natural to consider the following interrelated questions
+The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
 
@@
 \item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
-\item[c)] If the answer to b) is negative, how serious is the impact of the lack of Bayes covariance in practice?
+\item[c)] If the answer to b) is negative, is it better to apply change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
 \end{itemize}
 
-The following sections attempt to gather answers to these questions.
+These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.
 
@@
 
-\subsection{Binary classifiers}
+\subsection{Classification methodology}
 
@@
 
-For training LDA we used MASS library in R.
+For training LDA we used MASS library in R. We implemented coupling methods in C++ using Eigen library. As arguments to the coupling methods we use log-odds, i.e. instead of $r_{ij}$ they expect
+$$
+\tilde r_{ij} = \log \biggl(\frac{1}{r_{ji}} - 1\biggr).
+$$
+The resulting matrix $\tilde{\boldsymbol{R}}$ is skew symmetric (with the convention of having zeroes on the diagonal).
+
+This parametrization allows for precise representation of extremely small probabilities which are sometimes produced by LDA.
+These small probabilities might be expected given that a large fraction of binary problems is linearly separable.
+
+Small probabilities generally have very little effect on the implementation of Bayes covariant methods which generally operate using log-odds.
+However small probabilities do affect both the method of Wu-Lin-Weng as well sa radial method, because then Assumption \ref{ass:1} fails to hold.
 
@@
 
-\subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets}
+\subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets} \label{sec:exp1}
 
@@
 \subsection{Experiment 2: Accuracy of Bayes covariant methods with parameters}
+ \label{sec:exp2}
 
@@
 
-As a second step, we consider whether the three arboreal methods $ \boldsymbol{S}_1,~ \boldsymbol{S}_2,~ \boldsymbol{S}_3$ (which do not have any parameters) could bridge the gap.
+As a second step, we consider whether the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$ (which do not have any parameters) could bridge the gap.
 The statistics are shown in Table \ref{tab:step2}.
@@
 \begin{align}
-a_1 \boldsymbol{S}_1 + a_2 \boldsymbol{S}_2 + a_3 \boldsymbol{S}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1
+a_1 \boldsymbol{s}_1 + a_2 \boldsymbol{s}_2 + a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1
 \end{align}
@@
 
+\subsection{Experiment 3: Effect of change of priors}  \label{sec:exp3}
 %\subsection{Wu-Lin-Weng's method}

### 2025-04-21 paper.tex
Fix bibliography

@@
 \usepackage{tikz-cd}
+\usepackage[utf8]{inputenc} % Enable UTF-8 encoding
+\usepackage[T1]{fontenc}
+\usepackage{textgreek}
 
@@
 The most commonly used coupling method is that proposed by Wu-Lin-Weng.
-As noted in \cite{dohau}, the method is one of several non-canonical decisions used in multi-class SVM modelling.
+As noted in [\cite{dohau}], the method is one of several non-canonical decisions used in multi-class SVM modelling.
 The goal of this paper is to compare its behavior with canonical methods.
@@
 
-\emph{Bayes covariance} is a notion introduced in  \cite{vsuch2016bayes}.
+\emph{Bayes covariance} is a notion introduced in  [\cite{vsuch2016bayes}].
 It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
@@
 Let us finally mention \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction \cite[p.~467]{hastie1998classification}.
+Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction [\cite[p.~467]{hastie1998classification}].
 Suppose we are classifying objects from CIFAR-10 dataset.
@@
 
-A notable example which uses this principle is the coupling method introduced in \cite{hastie1998classification}. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
+A notable example which uses this principle is the coupling method introduced in [\cite{hastie1998classification}]. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
 \begin{align*}
@@
 \end{align}
-is Bayes covariant \emph{and} symmetric. A key result proved in \cite{vsuch2016bayes} is that it is a unique such classifier for $K=3$.
+is Bayes covariant \emph{and} symmetric. A key result proved in [\cite{vsuch2016bayes}] is that it is a unique such classifier for $K=3$.
 
@@
 
-It is natural to consider the benchmark datasets used in previous evaluation of coupling methods \cite{wu2004probability}.
+It is natural to consider the benchmark datasets used in previous evaluation of coupling methods [\cite{wu2004probability}].
 The authors considered altogether seven datasets with number of classes ranging from 3 to 26.
@@
 penalized logistic regression or SVM).
-It usually provides results close to logistic regression \cite{james2013introduction}.
+It usually provides results close to logistic regression [\cite{james2013introduction}].
 
@@
 
-Although previous evaluations of the latter two methods were done in \cite{vsuch2016bayes}, they used phonetic data for which ground truth may be imprecise.
+Although previous evaluations of the latter two methods were done in [\cite{vsuch2016bayes}], they used phonetic data for which ground truth may be imprecise.
 
@@
 \begin{align}
-a_1 \boldsymbol{s}_1 + a_2 \boldsymbol{s}_2 + a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1
+a_1 \boldsymbol{s}_1 \oplus a_2 \boldsymbol{s}_2 \oplus a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1 \label{eq:family}
 \end{align}
@@
 In order to facilitate computations we opted to conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
-
-In order to reduce computational burden we selected 1000 three-class subproblems. The results are shown in Figure \ref{fig:par-bc}.
+To further reduce computational burden we selected 1000 three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
+The results are shown in Figure \ref{fig:par-bc}.
 
@@
 
+We can see that only in minority of cases we found a parametric method matching the performance of Wu-Lin-Weng's. This finding comes with caveat that we searched only in the simplex $a_i \geq 0$.
+
+Therefore as the final step in our investigation we looked whether a parametric Bayes covariant method in family \eqref{eq:family} for parameters \emph{outside} of this simplex could perform better.
+We conducted another search but this time
+\begin{itemize}
+	\item We searched within a much larger rectangle $D$ containing the simplex $a_i\geq 0$, which in this case is a triangle $T$.
+	\item We used Brier score as a smooth proxy for measuring the quality of multi-class classifier. This score is much smoother than 0-1 score which measures accuracy.
+\end{itemize}
+
+The results are shown in Figure \ref{fig:score}
+
 \begin{figure}[!ht]
@@
 The vertices triangle indicate the arboreal coupling methods, and the black circle the location of the optimum.}
+	\label{fig:score}
 \end{figure}
+
+We can see that indeed the optimum over the rectangle lies outside of the simplex.
+Let us compare the resulting accuracy of the optima in $\Delta$ and $D$.
+The results are shown in Table \ref{tab:step5}.
+
+\input tab-step5.tex
 

### 2025-04-21 paper.tex
Fix definition of Bayes covariance

@@
 
-Suppose we have $K$ classes of objects, each distributed according to a probability distribution $p_i$, $i=1,\ldots, K$ on a feature space $X$.
+Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature space $X$.
 In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class.
@@
 \begin{assumption} \label{ass:1}
- For all $x$ in the feature space we have $p_i(x) > 0$.
+ For all $x$ in the feature space we have $d_i(x) > 0$.
 \end{assumption}
@@
 \begin{align}
- p^\Pi_i(x) = \frac{p_i(x) P_i}{\sum_{k=1}^K p_k(x)P_k}.
+ p^\Pi_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
 \end{align}
@@
 \begin{align}
-	p_{ij}^\Pi(x) = \frac{p_i(x) P_i}{p_i(x)P_i + p_j(x)P_j}.
+	p_{ij}^\Pi(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
 \end{align}
@@
 	\begin{tikzcd}[column sep=3cm]
-		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow{dr}[swap]{multi-class~ prediction} & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
+		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
 		\arrow{d}{coupling} \\
@@
 \begin{align}
-\boldsymbol{p}^{\Pi'} \propto (p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}). \label{eq:changePrior}
+\boldsymbol{p}^{\Pi'} \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr). \label{eq:changePrior}
 \end{align}
@@
 When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
-If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is Bayes covariant.
-Symbolically, let us denote by  $\pi$ the change of priors.
-Let $\boldsymbol{R}^\pi$ be pairwise datum when we apply \eqref{eq:changePrior} to each binary classifier.
-For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
+If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.
 
-\begin{figure}[!h]
-\centering
-\begin{tikzcd}
-	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
-	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
-\end{tikzcd}
-\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
-\label{fig:bc}
-\end{figure}
+Let us make this explicit.
+Let $\boldsymbol{v}$ be a coupling method.
+Denote by  $\pi$ the change of priors $\pi:\Pi \rightarrow \Pi'$.
+If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_2^{ij}(D)$ by requiring
+$$
+\pi_2^{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
+$$
+We denote by $\boldsymbol{R}^\pi$ the matrix with entries $\pi_2^{ij}(r_{ij})$.
+The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
+
+On the other hand we can apply \eqref{eq:changePrior} after coupling. Say we have a distribution on $K$ classes
+\begin{align}
+D \propto (p_1, \ldots, p_K)
+\end{align}
+then we define $D^\pi$ by requiring 
+\begin{align}
+D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr).
+\end{align}
+We now say that a method if Bayes covariant if
+\begin{align}
+\boldsymbol{v}(\boldsymbol{R}^\pi)=	\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi,
+\end{align}
+for any pairwise predictions satisfying Assumption \ref{ass:1}.
+
+%Let $\boldsymbol{R}^\pi$ be the matrix of pairwise predictions when we apply \eqref{eq:changePrior} to each binary classifier.
+%For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
+%
+%\begin{figure}[!h]
+%\centering
+%\begin{tikzcd}
+%	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
+%	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
+%\end{tikzcd}
+%\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
+%\label{fig:bc}
+%\end{figure}
 
@@
 \end{prop}
+\begin{proof}
+	We can proceed by induction.
+The statement is clear when $K=2$.
+Suppose the proposition is true for an integers $<K$ and we are given a spanning tree $T$ on $K$ vertices.
+Any tree has a vertex of degree one.
+We may assume that in the case of $T$ it is the vertex corresponding to $C_1$ and the unique edge incident to $C_1$ is $C_1C_2$.
+
+	 Denote by $\boldsymbol{t}$ the prediction corresponding to $T$ and by $\boldsymbol{t}'$ the prediction corresponding to the subgraph without the vertex $C_1$. Let us write 
+	\begin{align*}
+	\boldsymbol{t}(x) &= (t_1, t_2, \ldots, t_K) \\
+	\boldsymbol{t'}(x) &= ( t'_2, \ldots, t'_K) 
+\end{align*}
+These vectors are related as follows:
+\begin{align}
+\begin{split}
+\frac{t_1}{t_1+t_2} &= r_{12} \\
+(t_2, \ldots, t_K) &\propto (t'_2, \ldots, t'_{K})
+\end{split} \label{eq:ind1}
+\end{align}
+
+Now consider the effect of change of priors $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. Applying \eqref{eq:changePrior} to the multi-class prediction yields a vector 
+$$
+\boldsymbol{t}^{\Pi\rightarrow \Pi'} \propto (t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}).
+$$
+Now consider what happens when we apply \eqref{eq:changePrior} before coupling.
+By induction assumption the method $\boldsymbol{t}'$ is Bayes covariant and thus applying coupling \emph{after} change of priors yields
+$$
+\boldsymbol{t}'^{\Pi\rightarrow \Pi'} \propto (t_2 \frac{P'_2}{P_2}, \ldots, t_K \frac{P'_K}{P_K})
+$$
+
+\end{proof}
 
@@
 
-Suppose real numbers $\alpha_1, \alpha_L$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_L$ are coupling methods.
-We define their linear combination $\bigoplus_i a_i \boldsymbol{v}_i$ as the coupling method that for any $x$ yields the probability distribution on $L$ classes that satisfies
+Suppose real numbers $\alpha_1, \ldots,\alpha_L$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_L$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
+We define their linear combination $\bigoplus_i a_i \boldsymbol{v}_i$ as the classification method that for any $x$ yields the probability distribution on $L$ classes that satisfies
 \begin{align*}
@@
 \end{align*}
-where the symbol $\odot$ denotes componentwise multiplication. With this definition we have the following result.
+where the symbol $\odot$ denotes componentwise multiplication. With this definition we can state the following result.
 
@@
 \end{prop}
+
+\begin{proof}
+
+\end{proof}
 

### 2025-04-23 paper.tex
Added proof for proposition 3

@@
 
-\emph{Canonicity} refers to requirement that the method should be in a natural way unique.
+\emph{Canonicity} refers to requirement that the method should be natural.
 Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
 Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
+
 Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
+For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical [\cite{shannon1948mathematical,selten1998axiomatic}].
 
@@
 $$
-We denote by $\boldsymbol{R}^\pi$ the matrix with entries $\pi_2^{ij}(r_{ij})$.
-The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
+We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_2^{ij}(r_{ij})$.
+The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents the effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
 
@@
 \end{align}
-for any pairwise predictions satisfying Assumption \ref{ass:1}.
+for any matrix $\boldsymbol{R}$ with $r_{ij}> 0$.
 
@@
 \begin{prop}
-Any arboreal method is Bayes covariant.
+Any arboreal method $\boldsymbol{t}$ is Bayes covariant.
 \end{prop}
 \begin{proof}
-	We can proceed by induction.
+We start by defining property $BC_{ij}$ (short for Bayes covariant when restricted to classes $i$ and $j$) of a coupling method.
+A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
+
+Let us list some easy to verify properties of this concept:
+
+\begin{itemize}
+\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$,
+\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant,
+\item[c)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant,
+\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
+\end{itemize}
+
+An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$.
+It follows using from b) and d) that the method is Bayes covariant.
+
+%	
+%	
+%Let $\pi$ be a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $(P'_1, \ldots, P'_K)$.
+We need to verify $\boldsymbol{v}(\boldsymbol{R}^\pi) =\bigl( \boldsymbol{v}(\boldsymbol{R})\bigr)$ for any pairwise matrix $\boldsymbol{R}$.
+|We will rephrase this in an equivalent way.
+Let
+%\begin{align}
+%	\begin{split}
+%	\boldsymbol{v}(\boldsymbol{R}^\pi) &= (v'_1, \ldots, v'_K) \\
+%	\boldsymbol{v}(\boldsymbol{R}) &= (v_1, \ldots, v_K)
+%	\end{split}
+%\end{align}
+%Suppose $\pi$ is a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. If the prediction given $\Pi$ is $(t_1, \ldots, t_K)$ then we need to prove that
+%\begin{align*}
+%\boldsymbol{t}(R^\pi) = \bigl(t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}\bigr)
+%\end{align*}
+%	
+%	We can proceed by induction.
 The statement is clear when $K=2$.
@@
 We may assume that in the case of $T$ it is the vertex corresponding to $C_1$ and the unique edge incident to $C_1$ is $C_1C_2$.
-
-	 Denote by $\boldsymbol{t}$ the prediction corresponding to $T$ and by $\boldsymbol{t}'$ the prediction corresponding to the subgraph without the vertex $C_1$. Let us write 
-	\begin{align*}
-	\boldsymbol{t}(x) &= (t_1, t_2, \ldots, t_K) \\
-	\boldsymbol{t'}(x) &= ( t'_2, \ldots, t'_K) 
-\end{align*}
-These vectors are related as follows:
-\begin{align}
-\begin{split}
-\frac{t_1}{t_1+t_2} &= r_{12} \\
-(t_2, \ldots, t_K) &\propto (t'_2, \ldots, t'_{K})
-\end{split} \label{eq:ind1}
-\end{align}
-
-Now consider the effect of change of priors $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. Applying \eqref{eq:changePrior} to the multi-class prediction yields a vector 
-$$
-\boldsymbol{t}^{\Pi\rightarrow \Pi'} \propto (t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}).
-$$
-Now consider what happens when we apply \eqref{eq:changePrior} before coupling.
+%	
+%	 Denote by $\boldsymbol{t}$ the prediction corresponding to $T$ and by $\boldsymbol{t}'$ the prediction corresponding to the subgraph without the vertex $C_1$. Let us write 
+%	\begin{align*}
+%	\boldsymbol{t}(x) &= (t_1, t_2, \ldots, t_K) \\
+%	\boldsymbol{t'}(x) &= ( t'_2, \ldots, t'_K) 
+%\end{align*}
+%These vectors are related as follows:
+%\begin{align}
+%\begin{split}
+%\frac{t_1}{t_1+t_2} &= r_{12} \\
+%(t_2, \ldots, t_K) &\propto (t'_2, \ldots, t'_{K})
+%\end{split} \label{eq:ind1}
+%\end{align}
+%
+%Now consider the effect of change of priors $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. Applying \eqref{eq:changePrior} to the multi-class prediction yields a vector 
+%$$
+%\boldsymbol{t}^{\Pi\rightarrow \Pi'} \propto (t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}).
+%$$
+%Now consider what happens when we apply \eqref{eq:changePrior} before coupling.
 By induction assumption the method $\boldsymbol{t}'$ is Bayes covariant and thus applying coupling \emph{after} change of priors yields
-$$
-\boldsymbol{t}'^{\Pi\rightarrow \Pi'} \propto (t_2 \frac{P'_2}{P_2}, \ldots, t_K \frac{P'_K}{P_K})
-$$
+%$$
+%\boldsymbol{t}'^{\Pi\rightarrow \Pi'} \propto (t_2 \frac{P'_2}{P_2}, \ldots, t_K \frac{P'_K}{P_K})
+%$$
 
@@
 Suppose real numbers $\alpha_1, \ldots,\alpha_L$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_L$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
-We define their linear combination $\bigoplus_i a_i \boldsymbol{v}_i$ as the classification method that for any $x$ yields the probability distribution on $L$ classes that satisfies
+We define their linear combination $\bigoplus_i a_i \boldsymbol{v}_i$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
 \begin{align*}
@@
 \end{align*}
-where the symbol $\odot$ denotes componentwise multiplication. With this definition we can state the following result.
+where the symbol $\odot$ denotes componentwise multiplication, and exponentials are computed component-wise. With this definition we can state the following result.
 
@@
 \begin{proof}
+We will be using property $BC_{ij}$ from the proof of the previous proposition. It is sufficient to show that $BC_{ij}$ holds for any $i\not= j$.
 
+Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$.
+Let $o_l$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_l$.
+Then the odds of $C_i$ and $C_j$ predicted by $(\bigoplus_i a_i \boldsymbol{v}_i)^\pi$ are
+\begin{align}
+	\biggl(\bigoplus_i a_i \boldsymbol{v}_i\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_i a_i \boldsymbol{v}_i\biggr)(\boldsymbol{R}) \\
+	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_l o_l^{a_l}
+\end{align}
+
+Let us now use Bayes covariant of $\boldsymbol{v}_i$. We have
+\begin{align}
+	\biggl(\bigoplus_i a_i \boldsymbol{v}_i\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_i a_i \boldsymbol{v}_i^\pi\biggr)(\boldsymbol{R}) \\
+	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_l o_l^{a_l}
+\end{align}
+
+It follows that the odds of $C_i$ to $C_j$ for $\bigoplus_i a_i \boldsymbol{v}_i$ are 
+\begin{align}
+\biggl(\frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggr)^{\sum a_i} \prod_l o_l^{a_l}.
+\end{align}
+Clearly, under the assumption $\sum_i a_i = 1$, the classifier $\bigoplus_i a_i \boldsymbol{v}_i$ satisfies $BC_{ij}$ and it follows that it is Bayes covariant.
 \end{proof}

### 2025-04-24 paper.tex
Fixed indexes to be more readable (l is often confused with 1)

@@
 
-Suppose real numbers $\alpha_1, \ldots,\alpha_L$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_L$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
-We define their linear combination $\bigoplus_i a_i \boldsymbol{v}_i$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
+Suppose real numbers $\alpha_1, \ldots,\alpha_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
+We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
 \begin{align*}
- 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_L \boldsymbol{v}_L\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_L^{a_L}(x),
+ 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_M \boldsymbol{v}_M\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(x),
 \end{align*}
@@
 \begin{prop}
-Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_L$ are Bayes covariant. If $\sum a_i = 1$, then $\bigoplus_i a_i \boldsymbol{v}_i$ is also a Bayes covariant coupling method.
+Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
 \end{prop}
@@
 Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$.
-Let $o_l$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_l$.
+Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$.
 Then the odds of $C_i$ and $C_j$ predicted by $(\bigoplus_i a_i \boldsymbol{v}_i)^\pi$ are
 \begin{align}
-	\biggl(\bigoplus_i a_i \boldsymbol{v}_i\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_i a_i \boldsymbol{v}_i\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_l o_l^{a_l}
+	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R}) \\
+	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
 \end{align}
 
-Let us now use Bayes covariant of $\boldsymbol{v}_i$. We have
+Let us now use Bayes covariance of $\boldsymbol{v}_i$. We have
 \begin{align}
-	\biggl(\bigoplus_i a_i \boldsymbol{v}_i\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_i a_i \boldsymbol{v}_i^\pi\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_l o_l^{a_l}
+	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_m a_m \boldsymbol{v}_m^\pi\biggr)(\boldsymbol{R}) \\
+	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
 \end{align}
 
-It follows that the odds of $C_i$ to $C_j$ for $\bigoplus_i a_i \boldsymbol{v}_i$ are 
+It follows that the odds of $C_i$ to $C_j$ for $\bigoplus_m a_m \boldsymbol{v}_m$ are 
 \begin{align}
-\biggl(\frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggr)^{\sum a_i} \prod_l o_l^{a_l}.
+\biggl(\frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggr)^{\sum a_m} \prod_m o_m^{a_m}.
 \end{align}
-Clearly, under the assumption $\sum_i a_i = 1$, the classifier $\bigoplus_i a_i \boldsymbol{v}_i$ satisfies $BC_{ij}$ and it follows that it is Bayes covariant.
+Clearly, under the assumption $\sum_m a_m = 1$, the classifier $\bigoplus_m a_m \boldsymbol{v}_m$ satisfies $BC_{ij}$ and it follows that it is Bayes covariant.
 \end{proof}

### 2025-05-02 lda.R
Fix build

@@ -537,9 +537,11 @@ write_multi <- function(runs = 20, workers = 11, tol = 1/2^(2:12), score = "acc"
             lda_multi(dfs, tols = tol, score = score)$multi
         }) |> list_rbind()
     }) |> list_rbind() |> 
-        group_by(dataset, tol, method) |> summarize(acc = mean(correct))
-        #pivot_wider(names_from = "method", values_from = "correct")
-    write.csv(df, file = "data/multi.csv", row.names = F, quote = F)
+        group_by(dataset, tol, method) |> summarize(acc = mean(correct), correct = sum(correct)) |>
+        pivot_wider(names_from = "method", values_from = "correct")
+    df$score = score
+    write.csv(df, file = sprintf("data/multi-%s.csv", score), row.names = F, quote = F)
+    df
 }
 
 write_triples <- function(runs = 20, workers = 11) {

### 2025-05-07 paper.tex
Trying to make generated graphs
Fix build
Starting rewrite of proofs
Fix names of theory sections

@@
 
-\title{On probabilistic one-vs-one classification}
+\title{On change of priors in one-vs-one classification methods}
 
@@
 
-\subsection{Bayes classifier}
+\subsection{One-vs-on classification}
 
-An exact solution to this problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.
+An exact solution to a classification problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.
 
@@
 
-\begin{prop} \label{prop:binary2multi}
-The system of  equations \eqref{eq:bt1} in unknowns $p_i^\Pi(x)$ has a unique solution which is the multi-class Bayes classifier.
+\begin{prop}[Fundamental theorem of one-vs-one classification]
+	 \label{prop:binary2multi}
+	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
 \end{prop}
+\begin{proof}
+	Indeed, from \eqref{eq:bt1} we deduce the odds of classes $C_j$ to $C_i$
+	\begin{align}
+	\frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
+	\end{align}
+	Knowing the odds of $C_2$ to $C_1$, $C_3$ to $C_2$ up to $C_{K}$ to $C_{K-1}$ together with the requirement that probabilities sum to one uniquely determines the whole vector $\boldsymbol{p}^\Pi(x)$.
+\end{proof}
 %\begin{proof}
@@
 
-\subsection{One-vs-one classification }
+\subsection{Coupling methods}
 
-In practice one does not have know true probability distributions and hence cannot construct Bayes classifier.
+In practice one does not have know true probability distributions and hence cannot construct Bayes classifies.
 However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$.
@@
 Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
-The system is usually inconsistent and additional assumptions are needed.
-A method to solve Bradley-Terry equations is called a coupling method.
+The system is usually inconsistent and additional assumptions are needed to construct an estimator.
+A method to solve Bradley-Terry equations is called a \emph{coupling method}.
 Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
@@
 
-In order to obtain a regular system of equations for  larger values of $K$ , the resulting classifiers must represent a connected tree within the complete graph on all classes.
-Any arboreal method is non-canonical, because there is no natural way to choose a tree in a complete graph.
+For $K>3$ the three methods can be generalized to corresponds to the trees having the graph structure  of a star centered at class $C_i$ for $i=1, \ldots, K$.
+
+More generally, to obtain a regular system of equations for  any of $K$ , it is necessary that the tree corresponding to an arboreal method forms a spanning tree.
+Note that any arboreal method is non-canonical, because there is no natural way to choose a tree in a complete graph.
+In fact, a stronger statement is true -- no arboreal method is symmetric.
+%However, we will see in Section \ref{sec:bc2} that by ``averaging'' several stars we can obtain a canonical
 
@@
 In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
-Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
+Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centred at the class $C_i$.
 The predictions will generally span the vector space $R^K$.
@@
 %
-The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${{T}}_i$.
+The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${\boldsymbol{s}}_i$.
 
-\subsection{Bayes covariant methods}
+\subsection{Bayes covariant methods} \label{sec:bc2}
 
-There are many Bayes covariant methods. First examples are provided by arboreal coupling methods.
+There are many Bayes covariant methods. In this section we will show that 
+\begin{itemize} 
+	\item arboreal coupling methods are Bayes covariant,
+	\item Bayes covariant methods can be ensembled,
+	\item describe all Bayes covariant methods for $K=3$.
+\end{itemize}
 
-\begin{prop}
-Any arboreal method $\boldsymbol{t}$ is Bayes covariant.
-\end{prop}
-\begin{proof}
-We start by defining property $BC_{ij}$ (short for Bayes covariant when restricted to classes $i$ and $j$) of a coupling method.
+We start by defining the property $BC_{ij}$ (the notation stands for \emph{Bayes covariant when restricted to classes} $i$ and $j$) of a coupling method.
 A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
@@
 \end{itemize}
+
+Now we are ready to prove the our first result.
+
+\begin{prop}
+Any arboreal method is Bayes covariant.
+\end{prop}
+\begin{proof}
 
@@
 	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R}) \\
+\end{align}
+so the odds are
+
+\begin{align}
 	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
@@
 
-Let us now use Bayes covariance of $\boldsymbol{v}_i$. We have
+Let us now use Bayes covariance of $\boldsymbol{v}_i$. 
+We have
 \begin{align}
 	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_m a_m \boldsymbol{v}_m^\pi\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
+%	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
 \end{align}
@@
 
-Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$:
+Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$:
 \[
@@
 \begin{figure}[!ht]
-\includegraphics{graph/exp2-summary.pdf}
+\includegraphics{graphs/exp2-summary.pdf}
 \caption{Results of grid search for parametric Bayes covariant methods matching performance of Wu-Lin-Weng's method}
@@
 \begin{figure}[!ht]
-	\includegraphics{graph/exp2-detail.pdf}
+	\includegraphics{graphs/exp2-detail.pdf}
 	\caption{Color map indicates the value of Brier score computed for an ensemble of coupling methods on the testing dataset.

### 2025-05-07 paper.tex
Introduce odds notation

@@
 \begin{proof}
-	Indeed, from \eqref{eq:bt1} we deduce the odds of classes $C_j$ to $C_i$
+	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denotes the odds of $C_i$ to $C_j$:
 	\begin{align}
-	\frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
+		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j}
+	\end{align}
+
+	From \eqref{eq:bt1} we can deduce the odds of classes $C_j$ to $C_i$ as
+	\begin{align}
+	\alpha_{ij}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
 	\end{align}
@@
 
-Suppose real numbers $\alpha_1, \ldots,\alpha_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
+Suppose real numbers $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
 We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies

### 2025-05-08 appendix.tex
Restructure paper into multiple files

--- 2025-04-24 paper.tex
@@
-\documentclass[twoside,11pt]{article}
+\appendix
 
-\usepackage{blindtext}
+\section{}
+\label{app:bc1}
 
-% Any additional packages needed should be included after jmlr2e.
-% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
-% and defines many common macros, such as 'proof' and 'example'.
-%
-% It also sets the bibliographystyle to plainnat; for more information on
-% natbib citation styles, see the natbib documentation, a copy of which
-% is archived at http://www.jmlr.org/format/natbib.pdf
-
-% Available options for package jmlr2e are:
-%
-%   - abbrvbib : use abbrvnat for the bibliography style
-%   - nohyperref : do not load the hyperref package
-%   - preprint : remove JMLR specific information from the template,
-%         useful for example for posting to preprint servers.
-%
-% Example of using the package with custom options:
-%
-% \usepackage[abbrvbib, preprint]{jmlr2e}
-
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{jmlr2e}
-
-\usepackage{multirow}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{rotating}
-\usepackage{tikz-cd}
-\usepackage[utf8]{inputenc} % Enable UTF-8 encoding
-\usepackage[T1]{fontenc}
-\usepackage{textgreek}
-
-\newtheorem{prop}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{assumption}{Assumption}
-
-% Definitions of handy macros can go here
-
-\newcommand{\dataset}{{\cal D}}
-\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-\DeclareMathOperator*{\divm}{div}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
-
-\usepackage{lastpage}
-\jmlrheading{23}{2025}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Probabilistic OVO}{Probabilistic OVO}
-\firstpageno{1}
-
-\begin{document}
-
-\title{On probabilistic one-vs-one classification}
-
-\author{\name Ondrej Šuch \email ondrejs@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       \AND
-       \name Peter Novotný \email peter.novotny@uniza.sk \\
-       \addr Fakulta informatiky a riadenia\\
-       Žilinská Univerzita v Žiline\\
-       Žilina, 010 26, Slovakia
-       \AND
-       \name Ali Haidar \email haidar@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       }
-
-\editor{My editor}
-
-\maketitle
-
-\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-\blindtext
-\end{abstract}
-
-\begin{keywords}
-  keyword one, keyword two, keyword three
-\end{keywords}
-
-\section{Introduction}
-
-%\blindmathpaper
-
-Multi-class classification is considered to be a more challenging problem than binary classification.
-A natural approach to multi-class classification is to reduce it to a series of binary classification problems and deduce the multi-class decision by aggregating decisions for the binary problems.
-
-One popular method belonging to  this paradigm uses probabilistic modelling for one-vs-one series of binary problems.
-Notably, it is used as the basis for multi-class classification models using support vector machines (SVM) in LIBSVM library.
-However one can use the approach more generally,  because it can be applied to any probabilistic binary classification method.
-
-A key step in probabilistic one-vs-one modelling is the aggregation of results of individual binary classifiers - so-called \emph{coupling method}.
-The most commonly used coupling method is that proposed by Wu-Lin-Weng.
-As noted in [\cite{dohau}], the method is one of several non-canonical decisions used in multi-class SVM modelling.
-The goal of this paper is to compare its behavior with canonical methods.
-
-\section{Theoretical basis of coupling methods}
-
-Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature space $X$.
-In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class.
-Given $x$ in $X$ we aim to find the probability that $x$ belongs to $i$-th class.
-
-\subsection{Bayes classifier}
-
-An exact solution to this problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.
-
-\begin{assumption} \label{ass:1}
- For all $x$ in the feature space we have $d_i(x) > 0$.
-\end{assumption}
-Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.
-
-The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
-\begin{align}
- p^\Pi_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
-\end{align}
-
-Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of classes.
-Assuming prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier predicts the probability of $i$-th class as
-
-\begin{align}
-	p_{ij}^\Pi(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
-\end{align}
-
-Knowledge of vector $\boldsymbol{p}^\Pi(x)$ is  equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
-\begin{align}
-p_{ij}^\Pi(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
-\end{align}
-
-Conversely, it is easy to show that  the system of equations \eqref{eq:bt1} has a unique solution.
-
-\begin{prop} \label{prop:binary2multi}
-The system of  equations \eqref{eq:bt1} in unknowns $p_i^\Pi(x)$ has a unique solution which is the multi-class Bayes classifier.
-\end{prop}
-%\begin{proof}
-%Indeed, we have 
-%\begin{align*}
-%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
-%\end{align*}
-%\end{proof}
-
-\subsection{One-vs-one classification }
-
-In practice one does not have know true probability distributions and hence cannot construct Bayes classifier.
-However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$.
-The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$.
-One does it by finding an approximate solution of the system of equations
-%\begin{align}
-%
-%\end{align}
-%
-%
-%Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$.
-Let us denote the $r_{ij}(x)$ the output of Bayes (binary) classifier for $x$ in $X$ yielding the probability $p(x \in C_i \mid x\in C_i \cup C_j )$.
-Then we have
-%\begin{equation}
-%r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
-%\end{equation}
-%
-%
-%The system of equations is called Bradley--Terry equations.
-The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations.
-The theoretical basis for one-vs-one classification framework is provided by the following result.
-%
-%
-%
-%Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$.
-A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
-\begin{equation}
-	{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
-\end{equation}
-
-% One should note that 
-%\begin{itemize}
-%\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
-%\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
-%\end{itemize}
-
-Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
-The system is usually inconsistent and additional assumptions are needed.
-A method to solve Bradley-Terry equations is called a coupling method.
-Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
-Schematically, classification using coupling method $\boldsymbol{v}$ proceeds as indicated in Figure \ref{fig:coupling}.
-
-\begin{figure}[!h]
-	\centering
-	\begin{tikzcd}[column sep=3cm]
-		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
-		\arrow{d}{coupling} \\
-		 & \boldsymbol{v}(\boldsymbol{R}(x)) 
-	\end{tikzcd}
-	\caption{Multi-class classification using a coupling method $\boldsymbol{v}$}
-	\label{fig:coupling}
-\end{figure}
-
-\subsection{Exact desiderata on coupling method} \label{sec:des:exact}
-
-Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
-this section
- we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
-
-%\begin{itemize}
-%\item a coupling method should should always provide a unique solution, at least when all $r_{ij}>0$,
-%\item Bradley-Terry consistency,
-%\item canonicity,
-%\item symmetry,
-%\item Bayes covariance,
-%
-%\item good accuracy on benchmark tasks,
-%\item lack of parameters, or at least having a small number of parameters,
-%\item Hinton's minimality,
-%\item simplicity of computation.
-%\end{itemize}
-
-\emph{Unique solution} refers to the fact that the procedure to compute a multi-class probabilistic prediction always converges to a unique solution.
-One way to satisfy this condition would be that it amounts to a linear system of equations in $K$ variables, and the matrix of the system would be invertible.
-Another example would be when the procedure amounts to finding the minimum of a strongly convex function.
-
-\emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
-The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
-satisfies \eqref{eq:bt1}.
-
-\emph{Canonicity} refers to requirement that the method should be natural.
-Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
-Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
-
-Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
-For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical [\cite{shannon1948mathematical,selten1998axiomatic}].
-
-\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions.
-The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by
-\begin{equation}
-	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
-\end{equation}
-We say that a coupling method $V$ is \emph{symmetric} if 
-\begin{align}
-		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
-\end{align}
-
-\emph{Bayes covariance} is a notion introduced in  [\cite{vsuch2016bayes}].
-It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
-Any Bayes classifier, whether binary or multiclass changes its prediction when the priors change.
-Let us describe the process.
-Suppose we change priors from $\Pi = (P_1, \ldots, P_k)$ to $\Pi'= (P'_1, \ldots, P'_K)$.
-Then the prediction of Bayes classifiers changes from $\boldsymbol{p}^\Pi= (p_1, \ldots, p_K)$ to the vector
-\begin{align}
-\boldsymbol{p}^{\Pi'} \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr). \label{eq:changePrior}
-\end{align}
-
-When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
-If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.
-
-Let us make this explicit.
-Let $\boldsymbol{v}$ be a coupling method.
-Denote by  $\pi$ the change of priors $\pi:\Pi \rightarrow \Pi'$.
-If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_2^{ij}(D)$ by requiring
-$$
-\pi_2^{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
-$$
-We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_2^{ij}(r_{ij})$.
-The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents the effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
-
-On the other hand we can apply \eqref{eq:changePrior} after coupling. Say we have a distribution on $K$ classes
-\begin{align}
-D \propto (p_1, \ldots, p_K)
-\end{align}
-then we define $D^\pi$ by requiring 
-\begin{align}
-D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr).
-\end{align}
-We now say that a method if Bayes covariant if
-\begin{align}
-\boldsymbol{v}(\boldsymbol{R}^\pi)=	\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi,
-\end{align}
-for any matrix $\boldsymbol{R}$ with $r_{ij}> 0$.
-
-%Let $\boldsymbol{R}^\pi$ be the matrix of pairwise predictions when we apply \eqref{eq:changePrior} to each binary classifier.
-%For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
-%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzcd}
-%	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
-%	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
-%\end{tikzcd}
-%\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
-%\label{fig:bc}
-%\end{figure}
-
-\subsection{Inexact desiderata for coupling methods}
-
-\label{sec:des:inexact}
-
-In this section we describe several concepts that lack strict mathematical delineation, but may still be important to consider.
-
-\emph{Good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
-This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform.
-However a good coupling method should perform robustly across a variety of datasets.
-A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
-At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
-
-\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtain unbiased estimates of the parameters of the coupling method.
-This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters.
-For example, this is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
-
-\emph{Simplicity of computation}  may refer to the computational requirement for inference.
-With the dramatic increase of edge computing devices, such as smartphones, a simple, fast, energy-efficient algorithm may be preferable to a better performing one which would require more computational resources.
-
-Let us finally mention \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction [\cite[p.~467]{hastie1998classification}].
-Suppose we are classifying objects from CIFAR-10 dataset.
-If the true class is  a ``dog'', why should we care what is the output of the classifier distinguishing ``airplanes'' from ``ships''?
-The binary classifier is trained only on airplanes and ships, and has never seen a dog.
-One may thus prefer a classifier which somehow suppresses noisy output of (seemingly) irrelevant classifiers.
-
-%The first that the five conditions have a clear mathematical definition, whereas the rest are not exact.
-For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.
-
-\section{Examples of coupling methods} \label{sec:coupling}
-
-There is a plethora of methods available for coupling. In this section we describe four major classes.
-
-\subsection{Methods aiming to minimize binary divergence}
-
-A multi-class estimate $\hat{\boldsymbol{p}}$ obtained by a coupling method implies via \eqref{eq:bt1} probability distributions on each pair of classes:
-\begin{align*}
-	\hat D_{ij}^\textrm{multi}= \biggl(\frac{\hat{p_i}}{\hat p_i + \hat p_j},\frac{\hat{p_j}}{\hat p_i + \hat p_j}\biggr)	
-\end{align*}
-On the other hand, binary classifiers provide another distribution for each pair of  classes, namely
-\begin{align*}
-\hat D_{ij}^\textrm{binary} = (\hat r_{ij}, \hat r_{ji}).
-\end{align*}
-
-A natural way to find  $\hat{\boldsymbol{p}}$ is thus to minimize a functional incorporating divergence measures between these distributions
-\begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
-\end{align*}
-
-A notable example which uses this principle is the coupling method introduced in [\cite{hastie1998classification}]. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
-\begin{align*}
-	\divm\nolimits_\textrm{KL} (\boldsymbol{p}, \boldsymbol{q})= \sum p_i \log (p_i/ q_i)
-\end{align*}
-
-Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
-In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score [\cite{gneiting2007strictly, buja2005loss}].
-
-For instance, a popular alternative is divergence arising from the quadratic  score [\cite{gneiting2007strictly}] (also known as Brier score [\cite{brier1950verification}]).
-This divergence takes the form
-$$
-\divm\nolimits_\textrm{quad} (\boldsymbol{p}, \boldsymbol{q})= \sum (p_i - q_i)^2.
-$$
-Unlike Kullback-Leibler divergence, the penalty for incorrect prediction with arbitrarily low probability is bounded (by one).
-This quadratic score is the basis of the popular Wu-Lin-Weng's method [\cite{wu2004probability}].
-
-Their method uses an additional trick, which we term \emph{self-referentiality}.
-In the method of Hastie and Tibshirani, $w_{ij}$ are constants derived from observed class frequencies.
-However, we could use weights $w_{ij}$ that increase when the predicted probability of either class $i$ or $j$ is high.
-A reasonable choice would be for instance $w_{ij}= p_i + p_j$.
-In the case of quadratic score, it is more convenient to use weights $w_{ij} = (p_i + p_j)^2$ because then the resulting optimization problem is just minimization of a quadratic form
-\begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{i,j} (r_{ij}p_j - r_{ji}p_i)^2.
-\end{align*}
-
-We note that the method is symmetric.
-The choice of quadratic scoring rule can also be viewed as canonical in view of axiomatic characterization given in  [\cite{selten1998axiomatic}].
-However the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary.
-Thus we do not view Wu-Lin-Weng's method as canonical.
-
-\subsection{Arboreal methods}
-
-System of equations \eqref{eq:bt2} is overdetermined because there are $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.
-Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns.
-This principle underlies arboreal coupling methods.
-
-An arboreal coupling method ignores all but $K-1$ of the pairwise predictions.
-A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes 1 and 3.
-The two equations form \eqref{eq:bt2} together with the requirement that the prediction probabilities should sum to 1 yield the following system of equations
-\begin{equation}
-	\begin{split}
-		\frac{\hat p_1}{\hat p_1 + \hat p_2} &= {r}_{12}\\
-		\frac{\hat p_2}{\hat p_2 + \hat p_3} &= {r}_{23}\\
-		\hat p_1 + \hat p_2 + \hat p_3 &= 1
-	\end{split}
-	\label{eq:arb1}
-\end{equation}
-
-For $K=3$, there are three different arboreal coupling methods, which we shall call $\boldsymbol{s}_1$, $\boldsymbol{s}_2$, $\boldsymbol{s}_3$, where the system \eqref{eq:arb1} represents the coupling method $\boldsymbol{s}_2$.
-
-In order to obtain a regular system of equations for  larger values of $K$ , the resulting classifiers must represent a connected tree within the complete graph on all classes.
-Any arboreal method is non-canonical, because there is no natural way to choose a tree in a complete graph.
-
-\subsection{Methods emphasizing Hinton's minimality}
-
-A variant on arboreal methods is the following oracle method which we shall call Hinton's oracle.
-It  assumes it has the access to the ground truth $y = C_t$.
-It outputs probabilities by solving only the equations
-$$
-\frac{\hat p_t}{\hat p_t + \hat p_j} = {r}_{tj},\quad \textrm{for }j\not = t,
-$$
-together the  with total sum equation
-$$
-\sum_{i=1}^K  \hat p_i = 1.
-$$
-
-For any sample, its result is identical to the arboreal method where the underlying tree forms a star.
-This method is clearly the optimal one with respect to Hinton's minimality criterion, because it ignores the output of any classifier not trained on the true class.
-It is not a true classification method, however, because it ``peeks'' at the label.
-Its main utility is to provide a way to benchmark other methods with respect to Hinton's minimality.
-
-In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
-Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
-The predictions will generally span the vector space $R^K$.
-In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $\boldsymbol{s}_i(x)$.
-Let us now define \emph{radial} coupling method.
-The  method requires that for the  weights we could in fact use the components of $\boldsymbol{p}$ i.e.
-\begin{equation}
-	\begin{split}
-	\hat {\boldsymbol{p}} &= \hat p_1 \boldsymbol{s}_1(x) + \ldots + \hat p_K \boldsymbol{s}_K(x)\\
-	1 &= \hat p_1 + \ldots + \hat p_K
-	\end{split}
-	 \label{eq:radial}
-\end{equation}
-%
-The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${{T}}_i$.
-
-\subsection{Bayes covariant methods}
-
-There are many Bayes covariant methods. First examples are provided by arboreal coupling methods.
+In this appendix we provide proofs of statements used in Section \label{sec:bc2}.
 
 \begin{prop}
-Any arboreal method $\boldsymbol{t}$ is Bayes covariant.
+	Let $\boldsymbol{v}$ be a coupling method. The following statements are equivalent:
+	\begin{itemize}
+		\item[a)] The coupling method $\boldsymbol{v}$ is Bayes covariant.
+		\item[b)] The coupling method $\boldsymbol{v}$ satisfies $BC_{12}, BC_{23}, \ldots, BC_{K-1,K}$.
+		\item[c)] The coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ for any pair of integers between 1 and $K$ with $i\not= j$.
+	\end{itemize}
 \end{prop}
 \begin{proof}
-We start by defining property $BC_{ij}$ (short for Bayes covariant when restricted to classes $i$ and $j$) of a coupling method.
-A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
-
-Let us list some easy to verify properties of this concept:
-
-\begin{itemize}
-\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$,
-\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant,
-\item[c)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant,
-\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
-\end{itemize}
-
-An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$.
-It follows using from b) and d) that the method is Bayes covariant.
-
-%	
-%	
-%Let $\pi$ be a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $(P'_1, \ldots, P'_K)$.
-We need to verify $\boldsymbol{v}(\boldsymbol{R}^\pi) =\bigl( \boldsymbol{v}(\boldsymbol{R})\bigr)$ for any pairwise matrix $\boldsymbol{R}$.
-|We will rephrase this in an equivalent way.
-Let
-%\begin{align}
-%	\begin{split}
-%	\boldsymbol{v}(\boldsymbol{R}^\pi) &= (v'_1, \ldots, v'_K) \\
-%	\boldsymbol{v}(\boldsymbol{R}) &= (v_1, \ldots, v_K)
-%	\end{split}
-%\end{align}
-%Suppose $\pi$ is a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. If the prediction given $\Pi$ is $(t_1, \ldots, t_K)$ then we need to prove that
-%\begin{align*}
-%\boldsymbol{t}(R^\pi) = \bigl(t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}\bigr)
-%\end{align*}
-%	
-%	We can proceed by induction.
-The statement is clear when $K=2$.
-Suppose the proposition is true for an integers $<K$ and we are given a spanning tree $T$ on $K$ vertices.
-Any tree has a vertex of degree one.
-We may assume that in the case of $T$ it is the vertex corresponding to $C_1$ and the unique edge incident to $C_1$ is $C_1C_2$.
-%	
-%	 Denote by $\boldsymbol{t}$ the prediction corresponding to $T$ and by $\boldsymbol{t}'$ the prediction corresponding to the subgraph without the vertex $C_1$. Let us write 
-%	\begin{align*}
-%	\boldsymbol{t}(x) &= (t_1, t_2, \ldots, t_K) \\
-%	\boldsymbol{t'}(x) &= ( t'_2, \ldots, t'_K) 
-%\end{align*}
-%These vectors are related as follows:
-%\begin{align}
-%\begin{split}
-%\frac{t_1}{t_1+t_2} &= r_{12} \\
-%(t_2, \ldots, t_K) &\propto (t'_2, \ldots, t'_{K})
-%\end{split} \label{eq:ind1}
-%\end{align}
-%
-%Now consider the effect of change of priors $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. Applying \eqref{eq:changePrior} to the multi-class prediction yields a vector 
-%$$
-%\boldsymbol{t}^{\Pi\rightarrow \Pi'} \propto (t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}).
-%$$
-%Now consider what happens when we apply \eqref{eq:changePrior} before coupling.
-By induction assumption the method $\boldsymbol{t}'$ is Bayes covariant and thus applying coupling \emph{after} change of priors yields
-%$$
-%\boldsymbol{t}'^{\Pi\rightarrow \Pi'} \propto (t_2 \frac{P'_2}{P_2}, \ldots, t_K \frac{P'_K}{P_K})
-%$$
 
@@
 
-Given several Bayes covariant methods one can form  their ``linear combination'' - an ensemble which is also Bayes covariant. Let us make it explicit.
-
-Suppose real numbers $\alpha_1, \ldots,\alpha_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
-We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
-\begin{align*}
- 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_M \boldsymbol{v}_M\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(x),
-\end{align*}
-where the symbol $\odot$ denotes componentwise multiplication, and exponentials are computed component-wise. With this definition we can state the following result.
-
-\begin{prop}
-Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
-\end{prop}
-
+\begin{lem} \label{lem:transitivity}
+	If a coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
+\end{lem}
 \begin{proof}
-We will be using property $BC_{ij}$ from the proof of the previous proposition. It is sufficient to show that $BC_{ij}$ holds for any $i\not= j$.
-
-Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$.
-Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$.
-Then the odds of $C_i$ and $C_j$ predicted by $(\bigoplus_i a_i \boldsymbol{v}_i)^\pi$ are
+	Let $\pi$ be a change of priors. From the assumptions we have 
 	\begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
+		\alpha_{ij}(\boldsymbol{v}(\boldsymbol{R})^\pi ) &= \alpha_{ij}(\boldsymbol{v}(\boldsymbol{R}^\pi) ) \\
+		\alpha_{jk}(\boldsymbol{v}(\boldsymbol{R})^\pi ) &= \alpha_{jk}(\boldsymbol{v}(\boldsymbol{R}^\pi) )
 	\end{align}
-
-Let us now use Bayes covariance of $\boldsymbol{v}_i$. We have
+	Since $\alpha_{ik}(\boldsymbol{p}) = \alpha_{ij}(\boldsymbol{p})  \alpha_{jk}(\boldsymbol{p})$ it follows that for any $\boldsymbol{R}$
 	\begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_m a_m \boldsymbol{v}_m^\pi\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
+		\alpha_{ik}(\boldsymbol{v}(\boldsymbol{R})^\pi ) &= \alpha_{ik}(\boldsymbol{v}(\boldsymbol{R}^\pi) )
 	\end{align}
-
-It follows that the odds of $C_i$ to $C_j$ for $\bigoplus_m a_m \boldsymbol{v}_m$ are 
-\begin{align}
-\biggl(\frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggr)^{\sum a_m} \prod_m o_m^{a_m}.
-\end{align}
-Clearly, under the assumption $\sum_m a_m = 1$, the classifier $\bigoplus_m a_m \boldsymbol{v}_m$ satisfies $BC_{ij}$ and it follows that it is Bayes covariant.
+	which means that the coupling method satisfies $BC_{ik}$.
 \end{proof}
 
-% 
-% given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
-%\begin{align*}
-%	\boldsymbol{B}(x) = (p_1, \ldots, p_K)\quad\textrm{and}\quad \boldsymbol{\tilde B}(x) = (\tilde p_1, \ldots, \tilde p_K)
-%\end{align*}
-%then the prediction of the ensemble $\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}$ is given by
-%\begin{align*}
-%	\bigl(\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}\bigr)(x)\propto (\,p_1^\alpha \tilde p_1^\beta, \ldots, p_K^\alpha \tilde p_K^\beta).
-%\end{align*}
-
-As an example, consider the classification problem with three classes.
-We have three arboreal classifiers $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$ which correspond to star graphs centered respectively at classes $C_1, C_2, C_3$.
-The classifier
-\begin{align}
-\frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:bc1}
-\end{align}
-is Bayes covariant \emph{and} symmetric. A key result proved in [\cite{vsuch2016bayes}] is that it is a unique such classifier for $K=3$.
-
-\begin{thm} \label{thm:K3}
-	There exists a unique symmetric Bayes covariant coupling methods for $K=3$.
-\end{thm}
-
-Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$:
-\[
-\boldsymbol{E} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
-\]
-Note that here we use the plus symbol to denote the vector addition of vectors representing $K$-class probability distributions.
-This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.
-
-\subsection{Properties of coupling methods}
-
-The following table indicates which properties are enjoyed by each coupling method we described in this section.
-
-\begin{table}[!ht]
-\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
-&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
-\hline 
-\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
-&uniqueness &  yes & yes & yes & yes & yes & yes \\
-&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
-&canonicity & yes & no & yes & yes & no & yes \\
-&symmetry & yes & yes & yes & yes & no & yes \\
-& Bayes covariant & no & no & no & yes & yes & yes \\
-\hline
-\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
-&Hinton's minimality & ? & ?  & ++ & ?  & ? & +++ \\
-&lack of parameters & yes & yes & yes & yes & yes & yes \\
-& amounts to a linear system & no & yes & yes & yes & yes & yes\\
-& linear system of special form & no & no & yes & yes & yes & yes \\
-& iterative method & yes & yes & yes & no & not needed & not needed\\
-\hline
-\end{tabular}
-\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
-\label{tab:summaryCoupling}
-\end{table}
-
-\section{Experimental results.}
-
-The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
-
-\begin{itemize}
-\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
-\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
-\item[c)] If the answer to b) is negative, is it better to apply change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
-\end{itemize}
-
-These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.
-
-\subsection{Datasets}
-
-It is natural to consider the benchmark datasets used in previous evaluation of coupling methods [\cite{wu2004probability}].
-The authors considered altogether seven datasets with number of classes ranging from 3 to 26.
-For each dataset they extracted 40 pairs of training and testing datasets.
-Half of these were smaller (300 training samples and 500 testing samples) and the other half was larger (800 training samples and 1000 testing samples).
-In our experiments we use only the larger pairs.
-
-As a preliminary step we conducted analysis of linear separability of the datasets.
-We used ECOS solver in CVXR library to solve the underlying quadratic program.
-The results are reported in Table \ref{tab:sep}.
-
-\input{tab-sep.tex}
-
-We can infer that except for 'waveform' dataset, majority of binary problems are linearly separable.
-
-\subsection{Classification methodology}
-
-We have opted to use LDA as a binary classification tool.
-Its appeal is that it is applicable even for linearly separable datasets, thus obviating additional crossvalidation step incurred by methods that use regularization (e.g.
-penalized logistic regression or SVM).
-It usually provides results close to logistic regression [\cite{james2013introduction}].
-
-For preprocessing we first removed features that were constant across classes.
-Then we projected the data using PCA to the subspace for which corresponding singular values were at least $1/1000$.
-We used PCA without scaling or centering since the datasets' features were already normalized to interval $[-1,1]$.
-
-For training LDA we used MASS library in R. We implemented coupling methods in C++ using Eigen library. As arguments to the coupling methods we use log-odds, i.e. instead of $r_{ij}$ they expect
-$$
-\tilde r_{ij} = \log \biggl(\frac{1}{r_{ji}} - 1\biggr).
-$$
-The resulting matrix $\tilde{\boldsymbol{R}}$ is skew symmetric (with the convention of having zeroes on the diagonal).
-
-This parametrization allows for precise representation of extremely small probabilities which are sometimes produced by LDA.
-These small probabilities might be expected given that a large fraction of binary problems is linearly separable.
-
-Small probabilities generally have very little effect on the implementation of Bayes covariant methods which generally operate using log-odds.
-However small probabilities do affect both the method of Wu-Lin-Weng as well sa radial method, because then Assumption \ref{ass:1} fails to hold.
-
-%\begin{figure}[!ht]
-%	\includegraphics[width = 0.5\linewidth]{graph/dna-lda.pdf}
-%	\includegraphics[width = 0.5\linewidth]{graph/waveform-lda.pdf}
-%	\caption{Projections of three-class datasets using LDA Left: dna, right: waveform}
-%\end{figure}
-
-\subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets} \label{sec:exp1}
-
-The first experiment compares the performanc of three parameterless coupling methods
-\begin{itemize}
-\item method of Wu-Lin-Weng, which is widely used in software libraries, and thus can be viewed as an orthodox choice,
-\item normal coupling, which is a Bayes covariant method,
-\item radial coupling, which is not Bayes covariant.
-\end{itemize}
-
-Although previous evaluations of the latter two methods were done in [\cite{vsuch2016bayes}], they used phonetic data for which ground truth may be imprecise.
-
-\input{tab-multi.tex}
-
-From Table \ref{tab:multi} we can clearly see that Wu-Lin-Weng's method has the best performance.
-On some datasets it trounces normal coupling method by a wide margin.
-The edge over radial method is smaller, with the exception of usps dataset where its accuracy is higher by remarkable 30\%.
-
-\subsection{Experiment 2: Accuracy of Bayes covariant methods with parameters}
- \label{sec:exp2}
-
-In the previous experiment we established that the method of Wu-Lin-Weng provides leading performance. However in view of Theorem \ref{thm:K3} the method is not Bayes covariant.
-
-In this experiment we investigated whether we can (always) find  a Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method, if we allow it to have (a few) trainable parameters.
-Our experiment proceeds in five steps.
-
-First, we restrict our investigation to the case of three class datasets. This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask.
-
-As a second step, we consider whether the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$ (which do not have any parameters) could bridge the gap.
-The statistics are shown in Table \ref{tab:step2}.
-
-\input{tab-step2.tex}
-
-We can see that approximately half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
-Therefore we should extend search to Bayes covariant methods with trainable parameters.
-
-In the third step we define two parameter family of Bayes covariant coupling methods
-\begin{align}
-a_1 \boldsymbol{s}_1 \oplus a_2 \boldsymbol{s}_2 \oplus a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1 \label{eq:family}
-\end{align}
-Note that the parameter space of this family is not compact.
-In order to facilitate computations we opted to conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
-To further reduce computational burden we selected 1000 three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
-The results are shown in Figure \ref{fig:par-bc}.
-
-\begin{figure}[!ht]
-\includegraphics{graph/exp2-summary.pdf}
-\caption{Results of grid search for parametric Bayes covariant methods matching performance of Wu-Lin-Weng's method}
-\label{fig:par-bc}
-\end{figure}
-
-We can see that only in minority of cases we found a parametric method matching the performance of Wu-Lin-Weng's. This finding comes with caveat that we searched only in the simplex $a_i \geq 0$.
-
-Therefore as the final step in our investigation we looked whether a parametric Bayes covariant method in family \eqref{eq:family} for parameters \emph{outside} of this simplex could perform better.
-We conducted another search but this time
-\begin{itemize}
-	\item We searched within a much larger rectangle $D$ containing the simplex $a_i\geq 0$, which in this case is a triangle $T$.
-	\item We used Brier score as a smooth proxy for measuring the quality of multi-class classifier. This score is much smoother than 0-1 score which measures accuracy.
-\end{itemize}
-
-The results are shown in Figure \ref{fig:score}
-
-\begin{figure}[!ht]
-	\includegraphics{graph/exp2-detail.pdf}
-	\caption{Color map indicates the value of Brier score computed for an ensemble of coupling methods on the testing dataset.
-The vertices triangle indicate the arboreal coupling methods, and the black circle the location of the optimum.}
-	\label{fig:score}
-\end{figure}
-
-We can see that indeed the optimum over the rectangle lies outside of the simplex.
-Let us compare the resulting accuracy of the optima in $\Delta$ and $D$.
-The results are shown in Table \ref{tab:step5}.
-
-\input tab-step5.tex
-
-\subsection{Experiment 3: Effect of change of priors}  \label{sec:exp3}
-%\subsection{Wu-Lin-Weng's method}
-
-%\subsection{Linear kernel}
-
-%\begin{tabular}
-%\input{glm1-multi.tex}
-%\end{tabular}
-
-%Here is a citation \cite{chow:68}.
-
-% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references
-
-\acks{All acknowledgements go at the end of the paper before appendices and references.
-Moreover, you are required to declare funding (financial activities supporting the
-submitted work) and competing interests (related financial activities outside the submitted work).
-More information about this disclosure can be found on the JMLR website.}
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
-
-\appendix
 \section{}
@@
 {\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
-
-\vskip 0.2in 
-\bibliography{paper}
-
-\end{document}

### 2025-05-08 coupling.tex
Restructure paper into multiple files

--- 2025-05-07 paper.tex
@@
-\documentclass[twoside,11pt]{article}
-
-\usepackage{blindtext}
-
-% Any additional packages needed should be included after jmlr2e.
-% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
-% and defines many common macros, such as 'proof' and 'example'.
-%
-% It also sets the bibliographystyle to plainnat; for more information on
-% natbib citation styles, see the natbib documentation, a copy of which
-% is archived at http://www.jmlr.org/format/natbib.pdf
-
-% Available options for package jmlr2e are:
-%
-%   - abbrvbib : use abbrvnat for the bibliography style
-%   - nohyperref : do not load the hyperref package
-%   - preprint : remove JMLR specific information from the template,
-%         useful for example for posting to preprint servers.
-%
-% Example of using the package with custom options:
-%
-% \usepackage[abbrvbib, preprint]{jmlr2e}
-
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{jmlr2e}
-
-\usepackage{multirow}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{rotating}
-\usepackage{tikz-cd}
-\usepackage[utf8]{inputenc} % Enable UTF-8 encoding
-\usepackage[T1]{fontenc}
-\usepackage{textgreek}
-
-\newtheorem{prop}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{assumption}{Assumption}
-
-% Definitions of handy macros can go here
-
-\newcommand{\dataset}{{\cal D}}
-\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-\DeclareMathOperator*{\divm}{div}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
-
-\usepackage{lastpage}
-\jmlrheading{23}{2025}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Probabilistic OVO}{Probabilistic OVO}
-\firstpageno{1}
-
-\begin{document}
-
-\title{On change of priors in one-vs-one classification methods}
-
-\author{\name Ondrej Šuch \email ondrejs@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       \AND
-       \name Peter Novotný \email peter.novotny@uniza.sk \\
-       \addr Fakulta informatiky a riadenia\\
-       Žilinská Univerzita v Žiline\\
-       Žilina, 010 26, Slovakia
-       \AND
-       \name Ali Haidar \email haidar@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       }
-
-\editor{My editor}
-
-\maketitle
-
-\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-\blindtext
-\end{abstract}
-
-\begin{keywords}
-  keyword one, keyword two, keyword three
-\end{keywords}
-
-\section{Introduction}
-
-%\blindmathpaper
-
-Multi-class classification is considered to be a more challenging problem than binary classification.
-A natural approach to multi-class classification is to reduce it to a series of binary classification problems and deduce the multi-class decision by aggregating decisions for the binary problems.
-
-One popular method belonging to  this paradigm uses probabilistic modelling for one-vs-one series of binary problems.
-Notably, it is used as the basis for multi-class classification models using support vector machines (SVM) in LIBSVM library.
-However one can use the approach more generally,  because it can be applied to any probabilistic binary classification method.
-
-A key step in probabilistic one-vs-one modelling is the aggregation of results of individual binary classifiers - so-called \emph{coupling method}.
-The most commonly used coupling method is that proposed by Wu-Lin-Weng.
-As noted in [\cite{dohau}], the method is one of several non-canonical decisions used in multi-class SVM modelling.
-The goal of this paper is to compare its behavior with canonical methods.
-
-\section{Theoretical basis of coupling methods}
-
-Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature space $X$.
-In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class.
-Given $x$ in $X$ we aim to find the probability that $x$ belongs to $i$-th class.
-
-\subsection{One-vs-on classification}
-
-An exact solution to a classification problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.
-
-\begin{assumption} \label{ass:1}
-For all $x$ in the feature space we have $d_i(x) > 0$.
-\end{assumption}
-Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.
-
-The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
-\begin{align}
- p^\Pi_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
-\end{align}
-
-Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of classes.
-Assuming prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier predicts the probability of $i$-th class as
-
-\begin{align}
-	p_{ij}^\Pi(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
-\end{align}
-
-Knowledge of vector $\boldsymbol{p}^\Pi(x)$ is equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
-\begin{align}
-p_{ij}^\Pi(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
-\end{align}
-
-Conversely, it is easy to show that  the system of equations \eqref{eq:bt1} has a unique solution.
-
-\begin{prop}[Fundamental theorem of one-vs-one classification]
-	 \label{prop:binary2multi}
-	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
-\end{prop}
-\begin{proof}
-	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denotes the odds of $C_i$ to $C_j$:
-	\begin{align}
-		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j}
-	\end{align}
-
-	From \eqref{eq:bt1} we can deduce the odds of classes $C_j$ to $C_i$ as
-	\begin{align}
-	\alpha_{ij}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
-	\end{align}
-	Knowing the odds of $C_2$ to $C_1$, $C_3$ to $C_2$ up to $C_{K}$ to $C_{K-1}$ together with the requirement that probabilities sum to one uniquely determines the whole vector $\boldsymbol{p}^\Pi(x)$.
-\end{proof}
-%\begin{proof}
-%Indeed, we have 
-%\begin{align*}
-%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
-%\end{align*}
-%\end{proof}
-
-\subsection{Coupling methods}
-
-In practice one does not have know true probability distributions and hence cannot construct Bayes classifies.
-However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$.
-The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$.
-One does it by finding an approximate solution of the system of equations
-%\begin{align}
-%
-%\end{align}
-%
-%
-%Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$.
-Let us denote the $r_{ij}(x)$ the output of Bayes (binary) classifier for $x$ in $X$ yielding the probability $p(x \in C_i \mid x\in C_i \cup C_j )$.
-Then we have
-%\begin{equation}
-%r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
-%\end{equation}
-%
-%
-%The system of equations is called Bradley--Terry equations.
-The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations.
-The theoretical basis for one-vs-one classification framework is provided by the following result.
-%
-%
-%
-%Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$.
-A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
-\begin{equation}
-	{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
-\end{equation}
-
-% One should note that 
-%\begin{itemize}
-%\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
-%\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
-%\end{itemize}
-
-Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
-The system is usually inconsistent and additional assumptions are needed to construct an estimator.
-A method to solve Bradley-Terry equations is called a \emph{coupling method}.
-Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
-Schematically, classification using coupling method $\boldsymbol{v}$ proceeds as indicated in Figure \ref{fig:coupling}.
-
-\begin{figure}[!h]
-	\centering
-	\begin{tikzcd}[column sep=3cm]
-		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
-		\arrow{d}{coupling} \\
-		 & \boldsymbol{v}(\boldsymbol{R}(x)) 
-	\end{tikzcd}
-	\caption{Multi-class classification using a coupling method $\boldsymbol{v}$}
-	\label{fig:coupling}
-\end{figure}
-
-\subsection{Exact desiderata on coupling method} \label{sec:des:exact}
-
-Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
-this section
- we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
-
-%\begin{itemize}
-%\item a coupling method should should always provide a unique solution, at least when all $r_{ij}>0$,
-%\item Bradley-Terry consistency,
-%\item canonicity,
-%\item symmetry,
-%\item Bayes covariance,
-%
-%\item good accuracy on benchmark tasks,
-%\item lack of parameters, or at least having a small number of parameters,
-%\item Hinton's minimality,
-%\item simplicity of computation.
-%\end{itemize}
-
-\emph{Unique solution} refers to the fact that the procedure to compute a multi-class probabilistic prediction always converges to a unique solution.
-One way to satisfy this condition would be that it amounts to a linear system of equations in $K$ variables, and the matrix of the system would be invertible.
-Another example would be when the procedure amounts to finding the minimum of a strongly convex function.
-
-\emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
-The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
-satisfies \eqref{eq:bt1}.
-
-\emph{Canonicity} refers to requirement that the method should be natural.
-Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
-Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
-
-Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
-For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical [\cite{shannon1948mathematical,selten1998axiomatic}].
-
-\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions.
-The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by
-\begin{equation}
-	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
-\end{equation}
-We say that a coupling method $V$ is \emph{symmetric} if 
-\begin{align}
-		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
-\end{align}
-
-\emph{Bayes covariance} is a notion introduced in  [\cite{vsuch2016bayes}].
-It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
-Any Bayes classifier, whether binary or multiclass changes its prediction when the priors change.
-Let us describe the process.
-Suppose we change priors from $\Pi = (P_1, \ldots, P_k)$ to $\Pi'= (P'_1, \ldots, P'_K)$.
-Then the prediction of Bayes classifiers changes from $\boldsymbol{p}^\Pi= (p_1, \ldots, p_K)$ to the vector
-\begin{align}
-\boldsymbol{p}^{\Pi'} \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr). \label{eq:changePrior}
-\end{align}
-
-When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
-If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.
-
-Let us make this explicit.
-Let $\boldsymbol{v}$ be a coupling method.
-Denote by  $\pi$ the change of priors $\pi:\Pi \rightarrow \Pi'$.
-If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_2^{ij}(D)$ by requiring
-$$
-\pi_2^{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
-$$
-We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_2^{ij}(r_{ij})$.
-The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents the effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
-
-On the other hand we can apply \eqref{eq:changePrior} after coupling. Say we have a distribution on $K$ classes
-\begin{align}
-D \propto (p_1, \ldots, p_K)
-\end{align}
-then we define $D^\pi$ by requiring 
-\begin{align}
-D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr).
-\end{align}
-We now say that a method if Bayes covariant if
-\begin{align}
-\boldsymbol{v}(\boldsymbol{R}^\pi)=	\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi,
-\end{align}
-for any matrix $\boldsymbol{R}$ with $r_{ij}> 0$.
-
-%Let $\boldsymbol{R}^\pi$ be the matrix of pairwise predictions when we apply \eqref{eq:changePrior} to each binary classifier.
-%For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
-%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzcd}
-%	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
-%	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
-%\end{tikzcd}
-%\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
-%\label{fig:bc}
-%\end{figure}
-
-\subsection{Inexact desiderata for coupling methods}
-
-\label{sec:des:inexact}
-
-In this section we describe several concepts that lack strict mathematical delineation, but may still be important to consider.
-
-\emph{Good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
-This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform.
-However a good coupling method should perform robustly across a variety of datasets.
-A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
-At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
-
-\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtain unbiased estimates of the parameters of the coupling method.
-This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters.
-For example, this is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
-
-\emph{Simplicity of computation}  may refer to the computational requirement for inference.
-With the dramatic increase of edge computing devices, such as smartphones, a simple, fast, energy-efficient algorithm may be preferable to a better performing one which would require more computational resources.
-
-Let us finally mention \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction [\cite[p.~467]{hastie1998classification}].
-Suppose we are classifying objects from CIFAR-10 dataset.
-If the true class is  a ``dog'', why should we care what is the output of the classifier distinguishing ``airplanes'' from ``ships''?
-The binary classifier is trained only on airplanes and ships, and has never seen a dog.
-One may thus prefer a classifier which somehow suppresses noisy output of (seemingly) irrelevant classifiers.
-
-%The first that the five conditions have a clear mathematical definition, whereas the rest are not exact.
-For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.
-
 \section{Examples of coupling methods} \label{sec:coupling}
@@
 	\item[c)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant,
-	\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
+	\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Proposition \ref{lem:transitivity}).
 \end{itemize}
@@
 \end{table}
-
-\section{Experimental results.}
-
-The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
-
-\begin{itemize}
-\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
-\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
-\item[c)] If the answer to b) is negative, is it better to apply change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
-\end{itemize}
-
-These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.
-
-\subsection{Datasets}
-
-It is natural to consider the benchmark datasets used in previous evaluation of coupling methods [\cite{wu2004probability}].
-The authors considered altogether seven datasets with number of classes ranging from 3 to 26.
-For each dataset they extracted 40 pairs of training and testing datasets.
-Half of these were smaller (300 training samples and 500 testing samples) and the other half was larger (800 training samples and 1000 testing samples).
-In our experiments we use only the larger pairs.
-
-As a preliminary step we conducted analysis of linear separability of the datasets.
-We used ECOS solver in CVXR library to solve the underlying quadratic program.
-The results are reported in Table \ref{tab:sep}.
-
-\input{tab-sep.tex}
-
-We can infer that except for 'waveform' dataset, majority of binary problems are linearly separable.
-
-\subsection{Classification methodology}
-
-We have opted to use LDA as a binary classification tool.
-Its appeal is that it is applicable even for linearly separable datasets, thus obviating additional crossvalidation step incurred by methods that use regularization (e.g.
-penalized logistic regression or SVM).
-It usually provides results close to logistic regression [\cite{james2013introduction}].
-
-For preprocessing we first removed features that were constant across classes.
-Then we projected the data using PCA to the subspace for which corresponding singular values were at least $1/1000$.
-We used PCA without scaling or centering since the datasets' features were already normalized to interval $[-1,1]$.
-
-For training LDA we used MASS library in R. We implemented coupling methods in C++ using Eigen library. As arguments to the coupling methods we use log-odds, i.e. instead of $r_{ij}$ they expect
-$$
-\tilde r_{ij} = \log \biggl(\frac{1}{r_{ji}} - 1\biggr).
-$$
-The resulting matrix $\tilde{\boldsymbol{R}}$ is skew symmetric (with the convention of having zeroes on the diagonal).
-
-This parametrization allows for precise representation of extremely small probabilities which are sometimes produced by LDA.
-These small probabilities might be expected given that a large fraction of binary problems is linearly separable.
-
-Small probabilities generally have very little effect on the implementation of Bayes covariant methods which generally operate using log-odds.
-However small probabilities do affect both the method of Wu-Lin-Weng as well sa radial method, because then Assumption \ref{ass:1} fails to hold.
-
-%\begin{figure}[!ht]
-%	\includegraphics[width = 0.5\linewidth]{graph/dna-lda.pdf}
-%	\includegraphics[width = 0.5\linewidth]{graph/waveform-lda.pdf}
-%	\caption{Projections of three-class datasets using LDA Left: dna, right: waveform}
-%\end{figure}
-
-\subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets} \label{sec:exp1}
-
-The first experiment compares the performanc of three parameterless coupling methods
-\begin{itemize}
-\item method of Wu-Lin-Weng, which is widely used in software libraries, and thus can be viewed as an orthodox choice,
-\item normal coupling, which is a Bayes covariant method,
-\item radial coupling, which is not Bayes covariant.
-\end{itemize}
-
-Although previous evaluations of the latter two methods were done in [\cite{vsuch2016bayes}], they used phonetic data for which ground truth may be imprecise.
-
-\input{tab-multi.tex}
-
-From Table \ref{tab:multi} we can clearly see that Wu-Lin-Weng's method has the best performance.
-On some datasets it trounces normal coupling method by a wide margin.
-The edge over radial method is smaller, with the exception of usps dataset where its accuracy is higher by remarkable 30\%.
-
-\subsection{Experiment 2: Accuracy of Bayes covariant methods with parameters}
- \label{sec:exp2}
-
-In the previous experiment we established that the method of Wu-Lin-Weng provides leading performance. However in view of Theorem \ref{thm:K3} the method is not Bayes covariant.
-
-In this experiment we investigated whether we can (always) find  a Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method, if we allow it to have (a few) trainable parameters.
-Our experiment proceeds in five steps.
-
-First, we restrict our investigation to the case of three class datasets. This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask.
-
-As a second step, we consider whether the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$ (which do not have any parameters) could bridge the gap.
-The statistics are shown in Table \ref{tab:step2}.
-
-\input{tab-step2.tex}
-
-We can see that approximately half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
-Therefore we should extend search to Bayes covariant methods with trainable parameters.
-
-In the third step we define two parameter family of Bayes covariant coupling methods
-\begin{align}
-a_1 \boldsymbol{s}_1 \oplus a_2 \boldsymbol{s}_2 \oplus a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1 \label{eq:family}
-\end{align}
-Note that the parameter space of this family is not compact.
-In order to facilitate computations we opted to conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
-To further reduce computational burden we selected 1000 three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
-The results are shown in Figure \ref{fig:par-bc}.
-
-\begin{figure}[!ht]
-\includegraphics{graphs/exp2-summary.pdf}
-\caption{Results of grid search for parametric Bayes covariant methods matching performance of Wu-Lin-Weng's method}
-\label{fig:par-bc}
-\end{figure}
-
-We can see that only in minority of cases we found a parametric method matching the performance of Wu-Lin-Weng's. This finding comes with caveat that we searched only in the simplex $a_i \geq 0$.
-
-Therefore as the final step in our investigation we looked whether a parametric Bayes covariant method in family \eqref{eq:family} for parameters \emph{outside} of this simplex could perform better.
-We conducted another search but this time
-\begin{itemize}
-	\item We searched within a much larger rectangle $D$ containing the simplex $a_i\geq 0$, which in this case is a triangle $T$.
-	\item We used Brier score as a smooth proxy for measuring the quality of multi-class classifier. This score is much smoother than 0-1 score which measures accuracy.
-\end{itemize}
-
-The results are shown in Figure \ref{fig:score}
-
-\begin{figure}[!ht]
-	\includegraphics{graphs/exp2-detail.pdf}
-	\caption{Color map indicates the value of Brier score computed for an ensemble of coupling methods on the testing dataset.
-The vertices triangle indicate the arboreal coupling methods, and the black circle the location of the optimum.}
-	\label{fig:score}
-\end{figure}
-
-We can see that indeed the optimum over the rectangle lies outside of the simplex.
-Let us compare the resulting accuracy of the optima in $\Delta$ and $D$.
-The results are shown in Table \ref{tab:step5}.
-
-\input tab-step5.tex
-
-\subsection{Experiment 3: Effect of change of priors}  \label{sec:exp3}
-%\subsection{Wu-Lin-Weng's method}
-
-%\subsection{Linear kernel}
-
-%\begin{tabular}
-%\input{glm1-multi.tex}
-%\end{tabular}
-
-%Here is a citation \cite{chow:68}.
-
-% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references
-
-\acks{All acknowledgements go at the end of the paper before appendices and references.
-Moreover, you are required to declare funding (financial activities supporting the
-submitted work) and competing interests (related financial activities outside the submitted work).
-More information about this disclosure can be found on the JMLR website.}
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
-
-\appendix
-\section{}
-\label{app:explicit}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we provide explicit predictions of coupling methods used in the paper.
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\section{}
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
-
-\vskip 0.2in 
-\bibliography{paper}
-
-\end{document}

### 2025-05-08 experiment.tex
Restructure paper into multiple files

--- 2025-04-24 paper.tex
@@
-\documentclass[twoside,11pt]{article}
-
-\usepackage{blindtext}
-
-% Any additional packages needed should be included after jmlr2e.
-% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
-% and defines many common macros, such as 'proof' and 'example'.
-%
-% It also sets the bibliographystyle to plainnat; for more information on
-% natbib citation styles, see the natbib documentation, a copy of which
-% is archived at http://www.jmlr.org/format/natbib.pdf
-
-% Available options for package jmlr2e are:
-%
-%   - abbrvbib : use abbrvnat for the bibliography style
-%   - nohyperref : do not load the hyperref package
-%   - preprint : remove JMLR specific information from the template,
-%         useful for example for posting to preprint servers.
-%
-% Example of using the package with custom options:
-%
-% \usepackage[abbrvbib, preprint]{jmlr2e}
-
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{jmlr2e}
-
-\usepackage{multirow}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{rotating}
-\usepackage{tikz-cd}
-\usepackage[utf8]{inputenc} % Enable UTF-8 encoding
-\usepackage[T1]{fontenc}
-\usepackage{textgreek}
-
-\newtheorem{prop}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{assumption}{Assumption}
-
-% Definitions of handy macros can go here
-
-\newcommand{\dataset}{{\cal D}}
-\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-\DeclareMathOperator*{\divm}{div}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
-
-\usepackage{lastpage}
-\jmlrheading{23}{2025}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Probabilistic OVO}{Probabilistic OVO}
-\firstpageno{1}
-
-\begin{document}
-
-\title{On probabilistic one-vs-one classification}
-
-\author{\name Ondrej Šuch \email ondrejs@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       \AND
-       \name Peter Novotný \email peter.novotny@uniza.sk \\
-       \addr Fakulta informatiky a riadenia\\
-       Žilinská Univerzita v Žiline\\
-       Žilina, 010 26, Slovakia
-       \AND
-       \name Ali Haidar \email haidar@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       }
-
-\editor{My editor}
-
-\maketitle
-
-\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-\blindtext
-\end{abstract}
-
-\begin{keywords}
-  keyword one, keyword two, keyword three
-\end{keywords}
-
-\section{Introduction}
-
-%\blindmathpaper
-
-Multi-class classification is considered to be a more challenging problem than binary classification.
-A natural approach to multi-class classification is to reduce it to a series of binary classification problems and deduce the multi-class decision by aggregating decisions for the binary problems.
-
-One popular method belonging to  this paradigm uses probabilistic modelling for one-vs-one series of binary problems.
-Notably, it is used as the basis for multi-class classification models using support vector machines (SVM) in LIBSVM library.
-However one can use the approach more generally,  because it can be applied to any probabilistic binary classification method.
-
-A key step in probabilistic one-vs-one modelling is the aggregation of results of individual binary classifiers - so-called \emph{coupling method}.
-The most commonly used coupling method is that proposed by Wu-Lin-Weng.
-As noted in [\cite{dohau}], the method is one of several non-canonical decisions used in multi-class SVM modelling.
-The goal of this paper is to compare its behavior with canonical methods.
-
-\section{Theoretical basis of coupling methods}
-
-Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature space $X$.
-In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class.
-Given $x$ in $X$ we aim to find the probability that $x$ belongs to $i$-th class.
-
-\subsection{Bayes classifier}
-
-An exact solution to this problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.
-
-\begin{assumption} \label{ass:1}
- For all $x$ in the feature space we have $d_i(x) > 0$.
-\end{assumption}
-Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.
-
-The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
-\begin{align}
- p^\Pi_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
-\end{align}
-
-Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of classes.
-Assuming prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier predicts the probability of $i$-th class as
-
-\begin{align}
-	p_{ij}^\Pi(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
-\end{align}
-
-Knowledge of vector $\boldsymbol{p}^\Pi(x)$ is  equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
-\begin{align}
-p_{ij}^\Pi(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
-\end{align}
-
-Conversely, it is easy to show that  the system of equations \eqref{eq:bt1} has a unique solution.
-
-\begin{prop} \label{prop:binary2multi}
-The system of  equations \eqref{eq:bt1} in unknowns $p_i^\Pi(x)$ has a unique solution which is the multi-class Bayes classifier.
-\end{prop}
-%\begin{proof}
-%Indeed, we have 
-%\begin{align*}
-%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
-%\end{align*}
-%\end{proof}
-
-\subsection{One-vs-one classification }
-
-In practice one does not have know true probability distributions and hence cannot construct Bayes classifier.
-However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$.
-The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$.
-One does it by finding an approximate solution of the system of equations
-%\begin{align}
-%
-%\end{align}
-%
-%
-%Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$.
-Let us denote the $r_{ij}(x)$ the output of Bayes (binary) classifier for $x$ in $X$ yielding the probability $p(x \in C_i \mid x\in C_i \cup C_j )$.
-Then we have
-%\begin{equation}
-%r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
-%\end{equation}
-%
-%
-%The system of equations is called Bradley--Terry equations.
-The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations.
-The theoretical basis for one-vs-one classification framework is provided by the following result.
-%
-%
-%
-%Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$.
-A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
-\begin{equation}
-	{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
-\end{equation}
-
-% One should note that 
-%\begin{itemize}
-%\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
-%\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
-%\end{itemize}
-
-Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
-The system is usually inconsistent and additional assumptions are needed.
-A method to solve Bradley-Terry equations is called a coupling method.
-Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
-Schematically, classification using coupling method $\boldsymbol{v}$ proceeds as indicated in Figure \ref{fig:coupling}.
-
-\begin{figure}[!h]
-	\centering
-	\begin{tikzcd}[column sep=3cm]
-		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
-		\arrow{d}{coupling} \\
-		 & \boldsymbol{v}(\boldsymbol{R}(x)) 
-	\end{tikzcd}
-	\caption{Multi-class classification using a coupling method $\boldsymbol{v}$}
-	\label{fig:coupling}
-\end{figure}
-
-\subsection{Exact desiderata on coupling method} \label{sec:des:exact}
-
-Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
-this section
- we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
-
-%\begin{itemize}
-%\item a coupling method should should always provide a unique solution, at least when all $r_{ij}>0$,
-%\item Bradley-Terry consistency,
-%\item canonicity,
-%\item symmetry,
-%\item Bayes covariance,
-%
-%\item good accuracy on benchmark tasks,
-%\item lack of parameters, or at least having a small number of parameters,
-%\item Hinton's minimality,
-%\item simplicity of computation.
-%\end{itemize}
-
-\emph{Unique solution} refers to the fact that the procedure to compute a multi-class probabilistic prediction always converges to a unique solution.
-One way to satisfy this condition would be that it amounts to a linear system of equations in $K$ variables, and the matrix of the system would be invertible.
-Another example would be when the procedure amounts to finding the minimum of a strongly convex function.
-
-\emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
-The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
-satisfies \eqref{eq:bt1}.
-
-\emph{Canonicity} refers to requirement that the method should be natural.
-Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
-Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
-
-Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
-For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical [\cite{shannon1948mathematical,selten1998axiomatic}].
-
-\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions.
-The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by
-\begin{equation}
-	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
-\end{equation}
-We say that a coupling method $V$ is \emph{symmetric} if 
-\begin{align}
-		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
-\end{align}
-
-\emph{Bayes covariance} is a notion introduced in  [\cite{vsuch2016bayes}].
-It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
-Any Bayes classifier, whether binary or multiclass changes its prediction when the priors change.
-Let us describe the process.
-Suppose we change priors from $\Pi = (P_1, \ldots, P_k)$ to $\Pi'= (P'_1, \ldots, P'_K)$.
-Then the prediction of Bayes classifiers changes from $\boldsymbol{p}^\Pi= (p_1, \ldots, p_K)$ to the vector
-\begin{align}
-\boldsymbol{p}^{\Pi'} \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr). \label{eq:changePrior}
-\end{align}
-
-When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
-If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.
-
-Let us make this explicit.
-Let $\boldsymbol{v}$ be a coupling method.
-Denote by  $\pi$ the change of priors $\pi:\Pi \rightarrow \Pi'$.
-If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_2^{ij}(D)$ by requiring
-$$
-\pi_2^{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
-$$
-We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_2^{ij}(r_{ij})$.
-The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents the effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
-
-On the other hand we can apply \eqref{eq:changePrior} after coupling. Say we have a distribution on $K$ classes
-\begin{align}
-D \propto (p_1, \ldots, p_K)
-\end{align}
-then we define $D^\pi$ by requiring 
-\begin{align}
-D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr).
-\end{align}
-We now say that a method if Bayes covariant if
-\begin{align}
-\boldsymbol{v}(\boldsymbol{R}^\pi)=	\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi,
-\end{align}
-for any matrix $\boldsymbol{R}$ with $r_{ij}> 0$.
-
-%Let $\boldsymbol{R}^\pi$ be the matrix of pairwise predictions when we apply \eqref{eq:changePrior} to each binary classifier.
-%For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
-%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzcd}
-%	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
-%	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
-%\end{tikzcd}
-%\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
-%\label{fig:bc}
-%\end{figure}
-
-\subsection{Inexact desiderata for coupling methods}
-
-\label{sec:des:inexact}
-
-In this section we describe several concepts that lack strict mathematical delineation, but may still be important to consider.
-
-\emph{Good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
-This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform.
-However a good coupling method should perform robustly across a variety of datasets.
-A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
-At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
-
-\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtain unbiased estimates of the parameters of the coupling method.
-This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters.
-For example, this is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
-
-\emph{Simplicity of computation}  may refer to the computational requirement for inference.
-With the dramatic increase of edge computing devices, such as smartphones, a simple, fast, energy-efficient algorithm may be preferable to a better performing one which would require more computational resources.
-
-Let us finally mention \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction [\cite[p.~467]{hastie1998classification}].
-Suppose we are classifying objects from CIFAR-10 dataset.
-If the true class is  a ``dog'', why should we care what is the output of the classifier distinguishing ``airplanes'' from ``ships''?
-The binary classifier is trained only on airplanes and ships, and has never seen a dog.
-One may thus prefer a classifier which somehow suppresses noisy output of (seemingly) irrelevant classifiers.
-
-%The first that the five conditions have a clear mathematical definition, whereas the rest are not exact.
-For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.
-
-\section{Examples of coupling methods} \label{sec:coupling}
-
-There is a plethora of methods available for coupling. In this section we describe four major classes.
-
-\subsection{Methods aiming to minimize binary divergence}
-
-A multi-class estimate $\hat{\boldsymbol{p}}$ obtained by a coupling method implies via \eqref{eq:bt1} probability distributions on each pair of classes:
-\begin{align*}
-	\hat D_{ij}^\textrm{multi}= \biggl(\frac{\hat{p_i}}{\hat p_i + \hat p_j},\frac{\hat{p_j}}{\hat p_i + \hat p_j}\biggr)	
-\end{align*}
-On the other hand, binary classifiers provide another distribution for each pair of  classes, namely
-\begin{align*}
-\hat D_{ij}^\textrm{binary} = (\hat r_{ij}, \hat r_{ji}).
-\end{align*}
-
-A natural way to find  $\hat{\boldsymbol{p}}$ is thus to minimize a functional incorporating divergence measures between these distributions
-\begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
-\end{align*}
-
-A notable example which uses this principle is the coupling method introduced in [\cite{hastie1998classification}]. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
-\begin{align*}
-	\divm\nolimits_\textrm{KL} (\boldsymbol{p}, \boldsymbol{q})= \sum p_i \log (p_i/ q_i)
-\end{align*}
-
-Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
-In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score [\cite{gneiting2007strictly, buja2005loss}].
-
-For instance, a popular alternative is divergence arising from the quadratic  score [\cite{gneiting2007strictly}] (also known as Brier score [\cite{brier1950verification}]).
-This divergence takes the form
-$$
-\divm\nolimits_\textrm{quad} (\boldsymbol{p}, \boldsymbol{q})= \sum (p_i - q_i)^2.
-$$
-Unlike Kullback-Leibler divergence, the penalty for incorrect prediction with arbitrarily low probability is bounded (by one).
-This quadratic score is the basis of the popular Wu-Lin-Weng's method [\cite{wu2004probability}].
-
-Their method uses an additional trick, which we term \emph{self-referentiality}.
-In the method of Hastie and Tibshirani, $w_{ij}$ are constants derived from observed class frequencies.
-However, we could use weights $w_{ij}$ that increase when the predicted probability of either class $i$ or $j$ is high.
-A reasonable choice would be for instance $w_{ij}= p_i + p_j$.
-In the case of quadratic score, it is more convenient to use weights $w_{ij} = (p_i + p_j)^2$ because then the resulting optimization problem is just minimization of a quadratic form
-\begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{i,j} (r_{ij}p_j - r_{ji}p_i)^2.
-\end{align*}
-
-We note that the method is symmetric.
-The choice of quadratic scoring rule can also be viewed as canonical in view of axiomatic characterization given in  [\cite{selten1998axiomatic}].
-However the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary.
-Thus we do not view Wu-Lin-Weng's method as canonical.
-
-\subsection{Arboreal methods}
-
-System of equations \eqref{eq:bt2} is overdetermined because there are $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.
-Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns.
-This principle underlies arboreal coupling methods.
-
-An arboreal coupling method ignores all but $K-1$ of the pairwise predictions.
-A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes 1 and 3.
-The two equations form \eqref{eq:bt2} together with the requirement that the prediction probabilities should sum to 1 yield the following system of equations
-\begin{equation}
-	\begin{split}
-		\frac{\hat p_1}{\hat p_1 + \hat p_2} &= {r}_{12}\\
-		\frac{\hat p_2}{\hat p_2 + \hat p_3} &= {r}_{23}\\
-		\hat p_1 + \hat p_2 + \hat p_3 &= 1
-	\end{split}
-	\label{eq:arb1}
-\end{equation}
-
-For $K=3$, there are three different arboreal coupling methods, which we shall call $\boldsymbol{s}_1$, $\boldsymbol{s}_2$, $\boldsymbol{s}_3$, where the system \eqref{eq:arb1} represents the coupling method $\boldsymbol{s}_2$.
-
-In order to obtain a regular system of equations for  larger values of $K$ , the resulting classifiers must represent a connected tree within the complete graph on all classes.
-Any arboreal method is non-canonical, because there is no natural way to choose a tree in a complete graph.
-
-\subsection{Methods emphasizing Hinton's minimality}
-
-A variant on arboreal methods is the following oracle method which we shall call Hinton's oracle.
-It  assumes it has the access to the ground truth $y = C_t$.
-It outputs probabilities by solving only the equations
-$$
-\frac{\hat p_t}{\hat p_t + \hat p_j} = {r}_{tj},\quad \textrm{for }j\not = t,
-$$
-together the  with total sum equation
-$$
-\sum_{i=1}^K  \hat p_i = 1.
-$$
-
-For any sample, its result is identical to the arboreal method where the underlying tree forms a star.
-This method is clearly the optimal one with respect to Hinton's minimality criterion, because it ignores the output of any classifier not trained on the true class.
-It is not a true classification method, however, because it ``peeks'' at the label.
-Its main utility is to provide a way to benchmark other methods with respect to Hinton's minimality.
-
-In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
-Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
-The predictions will generally span the vector space $R^K$.
-In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $\boldsymbol{s}_i(x)$.
-Let us now define \emph{radial} coupling method.
-The  method requires that for the  weights we could in fact use the components of $\boldsymbol{p}$ i.e.
-\begin{equation}
-	\begin{split}
-	\hat {\boldsymbol{p}} &= \hat p_1 \boldsymbol{s}_1(x) + \ldots + \hat p_K \boldsymbol{s}_K(x)\\
-	1 &= \hat p_1 + \ldots + \hat p_K
-	\end{split}
-	 \label{eq:radial}
-\end{equation}
-%
-The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${{T}}_i$.
-
-\subsection{Bayes covariant methods}
-
-There are many Bayes covariant methods. First examples are provided by arboreal coupling methods.
-
-\begin{prop}
-Any arboreal method $\boldsymbol{t}$ is Bayes covariant.
-\end{prop}
-\begin{proof}
-We start by defining property $BC_{ij}$ (short for Bayes covariant when restricted to classes $i$ and $j$) of a coupling method.
-A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
-
-Let us list some easy to verify properties of this concept:
-
-\begin{itemize}
-\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$,
-\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant,
-\item[c)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant,
-\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
-\end{itemize}
-
-An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$.
-It follows using from b) and d) that the method is Bayes covariant.
-
-%	
-%	
-%Let $\pi$ be a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $(P'_1, \ldots, P'_K)$.
-We need to verify $\boldsymbol{v}(\boldsymbol{R}^\pi) =\bigl( \boldsymbol{v}(\boldsymbol{R})\bigr)$ for any pairwise matrix $\boldsymbol{R}$.
-|We will rephrase this in an equivalent way.
-Let
-%\begin{align}
-%	\begin{split}
-%	\boldsymbol{v}(\boldsymbol{R}^\pi) &= (v'_1, \ldots, v'_K) \\
-%	\boldsymbol{v}(\boldsymbol{R}) &= (v_1, \ldots, v_K)
-%	\end{split}
-%\end{align}
-%Suppose $\pi$ is a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. If the prediction given $\Pi$ is $(t_1, \ldots, t_K)$ then we need to prove that
-%\begin{align*}
-%\boldsymbol{t}(R^\pi) = \bigl(t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}\bigr)
-%\end{align*}
-%	
-%	We can proceed by induction.
-The statement is clear when $K=2$.
-Suppose the proposition is true for an integers $<K$ and we are given a spanning tree $T$ on $K$ vertices.
-Any tree has a vertex of degree one.
-We may assume that in the case of $T$ it is the vertex corresponding to $C_1$ and the unique edge incident to $C_1$ is $C_1C_2$.
-%	
-%	 Denote by $\boldsymbol{t}$ the prediction corresponding to $T$ and by $\boldsymbol{t}'$ the prediction corresponding to the subgraph without the vertex $C_1$. Let us write 
-%	\begin{align*}
-%	\boldsymbol{t}(x) &= (t_1, t_2, \ldots, t_K) \\
-%	\boldsymbol{t'}(x) &= ( t'_2, \ldots, t'_K) 
-%\end{align*}
-%These vectors are related as follows:
-%\begin{align}
-%\begin{split}
-%\frac{t_1}{t_1+t_2} &= r_{12} \\
-%(t_2, \ldots, t_K) &\propto (t'_2, \ldots, t'_{K})
-%\end{split} \label{eq:ind1}
-%\end{align}
-%
-%Now consider the effect of change of priors $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. Applying \eqref{eq:changePrior} to the multi-class prediction yields a vector 
-%$$
-%\boldsymbol{t}^{\Pi\rightarrow \Pi'} \propto (t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}).
-%$$
-%Now consider what happens when we apply \eqref{eq:changePrior} before coupling.
-By induction assumption the method $\boldsymbol{t}'$ is Bayes covariant and thus applying coupling \emph{after} change of priors yields
-%$$
-%\boldsymbol{t}'^{\Pi\rightarrow \Pi'} \propto (t_2 \frac{P'_2}{P_2}, \ldots, t_K \frac{P'_K}{P_K})
-%$$
-
-\end{proof}
-
-Given several Bayes covariant methods one can form  their ``linear combination'' - an ensemble which is also Bayes covariant. Let us make it explicit.
-
-Suppose real numbers $\alpha_1, \ldots,\alpha_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
-We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
-\begin{align*}
- 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_M \boldsymbol{v}_M\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(x),
-\end{align*}
-where the symbol $\odot$ denotes componentwise multiplication, and exponentials are computed component-wise. With this definition we can state the following result.
-
-\begin{prop}
-Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
-\end{prop}
-
-\begin{proof}
-We will be using property $BC_{ij}$ from the proof of the previous proposition. It is sufficient to show that $BC_{ij}$ holds for any $i\not= j$.
-
-Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$.
-Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$.
-Then the odds of $C_i$ and $C_j$ predicted by $(\bigoplus_i a_i \boldsymbol{v}_i)^\pi$ are
-\begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
-\end{align}
-
-Let us now use Bayes covariance of $\boldsymbol{v}_i$. We have
-\begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_m a_m \boldsymbol{v}_m^\pi\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
-\end{align}
-
-It follows that the odds of $C_i$ to $C_j$ for $\bigoplus_m a_m \boldsymbol{v}_m$ are 
-\begin{align}
-\biggl(\frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggr)^{\sum a_m} \prod_m o_m^{a_m}.
-\end{align}
-Clearly, under the assumption $\sum_m a_m = 1$, the classifier $\bigoplus_m a_m \boldsymbol{v}_m$ satisfies $BC_{ij}$ and it follows that it is Bayes covariant.
-\end{proof}
-
-% 
-% given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
-%\begin{align*}
-%	\boldsymbol{B}(x) = (p_1, \ldots, p_K)\quad\textrm{and}\quad \boldsymbol{\tilde B}(x) = (\tilde p_1, \ldots, \tilde p_K)
-%\end{align*}
-%then the prediction of the ensemble $\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}$ is given by
-%\begin{align*}
-%	\bigl(\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}\bigr)(x)\propto (\,p_1^\alpha \tilde p_1^\beta, \ldots, p_K^\alpha \tilde p_K^\beta).
-%\end{align*}
-
-As an example, consider the classification problem with three classes.
-We have three arboreal classifiers $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$ which correspond to star graphs centered respectively at classes $C_1, C_2, C_3$.
-The classifier
-\begin{align}
-\frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:bc1}
-\end{align}
-is Bayes covariant \emph{and} symmetric. A key result proved in [\cite{vsuch2016bayes}] is that it is a unique such classifier for $K=3$.
-
-\begin{thm} \label{thm:K3}
-	There exists a unique symmetric Bayes covariant coupling methods for $K=3$.
-\end{thm}
-
-Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$:
-\[
-\boldsymbol{E} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
-\]
-Note that here we use the plus symbol to denote the vector addition of vectors representing $K$-class probability distributions.
-This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.
-
-\subsection{Properties of coupling methods}
-
-The following table indicates which properties are enjoyed by each coupling method we described in this section.
-
-\begin{table}[!ht]
-\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
-&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
-\hline 
-\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
-&uniqueness &  yes & yes & yes & yes & yes & yes \\
-&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
-&canonicity & yes & no & yes & yes & no & yes \\
-&symmetry & yes & yes & yes & yes & no & yes \\
-& Bayes covariant & no & no & no & yes & yes & yes \\
-\hline
-\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
-&Hinton's minimality & ? & ?  & ++ & ?  & ? & +++ \\
-&lack of parameters & yes & yes & yes & yes & yes & yes \\
-& amounts to a linear system & no & yes & yes & yes & yes & yes\\
-& linear system of special form & no & no & yes & yes & yes & yes \\
-& iterative method & yes & yes & yes & no & not needed & not needed\\
-\hline
-\end{tabular}
-\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
-\label{tab:summaryCoupling}
-\end{table}
-
 \section{Experimental results.}
@@
 
-The first experiment compares the performanc of three parameterless coupling methods
+The first experiment compares the performance of three parameterless coupling methods
 \begin{itemize}
@@
 %\subsection{Wu-Lin-Weng's method}
-
-%\subsection{Linear kernel}
-
-%\begin{tabular}
-%\input{glm1-multi.tex}
-%\end{tabular}
-
-%Here is a citation \cite{chow:68}.
-
-% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references
-
-\acks{All acknowledgements go at the end of the paper before appendices and references.
-Moreover, you are required to declare funding (financial activities supporting the
-submitted work) and competing interests (related financial activities outside the submitted work).
-More information about this disclosure can be found on the JMLR website.}
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
-
-\appendix
-\section{}
-\label{app:explicit}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we provide explicit predictions of coupling methods used in the paper.
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\section{}
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
-
-\vskip 0.2in 
-\bibliography{paper}
-
-\end{document}

### 2025-05-08 paper.tex
Restructure paper into multiple files

--- 2025-04-24 paper.tex
@@
 \newtheorem{thm}{Theorem}
+\newtheorem{lem}{Lemma}
 \newtheorem{assumption}{Assumption}
@@
 
-\section{Theoretical basis of coupling methods}
+\input theory.tex
 
-Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature space $X$.
-In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class.
-Given $x$ in $X$ we aim to find the probability that $x$ belongs to $i$-th class.
+\input coupling.tex
 
-\subsection{Bayes classifier}
-
-An exact solution to this problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.
-
-\begin{assumption} \label{ass:1}
- For all $x$ in the feature space we have $d_i(x) > 0$.
-\end{assumption}
-Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.
-
-The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
-\begin{align}
- p^\Pi_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
-\end{align}
-
-Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of classes.
-Assuming prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier predicts the probability of $i$-th class as
-
-\begin{align}
-	p_{ij}^\Pi(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
-\end{align}
-
-Knowledge of vector $\boldsymbol{p}^\Pi(x)$ is  equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
-\begin{align}
-p_{ij}^\Pi(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
-\end{align}
-
-Conversely, it is easy to show that  the system of equations \eqref{eq:bt1} has a unique solution.
-
-\begin{prop} \label{prop:binary2multi}
-The system of  equations \eqref{eq:bt1} in unknowns $p_i^\Pi(x)$ has a unique solution which is the multi-class Bayes classifier.
-\end{prop}
-%\begin{proof}
-%Indeed, we have 
-%\begin{align*}
-%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
-%\end{align*}
-%\end{proof}
-
-\subsection{One-vs-one classification }
-
-In practice one does not have know true probability distributions and hence cannot construct Bayes classifier.
-However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$.
-The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$.
-One does it by finding an approximate solution of the system of equations
-%\begin{align}
-%
-%\end{align}
-%
-%
-%Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$.
-Let us denote the $r_{ij}(x)$ the output of Bayes (binary) classifier for $x$ in $X$ yielding the probability $p(x \in C_i \mid x\in C_i \cup C_j )$.
-Then we have
-%\begin{equation}
-%r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
-%\end{equation}
-%
-%
-%The system of equations is called Bradley--Terry equations.
-The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations.
-The theoretical basis for one-vs-one classification framework is provided by the following result.
-%
-%
-%
-%Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$.
-A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
-\begin{equation}
-	{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
-\end{equation}
-
-% One should note that 
-%\begin{itemize}
-%\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
-%\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
-%\end{itemize}
-
-Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
-The system is usually inconsistent and additional assumptions are needed.
-A method to solve Bradley-Terry equations is called a coupling method.
-Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
-Schematically, classification using coupling method $\boldsymbol{v}$ proceeds as indicated in Figure \ref{fig:coupling}.
-
-\begin{figure}[!h]
-	\centering
-	\begin{tikzcd}[column sep=3cm]
-		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
-		\arrow{d}{coupling} \\
-		 & \boldsymbol{v}(\boldsymbol{R}(x)) 
-	\end{tikzcd}
-	\caption{Multi-class classification using a coupling method $\boldsymbol{v}$}
-	\label{fig:coupling}
-\end{figure}
-
-\subsection{Exact desiderata on coupling method} \label{sec:des:exact}
-
-Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
-this section
- we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
-
-%\begin{itemize}
-%\item a coupling method should should always provide a unique solution, at least when all $r_{ij}>0$,
-%\item Bradley-Terry consistency,
-%\item canonicity,
-%\item symmetry,
-%\item Bayes covariance,
-%
-%\item good accuracy on benchmark tasks,
-%\item lack of parameters, or at least having a small number of parameters,
-%\item Hinton's minimality,
-%\item simplicity of computation.
-%\end{itemize}
-
-\emph{Unique solution} refers to the fact that the procedure to compute a multi-class probabilistic prediction always converges to a unique solution.
-One way to satisfy this condition would be that it amounts to a linear system of equations in $K$ variables, and the matrix of the system would be invertible.
-Another example would be when the procedure amounts to finding the minimum of a strongly convex function.
-
-\emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
-The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
-satisfies \eqref{eq:bt1}.
-
-\emph{Canonicity} refers to requirement that the method should be natural.
-Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
-Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
-
-Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
-For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical [\cite{shannon1948mathematical,selten1998axiomatic}].
-
-\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions.
-The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by
-\begin{equation}
-	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
-\end{equation}
-We say that a coupling method $V$ is \emph{symmetric} if 
-\begin{align}
-		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
-\end{align}
-
-\emph{Bayes covariance} is a notion introduced in  [\cite{vsuch2016bayes}].
-It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
-Any Bayes classifier, whether binary or multiclass changes its prediction when the priors change.
-Let us describe the process.
-Suppose we change priors from $\Pi = (P_1, \ldots, P_k)$ to $\Pi'= (P'_1, \ldots, P'_K)$.
-Then the prediction of Bayes classifiers changes from $\boldsymbol{p}^\Pi= (p_1, \ldots, p_K)$ to the vector
-\begin{align}
-\boldsymbol{p}^{\Pi'} \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr). \label{eq:changePrior}
-\end{align}
-
-When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
-If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.
-
-Let us make this explicit.
-Let $\boldsymbol{v}$ be a coupling method.
-Denote by  $\pi$ the change of priors $\pi:\Pi \rightarrow \Pi'$.
-If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_2^{ij}(D)$ by requiring
-$$
-\pi_2^{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
-$$
-We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_2^{ij}(r_{ij})$.
-The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents the effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
-
-On the other hand we can apply \eqref{eq:changePrior} after coupling. Say we have a distribution on $K$ classes
-\begin{align}
-D \propto (p_1, \ldots, p_K)
-\end{align}
-then we define $D^\pi$ by requiring 
-\begin{align}
-D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr).
-\end{align}
-We now say that a method if Bayes covariant if
-\begin{align}
-\boldsymbol{v}(\boldsymbol{R}^\pi)=	\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi,
-\end{align}
-for any matrix $\boldsymbol{R}$ with $r_{ij}> 0$.
-
-%Let $\boldsymbol{R}^\pi$ be the matrix of pairwise predictions when we apply \eqref{eq:changePrior} to each binary classifier.
-%For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
-%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzcd}
-%	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
-%	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
-%\end{tikzcd}
-%\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
-%\label{fig:bc}
-%\end{figure}
-
-\subsection{Inexact desiderata for coupling methods}
-
-\label{sec:des:inexact}
-
-In this section we describe several concepts that lack strict mathematical delineation, but may still be important to consider.
-
-\emph{Good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
-This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform.
-However a good coupling method should perform robustly across a variety of datasets.
-A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
-At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
-
-\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtain unbiased estimates of the parameters of the coupling method.
-This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters.
-For example, this is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
-
-\emph{Simplicity of computation}  may refer to the computational requirement for inference.
-With the dramatic increase of edge computing devices, such as smartphones, a simple, fast, energy-efficient algorithm may be preferable to a better performing one which would require more computational resources.
-
-Let us finally mention \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction [\cite[p.~467]{hastie1998classification}].
-Suppose we are classifying objects from CIFAR-10 dataset.
-If the true class is  a ``dog'', why should we care what is the output of the classifier distinguishing ``airplanes'' from ``ships''?
-The binary classifier is trained only on airplanes and ships, and has never seen a dog.
-One may thus prefer a classifier which somehow suppresses noisy output of (seemingly) irrelevant classifiers.
-
-%The first that the five conditions have a clear mathematical definition, whereas the rest are not exact.
-For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.
-
-\section{Examples of coupling methods} \label{sec:coupling}
-
-There is a plethora of methods available for coupling. In this section we describe four major classes.
-
-\subsection{Methods aiming to minimize binary divergence}
-
-A multi-class estimate $\hat{\boldsymbol{p}}$ obtained by a coupling method implies via \eqref{eq:bt1} probability distributions on each pair of classes:
-\begin{align*}
-	\hat D_{ij}^\textrm{multi}= \biggl(\frac{\hat{p_i}}{\hat p_i + \hat p_j},\frac{\hat{p_j}}{\hat p_i + \hat p_j}\biggr)	
-\end{align*}
-On the other hand, binary classifiers provide another distribution for each pair of  classes, namely
-\begin{align*}
-\hat D_{ij}^\textrm{binary} = (\hat r_{ij}, \hat r_{ji}).
-\end{align*}
-
-A natural way to find  $\hat{\boldsymbol{p}}$ is thus to minimize a functional incorporating divergence measures between these distributions
-\begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
-\end{align*}
-
-A notable example which uses this principle is the coupling method introduced in [\cite{hastie1998classification}]. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
-\begin{align*}
-	\divm\nolimits_\textrm{KL} (\boldsymbol{p}, \boldsymbol{q})= \sum p_i \log (p_i/ q_i)
-\end{align*}
-
-Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
-In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score [\cite{gneiting2007strictly, buja2005loss}].
-
-For instance, a popular alternative is divergence arising from the quadratic  score [\cite{gneiting2007strictly}] (also known as Brier score [\cite{brier1950verification}]).
-This divergence takes the form
-$$
-\divm\nolimits_\textrm{quad} (\boldsymbol{p}, \boldsymbol{q})= \sum (p_i - q_i)^2.
-$$
-Unlike Kullback-Leibler divergence, the penalty for incorrect prediction with arbitrarily low probability is bounded (by one).
-This quadratic score is the basis of the popular Wu-Lin-Weng's method [\cite{wu2004probability}].
-
-Their method uses an additional trick, which we term \emph{self-referentiality}.
-In the method of Hastie and Tibshirani, $w_{ij}$ are constants derived from observed class frequencies.
-However, we could use weights $w_{ij}$ that increase when the predicted probability of either class $i$ or $j$ is high.
-A reasonable choice would be for instance $w_{ij}= p_i + p_j$.
-In the case of quadratic score, it is more convenient to use weights $w_{ij} = (p_i + p_j)^2$ because then the resulting optimization problem is just minimization of a quadratic form
-\begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{i,j} (r_{ij}p_j - r_{ji}p_i)^2.
-\end{align*}
-
-We note that the method is symmetric.
-The choice of quadratic scoring rule can also be viewed as canonical in view of axiomatic characterization given in  [\cite{selten1998axiomatic}].
-However the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary.
-Thus we do not view Wu-Lin-Weng's method as canonical.
-
-\subsection{Arboreal methods}
-
-System of equations \eqref{eq:bt2} is overdetermined because there are $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.
-Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns.
-This principle underlies arboreal coupling methods.
-
-An arboreal coupling method ignores all but $K-1$ of the pairwise predictions.
-A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes 1 and 3.
-The two equations form \eqref{eq:bt2} together with the requirement that the prediction probabilities should sum to 1 yield the following system of equations
-\begin{equation}
-	\begin{split}
-		\frac{\hat p_1}{\hat p_1 + \hat p_2} &= {r}_{12}\\
-		\frac{\hat p_2}{\hat p_2 + \hat p_3} &= {r}_{23}\\
-		\hat p_1 + \hat p_2 + \hat p_3 &= 1
-	\end{split}
-	\label{eq:arb1}
-\end{equation}
-
-For $K=3$, there are three different arboreal coupling methods, which we shall call $\boldsymbol{s}_1$, $\boldsymbol{s}_2$, $\boldsymbol{s}_3$, where the system \eqref{eq:arb1} represents the coupling method $\boldsymbol{s}_2$.
-
-In order to obtain a regular system of equations for  larger values of $K$ , the resulting classifiers must represent a connected tree within the complete graph on all classes.
-Any arboreal method is non-canonical, because there is no natural way to choose a tree in a complete graph.
-
-\subsection{Methods emphasizing Hinton's minimality}
-
-A variant on arboreal methods is the following oracle method which we shall call Hinton's oracle.
-It  assumes it has the access to the ground truth $y = C_t$.
-It outputs probabilities by solving only the equations
-$$
-\frac{\hat p_t}{\hat p_t + \hat p_j} = {r}_{tj},\quad \textrm{for }j\not = t,
-$$
-together the  with total sum equation
-$$
-\sum_{i=1}^K  \hat p_i = 1.
-$$
-
-For any sample, its result is identical to the arboreal method where the underlying tree forms a star.
-This method is clearly the optimal one with respect to Hinton's minimality criterion, because it ignores the output of any classifier not trained on the true class.
-It is not a true classification method, however, because it ``peeks'' at the label.
-Its main utility is to provide a way to benchmark other methods with respect to Hinton's minimality.
-
-In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
-Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at class $C_i$.
-The predictions will generally span the vector space $R^K$.
-In that case the prediction $\hat{\boldsymbol{p}}$ of the method  can be expressed as a linear combination of $\boldsymbol{s}_i(x)$.
-Let us now define \emph{radial} coupling method.
-The  method requires that for the  weights we could in fact use the components of $\boldsymbol{p}$ i.e.
-\begin{equation}
-	\begin{split}
-	\hat {\boldsymbol{p}} &= \hat p_1 \boldsymbol{s}_1(x) + \ldots + \hat p_K \boldsymbol{s}_K(x)\\
-	1 &= \hat p_1 + \ldots + \hat p_K
-	\end{split}
-	 \label{eq:radial}
-\end{equation}
-%
-The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${{T}}_i$.
-
-\subsection{Bayes covariant methods}
-
-There are many Bayes covariant methods. First examples are provided by arboreal coupling methods.
-
-\begin{prop}
-Any arboreal method $\boldsymbol{t}$ is Bayes covariant.
-\end{prop}
-\begin{proof}
-We start by defining property $BC_{ij}$ (short for Bayes covariant when restricted to classes $i$ and $j$) of a coupling method.
-A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
-
-Let us list some easy to verify properties of this concept:
-
-\begin{itemize}
-\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$,
-\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant,
-\item[c)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant,
-\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
-\end{itemize}
-
-An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$.
-It follows using from b) and d) that the method is Bayes covariant.
-
-%	
-%	
-%Let $\pi$ be a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $(P'_1, \ldots, P'_K)$.
-We need to verify $\boldsymbol{v}(\boldsymbol{R}^\pi) =\bigl( \boldsymbol{v}(\boldsymbol{R})\bigr)$ for any pairwise matrix $\boldsymbol{R}$.
-|We will rephrase this in an equivalent way.
-Let
-%\begin{align}
-%	\begin{split}
-%	\boldsymbol{v}(\boldsymbol{R}^\pi) &= (v'_1, \ldots, v'_K) \\
-%	\boldsymbol{v}(\boldsymbol{R}) &= (v_1, \ldots, v_K)
-%	\end{split}
-%\end{align}
-%Suppose $\pi$ is a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. If the prediction given $\Pi$ is $(t_1, \ldots, t_K)$ then we need to prove that
-%\begin{align*}
-%\boldsymbol{t}(R^\pi) = \bigl(t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}\bigr)
-%\end{align*}
-%	
-%	We can proceed by induction.
-The statement is clear when $K=2$.
-Suppose the proposition is true for an integers $<K$ and we are given a spanning tree $T$ on $K$ vertices.
-Any tree has a vertex of degree one.
-We may assume that in the case of $T$ it is the vertex corresponding to $C_1$ and the unique edge incident to $C_1$ is $C_1C_2$.
-%	
-%	 Denote by $\boldsymbol{t}$ the prediction corresponding to $T$ and by $\boldsymbol{t}'$ the prediction corresponding to the subgraph without the vertex $C_1$. Let us write 
-%	\begin{align*}
-%	\boldsymbol{t}(x) &= (t_1, t_2, \ldots, t_K) \\
-%	\boldsymbol{t'}(x) &= ( t'_2, \ldots, t'_K) 
-%\end{align*}
-%These vectors are related as follows:
-%\begin{align}
-%\begin{split}
-%\frac{t_1}{t_1+t_2} &= r_{12} \\
-%(t_2, \ldots, t_K) &\propto (t'_2, \ldots, t'_{K})
-%\end{split} \label{eq:ind1}
-%\end{align}
-%
-%Now consider the effect of change of priors $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. Applying \eqref{eq:changePrior} to the multi-class prediction yields a vector 
-%$$
-%\boldsymbol{t}^{\Pi\rightarrow \Pi'} \propto (t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}).
-%$$
-%Now consider what happens when we apply \eqref{eq:changePrior} before coupling.
-By induction assumption the method $\boldsymbol{t}'$ is Bayes covariant and thus applying coupling \emph{after} change of priors yields
-%$$
-%\boldsymbol{t}'^{\Pi\rightarrow \Pi'} \propto (t_2 \frac{P'_2}{P_2}, \ldots, t_K \frac{P'_K}{P_K})
-%$$
-
-\end{proof}
-
-Given several Bayes covariant methods one can form  their ``linear combination'' - an ensemble which is also Bayes covariant. Let us make it explicit.
-
-Suppose real numbers $\alpha_1, \ldots,\alpha_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
-We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
-\begin{align*}
- 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_M \boldsymbol{v}_M\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(x),
-\end{align*}
-where the symbol $\odot$ denotes componentwise multiplication, and exponentials are computed component-wise. With this definition we can state the following result.
-
-\begin{prop}
-Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
-\end{prop}
-
-\begin{proof}
-We will be using property $BC_{ij}$ from the proof of the previous proposition. It is sufficient to show that $BC_{ij}$ holds for any $i\not= j$.
-
-Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$.
-Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$.
-Then the odds of $C_i$ and $C_j$ predicted by $(\bigoplus_i a_i \boldsymbol{v}_i)^\pi$ are
-\begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
-\end{align}
-
-Let us now use Bayes covariance of $\boldsymbol{v}_i$. We have
-\begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_m a_m \boldsymbol{v}_m^\pi\biggr)(\boldsymbol{R}) \\
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
-\end{align}
-
-It follows that the odds of $C_i$ to $C_j$ for $\bigoplus_m a_m \boldsymbol{v}_m$ are 
-\begin{align}
-\biggl(\frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggr)^{\sum a_m} \prod_m o_m^{a_m}.
-\end{align}
-Clearly, under the assumption $\sum_m a_m = 1$, the classifier $\bigoplus_m a_m \boldsymbol{v}_m$ satisfies $BC_{ij}$ and it follows that it is Bayes covariant.
-\end{proof}
-
-% 
-% given such $\alpha + \beta = 1$. If the prediction of the two Bayes covariant methods $\boldsymbol{B}$ and $\boldsymbol{\tilde B}$ are
-%\begin{align*}
-%	\boldsymbol{B}(x) = (p_1, \ldots, p_K)\quad\textrm{and}\quad \boldsymbol{\tilde B}(x) = (\tilde p_1, \ldots, \tilde p_K)
-%\end{align*}
-%then the prediction of the ensemble $\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}$ is given by
-%\begin{align*}
-%	\bigl(\alpha 	\boldsymbol{B} \oplus \beta \boldsymbol{\tilde B}\bigr)(x)\propto (\,p_1^\alpha \tilde p_1^\beta, \ldots, p_K^\alpha \tilde p_K^\beta).
-%\end{align*}
-
-As an example, consider the classification problem with three classes.
-We have three arboreal classifiers $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$ which correspond to star graphs centered respectively at classes $C_1, C_2, C_3$.
-The classifier
-\begin{align}
-\frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:bc1}
-\end{align}
-is Bayes covariant \emph{and} symmetric. A key result proved in [\cite{vsuch2016bayes}] is that it is a unique such classifier for $K=3$.
-
-\begin{thm} \label{thm:K3}
-	There exists a unique symmetric Bayes covariant coupling methods for $K=3$.
-\end{thm}
-
-Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{T}_2, \boldsymbol{T}_3$:
-\[
-\boldsymbol{E} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
-\]
-Note that here we use the plus symbol to denote the vector addition of vectors representing $K$-class probability distributions.
-This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.
-
-\subsection{Properties of coupling methods}
-
-The following table indicates which properties are enjoyed by each coupling method we described in this section.
-
-\begin{table}[!ht]
-\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
-&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
-\hline 
-\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
-&uniqueness &  yes & yes & yes & yes & yes & yes \\
-&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
-&canonicity & yes & no & yes & yes & no & yes \\
-&symmetry & yes & yes & yes & yes & no & yes \\
-& Bayes covariant & no & no & no & yes & yes & yes \\
-\hline
-\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
-&Hinton's minimality & ? & ?  & ++ & ?  & ? & +++ \\
-&lack of parameters & yes & yes & yes & yes & yes & yes \\
-& amounts to a linear system & no & yes & yes & yes & yes & yes\\
-& linear system of special form & no & no & yes & yes & yes & yes \\
-& iterative method & yes & yes & yes & no & not needed & not needed\\
-\hline
-\end{tabular}
-\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
-\label{tab:summaryCoupling}
-\end{table}
-
-\section{Experimental results.}
-
-The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
-
-\begin{itemize}
-\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
-\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
-\item[c)] If the answer to b) is negative, is it better to apply change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
-\end{itemize}
-
-These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.
-
-\subsection{Datasets}
-
-It is natural to consider the benchmark datasets used in previous evaluation of coupling methods [\cite{wu2004probability}].
-The authors considered altogether seven datasets with number of classes ranging from 3 to 26.
-For each dataset they extracted 40 pairs of training and testing datasets.
-Half of these were smaller (300 training samples and 500 testing samples) and the other half was larger (800 training samples and 1000 testing samples).
-In our experiments we use only the larger pairs.
-
-As a preliminary step we conducted analysis of linear separability of the datasets.
-We used ECOS solver in CVXR library to solve the underlying quadratic program.
-The results are reported in Table \ref{tab:sep}.
-
-\input{tab-sep.tex}
-
-We can infer that except for 'waveform' dataset, majority of binary problems are linearly separable.
-
-\subsection{Classification methodology}
-
-We have opted to use LDA as a binary classification tool.
-Its appeal is that it is applicable even for linearly separable datasets, thus obviating additional crossvalidation step incurred by methods that use regularization (e.g.
-penalized logistic regression or SVM).
-It usually provides results close to logistic regression [\cite{james2013introduction}].
-
-For preprocessing we first removed features that were constant across classes.
-Then we projected the data using PCA to the subspace for which corresponding singular values were at least $1/1000$.
-We used PCA without scaling or centering since the datasets' features were already normalized to interval $[-1,1]$.
-
-For training LDA we used MASS library in R. We implemented coupling methods in C++ using Eigen library. As arguments to the coupling methods we use log-odds, i.e. instead of $r_{ij}$ they expect
-$$
-\tilde r_{ij} = \log \biggl(\frac{1}{r_{ji}} - 1\biggr).
-$$
-The resulting matrix $\tilde{\boldsymbol{R}}$ is skew symmetric (with the convention of having zeroes on the diagonal).
-
-This parametrization allows for precise representation of extremely small probabilities which are sometimes produced by LDA.
-These small probabilities might be expected given that a large fraction of binary problems is linearly separable.
-
-Small probabilities generally have very little effect on the implementation of Bayes covariant methods which generally operate using log-odds.
-However small probabilities do affect both the method of Wu-Lin-Weng as well sa radial method, because then Assumption \ref{ass:1} fails to hold.
-
-%\begin{figure}[!ht]
-%	\includegraphics[width = 0.5\linewidth]{graph/dna-lda.pdf}
-%	\includegraphics[width = 0.5\linewidth]{graph/waveform-lda.pdf}
-%	\caption{Projections of three-class datasets using LDA Left: dna, right: waveform}
-%\end{figure}
-
-\subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets} \label{sec:exp1}
-
-The first experiment compares the performanc of three parameterless coupling methods
-\begin{itemize}
-\item method of Wu-Lin-Weng, which is widely used in software libraries, and thus can be viewed as an orthodox choice,
-\item normal coupling, which is a Bayes covariant method,
-\item radial coupling, which is not Bayes covariant.
-\end{itemize}
-
-Although previous evaluations of the latter two methods were done in [\cite{vsuch2016bayes}], they used phonetic data for which ground truth may be imprecise.
-
-\input{tab-multi.tex}
-
-From Table \ref{tab:multi} we can clearly see that Wu-Lin-Weng's method has the best performance.
-On some datasets it trounces normal coupling method by a wide margin.
-The edge over radial method is smaller, with the exception of usps dataset where its accuracy is higher by remarkable 30\%.
-
-\subsection{Experiment 2: Accuracy of Bayes covariant methods with parameters}
- \label{sec:exp2}
-
-In the previous experiment we established that the method of Wu-Lin-Weng provides leading performance. However in view of Theorem \ref{thm:K3} the method is not Bayes covariant.
-
-In this experiment we investigated whether we can (always) find  a Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method, if we allow it to have (a few) trainable parameters.
-Our experiment proceeds in five steps.
-
-First, we restrict our investigation to the case of three class datasets. This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask.
-
-As a second step, we consider whether the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$ (which do not have any parameters) could bridge the gap.
-The statistics are shown in Table \ref{tab:step2}.
-
-\input{tab-step2.tex}
-
-We can see that approximately half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
-Therefore we should extend search to Bayes covariant methods with trainable parameters.
-
-In the third step we define two parameter family of Bayes covariant coupling methods
-\begin{align}
-a_1 \boldsymbol{s}_1 \oplus a_2 \boldsymbol{s}_2 \oplus a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1 \label{eq:family}
-\end{align}
-Note that the parameter space of this family is not compact.
-In order to facilitate computations we opted to conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
-To further reduce computational burden we selected 1000 three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
-The results are shown in Figure \ref{fig:par-bc}.
-
-\begin{figure}[!ht]
-\includegraphics{graph/exp2-summary.pdf}
-\caption{Results of grid search for parametric Bayes covariant methods matching performance of Wu-Lin-Weng's method}
-\label{fig:par-bc}
-\end{figure}
-
-We can see that only in minority of cases we found a parametric method matching the performance of Wu-Lin-Weng's. This finding comes with caveat that we searched only in the simplex $a_i \geq 0$.
-
-Therefore as the final step in our investigation we looked whether a parametric Bayes covariant method in family \eqref{eq:family} for parameters \emph{outside} of this simplex could perform better.
-We conducted another search but this time
-\begin{itemize}
-	\item We searched within a much larger rectangle $D$ containing the simplex $a_i\geq 0$, which in this case is a triangle $T$.
-	\item We used Brier score as a smooth proxy for measuring the quality of multi-class classifier. This score is much smoother than 0-1 score which measures accuracy.
-\end{itemize}
-
-The results are shown in Figure \ref{fig:score}
-
-\begin{figure}[!ht]
-	\includegraphics{graph/exp2-detail.pdf}
-	\caption{Color map indicates the value of Brier score computed for an ensemble of coupling methods on the testing dataset.
-The vertices triangle indicate the arboreal coupling methods, and the black circle the location of the optimum.}
-	\label{fig:score}
-\end{figure}
-
-We can see that indeed the optimum over the rectangle lies outside of the simplex.
-Let us compare the resulting accuracy of the optima in $\Delta$ and $D$.
-The results are shown in Table \ref{tab:step5}.
-
-\input tab-step5.tex
-
-\subsection{Experiment 3: Effect of change of priors}  \label{sec:exp3}
-%\subsection{Wu-Lin-Weng's method}
-
-%\subsection{Linear kernel}
-
-%\begin{tabular}
-%\input{glm1-multi.tex}
-%\end{tabular}
-
-%Here is a citation \cite{chow:68}.
+\input experiment.tex
 
@@
 
-\appendix
-\section{}
-\label{app:explicit}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we provide explicit predictions of coupling methods used in the paper.
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\section{}
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
+\input appendix.tex
 

### 2025-05-08 theory.tex
Restructure paper into multiple files

\section{Theoretical basis of coupling methods}

Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature space $X$. In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class. Given $x$ in $X$ we aim to find the probability that $x$ belongs to $i$-th class.

\subsection{One-vs-on classification}

An exact solution to a classification problem is provided by the Bayes classifier. To simplify the discussion we will make the following assumption.

\begin{assumption} \label{ass:1}
For all $x$ in the feature space we have $d_i(x) > 0$.
\end{assumption}
Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.

The Bayes classifier predicts that the probability of $x$ belonging to the $i$-th class is
\begin{align}
 p^\Pi_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
\end{align}

Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of classes. Assuming prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier predicts the probability of $i$-th class as

\begin{align}
	p_{ij}^\Pi(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
\end{align}

Knowledge of vector $\boldsymbol{p}^\Pi(x)$ is equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
\begin{align}
p_{ij}^\Pi(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
\end{align}

Conversely, it is easy to show that  the system of equations \eqref{eq:bt1} has a unique solution.

\begin{prop}[Fundamental theorem of one-vs-one classification]
	 \label{prop:binary2multi}
	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
\end{prop}
\begin{proof}
	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denote the odds of $C_i$ to $C_j$:
	\begin{align}
		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j}
	\end{align}

	From \eqref{eq:bt1} we can deduce the odds of classes $C_j$ to $C_i$ for the Bayes classifier since
	\begin{align}
	\alpha_{ij}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
	\end{align}
	Knowing the odds of $C_2$ to $C_1$, $C_3$ to $C_2$ up to $C_{K}$ to $C_{K-1}$ together with the requirement that probabilities sum to one uniquely determines the whole vector $\boldsymbol{p}^\Pi(x)$.
\end{proof}
%\begin{proof}
%Indeed, we have 
%\begin{align*}
%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
%\end{align*}
%\end{proof}

\subsection{Coupling methods}

In practice one does not have know true probability distributions and hence cannot construct Bayes classifies. However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$. The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$. One does it by finding an approximate solution of the system of equations
%\begin{align}
%
%\end{align}
%
%
%Suppose that $K$ classes $C_1, \ldots, C_K$ are distributed according to probability distributions $p_i$ on a  space $X$. Let us denote the $r_{ij}(x)$ the output of Bayes (binary) classifier for $x$ in $X$ yielding the probability $p(x \in C_i \mid x\in C_i \cup C_j )$. Then we have
%\begin{equation}
%r_{ij}(x)= \frac {p_i(x)}{p_i(x) + p_j(x)}.
%\end{equation}
%
%
%The system of equations is called Bradley--Terry equations.  The equations in \eqref{eq:bt1}  can be transformed to a system of linear equations. The theoretical basis for one-vs-one classification framework is provided by the following result.
%
%
%
%Suppose we have estimators $\hat r_{ij}$ for Bayes predictions $r_{ij}$ for all pairs $i\not= j$. A \emph{coupling method} obtains a multi-class probabilistic estimate $\boldsymbol{\hat p}= (\hat p_1, \ldots, \hat p_K)$ that satisfy
\begin{equation}
	{r}_{ij}(x) \approx \frac {\hat p_i(x)}{\hat p_i(x) + \hat p_j(x)}. \label{eq:bt2}
\end{equation}

% One should note that 
%\begin{itemize}
%\item the resulting system of equations will usually not be consistent, because $\hat{r}_{ij}$ are only estimates of true values $r_{ij}$,
%\item when probabilities are parametrized in other ways (e.g. other common parametrizations are as odds, or log-odds), the system of equations \eqref{eq:bt} is non-linear.
%\end{itemize}

Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
The system is usually inconsistent and additional assumptions are needed to construct an estimator. A method to solve Bradley-Terry equations is called a \emph{coupling method}. Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$. Schematically, classification using coupling method $\boldsymbol{v}$ proceeds as indicated in Figure \ref{fig:coupling}.

\begin{figure}[!h]
	\centering
	\begin{tikzcd}[column sep=3cm]
		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
		\arrow{d}{coupling} \\
		 & \boldsymbol{v}(\boldsymbol{R}(x)) 
	\end{tikzcd}
	\caption{Multi-class classification using a coupling method $\boldsymbol{v}$}
	\label{fig:coupling}
\end{figure}

\subsection{Exact desiderata on coupling method} \label{sec:des:exact}

Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
this section
 we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.

%\begin{itemize}
%\item a coupling method should should always provide a unique solution, at least when all $r_{ij}>0$,
%\item Bradley-Terry consistency,
%\item canonicity,
%\item symmetry,
%\item Bayes covariance,
%
%\item good accuracy on benchmark tasks,
%\item lack of parameters, or at least having a small number of parameters,
%\item Hinton's minimality,
%\item simplicity of computation.
%\end{itemize}

\emph{Unique solution} refers to the fact that the procedure to compute a multi-class probabilistic prediction always converges to a unique solution. One way to satisfy this condition would be that it amounts to a linear system of equations in $K$ variables, and the matrix of the system would be invertible. Another example would be when the procedure amounts to finding the minimum of a strongly convex function.

\emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution. The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e. satisfies \eqref{eq:bt1}.

\emph{Canonicity} refers to requirement that the method should be natural. Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model. Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.

Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions. For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical [\cite{shannon1948mathematical,selten1998axiomatic}].

\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions. The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by 
\begin{equation}
	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
\end{equation}
We say that a coupling method $V$ is \emph{symmetric} if 
\begin{align}
		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
\end{align}

\emph{Bayes covariance} is a notion introduced in  [\cite{vsuch2016bayes}]. It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change. Any Bayes classifier, whether binary or multiclass changes its prediction when the priors change. Let us describe the process. Suppose we change priors from $\Pi = (P_1, \ldots, P_k)$ to $\Pi'= (P'_1, \ldots, P'_K)$. Then the prediction of Bayes classifiers changes from $\boldsymbol{p}^\Pi= (p_1, \ldots, p_K)$ to the vector 
\begin{align}
\boldsymbol{p}^{\Pi'} \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr). \label{eq:changePrior}
\end{align}

When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling. If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.

Let us make this explicit. Let $\boldsymbol{v}$ be a coupling method. Denote by  $\pi$ the change of priors $\pi:\Pi \rightarrow \Pi'$. If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_2^{ij}(D)$ by requiring
$$
\pi_2^{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
$$
We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_2^{ij}(r_{ij})$. The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents the effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.

On the other hand we can apply \eqref{eq:changePrior} after coupling. Say we have a distribution on $K$ classes
\begin{align}
D \propto (p_1, \ldots, p_K)
\end{align}
then we define $D^\pi$ by requiring 
\begin{align}
D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr).
\end{align}
We now say that a method if Bayes covariant if
\begin{align}
\boldsymbol{v}(\boldsymbol{R}^\pi)=	\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi,
\end{align}
for any matrix $\boldsymbol{R}$ with $r_{ij}> 0$.

%Let $\boldsymbol{R}^\pi$ be the matrix of pairwise predictions when we apply \eqref{eq:changePrior} to each binary classifier.
%For Bayes covariant method $\boldsymbol{v}$ the following diagram commutes.
%
%\begin{figure}[!h]
%\centering
%\begin{tikzcd}
%	\boldsymbol{R} \arrow[r, "\pi"] \arrow[d, "coupling"] & \boldsymbol{R}^\pi \arrow[d, "coupling"] \\
%	\boldsymbol{v}(\boldsymbol{R}) \arrow[r, "\pi"] & \boldsymbol{v}(\boldsymbol{R}^\pi) =\boldsymbol{v}(\boldsymbol{R})^\pi
%\end{tikzcd}
%\caption{Diagrammatical description of Bayes covariance for a coupling method $\boldsymbol{v}$}
%\label{fig:bc}
%\end{figure}

\subsection{Inexact desiderata for coupling methods}

\label{sec:des:inexact}

In this section we describe several concepts that lack strict mathematical delineation, but may still be important to consider.

\emph{Good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method. This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform. However a good coupling method should perform robustly across a variety of datasets. A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher. At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.

\emph{Lack of parameters} is strongly beneficial for situations when the dataset is small and it would be imprudent to reserve a sizeable portion to obtain unbiased estimates of the parameters of the coupling method. This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters. For example, this is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.

\emph{Simplicity of computation}  may refer to the computational requirement for inference. With the dramatic increase of edge computing devices, such as smartphones, a simple, fast, energy-efficient algorithm may be preferable to a better performing one which would require more computational resources.

Let us finally mention \emph{Hinton's minimality}. Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction [\cite[p.~467]{hastie1998classification}]. Suppose we are classifying objects from CIFAR-10 dataset.  If the true class is  a ``dog'', why should we care what is the output of the classifier distinguishing ``airplanes'' from ``ships''? The binary classifier is trained only on airplanes and ships, and has never seen a dog. One may thus prefer a classifier which somehow suppresses noisy output of (seemingly) irrelevant classifiers.

%The first that the five conditions have a clear mathematical definition, whereas the rest are not exact. For instance while the ideal situation for a coupling method is to have no parameters, the presence of one or two trainable parameters may be justified, if it yields noticeably better performance.

### 2025-05-08 coupling.tex
Fix proposition 2

@@
 
-There are many Bayes covariant methods. In this section we will show that 
-\begin{itemize} 
-	\item arboreal coupling methods are Bayes covariant,
-	\item Bayes covariant methods can be ensembled,
-	\item describe all Bayes covariant methods for $K=3$.
-\end{itemize}
+There are many Bayes covariant methods. The simplest example are arboreal coupling methods. They are not canonical, but with the help of ensembling, one can construct also canonical coupling methods.
 
-We start by defining the property $BC_{ij}$ (the notation stands for \emph{Bayes covariant when restricted to classes} $i$ and $j$) of a coupling method.
+A very helpful aid to study Bayes covariant methods is property $BC_{ij}$ (the notation stands for \emph{Bayes covariant when restricted to classes} $i$ and $j$).
 A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
+Using  notation for odds from Section \ref{sec:one-vs-one}, one has
+\begin{align}
+	\alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R}^\pi) \bigr) = \alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R})^\pi \bigr)
+\end{align}
 
@@
 \begin{itemize}
-	\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$,
-	\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant,
-	\item[c)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant,
-	\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Proposition \ref{lem:transitivity}).
+	\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$ (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
+	%\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant (see Proposition \ref{prop:bcprop}),
+	\item[b)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
+	\item[c)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Lemma \ref{lem:transitivity}).
 \end{itemize}
@@
 An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$.
-It follows using from b) and d) that the method is Bayes covariant.
+Since any pair of vertices is connected by a path, it follows from transitivity of $BC_{ij}$ (property c) that the assumption of b) holds and thus the coupling method is Bayes covariant.
 

### 2025-05-08 theory.tex
Fix proposition 2

@@
 
-\subsection{One-vs-on classification}
+\subsection{One-vs-one classification} \label{sec:one-vs-one}
 
@@
 
-Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
+%Let us outline what kind of exact conditions may be desirable in a coupling method. 
+In %Section \ref{sec:des:exact} 
 this section
- we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
+ we will describe exact mathematical criteria that one may impose on a coupling method, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
 

### 2025-05-08 theory.tex
Fix symmetry definition

@@
 	\begin{align}
-		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j}
+		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j} \label{eq:alpha}
 	\end{align}
@@
 
-\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions.
-The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by
-\begin{equation}
-	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
-\end{equation}
+\emph{Symmetry} We can define two natural actions on permutation group on $K$-elements. Suppose $\sigma$ is a permutation on $K$ elements.
+
+\begin{itemize}
+	\item Given  distributions on the classes $\boldsymbol{p}= (p_1, \ldots, p_K)$, we can define
+	\begin{align}
+		\sigma(\boldsymbol{p})= (p_{\sigma(1)},p_{\sigma(2)}, \ldots, p_{\sigma(K)}).
+	\end{align}
+	 \item $\sigma$ also acts on the matrix of binary predictions. Namely, the entry of $\sigma(\boldsymbol{R})$ in $i$-th row and $j$-th column is defined to be $r_{\sigma(i), \sigma(j)}$.
+	 \end{itemize}
 We say that a coupling method $V$ is \emph{symmetric} if 
 \begin{align}
-		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
+		\sigma(\boldsymbol{v}(\boldsymbol{R})) = \boldsymbol{v}(\sigma(\boldsymbol{R}))\quad\textrm{for any permutation $\sigma$}.
 \end{align}

### 2025-05-08 coupling.tex
Fix proof of Proposition 3

@@
 
-For any sample, its result is identical to the arboreal method where the underlying tree forms a star.
+For any one sample belonging to class $C_t$, its result is identical to the arboreal method where the underlying tree forms a star with center at $C_t$.
 This method is clearly the optimal one with respect to Hinton's minimality criterion, because it ignores the output of any classifier not trained on the true class.
@@
 A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
-Using  notation for odds from Section \ref{sec:one-vs-one}, one has
+Using earlier notation for odds (see \eqref{eq:alpha}), one has
 \begin{align}
@@
 
-%	
-%	
-%Let $\pi$ be a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $(P'_1, \ldots, P'_K)$.
-We need to verify $\boldsymbol{v}(\boldsymbol{R}^\pi) =\bigl( \boldsymbol{v}(\boldsymbol{R})\bigr)$ for any pairwise matrix $\boldsymbol{R}$.
-|We will rephrase this in an equivalent way.
-Let
-%\begin{align}
-%	\begin{split}
-%	\boldsymbol{v}(\boldsymbol{R}^\pi) &= (v'_1, \ldots, v'_K) \\
-%	\boldsymbol{v}(\boldsymbol{R}) &= (v_1, \ldots, v_K)
-%	\end{split}
-%\end{align}
-%Suppose $\pi$ is a change of priors from $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. If the prediction given $\Pi$ is $(t_1, \ldots, t_K)$ then we need to prove that
-%\begin{align*}
-%\boldsymbol{t}(R^\pi) = \bigl(t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}\bigr)
-%\end{align*}
-%	
-%	We can proceed by induction.
-The statement is clear when $K=2$.
-Suppose the proposition is true for an integers $<K$ and we are given a spanning tree $T$ on $K$ vertices.
-Any tree has a vertex of degree one.
-We may assume that in the case of $T$ it is the vertex corresponding to $C_1$ and the unique edge incident to $C_1$ is $C_1C_2$.
-%	
-%	 Denote by $\boldsymbol{t}$ the prediction corresponding to $T$ and by $\boldsymbol{t}'$ the prediction corresponding to the subgraph without the vertex $C_1$. Let us write 
-%	\begin{align*}
-%	\boldsymbol{t}(x) &= (t_1, t_2, \ldots, t_K) \\
-%	\boldsymbol{t'}(x) &= ( t'_2, \ldots, t'_K) 
-%\end{align*}
-%These vectors are related as follows:
-%\begin{align}
-%\begin{split}
-%\frac{t_1}{t_1+t_2} &= r_{12} \\
-%(t_2, \ldots, t_K) &\propto (t'_2, \ldots, t'_{K})
-%\end{split} \label{eq:ind1}
-%\end{align}
-%
-%Now consider the effect of change of priors $\Pi = (P_1, \ldots, P_K)$ to $\Pi' = (P'_1, \ldots, P'_K)$. Applying \eqref{eq:changePrior} to the multi-class prediction yields a vector 
-%$$
-%\boldsymbol{t}^{\Pi\rightarrow \Pi'} \propto (t_1 \frac{P'_1}{P_1}, \ldots, t_K \frac{P'_K}{P_K}).
-%$$
-%Now consider what happens when we apply \eqref{eq:changePrior} before coupling.
-By induction assumption the method $\boldsymbol{t}'$ is Bayes covariant and thus applying coupling \emph{after} change of priors yields
-%$$
-%\boldsymbol{t}'^{\Pi\rightarrow \Pi'} \propto (t_2 \frac{P'_2}{P_2}, \ldots, t_K \frac{P'_K}{P_K})
-%$$
-
 \end{proof}
 
-Given several Bayes covariant methods one can form  their ``linear combination'' - an ensemble which is also Bayes covariant. Let us make it explicit.
+Given several Bayes covariant methods one can form  their ``linear combination'' - an ensemble which is also Bayes covariant. Let us make the construction explicit.
 
-Suppose real numbers $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}.
+Suppose first that real numbers $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:2}.
 We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
@@
 \begin{prop}
-Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
+Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant.
+If $\sum a_m = 1$, then $\boldsymbol{e} = \bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
 \end{prop}
@@
 \begin{proof}
-We will be using property $BC_{ij}$ from the proof of the previous proposition. It is sufficient to show that $BC_{ij}$ holds for any $i\not= j$.
+It is sufficient to show that $BC_{ij}$ holds for any $i\not= j$.
 
-Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$.
-Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$.
-Then the odds of $C_i$ and $C_j$ predicted by $(\bigoplus_i a_i \boldsymbol{v}_i)^\pi$ are
+Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$. Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$ i.e.
+$$
+o_m = \alpha_{ij}(\boldsymbol{v}_m(\boldsymbol{R})).
+$$
+
+It follows from the definition of linear combination of coupling methods that the odds of $C_i$ to $C_j$ for $\boldsymbol{e}$ are
 \begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)^\pi(\boldsymbol{R}) & = \frac{P'_i}{P_i} \frac{P_j}{P'_j} \biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R}) \\
+\prod_m o_m^{a_m}.
 \end{align}
-so the odds are
-
+It follows that the odds of $\boldsymbol{e}^\pi$ are 
 \begin{align}
-	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
+\frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}.
 \end{align}
@@
 \begin{align}
-	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & =  \biggl(\bigoplus_m a_m \boldsymbol{v}_m^\pi\biggr)(\boldsymbol{R}) \\
+	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & \propto 
+	\boldsymbol{v}_1^{a_1}(\boldsymbol{R}^\pi) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(\boldsymbol{R}^\pi) =  \bigodot_m  (\boldsymbol{v}_m^\pi(\boldsymbol{R}))^{a_m} \\
 %	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
@@
 \end{align}
-Clearly, under the assumption $\sum_m a_m = 1$, the classifier $\bigoplus_m a_m \boldsymbol{v}_m$ satisfies $BC_{ij}$ and it follows that it is Bayes covariant.
+Clearly, under the assumption $\sum_m a_m = 1$, the classifier $\bigoplus_m a_m \boldsymbol{v}_m$ satisfies $BC_{ij}$.
+Since this holds for any $i\not=j$,  it follows that $\boldsymbol{e}$ is Bayes covariant.
 \end{proof}

### 2025-05-08 appendix.tex
Finished Section 3.4

@@
 
-\begin{prop}
-	Let $\boldsymbol{v}$ be a coupling method. The following statements are equivalent:
+\begin{prop} \label{prop:bcprop}
+	Let $\boldsymbol{v}$ be a coupling method. If Assumption \ref{ass:1} holds, the following statements are equivalent:
 	\begin{itemize}
 		\item[a)] The coupling method $\boldsymbol{v}$ is Bayes covariant.
-		\item[b)] The coupling method $\boldsymbol{v}$ satisfies $BC_{12}, BC_{23}, \ldots, BC_{K-1,K}$.
-		\item[c)] The coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ for any pair of integers between 1 and $K$ with $i\not= j$.
+		\item[b)] The coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ for any pair of integers  $i\not= j$ with $1\leq i,j \leq K$.
+		\item[c)] The coupling method $\boldsymbol{v}$ satisfies $BC_{12}, BC_{23}, \ldots, BC_{K-1,K}$.
 	\end{itemize}
@@
 \begin{proof}
-
+It follows directly from the definition of $BC_{ij}$ that a) implies b).
+Also, clearly b) implies c).
+If the assumptions of c) hold, then the vectors $\boldsymbol{v}(\boldsymbol{R})^\pi$ and $ \boldsymbol{v}(\boldsymbol{R}^\pi)$ are proportional, but since both have components adding up to one, it follows they are equal and thus a) holds.
 \end{proof}
@@
 \begin{lem} \label{lem:transitivity}
-	If a coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
+	Suppose Assumption \ref{ass:1} holds. If a coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$.
 \end{lem}
@@
 
-\section{}
-\label{app:explicit}
+The following proposition restricts the set of Bayes covariant coupling methods for $K=3$.
 
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
+\begin{prop} \label{prop:bc3}
+	For $K=3$ any Bayes covariant coupling method is uniquely determined by its prediction for  matrices of the form
+	$$
+	\boldsymbol{R_s} = \begin{pmatrix} \cdot & s & 1 -s \\  1-s & \cdot & s \\ s & 1-s & \cdot \end{pmatrix}.
+	$$
+\end{prop}
+\begin{proof}
+	Suppose $\boldsymbol{v}$ is a coupling method,  the priors are $\Pi = (P_1, P_2,P_3)$, and the binary classifiers yield prediction matrix 
+	\begin{align}
+		\boldsymbol{R} = \begin{pmatrix} \cdot & r_{12} & 1 - r_{31} \\ 1-r_{12} & \cdot & r_{23} \\
+			r_{31} & 1- r_{23} & \cdot \end{pmatrix}.
+	\end{align}
 
+	Suppose there was a change of priors $\pi$ such that $\boldsymbol{R}^\pi$ would be belong to the one-parameter family $\boldsymbol{r}_s$ with $s$ in $(0,1)$. Then we have
+	$$
+	\boldsymbol{v}(\boldsymbol{R})^\pi = \boldsymbol{v}(\boldsymbol{R}^\pi) = \boldsymbol{v}(\boldsymbol{R}_s).
+	$$
+	Inverting action of $\pi$ would then determine $\boldsymbol{v}(\boldsymbol{R})$.
+
+	In order to construct such $\pi$ let us introduce a new parametrization of the matrix of binary  predictions
+	\begin{align}
+		\begin{split}
+			q_{12} &= \frac{1}{r_{12}} -1 \\
+			q_{23} &= \frac{1}{r_{23}} -1 \\
+			q_{31} &= \frac{1}{r_{31}} -1 
+		\end{split}
+	\end{align}
+	Under the change of priors $\pi:\Pi \rightarrow \Pi' = (P'_1, P'_2, P'_3)$ we have
+	\begin{align}
+		q'_{ij}	= q_{ij} \cdot \frac{P_i'}{P_i} \frac{P_j}{P'_j}.
+	\end{align}
+	One checks easily that $\Pi' \propto (1, \frac{q_{12}}{q_{23}}, \frac{q_{12}}{q_{23}})$ yields the desired change of priors.
+
+\end{proof}
+
+%\section{}
+%\label{app:explicit}
+%
+%% Note: in this sample, the section number is hard-coded in. Following
+%% proper LaTeX conventions, it should properly be coded as a reference:
+%
+%%In this appendix we prove the following theorem from
+%%Section~\ref{sec:textree-generalization}:
+%
+%In this appendix we provide explicit predictions of coupling methods used in the paper.
+%
+%
+%
 %In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we provide explicit predictions of coupling methods used in the paper.
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-	not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-	dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-	which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-	respective empirical mutual information values based on the sample
-	$\dataset$. Then
-	\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-	\]
-	with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\section{}
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
+%Section~6.2:
+%
+%\noindent
+%{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
+%	not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
+%	dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
+%	which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
+%	respective empirical mutual information values based on the sample
+%	$\dataset$. Then
+%	\[
+%	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
+%	\]
+%	with equality only if $u$ is identically 0.} \hfill\BlackBox
+%
+%\section{}
+%
+%\noindent
+%{\bf Proof}. We use the notation:
+%\[
+%P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
+%P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
+%\]
+%These values represent the (empirical) probabilities of $v$
+%taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
+%by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
+%
+%{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}

### 2025-05-08 coupling.tex
Finished Section 3.4

@@
 	\item[b)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
-	\item[c)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Lemma \ref{lem:transitivity}).
+	\item[c)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Lemma \ref{lem:transitivity} in Appendix \ref{app:bc1}).
 \end{itemize}
@@
 An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$.
-Since any pair of vertices is connected by a path, it follows from transitivity of $BC_{ij}$ (property c) that the assumption of b) holds and thus the coupling method is Bayes covariant.
+Since any pair of vertices is connected by a path, it follows from transitivity of $BC_{ij}$ (property c)\,) that the assumption of b) holds and thus the coupling method is Bayes covariant.
 
@@
 \begin{align}
-\frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:bc1}
+\boldsymbol{e}_3 \stackrel{def}{=} \frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:bc1}
 \end{align}
-is Bayes covariant \emph{and} symmetric. A key result proved in [\cite{vsuch2016bayes}] is that it is a unique such classifier for $K=3$.
+is Bayes covariant \emph{and} symmetric. A key result proved in [\cite{vsuch2016bayes}] is that it is a unique  classifier having these two properties.
 
@@
 
-Let us point out one consequence of the theorem. We could define another ensemble $\boldsymbol{E}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$:
+\begin{proof}
+Let 
+\begin{align}
+	\boldsymbol{R}_s \stackrel{def}{=} \begin{pmatrix} \cdot & s & 1 -s \\  1-s & \cdot & s \\ s & 1-s & \cdot \end{pmatrix}
+\end{align}
+Since $R_s$ is invariant under the action of any permutation of 3 elements, 
+for a symmetric coupling method we have 
+\begin{align}
+	\boldsymbol{v} (\boldsymbol{R}_s) = \biggl(\frac 13, \frac 13, \frac 13 \biggr).
+\end{align}
+Now applying  Proposition \ref{prop:bc3} from Appendix \ref{app:bc1} yields uniqueness. The existence of the method was already shown above.
+\end{proof}
+
+Let us point out one consequence of the theorem. We could define another ensemble $\tilde{\boldsymbol{e}}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$:
 \[
-\boldsymbol{E} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
+\tilde{\boldsymbol{e}} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
 \]
@@
 This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.
+
+The classifier $\boldsymbol{e}_3$ has a canonical generalization for any $K>3$, namely the classifier
+\begin{align}
+\boldsymbol{e}_K \stackrel{def}{=} \frac1K \boldsymbol{s}_1 \oplus \frac1K \boldsymbol{s}_2 \oplus \ldots \oplus \frac 1K \boldsymbol{s}_K  \label{eq:bc1}
+\end{align}
+We call this coupling method the \emph{normal} coupling method.
 

### 2025-05-08 coupling.tex
Fix Table1

@@
 \begin{prop}
+	\label{prop:ensemble}
 Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant.
@@
 \end{align}
-Now applying  Proposition \ref{prop:bc3} from Appendix \ref{app:bc1} yields uniqueness. The existence of the method was already shown above.
+Now applying  Proposition \ref{prop:bc3} from Appendix \ref{app:bc1} yields uniqueness. The existence of the method was already shown above using Proposition \ref{prop:ensemble}.
 \end{proof}
@@
 \]
-Note that here we use the plus symbol to denote the vector addition of vectors representing $K$-class probability distributions.
+Note that here we use the plus symbol to denote the vector addition of vectors representing  probability distributions over $K$ classes.
 This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.
@@
 
-The following table indicates which properties are enjoyed by each coupling method we described in this section.
+In this section  we summarize properties of coupling methods described earlier in this section.
+Table \ref{tab:summaryCoupling} concisely lists the relevant properties enjoyed by each method.
+Note that we have split the desideratum ``simplicity of computation'' into three different aspects:
+\begin{itemize}
+	\item whether a coupling method amounts to a linear system of equations,
+	\item if the coupling method amounts to a linear system of equations, whether the equations are of a special form (e.g. a Markov matrix) that facilitates their solution,
+	\item whether the authors who published the method provide an iterative method that implements the estimate.
+Iterative methods are often  faster than Gaussian elimination, and less prone to numerical issues.
+\end{itemize}
+
+ %interpretation of exact desiderate is unambiguous.
+
+%The following table indicates which properties are enjoyed by each coupling method we described in this section.
 
@@
 \multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
-&Hinton's minimality & ? & ?  & ++ & ?  & ? & +++ \\
+&Hinton's minimality & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
+&robustness & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
 &lack of parameters & yes & yes & yes & yes & yes & yes \\
 & amounts to a linear system & no & yes & yes & yes & yes & yes\\
-& linear system of special form & no & no & yes & yes & yes & yes \\
+& linear system of special form & N/A & no & yes & yes & yes & yes \\
 & iterative method & yes & yes & yes & no & not needed & not needed\\

### 2025-05-13 theory.tex
Fix Assumption 1 and notation of binary classifiers

@@
 \end{assumption}
-Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.
 
@@
 \begin{align}
-	p_{ij}^\Pi(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
+	p_{ij}(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
 \end{align}
@@
 \begin{align}
-p_{ij}^\Pi(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
+p_{ij}(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
 \end{align}
@@
 	 \label{prop:binary2multi}
-	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
+	 Knowledge of binary Bayes classifiers $p_{ij}$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
 \end{prop}
@@
 	\begin{align}
-	\alpha_{ij}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
+	\alpha_{ij}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p_{ij}(x)}- 1.
 	\end{align}
@@
 
-Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations.
-The system is usually inconsistent and additional assumptions are needed to construct an estimator.
+Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations. In parallel to Assumption \ref{ass:1} it is customary to make the following assumption on estimates $r_{ij}$.
+
+\begin{assumption} \label{ass:2}
+For any $x$ in the feature space $r_{ij}(x) > 0$.
+\end{assumption}
+
+Commonly used classifiers such as linear discriminant analysis, (penalized) logistic regression or support vector machines all satisfy this assumption.
+
 A method to solve Bradley-Terry equations is called a \emph{coupling method}.
@@
 \end{figure}
+
+The system of Bradley-Terry equations is usually inconsistent and additional assumptions are needed to construct an estimator.
+In Sections \ref{sec:des:exact} and \ref{sec:des:inexact} we review various approaches to construct coupling methods.
 

### 2025-05-13 coupling.tex
Explanation remark in the caption of summary table

@@
 \end{tabular}
-\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
+\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.
+The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu-Lin-Weng [\cite{wu2004probability}].}
 \label{tab:summaryCoupling}

### 2025-05-20 paper.tex
Revised introduction; added graph to Experiment 1

@@
 
-Multi-class classification is considered to be a more challenging problem than binary classification.
-A natural approach to multi-class classification is to reduce it to a series of binary classification problems and deduce the multi-class decision by aggregating decisions for the binary problems.
+Distribution shift is an important problem facing machine-learning practitioners.
+The shift is almost inevitable since most real-worlds environments evolve over time.
+One particular way a distribution shift may manifest in classification problems  is when the class priors change.
+To make a concrete example, imagine a driver assistance system recognizing traffic signs.
+The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city.
+This of course affects classification, and a good classification system will be able to improve its performance when supplied with a new set of more accurate class priors.
 
-One popular method belonging to  this paradigm uses probabilistic modelling for one-vs-one series of binary problems.
-Notably, it is used as the basis for multi-class classification models using support vector machines (SVM) in LIBSVM library.
-However one can use the approach more generally,  because it can be applied to any probabilistic binary classification method.
+Change of priors can be effectively dealt with in probabilistic classifiers.
+The basic idea is that Bayes theorem stipulates \emph{exactly} what should happen  to the prediction of the  Bayes classifier.
+In practice we assume that a trained classifier closely approximates the Bayes classifier.
+Therefore we can make adjustment to our prediction by applying the same transformation of posterior as would happen with the Bayes classifier.
+
+There is a subtle issue with this approach  when handling probabilistic classifiers arising in one-vs-one classification framework.
+One-vs-one classification is a natural framework to approach  multi-class classification by reducing it to a series of binary classification problems.
+One then deduces the multi-class decision by aggregating decisions for the binary problems.
+Since the procedure is two-step, there is possibility to apply adjustment of priors either during the first step, or the second step, and it is not clear what should be the preferred course of action.
+
+One-vs-one classification is commonly by machine learning practitioners when they opt to use support vector classifiers or support vector machines.
+Why is that users opt one-vs-one classification when there are multi-class extensions of SVM such as the proposed by Crammer-Singer?
+One possible reason is that there is no \emph{canonical} extension.
+A second reason is that the multi-class optimization problems have to deal with multiple
 

### 2025-05-20 exp1-plot1.R

@@ -1,0 +1,24 @@
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+df <- read.csv("data/multi-acc.csv") |> pivot_longer(3:6) |>
+  mutate(name = ifelse(name == "Hinton.s.oracle", "Hinton's oracle", name))
+
+plt1 <- ggplot(df, aes(x = log2(tol), 
+                       y = value, 
+                       group = name, 
+                       color = name )) + 
+  geom_line() + facet_wrap(~dataset) + 
+  scale_x_continuous(breaks = c(-12, -8, -4)) +
+  ylab("0-1 score")
+
+ggsave(
+  filename = "graphs/exp1-plot1.pdf",
+  plot = plt1,
+  width = 5.5,
+  height = 3.5,
+  units = "in"
+)
+
+#print(plt1)

### 2025-05-21 experiment.tex
Revised introduction; added graph to Experiment 1
Better caption

@@
 For preprocessing we first removed features that were constant across classes.
-Then we projected the data using PCA to the subspace for which corresponding singular values were at least $1/1000$.
+Then we projected the data using PCA to the subspace for which corresponding singular values were $> tol$, where $tol$ is a hyper-parameter of an experiment.
 We used PCA without scaling or centering since the datasets' features were already normalized to interval $[-1,1]$.
@@
 The edge over radial method is smaller, with the exception of usps dataset where its accuracy is higher by remarkable 30\%.
+
+\begin{figure}
+	\includegraphics{graphs/exp1-plot1.pdf}
+	\caption{0-1 score plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
+	\label{fig:exp1-plot1}
+\end{figure}
 

### 2025-05-22 lda.R
Possibly fix the graph

@@ -509,11 +509,12 @@ lda_multi <- function(dfs, tols, score = "acc") {
         # Now, let's do Hinton's oracle
         mr <- sapply(1:N, function(i) {
             true_cl <- dft$class_id[i]
-            v <- r[true_cl,,i]
+            v <- r[,true_cl,i]
             maxv <- max(v)
             v1 <- exp(v - maxv)
             v1 / sum(v1)
         }) |> t()
+        print(dim(mr))
         scores <- score_matrix(mr, dft$class_id, score)
         multi <- rbind(multi,
             data.frame(n = n, K = K, method = "Hinton's oracle", correct =
@@ -537,8 +538,8 @@ write_multi <- function(runs = 20, workers = 11, tol = 1/2^(2:12), score = "acc"
             lda_multi(dfs, tols = tol, score = score)$multi
         }) |> list_rbind()
     }) |> list_rbind() |> 
-        group_by(dataset, tol, method) |> summarize(acc = mean(correct), correct = sum(correct)) |>
-        pivot_wider(names_from = "method", values_from = "correct")
+        group_by(dataset, tol, method) |> summarize(acc = mean(correct)) |>
+        pivot_wider(names_from = "method", values_from = "acc")
     df$score = score
     write.csv(df, file = sprintf("data/multi-%s.csv", score), row.names = F, quote = F)
     df

### 2025-05-24 exp1-plot1.R
Fix Figure 2 (from 1st experiment)

@@ -2,13 +2,12 @@ library(ggplot2)
 library(dplyr)
 library(tidyr)
 
-df <- read.csv("data/multi-acc.csv") |> pivot_longer(3:6) |>
-  mutate(name = ifelse(name == "Hinton.s.oracle", "Hinton's oracle", name))
+df <- read.csv("data/multi-acc.csv") 
 
 plt1 <- ggplot(df, aes(x = log2(tol), 
-                       y = value, 
-                       group = name, 
-                       color = name )) + 
+                       y = acc, 
+                       group = method, 
+                       color = method )) + 
   geom_line() + facet_wrap(~dataset) + 
   scale_x_continuous(breaks = c(-12, -8, -4)) +
   ylab("0-1 score")

### 2025-05-24 lda.R

@@ -538,8 +538,9 @@ write_multi <- function(runs = 20, workers = 11, tol = 1/2^(2:12), score = "acc"
             lda_multi(dfs, tols = tol, score = score)$multi
         }) |> list_rbind()
     }) |> list_rbind() |> 
-        group_by(dataset, tol, method) |> summarize(acc = mean(correct)) |>
-        pivot_wider(names_from = "method", values_from = "acc")
+        group_by(dataset, tol, method) |> summarize(acc = mean(correct)) 
+# |>
+ #       pivot_wider(names_from = "method", values_from = "acc")
     df$score = score
     write.csv(df, file = sprintf("data/multi-%s.csv", score), row.names = F, quote = F)
     df

### 2025-05-24 msvm.R
Add automatic normalization of data

@@ -75,12 +75,26 @@ read_wlws <- function(nsamp, dataset, i) {
         r1 <- read_wlw(name1)
         name2 <- sub("-", ".t-", name1)
         r2 <- read_wlw(name2)
+        normalized <- F
 
         if ((r1$min_col != r2$min_col) | (r1$max_col != r2$max_col)) {
             mc = min(r1$min_col, r2$min_col)
             xc = max(1 + r1$ncol - r1$min_col, 1 + r2$ncol - r2$min_col)
             r1 <- read_wlw(name1, min_col = mc, max_col = xc)
             r2 <- read_wlw(name2, min_col = mc, max_col = xc)
+        }
+        
+        for (i in 2:ncol(r1$df)) {
+            r <- range(r1$df[,i])
+            dr <- r[2] - r[1]
+            if (max(abs(r)) > 1 & dr > 0) {
+                r1$df[,i] <- (r1$df[,i] - r[1]) / dr
+                r2$df[,i] <- (r2$df[,i] - r[1]) / dr
+                normalized <- T
+            }
+        }
+        if (normalized) {
+            print("Some features were normalized to interval [0,1]")
         }
         list(train = r1$df, test = r2$df, n = nsamp, dataset = dataset, run = i)
 }

### 2025-05-24 lda.R
Handle unnormalized files

@@ -4,6 +4,7 @@ library(CalibratR)
 suppressPackageStartupMessages(library(MASS))
 library(dplyr)
 suppressPackageStartupMessages(library(tidyr))
+library(stringr)
 
 files <- c( "dna", 
             "letter", 
@@ -12,6 +13,12 @@ files <- c( "dna",
             "segment", 
             "usps", 
             "waveform")
+
+dataset_names <- function() {
+    fs <- dir("unzips/n800", pattern = "*.t-\\d*")
+    m1 <- str_match(fs, "(.*).scale.t-(\\d+)")
+    unique(m1[,2])
+}
 
 make_folds <- function(grp, f = 5) {
     gs <- unique(grp)
@@ -532,7 +539,7 @@ lda_multi <- function(dfs, tols, score = "acc") {
 
 write_multi <- function(runs = 20, workers = 11, tol = 1/2^(2:12), score = "acc") {
     plan(multicore, workers = workers)
-    df <- map(files, function(f) {
+    df <- map(dataset_names(), function(f) {
         future_map(0:(runs - 1), function (r) {
             dfs <- read_wlws(800, f, r)
             lda_multi(dfs, tols = tol, score = score)$multi
@@ -548,7 +555,7 @@ write_multi <- function(runs = 20, workers = 11, tol = 1/2^(2:12), score = "acc"
 
 write_triples <- function(runs = 20, workers = 11) {
     plan(multicore, workers = workers)
-    df <- map(files, function(f) {
+    df <- map(dataset_names(), files, function(f) {
         future_map(0:(runs - 1), function (r) {
             dfs <- read_wlws(800, f, r)
             df1 <- lda_triples(dfs) |> 

### 2025-05-26 coupling.tex
Various fixes

@@
 
-Suppose first that real numbers $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:2}.
+Suppose first that $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabilistic multi-class classification methods satisfying Assumption \ref{ass:2}.
 We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
@@
 
-It follows from the definition of linear combination of coupling methods that the odds of $C_i$ to $C_j$ for $\boldsymbol{e}$ are
+From the definition of linear combination of coupling methods that the odds of $C_i$ to $C_j$ for $\boldsymbol{e}$ are
 \begin{align}
@@
 \end{align}
-It follows that the odds of $\boldsymbol{e}^\pi$ are 
+
+It follows from \eqref{def:prior:effect} that the odds of $\boldsymbol{e}^\pi$ are 
 \begin{align}
@@
 	\biggl(\bigoplus_m a_m \boldsymbol{v}_m\biggr)(\boldsymbol{R^\pi}) & \propto 
-	\boldsymbol{v}_1^{a_1}(\boldsymbol{R}^\pi) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(\boldsymbol{R}^\pi) =  \bigodot_m  (\boldsymbol{v}_m^\pi(\boldsymbol{R}))^{a_m} \\
+	\boldsymbol{v}_1^{a_1}(\boldsymbol{R}^\pi) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(\boldsymbol{R}^\pi) =  \bigodot_m  (\boldsymbol{v}_m^\pi(\boldsymbol{R}))^{a_m}. \\
 %	&= \frac{P'_i}{P_i} \frac{P_j}{P'_j} \prod_m o_m^{a_m}
 \end{align}
-
-It follows that the odds of $C_i$ to $C_j$ for $\bigoplus_m a_m \boldsymbol{v}_m$ are 
+Therefore the odds of $C_i$ to $C_j$ for $\bigoplus_m a_m \boldsymbol{v}_m$ are 
 \begin{align}
@@
 \end{align}
+
 Clearly, under the assumption $\sum_m a_m = 1$, the classifier $\bigoplus_m a_m \boldsymbol{v}_m$ satisfies $BC_{ij}$.

### 2025-05-26 discussion.tex
Various fixes

\section{Discussion}

Let us discuss our findings with the focus on applications.

One-vs-one classification framework is commonly used by machine learning practitioners, for instance whenever one uses radial basis function SVM implemented in  standard libraries. Since those method rely on coupling method of Wu-Lin-Weng, one is faced with the decision how to handle differing predictions when priors change.

Of course, one option is to use other classification models. For instance, random forests provide a flexible alternative. Nevertheless, RBF SVM are still one of the best choices for classification tasks with non-linear boundaries.

We have shown in Experiment 1, that substituting parameterless Bayes covariant method for Wu-Lin-Weng coupling methods incurs penalty in accuracy metric.

In our Experiment 2 we showed that the penalty can be often, but not always, eliminated when one opts for one of the parametric Bayes covariant methods.

Finally, in Experiment 3 we showed that the impact of the

### 2025-05-26 experiment.tex
Fix Figure 2 (from 1st experiment)
Various fixes

@@
-\section{Experimental results.}
-
-The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
-
-\begin{itemize}
-\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
-\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
-\item[c)] If the answer to b) is negative, is it better to apply change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
-\end{itemize}
-
-These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.
+\section{Methodology.}
 
@@
 
+\section{Experimental results.}
+
+The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
+
+\begin{itemize}
+\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
+\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
+\item[c)] If the answer to b) is negative, is it better to apply change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
+\end{itemize}
+
+These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.
+
 \subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets} \label{sec:exp1}
@@
 
-\input{tab-multi.tex}
+% \input{tab-multi.tex}
 
-From Table \ref{tab:multi} we can clearly see that Wu-Lin-Weng's method has the best performance.
+From Figure \ref{fig:exp1-plot1} we can clearly see that Wu-Lin-Weng's method has the best performance.
 On some datasets it trounces normal coupling method by a wide margin.
@@
 \begin{figure}
-	\includegraphics{graphs/exp1-plot1.pdf}
+	\includegraphics{graphs/exp1-plot2.pdf}
 	\caption{0-1 score plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
@@
 
-In this experiment we investigated whether we can (always) find  a Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method, if we allow it to have (a few) trainable parameters.
-Our experiment proceeds in five steps.
+In this experiment we investigated whether we can (always) find  a Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method.
+We investigate  the case of three class datasets.
+This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask if we allow it to have (a few) trainable parameters.
+Our experiment has three parts.
 
-First, we restrict our investigation to the case of three class datasets. This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask.
-
-As a second step, we consider whether the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$ (which do not have any parameters) could bridge the gap.
+In the first part, we consider whether four parameterless Bayes covariant method could match the performance of Wu-Lin-Weng method.
+In our comparison we include the normal method, as well as the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$.
 The statistics are shown in Table \ref{tab:step2}.
@@
 
-We can see that approximately half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
-Therefore we should extend search to Bayes covariant methods with trainable parameters.
+We can see that in slightly less than half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
+Therefore next we will extend search to Bayes covariant methods with trainable parameters.
 
-In the third step we define two parameter family of Bayes covariant coupling methods
+Let us define two parameter family of Bayes covariant coupling methods
 \begin{align}
@@
 Note that the parameter space of this family is not compact.
-In order to facilitate computations we opted to conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
+
+In the second part of our experiment we  conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
 To further reduce computational burden we selected 1000 three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
-The results are shown in Figure \ref{fig:par-bc}.
+The summary statistics are shown in Figure \ref{fig:par-bc}.
 

### 2025-05-26 paper.tex
Various fixes

--- 2025-05-08 paper.tex
@@
 
-\title{On change of priors in one-vs-one classification methods}
+\title{On selection of a coupling method to cope with change of priors in one-vs-one classification }
 
@@
        \name Ali Haidar \email haidar@savbb.sk \\
+       \begin{minipage}[t]{0.45\textwidth}
        \addr Matematický ústav SAV\\
@@
        Banská Bystrica, 974 01, Slovakia
+       \end{minipage}\hfill
+       \begin{minipage}[t]{0.45\textwidth}
+       \addr Fakulta matematiky, fyziky a informatiky\\
+       Univerzity Komenského \\
+       Mlynská dolina F1 \\
+       Bratislava, 842 48, Slovakia
+       \end{minipage}
        }
@@
 
-Multi-class classification is considered to be a more challenging problem than binary classification.
-A natural approach to multi-class classification is to reduce it to a series of binary classification problems and deduce the multi-class decision by aggregating decisions for the binary problems.
+Distribution shift is an important problem facing machine-learning practitioners  [\cite{zhang2023dive, sugiyama2007covariate}].
+One particular way a distribution shift may manifest in classification problems  is when the class priors change between the training set used to train a model, and the data distribution in deployment - the so called label shift [\cite{vsipka2022hitchhiker,lipton2018detecting}].
+To make a concrete example, consider a driver assistance system recognizing traffic signs.
+Suppose a speed limit sign was maliciously altered to indicate 80mph limit instead of 30mph.
+To avoid being fooled by the alteration, the system could utilize priors.
+The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city.
+It is very unlikely to encounter 80mph limit in a city setting.
+By taking into account the city priors, a driver assistance is likely to make the proper classification.
+In general a good classification system will be able to improve its performance when supplied with a new set of class priors that correspond to the true distribution of classes.
 
-One popular method belonging to  this paradigm uses probabilistic modelling for one-vs-one series of binary problems.
-Notably, it is used as the basis for multi-class classification models using support vector machines (SVM) in LIBSVM library.
-However one can use the approach more generally,  because it can be applied to any probabilistic binary classification method.
+Change of priors can be effectively dealt with in probabilistic classifiers.
+The basic idea is that Bayes theorem stipulates \emph{exactly} what should happen  to the prediction of the  Bayes classifier when priors change.
+In practice we assume that a trained classifier closely approximates the Bayes classifier.
+Therefore we can make adjustment to our prediction by applying the same transformation of posterior as would happen with the Bayes classifier.
 
-A key step in probabilistic one-vs-one modelling is the aggregation of results of individual binary classifiers - so-called \emph{coupling method}.
-The most commonly used coupling method is that proposed by Wu-Lin-Weng.
-As noted in [\cite{dohau}], the method is one of several non-canonical decisions used in multi-class SVM modelling.
-The goal of this paper is to compare its behavior with canonical methods.
+There is a subtle issue with this approach  when handling probabilistic classifiers arising in one-vs-one classification framework.
+One-vs-one classification is a two-step framework to approach  multi-class classification.
+In the first step it reduces the multiclass problem to a series of binary classification problems.
+In the second step it deduces the multi-class decision by aggregating decisions for the binary problems.
+Since the procedure is two-step, there is a possibility to apply adjustment of priors either to the probabilistic distributions obtained after the first step, or after the second step.
+It is not clear what should be the preferred course of action and this problem motivates our paper.
+
+The focus of efforts is in presenting and evaluating the methods to aggregate binary predictions.
+We formulate the underlying principles of one-vs-one probabilistic classification in Section 2.
+Section is 3 is devoted to presenting different classes that one
 
@@
 \input experiment.tex
+
+\input discussion.tex
 

### 2025-05-27 tab-sep.R
Added file

@@ -1,0 +1,20 @@
+library(tidyr)
+library(dplyr)
+library(xtable)
+
+df <- read.csv("data/separation.csv")
+
+df1 <- df |> group_by(dataset, status, K) |> summarize(count = n() ) |>
+  mutate(pct = count / (10 * K * (K-1))) |>
+  pivot_wider(id_cols = c("dataset", "K"), 
+              names_from = "status", 
+              values_from = "pct", 
+              values_fill = 0) |>
+  mutate(separable = optimal) |>
+  select(dataset, K)
+
+sink("tab-sep.tex")
+print(xtable(df1, label = "tab:sep", digits = 2,
+             caption = "The benchmark datasets with indication of the number of classes $K$ ",
+),  include.rownames = FALSE)
+sink()

### 2025-05-27 paper.tex
oprava pomlcky a rovnice (5)

@@
 Distribution shift is an important problem facing machine-learning practitioners  [\cite{zhang2023dive, sugiyama2007covariate}].
-One particular way a distribution shift may manifest in classification problems  is when the class priors change between the training set used to train a model, and the data distribution in deployment - the so called label shift [\cite{vsipka2022hitchhiker,lipton2018detecting}].
+One particular way a distribution shift may manifest in classification problems  is when the class priors change between the training set used to train a model, and the data distribution in deployment -- the so called label shift [\cite{vsipka2022hitchhiker,lipton2018detecting}].
 To make a concrete example, consider a driver assistance system recognizing traffic signs.

### 2025-05-28 paper.tex
More references in the introduction

--- 2025-05-26 paper.tex
@@
        \AND
-       \name Peter Novotný \email peter.novotny@uniza.sk \\
+       \name Peter Novotný \email peter.novotny@fri.uniza.sk \\
        \addr Fakulta informatiky a riadenia\\
@@
 
-The focus of efforts is in presenting and evaluating the methods to aggregate binary predictions.
+Our approach to the problem is to evaluate practical performance of different methods to aggregate binary predictions.
+Such methods -- called coupling methods -- first appeared in work of \cite{refregier1991probabilistic}.
+Many authors followed with alternative proposals [\cite{price1994pairwise, hastie1998classification,  zahorian1999partitioned, wu2004probability, vsuch2015new, vsuch2016bayes}].
+
 We formulate the underlying principles of one-vs-one probabilistic classification in Section 2.
-Section is 3 is devoted to presenting different classes that one
+In Section 3 we present  different classes of coupling methods.
+We pay special focus to methods that commute with change of priors -- Bayes covariant methods, since such methods provide an unexpected, and elegant solution to our problem.
+We introduce new coupling methods by forming weighted ensembles, which we prove are also Bayes covariant when a normalizing condition on weights hold (Proposition \ref{prop:ensemble}).
+In Section 4 we summarize our methodology.
+The results of our experiments are described in Section 5.
+In Section 6 we summarize our findings and provide practical guidance to solving the problem.
 

### 2025-05-28 appendix.tex
Fix typo in indexes

@@
 
-	Suppose there was a change of priors $\pi$ such that $\boldsymbol{R}^\pi$ would be belong to the one-parameter family $\boldsymbol{r}_s$ with $s$ in $(0,1)$. Then we have
+	Suppose there was a change of priors $\pi$ such that $\boldsymbol{R}^\pi$ would be belong to the one-parameter family $\boldsymbol{R}_s$ with $s$ in $(0,1)$. Then we have
 	$$
@@
 	\end{align}
-	One checks easily that $\Pi' \propto (1, \frac{q_{12}}{q_{23}}, \frac{q_{12}}{q_{23}})$ yields the desired change of priors.
+	One checks easily that $\Pi' \propto (1, \frac{q_{12}}{q_{23}}, \frac{q_{12}}{q_{31}})$ yields the desired change of priors.
 

### 2025-06-09 experiment.tex
Revert to ggplot figure

@@
 \begin{figure}
-	\includegraphics{graphs/exp1-plot2.pdf}
+	\includegraphics{graphs/exp1-plot1.pdf}
 	\caption{0-1 score plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
@@
 
-In the previous experiment we established that the method of Wu-Lin-Weng provides leading performance. However in view of Theorem \ref{thm:K3} the method is not Bayes covariant.
+The method of Wu-Lin-Weng provides leading performance among the \emph{non-parametric} methods examined in the previous experiment.
+However in view of Theorem \ref{thm:K3} the Wu-Lin-Weng's method is not Bayes covariant.
 
-In this experiment we investigated whether we can (always) find  a Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method.
+In this experiment we investigated whether we can (always) find  a (possibly \emph{parametric}) Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method.
 We investigate  the case of three class datasets.
-This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask if we allow it to have (a few) trainable parameters.
+This is a natural starting point, since it is the smallest number of classes where the question is meaningful to asks.
 Our experiment has three parts.
@@
 In our comparison we include the normal method, as well as the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$.
-The statistics are shown in Table \ref{tab:step2}.
+We consider all possible triples of classes in all datasets.
+The resulting statistics are shown in Table \ref{tab:step2}.
 
@@
 We can see that in slightly less than half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
-Therefore next we will extend search to Bayes covariant methods with trainable parameters.
-
+Therefore we will extend search to Bayes covariant methods with trainable parameters.
 Let us define two parameter family of Bayes covariant coupling methods
@@
 \end{align}
-Note that the parameter space of this family is not compact.
+We note that the parameter space of this family (the hyperplane $a_1 + a_2 + a_3 =1$) is not compact.
 
-In the second part of our experiment we  conduct a grid search on points in the simplex where the coefficients $a_i$ are nonnegative $a_i \geq 0$.
-To further reduce computational burden we selected 1000 three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
+In the second part of our experiment we  conduct a grid search for methods matching performance of Wu-Lin-Weng method.
+We examine methods for which the coefficients $a_i$ are nonnegative $a_i \geq 0$.
+To reduce computational burden we selected 1000 random chosen three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
 The summary statistics are shown in Figure \ref{fig:par-bc}.
@@
 
-Therefore as the final step in our investigation we looked whether a parametric Bayes covariant method in family \eqref{eq:family} for parameters \emph{outside} of this simplex could perform better.
+Therefore in the third part of our experiment  we looked whether a parametric Bayes covariant method in family \eqref{eq:family} for parameters \emph{outside} of this simplex could perform better.
 We conducted another search but this time

### 2025-06-09 exp1-plot1.R
Add consistent theme

@@ -2,7 +2,10 @@ library(ggplot2)
 library(dplyr)
 library(tidyr)
 
-df <- read.csv("data/multi-acc.csv") 
+source("theme.R")
+
+df <- read.csv("data/multi-acc.csv")  
+df$method = if_else(df$method == "wlw2", "Wu-Lin-Weng", df$method)
 
 plt1 <- ggplot(df, aes(x = log2(tol), 
                        y = acc, 
@@ -10,7 +13,7 @@ plt1 <- ggplot(df, aes(x = log2(tol),
                        color = method )) + 
   geom_line() + facet_wrap(~dataset) + 
   scale_x_continuous(breaks = c(-12, -8, -4)) +
-  ylab("0-1 score")
+  ylab("0-1 score")  + pub_theme
 
 ggsave(
   filename = "graphs/exp1-plot1.pdf",
@@ -19,5 +22,16 @@ ggsave(
   height = 3.5,
   units = "in"
 )
+
+library(lattice)
+
+plt2 <- xyplot(acc ~ log2(tol) | dataset, data = df, type= "l", group = method, auto.key = list(space = "top", columns =
+2), par.settings =
+list(superpose.line = list(lty = c(1, 2,3 ,4 ))), 
+ylab = "0-1 score")
+
+pdf("graphs/exp1-plot2.pdf", width = 5.5, height = 3.5)
+print(plt2)
+dev.off()
 
 #print(plt1)

### 2025-06-09 exp2-summary.R

@@ -6,18 +6,20 @@ source('lda.R')
 
 
 pt <- par_triples(limit = 1000)
-df1 <- pt$df |> mutate(outcome = if_else(cv_acc >= wlw2, "parametric >= WLW", "parametric < WLW")) |> group_by(dataset, outcome) |>
-summarize(count = n())
+df1 <- pt$df |> 
+    mutate(outcome = if_else(cv_acc >= wlw2, "parametric >= WLW", "parametric < WLW")) |> 
+    group_by(dataset, outcome) |>
+    summarize(count = n())
 
-plt1 <- ggplot(df1, aes(x = dataset, y = count, color = outcome, fill = outcome)) + geom_col() + theme_minimal(base_size
-= 9)
+plt1 <- ggplot(df1, aes(x = dataset, y = count, color = outcome, fill = outcome)) + 
+    geom_col() + theme_minimal(base_size = 9) + coord_flip()
 
 
 ggsave(
   filename = "graphs/exp2-summary.pdf",
     plot = plt1,
     width = 5.5,   # Width in inches
-    height = 3.5,  # Height in inches
+    height = 2.5,  # Height in inches
     units = "in"   # Specify units as inches
 )
 

### 2025-06-09 theme.R

@@ -1,0 +1,8 @@
+pub_theme <- theme(
+  text = element_text(size = 10),
+  plot.title = element_text(size = 10, face = "bold"),
+  axis.title = element_text(size = 10),
+  axis.text = element_text(size = 9),
+  legend.title = element_text(size = 10),
+  legend.text = element_text(size = 9)
+)  + theme_minimal()

### 2025-06-09 lda.R
Add an explicit seed

@@ -763,7 +763,7 @@ eval_scores <- function(bcp, W = gen_W(qL = length(bcp$pl)), score = "brier") {
     list(scores = scores, W = W, score = score)
 }
 
-par_triples <- function(div = 10, score = "acc", workers = 12, limit = 100) {
+par_triples <- function(div = 10, score = "acc", workers = 12, limit = 100, seed = 123) {
     df <- read.csv("data/triples.csv")
     # df1 <- df |> mutate(m = pmax(normal, omit12, omit13, omit23)) |> 
     df1 <- df |>  filter(wlw2 > normal)
@@ -773,6 +773,7 @@ par_triples <- function(div = 10, score = "acc", workers = 12, limit = 100) {
     W <- gen_W2(div)
 
     #df2 <- map(1:nrow(df1), function(i) {
+    set.seed(seed)
     plan(multicore, workers = workers)
     rows <- if (nrow(df1) > limit) {
         sample(1:nrow(df1), limit)

### 2025-06-11 lda.R
Modularize code to compute BC stack for K=3

@@ -572,15 +572,15 @@ write_triples <- function(runs = 20, workers = 11) {
 #
 gen_W <- function(n = 200, div = 100, qL = 4) {
   sapply( 1:n,  function(i) { 
-    s <- sample(0:div , qL - 1, replace = T) |> 
-            sort()
-    if (qL == 2)
-        c(s[1], div - s[1]) / div
-    else 
-        c(s[1], 
-        sapply(1:(qL - 2), function(i) (s[i + 1] - s[i])),
-        (div - s[qL - 1])) / div
-    })  |> t()
+  s <- sample(0:div , qL - 1, replace = T) |> 
+       sort()
+  if (qL == 2)
+      c(s[1], div - s[1]) / div
+  else 
+      c(s[1], 
+      sapply(1:(qL - 2), function(i) (s[i + 1] - s[i])),
+      (div - s[qL - 1])) / div
+  })  |> t()
 }
 
 
@@ -774,11 +774,16 @@ par_triples <- function(div = 10, score = "acc", workers = 12, limit = 100, seed
 
     #df2 <- map(1:nrow(df1), function(i) {
     set.seed(seed)
-    plan(multicore, workers = workers)
     rows <- if (nrow(df1) > limit) {
         sample(1:nrow(df1), limit)
     } else 1:nrow(df1)
-    df2 <- future_map(rows, function(i) {
+    cv_triples(df1[rows,], W = W, score = score, workers = workers, seed = seed)
+}
+
+cv_triples <- function(df1, W, score = "acc", workers = 12, seed = 123) {
+    plan(multicore, workers = workers)
+    df2 <- future_map(1:nrow(df1), function(i) {
+        set.seed(seed + i)
         dfs <- read_wlws(800, df1$dataset[i], df1$run[i]) 
         bcp <- get_bcp(dfs, df1$i[i], df1$j[i], df1$k[i])
         acc <- eval_scores(bcp, W = W, score = "acc")$scores

### 2025-06-12 experiment.tex
Revision

@@
 
-\subsection{Experiment 1: Accuracy of parameter-less coupling methods on benchmark datasets} \label{sec:exp1}
+\subsection{Experiment: Accuracy of canonical coupling methods on benchmark datasets} \label{sec:exp1}
 
@@
 On some datasets it trounces normal coupling method by a wide margin.
-The edge over radial method is smaller, with the exception of usps dataset where its accuracy is higher by remarkable 30\%.
+The edge over the radial method is smaller with only mnist and usps datasets showing a significant difference for smaller values of $tol$ hyperparameter.
 
@@
 	\includegraphics{graphs/exp1-plot1.pdf}
-	\caption{0-1 score plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
+	\caption{Success rate plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
 	\label{fig:exp1-plot1}
@@
 
-\subsection{Experiment 2: Accuracy of Bayes covariant methods with parameters}
+\subsection{Experiment: Accuracy of Bayes covariant methods without parameters}
  \label{sec:exp2}
 
-The method of Wu-Lin-Weng provides leading performance among the \emph{non-parametric} methods examined in the previous experiment.
+The method of Wu-Lin-Weng provides leading performance among the canonical {nonparametric} methods examined in the previous experiment.
 However in view of Theorem \ref{thm:K3} the Wu-Lin-Weng's method is not Bayes covariant.
@@
 This is a natural starting point, since it is the smallest number of classes where the question is meaningful to asks.
+All experiments use value of 0.05 for $tol$ hyperparameter based on results of Section \ref{sec:exp1}.
 Our experiment has three parts.
@@
 In the first part, we consider whether four parameterless Bayes covariant method could match the performance of Wu-Lin-Weng method.
-In our comparison we include the normal method, as well as the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$.
+In our comparison we include the normal method, as well as the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$ that are not canonical.
 We consider all possible triples of classes in all datasets.
@@
 Therefore we will extend search to Bayes covariant methods with trainable parameters.
+
+\subsection{Experiment: A parametric family}
+
 Let us define two parameter family of Bayes covariant coupling methods
 \begin{align}
-a_1 \boldsymbol{s}_1 \oplus a_2 \boldsymbol{s}_2 \oplus a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1 \label{eq:family}
+a_1 \boldsymbol{s}_1 \oplus a_2 \boldsymbol{s}_2 \oplus a_3 \boldsymbol{s}_3,\quad\textrm{where } a_1 + a_2 +a_3 = 1. \label{eq:family}
 \end{align}
-We note that the parameter space of this family (the hyperplane $a_1 + a_2 + a_3 =1$) is not compact.
+Note that this family includes the normal coupling method as well as the three arboreal methods $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$.
 
-In the second part of our experiment we  conduct a grid search for methods matching performance of Wu-Lin-Weng method.
-We examine methods for which the coefficients $a_i$ are nonnegative $a_i \geq 0$.
+In this experiment we  conduct a grid search for methods matching performance of Wu-Lin-Weng method.
+Grid search works best in low dimension, when restricted to a compact subset.
+To that end we restrict our search to the simplex formed with nonnegative coefficients $a_i \geq 0$, which form a compact subset.
 To reduce computational burden we selected 1000 random chosen three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
@@
 \includegraphics{graphs/exp2-summary.pdf}
-\caption{Results of grid search for parametric Bayes covariant methods matching performance of Wu-Lin-Weng's method}
+\caption{Comparison of success rate for parametric Bayes covariant methods \eqref{eq:family} vs. Wu-Lin-Weng's method}
 \label{fig:par-bc}
@@
 
-We can see that only in minority of cases we found a parametric method matching the performance of Wu-Lin-Weng's. This finding comes with caveat that we searched only in the simplex $a_i \geq 0$.
+We can see that only in minority of cases we found a parametric Bayes covariant coupling method matching the performance of Wu-Lin-Weng's method.
+This finding comes with caveat that we searched only in the simplex $a_i \geq 0$.
 
-Therefore in the third part of our experiment  we looked whether a parametric Bayes covariant method in family \eqref{eq:family} for parameters \emph{outside} of this simplex could perform better.
-We conducted another search but this time
+\subsection{Example: }
+
+We determined that among the 1000 three-class problems we have examined, the largest gap between Bayes-covariant parametric methods and Wu-Lin-Weng method occurred for mnist dataset and classes 5,6,9.
+Figure
+
 \begin{itemize}

### 2025-06-12 exp1-plot1.R
Use different line types for different methods

@@ -10,6 +10,7 @@ df$method = if_else(df$method == "wlw2", "Wu-Lin-Weng", df$method)
 plt1 <- ggplot(df, aes(x = log2(tol), 
                        y = acc, 
                        group = method, 
+                       linetype = method,
                        color = method )) + 
   geom_line() + facet_wrap(~dataset) + 
   scale_x_continuous(breaks = c(-12, -8, -4)) +

### 2025-06-12 experiment.tex
Provided a detailed explanatin of parametric Bayes covariant experiment; removed the next experiment

@@
 \item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
-\item[c)] If the answer to b) is negative, is it better to apply change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
+\item[c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
 \end{itemize}
@@
 
-The first experiment compares the performance of three parameterless coupling methods
+The first experiment compares the performance the following canonical coupling methods
 \begin{itemize}
@@
 \item normal coupling, which is a Bayes covariant method,
-\item radial coupling, which is not Bayes covariant.
+\item radial coupling, which is not Bayes covariant,
+\item Hinton's oracle.
 \end{itemize}
 
-Although previous evaluations of the latter two methods were done in [\cite{vsuch2016bayes}], they used phonetic data for which ground truth may be imprecise.
-
 % \input{tab-multi.tex}
-
-From Figure \ref{fig:exp1-plot1} we can clearly see that Wu-Lin-Weng's method has the best performance.
+The results are shown in Figure \ref{fig:exp1-plot1}.
+We can clearly see that Wu-Lin-Weng's method has the most robust performance.
 On some datasets it trounces normal coupling method by a wide margin.
 The edge over the radial method is smaller with only mnist and usps datasets showing a significant difference for smaller values of $tol$ hyperparameter.
+However in view of Theorem \ref{thm:K3} the Wu-Lin-Weng's method is not Bayes covariant, therefore we will extend the set of Bayes covariant methods beyond the canonical normal coupling.
 
@@
 
-The method of Wu-Lin-Weng provides leading performance among the canonical {nonparametric} methods examined in the previous experiment.
-However in view of Theorem \ref{thm:K3} the Wu-Lin-Weng's method is not Bayes covariant.
-
-In this experiment we investigated whether we can (always) find  a (possibly \emph{parametric}) Bayes covariant coupling method that could match the performance of Wu-Lin-Weng's method.
+In this experiment we compare  Bayes covariant coupling methods \emph{without} parameters that could match the performance of Wu-Lin-Weng's method.
 We investigate  the case of three class datasets.
-This is a natural starting point, since it is the smallest number of classes where the question is meaningful to asks.
+This is a natural starting point, since it is the smallest number of classes where the question is meaningful to ask.
 All experiments use value of 0.05 for $tol$ hyperparameter based on results of Section \ref{sec:exp1}.
-Our experiment has three parts.
-
-In the first part, we consider whether four parameterless Bayes covariant method could match the performance of Wu-Lin-Weng method.
 In our comparison we include the normal method, as well as the three arboreal methods $ \boldsymbol{s}_1,~ \boldsymbol{s}_2,~ \boldsymbol{s}_3$ that are not canonical.
@@
 We can see that in slightly less than half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
-Therefore we will extend search to Bayes covariant methods with trainable parameters.
+This leads us to extend evaluation to Bayes covariant methods with parameters.
 
-\subsection{Experiment: A parametric family}
+\subsection{Experiment: A parametric family of Bayes covariant methods}
 
@@
 \end{align}
-Note that this family includes the normal coupling method as well as the three arboreal methods $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$.
+Note that this family includes the normal coupling method \eqref{eq:normal3} as well as the three arboreal methods $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$.
 
-In this experiment we  conduct a grid search for methods matching performance of Wu-Lin-Weng method.
-Grid search works best in low dimension, when restricted to a compact subset.
-To that end we restrict our search to the simplex formed with nonnegative coefficients $a_i \geq 0$, which form a compact subset.
-To reduce computational burden we selected 1000 random chosen three-class subproblems from those where Wu-Lin-Weng's method outperformed normal coupling.
-The summary statistics are shown in Figure \ref{fig:par-bc}.
+We start by selecting 1000 three class subsets from all datasets for problems where normal method was outperformed by Wu-Lin-Weng's method.
+For each three-class classification problem we will try to match the performance of Wu-Lin-Weng method with a Bayes covariant method in family \eqref{eq:family}.
+
+Selecting parameters for methods in family \eqref{eq:family} requires several methodological choices. 
+\begin{itemize}
+\item To avoid bias in selection of parameters $a_1, a_2, a_3$ we use a subset of testing dataset to find their optimal values.
+As a result, we will be comparing the accuracy of Wu-Lin-Weng method evaluated with repeated five-fold cross-validation accuracy of a method in family \eqref{eq:family}.
+We use 20 repetitions.
+\item To compare two parameter vectors, we compare their resulting cross-validation accuracy.
+An alternative approach would be to use  a gradient based optimization for a smooth proxy (e.g.
+cross-entropy) of empirical accuracy.
+We opted for the former because the problem is two-dimensional, and we can use grid search instead.
+\item Our choice of grid search necessitates a selection of a compact subset of parameter space that will be sampled.
+We choose to examine points in the simplex defined by  $a_i\geq 0$, for $i=1,2,3$.
+As Table \ref{tab:step2} shows, this simplex contained in more than half case a Bayes covariant method matching the performance of Wu-Lin-Weng's method.
+\end{itemize}
 
@@
 
+The summary statistics are shown in Figure \ref{fig:par-bc}.
 We can see that only in minority of cases we found a parametric Bayes covariant coupling method matching the performance of Wu-Lin-Weng's method.
-This finding comes with caveat that we searched only in the simplex $a_i \geq 0$.
 
-\subsection{Example: }
-
-We determined that among the 1000 three-class problems we have examined, the largest gap between Bayes-covariant parametric methods and Wu-Lin-Weng method occurred for mnist dataset and classes 5,6,9.
+%\subsection{Experiment: }
+%
+%We determined that among the 1000 three-class problems we have examined, the largest gap between Bayes-covariant parametric methods and Wu-Lin-Weng method occurred for mnist dataset and classes 5,6,9.
 Figure
-
-\begin{itemize}
-	\item We searched within a much larger rectangle $D$ containing the simplex $a_i\geq 0$, which in this case is a triangle $T$.
-	\item We used Brier score as a smooth proxy for measuring the quality of multi-class classifier. This score is much smoother than 0-1 score which measures accuracy.
-\end{itemize}
-
-The results are shown in Figure \ref{fig:score}
-
-\begin{figure}[!ht]
-	\includegraphics{graphs/exp2-detail.pdf}
-	\caption{Color map indicates the value of Brier score computed for an ensemble of coupling methods on the testing dataset.
+%
+%\begin{itemize}
+%	\item We searched within a much larger rectangle $D$ containing the simplex $a_i\geq 0$, which in this case is a triangle $T$.
+%	\item We used Brier score as a smooth proxy for measuring the quality of multi-class classifier. This score is much smoother than 0-1 score which measures accuracy.
+%\end{itemize}
+%
+%The results are shown in Figure \ref{fig:score}
+%
+%
+%\begin{figure}[!ht]
+%	\includegraphics{graphs/exp2-detail.pdf}
+%	\caption{Color map indicates the value of Brier score computed for an ensemble of coupling methods on the testing dataset.
 The vertices triangle indicate the arboreal coupling methods, and the black circle the location of the optimum.}
-	\label{fig:score}
-\end{figure}
-
-We can see that indeed the optimum over the rectangle lies outside of the simplex.
+%	\label{fig:score}
+%\end{figure}
+%
+%We can see that indeed the optimum over the rectangle lies outside of the simplex.
 Let us compare the resulting accuracy of the optima in $\Delta$ and $D$.
 The results are shown in Table \ref{tab:step5}.
+%
+%\input tab-step5.tex
 
-\input tab-step5.tex
-
-\subsection{Experiment 3: Effect of change of priors}  \label{sec:exp3}
+\subsection{Experiment: Effect of change of priors}  \label{sec:exp3}
 %\subsection{Wu-Lin-Weng's method}

### 2025-06-13 lda.R
Fix Experiment 4: change of priors

@@ -1011,7 +1011,7 @@ bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
     dft <- dfs$test
     N <- nrow(dft)
     t2 <- truth[idx]
-    q <- sapply(1:length(t2), function(k) {
+    tuple_truth <- sapply(1:length(t2), function(k) {
             which(t2[k] == tuple) 
         })
 
@@ -1029,18 +1029,23 @@ bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
             #w[which(n == triple)] = (1 + add)
             # p <- w * p
             wp <- p
-            old_predictions <- apply(p, 1, which.max)
-            wp[, it] = (1 + add) * wp[,it]
+            old_predictions <- apply(p[idx,], 1, which.max)
+            wp[idx, it] = (1 + add) * wp[idx, it]
             # also could use t(w * t(p))
-            predictions <- apply(wp, 1, which.max)
+            predictions <- apply(wp[idx,], 1, which.max)
             weight <- if_else (t2 == n, 1 + add, 1)
-            correct <- weight * (predictions[idx] == q)
-            acc <- sum(correct) / sum(weight[idx])
-            flipped = mean(predictions[idx] != old_predictions[idx])
+            correct <- weight * (predictions == tuple_truth)
+            # print(correct)
+            stopifnot(!is.na(correct))
+            acc <- sum(correct) / sum(weight)
+            print(sum(weight))
+            print(sum(correct))
+            stopifnot(!is.na(acc))
+            flipped = mean(predictions != old_predictions)
 
             p2 <- sapply(1:N, function(k) {
                 r2 <- r[,,k]
-                for (s in 1:3) {
+                for (s in 1:length(tuple)) {
                     if (s == it) 
                         next
                     r2[it, s] = r2[it,s] + log((1 + add))
@@ -1050,8 +1055,8 @@ bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
             }) |> t()
 
             pred <- apply(p2[idx,],1, which.max)
-            correct2 <- weight * (pred == q)
-            acc2 <- sum(correct2) / sum(weight[idx])
+            correct2 <- weight * (pred == tuple_truth)
+            acc2 <- sum(correct2) / sum(weight)
             data.frame(changed = n, factor = (1 + add) , binary = acc2, multi = acc, method = m, flipped = flipped)
         }) |>  list_rbind()
     }) |>  list_rbind()

### 2025-06-15 lda.R
Add more statitistics for evaluaing non-Bayes covariant methods

@@ -997,6 +997,16 @@ hinton <- function(dfs) {
     list(triple = triple1, multi = multi)
 }
 
+bc_dataset <- function(dataset, workers = 12, add = 9) {
+    plan(multicore, workers = workers)
+    df <- future_map(0:19 , function(run) {
+        dfs <- read_wlws(800, dataset, run)
+        df1 <- bc_tuple(dfs, 1:max(dfs$train$class_id), add = add)
+        df1 |> mutate(run = run)
+    }) |> list_rbind() |> 
+        mutate(dataset = dataset)
+}
+
 bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
     stopifnot(all(as.logical(sapply(ns, function(n) n %in% tuple))))
     df1 <- dfs$train
@@ -1041,7 +1051,7 @@ bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
             print(sum(weight))
             print(sum(correct))
             stopifnot(!is.na(acc))
-            flipped = mean(predictions != old_predictions)
+            c2c0 = mean(predictions != old_predictions)
 
             p2 <- sapply(1:N, function(k) {
                 r2 <- r[,,k]
@@ -1055,9 +1065,11 @@ bc_tuple <- function(dfs, tuple, ns = tuple, add = 2) {
             }) |> t()
 
             pred <- apply(p2[idx,],1, which.max)
+            c1c0 = mean(pred != old_predictions)
+            c2c1 = mean(predictions != pred)
             correct2 <- weight * (pred == tuple_truth)
             acc2 <- sum(correct2) / sum(weight)
-            data.frame(changed = n, factor = (1 + add) , binary = acc2, multi = acc, method = m, flipped = flipped)
+            data.frame(changed = n, factor = (1 + add) , binary = acc2, multi = acc, method = m, c2c0 = c2c0, c1c0 = c1c0, c2c1 = c2c1)
         }) |>  list_rbind()
     }) |>  list_rbind()
 }

### 2025-06-16 exp4.R
First part of the last experiment

@@ -1,0 +1,9 @@
+source("lda.R")
+
+# df1 <- bc_dataset("mnist")
+# df2 <- bc_dataset("satimage")
+
+df <- map(files, function(f) bc_dataset(f)) |> list_rbind()
+
+#write.csv(rbind(df1, df2), file = "data/exp4.csv")
+write.csv(df, file = "data/exp4.csv")

### 2025-06-16 tab-exp4.R

@@ -1,0 +1,18 @@
+library(tidyr)
+library(dplyr)
+library(xtable)
+
+
+
+df <- read.csv("data/exp4.csv")
+
+df1 <- df |> group_by(dataset, method) |> 
+    summarize(c2c1 = mean(c2c1)) |> pivot_wider(names_from = "dataset", values_from = c2c1)
+# colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
+sink("tab-exp4.tex")
+print(xtable(df1, label = "tab:exp4", digits = 3,
+             caption = "Comparison of the difference in accuracies between methods $\\boldsymbol{c}_1$ and
+             $\\boldsymbol{c}_2$"
+),  include.rownames = FALSE)
+sink()
+

### 2025-06-16 experiment.tex

@@
 
-These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.
+These questions will be put to test in Sections \ref{sec:exp1} --\ref{sec:exp4}.
 
-\subsection{Experiment: Accuracy of canonical coupling methods on benchmark datasets} \label{sec:exp1}
+\subsection{Experiment: Accuracy of canonical coupling methods} \label{sec:exp1}
 
@@
 \subsection{Experiment: A parametric family of Bayes covariant methods}
+\label{sec:exp3}
 
@@
 
-\subsection{Experiment: Effect of change of priors}  \label{sec:exp3}
+\subsection{Experiment: Effect of change of priors}  \label{sec:exp4}
 %\subsection{Wu-Lin-Weng's method}
+
+We have shown that are situations when Wu-Lin-Weng's method outperforms even the best Bayes-covariant parametric methods.
+In this section we thus ponder the question whether some non-Bayes covariant method would be more resilients to change of priors.
+We consider two facets to this question.
+
+Let us start with some notation.
+Consider a classification method $\boldsymbol{c}_0$ based on coupling.
+Suppose the priors change, and let us denote by $\boldsymbol{c}_1$ the classification model where we apply \eqref{eq:changePrior} to binary classifiers, and by $\boldsymbol{c}_2$ the classification method when we apply \eqref{eq:changePrior} after coupling.
+
+The first question is whether for some coupling method the difference in predictions between $\boldsymbol{c}_1$ and $\boldsymbol{c}_2$ would be smaller. The results are shown in Table \ref{tab:exp4}.
+
+\input tab-exp4.tex
+
+The second question is whether a coupling method would more consistently provide true answers. Let us remark that Assumption 1 is inconsistent with ground truth being certain. But we may

### 2025-06-16 lda.R
Fix bug in write_triples

@@ -17,6 +17,7 @@ files <- c( "dna",
 dataset_names <- function() {
     fs <- dir("unzips/n800", pattern = "*.t-\\d*")
     m1 <- str_match(fs, "(.*).scale.t-(\\d+)")
+    # print(unique(m1[,2]))
     unique(m1[,2])
 }
 
@@ -555,8 +556,10 @@ write_multi <- function(runs = 20, workers = 11, tol = 1/2^(2:12), score = "acc"
 
 write_triples <- function(runs = 20, workers = 11) {
     plan(multicore, workers = workers)
-    df <- map(dataset_names(), files, function(f) {
-        future_map(0:(runs - 1), function (r) {
+    n1 <- dataset_names()
+    df <- map(dataset_names(), function(f) {
+        print(f)
+        map(0:(runs - 1), function (r) {
             dfs <- read_wlws(800, f, r)
             df1 <- lda_triples(dfs) |> 
                 pivot_wider(names_from = "method", values_from = "acc")

### 2025-06-16 lda.R
Add parallel execution

@@ -559,7 +559,7 @@ write_triples <- function(runs = 20, workers = 11) {
     n1 <- dataset_names()
     df <- map(dataset_names(), function(f) {
         print(f)
-        map(0:(runs - 1), function (r) {
+        future_map(0:(runs - 1), function (r) {
             dfs <- read_wlws(800, f, r)
             df1 <- lda_triples(dfs) |> 
                 pivot_wider(names_from = "method", values_from = "acc")

### 2025-06-19 exp4-truth.R
Move graphs to the current directory; add graph for truth

@@ -1,0 +1,19 @@
+library(ggplot2)
+library(dplyr)
+
+df <- read.csv("data/exp4.csv") |> mutate(diff = multi-binary) |> mutate(step2 = multi) |> mutate(step1 = binary)
+df$class = as.factor(df$changed - 1)
+
+df1 <- df |> filter(dataset ==  "mnist")
+
+plt1 <- ggplot(df1, aes(x = class, y = step2 - step1, color = method)) +  facet_wrap(~ method) + 
+geom_col(data = df1, aes(x = class, y = step2 - step1, color = method), fill = "black", width = 0.7) +
+theme_minimal() + ylab("count")
+
+ggsave(
+    filename = "exp4-truth.pdf",
+    plot = plt1,
+    width = 5.5,
+    height  = 2.5,
+    units = "in"
+    )

### 2025-06-20 intro.tex
Split intro

--- 2025-05-28 paper.tex
@@
-\documentclass[twoside,11pt]{article}
-
-\usepackage{blindtext}
-
-% Any additional packages needed should be included after jmlr2e.
-% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
-% and defines many common macros, such as 'proof' and 'example'.
-%
-% It also sets the bibliographystyle to plainnat; for more information on
-% natbib citation styles, see the natbib documentation, a copy of which
-% is archived at http://www.jmlr.org/format/natbib.pdf
-
-% Available options for package jmlr2e are:
-%
-%   - abbrvbib : use abbrvnat for the bibliography style
-%   - nohyperref : do not load the hyperref package
-%   - preprint : remove JMLR specific information from the template,
-%         useful for example for posting to preprint servers.
-%
-% Example of using the package with custom options:
-%
-% \usepackage[abbrvbib, preprint]{jmlr2e}
-
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{jmlr2e}
-
-\usepackage{multirow}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{rotating}
-\usepackage{tikz-cd}
-\usepackage[utf8]{inputenc} % Enable UTF-8 encoding
-\usepackage[T1]{fontenc}
-\usepackage{textgreek}
-
-\newtheorem{prop}{Proposition}
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}{Lemma}
-\newtheorem{assumption}{Assumption}
-
-% Definitions of handy macros can go here
-
-\newcommand{\dataset}{{\cal D}}
-\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-\DeclareMathOperator*{\divm}{div}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
-
-\usepackage{lastpage}
-\jmlrheading{23}{2025}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Probabilistic OVO}{Probabilistic OVO}
-\firstpageno{1}
-
-\begin{document}
-
-\title{On selection of a coupling method to cope with change of priors in one-vs-one classification }
-
-\author{\name Ondrej Šuch \email ondrejs@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       \AND
-       \name Peter Novotný \email peter.novotny@fri.uniza.sk \\
-       \addr Fakulta informatiky a riadenia\\
-       Žilinská Univerzita v Žiline\\
-       Žilina, 010 26, Slovakia
-       \AND
-       \name Ali Haidar \email haidar@savbb.sk \\
-       \begin{minipage}[t]{0.45\textwidth}
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       \end{minipage}\hfill
-       \begin{minipage}[t]{0.45\textwidth}
-       \addr Fakulta matematiky, fyziky a informatiky\\
-       Univerzity Komenského \\
-       Mlynská dolina F1 \\
-       Bratislava, 842 48, Slovakia
-       \end{minipage}
-       }
-
-\editor{My editor}
-
-\maketitle
-
-\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-\blindtext
-\end{abstract}
-
-\begin{keywords}
-  keyword one, keyword two, keyword three
-\end{keywords}
-
 \section{Introduction}
@@
 It is very unlikely to encounter 80mph limit in a city setting.
-By taking into account the city priors, a driver assistance is likely to make the proper classification.
-In general a good classification system will be able to improve its performance when supplied with a new set of class priors that correspond to the true distribution of classes.
+By taking into account the city priors, the system is likely to make the proper classification.
+In general a well-designed classification system will be able to improve its performance when supplied with a new set of class priors that correspond to the true distribution of classes.
 
 Change of priors can be effectively dealt with in probabilistic classifiers.
-The basic idea is that Bayes theorem stipulates \emph{exactly} what should happen  to the prediction of the  Bayes classifier when priors change.
+The basic idea is that Bayes theorem stipulates \emph{exactly} what should happen  to the prediction of the  Bayes classifier when priors change (see \eqref{eq:changePrior}).
 In practice we assume that a trained classifier closely approximates the Bayes classifier.
@@
 In Section 6 we summarize our findings and provide practical guidance to solving the problem.
-
-\input theory.tex
-
-\input coupling.tex
-
-\input experiment.tex
-
-\input discussion.tex
-
-% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references
-
-\acks{All acknowledgements go at the end of the paper before appendices and references.
-Moreover, you are required to declare funding (financial activities supporting the
-submitted work) and competing interests (related financial activities outside the submitted work).
-More information about this disclosure can be found on the JMLR website.}
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
-
-\input appendix.tex
-
-\vskip 0.2in 
-\bibliography{paper}
-
-\end{document}

### 2025-06-20 paper.tex
Split intro

--- 2025-05-27 paper.tex
@@
 
-\title{On selection of a coupling method to cope with change of priors in one-vs-one classification }
+\title{New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification }
 
@@
 \begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-\blindtext
+%\blindtext
+Label shift is one kind of distribution shift affecting classification models. Generally, one uses transformation inspired by Bayes classifiers to 
+adjust predictions of probabilistic classification models.
+However, there is an ambiguity how to apply this transformation in the case of  probabilistic models built in one-vs-one (also called pairwise) fashion.
+One-vs-one classification relies on the choice of a coupling method.
+Some coupling methods -- called Bayes covariant --  are not affected by the ambiguity.
+Adopting a Bayes covariant method would be the ideal solution to the ambiguity.
+However, the most commonly used coupling  method of Wu-Lin-Weng is not Bayes covariant.
+In our study we present elements of theory of coupling methods and exhibit new Bayes covariant coupling methods.
+One class is formed by arboreal methods.
+Still more methods can be formed by the way of ensembling.
+We compare their performance with that of Wu-Lin-Weng's coupling method.
+In majority of cases, it is possible to find a Bayes covariant method matching performance of Wu-Lin-Weng's method.
+
 \end{abstract}
@@
 \begin{keywords}
-  keyword one, keyword two, keyword three
+  distribution shift, label shift, pairwise coupling, one-vs-one classification, Bayes classifier
 \end{keywords}
 
-\section{Introduction}
-
-%\blindmathpaper
-
-Distribution shift is an important problem facing machine-learning practitioners  [\cite{zhang2023dive, sugiyama2007covariate}].
-One particular way a distribution shift may manifest in classification problems  is when the class priors change between the training set used to train a model, and the data distribution in deployment -- the so called label shift [\cite{vsipka2022hitchhiker,lipton2018detecting}].
-To make a concrete example, consider a driver assistance system recognizing traffic signs.
-Suppose a speed limit sign was maliciously altered to indicate 80mph limit instead of 30mph.
-To avoid being fooled by the alteration, the system could utilize priors.
-The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city.
-It is very unlikely to encounter 80mph limit in a city setting.
-By taking into account the city priors, a driver assistance is likely to make the proper classification.
-In general a good classification system will be able to improve its performance when supplied with a new set of class priors that correspond to the true distribution of classes.
-
-Change of priors can be effectively dealt with in probabilistic classifiers.
-The basic idea is that Bayes theorem stipulates \emph{exactly} what should happen  to the prediction of the  Bayes classifier when priors change.
-In practice we assume that a trained classifier closely approximates the Bayes classifier.
-Therefore we can make adjustment to our prediction by applying the same transformation of posterior as would happen with the Bayes classifier.
-
-There is a subtle issue with this approach  when handling probabilistic classifiers arising in one-vs-one classification framework.
-One-vs-one classification is a two-step framework to approach  multi-class classification.
-In the first step it reduces the multiclass problem to a series of binary classification problems.
-In the second step it deduces the multi-class decision by aggregating decisions for the binary problems.
-Since the procedure is two-step, there is a possibility to apply adjustment of priors either to the probabilistic distributions obtained after the first step, or after the second step.
-It is not clear what should be the preferred course of action and this problem motivates our paper.
-
-The focus of efforts is in presenting and evaluating the methods to aggregate binary predictions.
-We formulate the underlying principles of one-vs-one probabilistic classification in Section 2.
-Section is 3 is devoted to presenting different classes that one
+\input intro.tex
 

### 2025-06-20 discussion.tex
More discussion

@@
 
-Let us discuss our findings with the focus on applications.
+In this paper we set out to investigate the curious phenomenon of divergent prediction in one-vs-one probabilistic models. Let us first summarize the new results we have uncovered.
+
+In Section \ref{sec:theory} we have formulated the theoretical basis of one-vs-one classification.
+In Section \ref{sec:des:exact} we put down the basis for axiomatic development of coupling methods.
+In complementary Section \ref{sec:des:inexact} we formulated properties of coupling methods that are likely of importance in practice.
+
+Important examples of coupling methods has been presented in Section \ref{sec:coupling}.
+We were able to provide a unifying formulation for method of Hastie-Tibshirani and Wu-Lin-Weng.
+We discusses arboreal coupling methods, which are an important example of methods without parameters, albeit noncanonical.
+We recast previously known normal coupling method in a new way.
+Although this is a canonical example of Bayes covariant coupling methods,  it is lacking in practical performance, as  we uncovered in the experimental section.
+This creates impetus to study more general Bayes covariant method.
+The  ensembling approach we proposed in Section \ref{sec:bc2} allows one to build parametric families of Bayes covariant methods.
+
+The results highlight key findings from the experimental section.
+
+\begin{itemize}
+	\item The orthodox method of Wu-Lin-Weng dominates others across diverse classification tasks.
+	\item The only method close to Wu-Lin-Weng is the radial coupling method.
+	\item The concern of Hinton about one-vs-one classification is unwarranted.
+The method that ignores binary classifiers not trained on a given sample (we call it Hinton's oracle) underperforms the method of Wu-Lin-Weng.
+	\item In more than half of classification problems we were able to find a Bayes covariant coupling method which matches performance of the Wu-Lin-Weng method. 
+\end{itemize}
+
+Let us now turn to recommendation to practitioners. Given
 

### 2025-06-20 paper.tex
Grant number

@@
 
-\acks{All acknowledgements go at the end of the paper before appendices and references.
-Moreover, you are required to declare funding (financial activities supporting the
-submitted work) and competing interests (related financial activities outside the submitted work).
-More information about this disclosure can be found on the JMLR website.}
+\acks{Research on this paper was partially supported by grant VEGA 2/0172/22 Classification using ensembles of neural networks.  }
 

### 2025-06-20 intro.tex
Added references to the intro

@@
 Distribution shift is an important problem facing machine-learning practitioners  [\cite{zhang2023dive, sugiyama2007covariate}].
-One particular way a distribution shift may manifest in classification problems  is when the class priors change between the training set used to train a model, and the data distribution in deployment -- the so called label shift [\cite{vsipka2022hitchhiker,lipton2018detecting}].
-To make a concrete example, consider a driver assistance system recognizing traffic signs.
+Using probabilistic formulation, we say the distribution shift occurs if there is a change  in the joint probability distribution $p(X,Y)$ of covariates $X$ with the dependent variable $Y$  between training and testing.
+Noting the factorizations
+$$
+p(X,Y) = p(Y\mid X)p(X) = p(X \mid Y )p(Y)
+$$
+one may distinguish the following subcategories of distribution shift:
+\begin{itemize}
+	\item covariate shift, if $p(X)$ changes, but $p(Y\mid X)$ is unchanged,
+	\item label shift, if $p(Y)$ changes, but $P(X \mid Y)$ remains the same,
+	\item concept shift, if $p(Y \mid X)$ itself changes.
+\end{itemize}
+
+We will be concerned with label shift in classification problems, where $p(Y)$ is just the prior on classes.
+To provide a concrete example, consider a driver assistance system recognizing traffic signs.
 Suppose a speed limit sign was maliciously altered to indicate 80mph limit instead of 30mph.
@@
 There is a subtle issue with this approach  when handling probabilistic classifiers arising in one-vs-one classification framework.
-One-vs-one classification is a two-step framework to approach  multi-class classification.
+One-vs-one classification is a two-step framework to solve  multi-class classification problems.
 In the first step it reduces the multiclass problem to a series of binary classification problems.
 In the second step it deduces the multi-class decision by aggregating decisions for the binary problems.
-Since the procedure is two-step, there is a possibility to apply adjustment of priors either to the probabilistic distributions obtained after the first step, or after the second step.
+Since the procedure is two-step, there is a possibility to apply the adjustment of priors either to the probabilistic distributions obtained after the first step, or after the second step.
 It is not clear what should be the preferred course of action and this problem motivates our paper.
+
+Some aspects of label shift were studied in earlier works including test time adaptation
+[\cite{vsipka2022hitchhiker}], shift detection and quantification [\cite{lipton2018detecting}], statistical properties of label shift estimators [\cite{garg2020unified}], and Fisher consistency of estimators of priors [\cite{tasche2017fisher}].
 

### 2025-06-24 single.py
File to convert paper to a single latex file

@@ -1,0 +1,67 @@
+import os
+import re
+import sys
+
+def process_tex_file(filepath: str) -> str:
+    """
+    Recursively processes a LaTeX (.tex) file, replacing \input{} commands
+    with the content of the specified input files.
+
+    Args:
+        filepath (str): The path to the LaTeX file to process.
+
+    Returns:
+        str: The fully processed content of the LaTeX file.
+    """
+    if not os.path.exists(filepath):
+        print(f"Warning: File not found - {filepath}. Skipping input.", file=sys.stderr)
+        return ""
+
+    try:
+        with open(filepath, 'r', encoding='utf-8') as f:
+            lines = f.readlines()
+    except Exception as e:
+        print(f"Error reading file {filepath}: {e}", file=os.stderr)
+        return ""
+
+    processed_content = []
+    # Regex to find \input{filename} or \input{filename.tex}
+    # It captures the filename inside the curly braces.
+    input_pattern = re.compile(r'\\input\{(.*?)\}')
+
+    for line in lines:
+        match = input_pattern.search(line)
+        if match:
+            # Extract the filename from the match object
+            input_filename = match.group(1)
+
+            # Construct the full path for the input file
+            # Assuming input files are relative to the current file's directory
+            current_dir = os.path.dirname(filepath)
+            
+            # Add .tex extension if it's missing, as common in LaTeX
+            if not input_filename.endswith('.tex'):
+                input_filename += '.tex'
+            
+            full_input_path = os.path.join(current_dir, input_filename)
+
+            print(f"Processing \\input: {full_input_path}")
+            # Recursively process the input file and append its content
+            processed_content.append(process_tex_file(full_input_path))
+        else:
+            # If no \input command, append the line as is
+            processed_content.append(line)
+
+    return "".join(processed_content)
+
+if __name__ == "__main__":
+    print("--- Starting LaTeX File Processing ---")
+    output_content = process_tex_file("springer.tex")
+    print("\n--- Processed Content ---")
+    print(output_content)
+
+    # Optionally, save the output to a new file
+    output_filename = "springer_full.tex"
+    with open(output_filename, "w", encoding="utf-8") as f:
+        f.write(output_content)
+    print(f"\nProcessed content saved to {output_filename}")

### 2025-06-26 intro.tex
Change cite

@@
 Some aspects of label shift were studied in earlier works including test time adaptation
-[\cite{vsipka2022hitchhiker}], shift detection and quantification [\cite{lipton2018detecting}], statistical properties of label shift estimators [\cite{garg2020unified}], and Fisher consistency of estimators of priors [\cite{tasche2017fisher}].
+\cite{vsipka2022hitchhiker}, shift detection and quantification \cite{lipton2018detecting}, statistical properties of label shift estimators \cite{garg2020unified}, and Fisher consistency of estimators of priors \cite{tasche2017fisher}.
 
@@
 Such methods -- called coupling methods -- first appeared in work of \cite{refregier1991probabilistic}.
-Many authors followed with alternative proposals [\cite{price1994pairwise, hastie1998classification,  zahorian1999partitioned, wu2004probability, vsuch2015new, vsuch2016bayes}].
+Many authors followed with alternative proposals \cite{price1994pairwise, hastie1998classification,  zahorian1999partitioned, wu2004probability, vsuch2015new, vsuch2016bayes}.
 
@@
 The results of our experiments are described in Section 5.
-In Section 6 we summarize our findings and provide practical guidance to solving the problem.
+In Section 6 we summarize our findings, provide practical guidance and outline future research directions.

### 2025-06-26 coupling.tex
Fix cite

@@
 
-A notable example which uses this principle is the coupling method introduced in [\cite{hastie1998classification}]. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
+A notable example which uses this principle is the coupling method introduced in \cite{hastie1998classification}. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
 \begin{align*}
@@
 Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
-In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score [\cite{gneiting2007strictly, buja2005loss}].
+In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score \cite{gneiting2007strictly, buja2005loss}.
 
-For instance, a popular alternative is divergence arising from the quadratic  score [\cite{gneiting2007strictly}] (also known as Brier score [\cite{brier1950verification}]).
-This divergence takes the form
+For instance, a popular alternative is divergence arising from the quadratic  score \cite{gneiting2007strictly} (also known as Brier score \cite{brier1950verification}). This divergence takes the form
 $$
@@
 Unlike Kullback-Leibler divergence, the penalty for incorrect prediction with arbitrarily low probability is bounded (by one).
-This quadratic score is the basis of the popular Wu-Lin-Weng's method [\cite{wu2004probability}].
+This quadratic score is the basis of the popular Wu-Lin-Weng's method \cite{wu2004probability}.
 
@@
 We note that the method is symmetric.
-The choice of quadratic scoring rule can also be viewed as canonical in view of axiomatic characterization given in  [\cite{selten1998axiomatic}].
+The choice of quadratic scoring rule can also be viewed as canonical in view of axiomatic characterization given in  \cite{selten1998axiomatic}.
 However the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary.
@@
 \begin{align}
-\boldsymbol{e}_3 \stackrel{def}{=} \frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:bc1}
+\boldsymbol{e}_3 \stackrel{def}{=} \frac13 \boldsymbol{s}_1 \oplus \frac13 \boldsymbol{s}_2 \oplus \frac 13 \boldsymbol{s}_3  \label{eq:normal3}
 \end{align}
-is Bayes covariant \emph{and} symmetric. A key result proved in [\cite{vsuch2016bayes}] is that it is a unique  classifier having these two properties.
+is Bayes covariant \emph{and} symmetric. A key result proved in \cite{vsuch2016bayes} is that it is a unique  classifier having these two properties.
 
@@
 \caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.
-The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu-Lin-Weng [\cite{wu2004probability}].}
+The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu-Lin-Weng \cite{wu2004probability}.}
 \label{tab:summaryCoupling}

### 2025-06-26 experiment.tex
Add new figure

@@
 \begin{itemize}
-\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
-\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
+\item[a)] Which coupling methods without parameters show good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
+\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric Bayes covariant method which  matches its performance?
 \item[c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
@@
 
-The first question is whether for some coupling method the difference in predictions between $\boldsymbol{c}_1$ and $\boldsymbol{c}_2$ would be smaller. The results are shown in Table \ref{tab:exp4}.
+The first question is whether for some coupling method the difference in predictions (we call it \emph{spread}) between $\boldsymbol{c}_1$ and $\boldsymbol{c}_2$ would be smaller.
+To gauge this question we apply change of priors by increasing tenfold the prior for every class in turn.
+The averaged results are shown in Table \ref{tab:exp4}.
 
-\input tab-exp4.tex
+\input {tab-exp4.tex}
 
-The second question is whether a coupling method would more consistently provide true answers. Let us remark that Assumption 1 is inconsistent with ground truth being certain. But we may
+The results, as expected, detect no change between $\boldsymbol{c}_1, \boldsymbol{c}_2$ for normal coupling method.
+However, there is no consistent difference in spread between radial and Wu-Lin-Weng's coupling method.
+Spread for the radial method is lower for 3 datasets (letter, mnist, usps datasets), higher for 3 datasets (dna, satimage, segment) and tied for waveform dataset.
+
+The second question is whether a coupling method would more consistently provide true answers.
+Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large.
+Thus to evaluate this question
+
+\begin{figure}[!ht]
+	\includegraphics{exp4-truth.pdf}
+	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for radial and Wu-Lin-Weng's coupling method.}
+	\label{fig:score}
+\end{figure}

### 2025-06-26 theory.tex
Various fixes
Change reference to the fundamental theorem

@@
-\section{Theoretical basis of coupling methods}
+\section{Theoretical basis of coupling methods} \label{sec:theory}
 
@@
 \begin{assumption} \label{ass:1}
-For all $x$ in the feature space we have $d_i(x) > 0$.
+For all $x$ in the feature space we have $d_i(x) P_i > 0$.
 \end{assumption}
@@
 
-Conversely, it is easy to show that  the system of equations \eqref{eq:bt1} has a unique solution.
+Conversely, it is easy to show that  given values of $p_{ij}(x)$ the system of equations \eqref{eq:bt1} has a unique solution.
+This result (Proposition \ref{prop:binary2multi}) can be viewed as the fundamental theorem of one-vs-one classification.
 
-\begin{prop}[Fundamental theorem of one-vs-one classification]
+\begin{prop}
 	 \label{prop:binary2multi}
@@
 	\begin{align}
-	\alpha_{ij}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p_{ij}(x)}- 1.
+	\alpha_{ji}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_i^\Pi(x)} = \frac{1}{p_{ij}(x)}- 1.
 	\end{align}
@@
 \begin{align}
-D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr).
+D^\pi \propto \biggl(p_1 \frac{P'_1}{P_1}, \ldots, p_K \frac{P'_K}{P_K}\biggr). \label{def:prior:effect}
 \end{align}

### 2025-06-26 theory.tex
Fix par references

@@
 Note that potentially there may be multiple canonical methods, derived from (or satisfying) differing sets of assumptions.
-For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical [\cite{shannon1948mathematical,selten1998axiomatic}].
+For instance, in the theory of scoring rules, both logarithmic and quadratic scores can be viewed as canonical \cite{shannon1948mathematical,selten1998axiomatic}.
 
@@
 
-\emph{Bayes covariance} is a notion introduced in  [\cite{vsuch2016bayes}].
+\emph{Bayes covariance} is a notion introduced in  \cite{vsuch2016bayes}.
 It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
@@
 A historical  example to follow is linear discriminant (LDA) of  Sir Ronald Fisher.
-At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists.
+At the time he was submitting his paper describing LDA, he had confirmed usefulness of his method not only on the famous iris dataset, but also on two separate collaborations with archaeologists \cite{barnard1935secular, martin1936study}.
 
@@
 Let us finally mention \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction [\cite[p.~467]{hastie1998classification}].
+Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction \cite[p.~467]{hastie1998classification}.
 Suppose we are classifying objects from CIFAR-10 dataset.

### 2025-07-15 intro.tex
Addressing Peters' review

@@
 
-We formulate the underlying principles of one-vs-one probabilistic classification in Section 2.
-In Section 3 we present  different classes of coupling methods.
-We pay special focus to methods that commute with change of priors -- Bayes covariant methods, since such methods provide an unexpected, and elegant solution to our problem.
-We introduce new coupling methods by forming weighted ensembles, which we prove are also Bayes covariant when a normalizing condition on weights hold (Proposition \ref{prop:ensemble}).
-In Section 4 we summarize our methodology.
-The results of our experiments are described in Section 5.
-In Section 6 we summarize our findings, provide practical guidance and outline future research directions.
+We formulate the underlying principles of one-vs-one probabilistic classification in Section 2. In Section 3 we present  different classes of coupling methods. 
+We pay special attention to methods that commute with change of priors -- Bayes covariant methods, 
+since such methods provide an unexpected, and elegant solution to our problem. 
+We introduce new coupling methods by forming weighted ensembles. We prove such ensemble of Bayes covariant methods is again Bayes covariant
+when a normalizing condition on weights hold (Proposition \ref{prop:ensemble}).  
+Our experiments are described in Section 4. In Section 5 we summarize our findings, 
+provide practical guidance and outline future research directions.

### 2025-07-15 intro.tex
Include proper prerequisities;

@@
 
-Distribution shift is an important problem facing machine-learning practitioners  [\cite{zhang2023dive, sugiyama2007covariate}].
+Distribution shift is an important problem facing machine-learning practitioners 
+\cite{zhang2023dive, sugiyama2007covariate}.
 Using probabilistic formulation, we say the distribution shift occurs if there is a change  in the joint probability distribution $p(X,Y)$ of covariates $X$ with the dependent variable $Y$  between training and testing.
@@
 
-We will be concerned with label shift in classification problems, where $p(Y)$ is just the prior on classes.
+We will be concerned with label shift in classification problems, where $p(Y)$ 
+is just the prior on classes.  Some aspects of label shift were studied in
+earlier works including test time adaptation
+\cite{vsipka2022hitchhiker}, shift detection and quantification 
+\cite{lipton2018detecting}, 
+statistical properties of label shift estimators \cite{garg2020unified}, 
+and Fisher consistency of estimators of priors \cite{tasche2017fisher}. 
+Let us consider  the question 
+how to adapt a classifier when the  prior is updated.
+
 To provide a concrete example, consider a driver assistance system recognizing traffic signs. 
@@
 The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city.
-It is very unlikely to encounter 80mph limit in a city setting.
-By taking into account the city priors, the system is likely to make the proper classification.
-In general a well-designed classification system will be able to improve its performance when supplied with a new set of class priors that correspond to the true distribution of classes.
+unlikely to encounter 80mph limit in a city setting. By taking into account 
+the city priors, the system would be more likely to make the proper classification.
 
-Change of priors can be effectively dealt with in probabilistic classifiers.
-The basic idea is that Bayes theorem stipulates \emph{exactly} what should happen  to the prediction of the  Bayes classifier when priors change (see \eqref{eq:changePrior}).
-In practice we assume that a trained classifier closely approximates the Bayes classifier.
-Therefore we can make adjustment to our prediction by applying the same transformation of posterior as would happen with the Bayes classifier.
+Some systems are unable to do incorporate new priors without rebuilding 
+the classifier  e.g. those based 
+on fuzzy logic, or some tree methods. 
+However, change of priors can be effectively dealt with in probabilistic 
+classifiers. The basic idea is that Bayes theorem stipulates \emph{exactly} 
+what should happen  to the prediction of the  Bayes classifier when priors 
+change (see \eqref{eq:changePrior}).  In practice we assume that a trained 
+classifier closely approximates the Bayes classifier. Therefore we can make 
+adjustment to our prediction by applying the same transformation of posterior 
+as would happen with the Bayes classifier.
 
-There is a subtle issue with this approach  when handling probabilistic classifiers arising in one-vs-one classification framework.
-One-vs-one classification is a two-step framework to solve  multi-class classification problems.
-In the first step it reduces the multiclass problem to a series of binary classification problems.
-In the second step it deduces the multi-class decision by aggregating decisions for the binary problems.
-Since the procedure is two-step, there is a possibility to apply the adjustment of priors either to the probabilistic distributions obtained after the first step, or after the second step.
-It is not clear what should be the preferred course of action and this problem motivates our paper.
+There is a subtle issue with this approach  when handling probabilistic 
+classifiers arising in one-vs-one classification framework.   
+One-vs-one classification is a two-step framework to solve 
+multi-class classification problems.
+In the first step it reduces the multiclass problem to a series of binary
+classification problems. 
+In the second step it deduces the multi-class decision by aggregating decisions 
+for the binary problems. Since the procedure is two-step, there is a possibility 
+to apply the adjustment of priors either to the probabilistic distributions 
+obtained after the first step, or after the second step. It is not clear what 
+should be the preferred course of action and this problem motivates our paper.
 
-Some aspects of label shift were studied in earlier works including test time adaptation
-\cite{vsipka2022hitchhiker}, shift detection and quantification \cite{lipton2018detecting}, statistical properties of label shift estimators \cite{garg2020unified}, and Fisher consistency of estimators of priors \cite{tasche2017fisher}.
-
-Our approach to the problem is to evaluate practical performance of different methods to aggregate binary predictions.
-Such methods -- called coupling methods -- first appeared in work of \cite{refregier1991probabilistic}.
-Many authors followed with alternative proposals \cite{price1994pairwise, hastie1998classification,  zahorian1999partitioned, wu2004probability, vsuch2015new, vsuch2016bayes}.
+Our approach to the problem is to evaluate practical performance of different 
+methods to aggregate binary predictions. Such methods -- called coupling methods
+-- first appeared in work of \cite{refregier1991probabilistic} when making 
+multi-class classification using neural networks. 
+Many authors followed with alternative proposals 
+\cite{price1994pairwise, hastie1998classification,  zahorian1999partitioned,
+wu2004probability, vsuch2015new, vsuch2016bayes}.
 

### 2025-07-16 theory.tex
Theory changes

@@
 
-Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature space $X$.
-In a multi-class classification problem we are provided with the prior probabilities $\Pi = (P_1, \ldots, P_k)$ of each class.
-Given $x$ in $X$ we aim to find the probability that $x$ belongs to $i$-th class.
+Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature 
+space $X$. In a multi-class classification problem we are provided with 
+the prior probabilities $\Pi = (P_1, \ldots, P_K)$ of each class. Given $x$ in $X$ we aim to find 
+the probability that $x$ belongs to the $i$-th class.
 
@@
 \begin{align}
- p^\Pi_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
+ p^\textrm{multi}_i(x) = \frac{d_i(x) P_i}{\sum_{k=1}^K d_k(x)P_k}.
 \end{align}
 
-Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of classes.
-Assuming prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier predicts the probability of $i$-th class as
+Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of 
+classes. Assuming the prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier 
+predicts the probability of the $i$-th class as
 
 \begin{align}
-	p_{ij}(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
+	p_{ij}^\textrm{binary}(x) = \frac{d_i(x) P_i}{d_i(x)P_i + d_j(x)P_j}.
 \end{align}
 
-Knowledge of vector $\boldsymbol{p}^\Pi(x)$ is equivalent to knowing the functions $p^\Pi_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
+Knowledge of vector $\boldsymbol{p}^\textrm{multi}(x)$ is equivalent to knowing the functions $p^\textrm{binary}_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
 \begin{align}
-p_{ij}(x) = \frac{p_i^\Pi(x)}{p_i^\Pi(x) + p_j^\Pi(x)}. \label{eq:bt1}
+p_{ij}^\textrm{binary}(x) = \frac{p_i^\textrm{multi}(x)}{p_i^\textrm{multi}(x) + p_j^\textrm{multi}(x)}. \label{eq:bt1}
 \end{align}
@@
 	 \label{prop:binary2multi}
-	 Knowledge of binary Bayes classifiers $p_{ij}$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
+	 Knowledge of binary Bayes classifiers $p^\textrm{binary}_{ij}$ determines the multiclass Bayes classifier 
+	 $\boldsymbol{p}^\textrm{multi}$.
 \end{prop}
@@
 	\begin{align}
-	\alpha_{ji}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_i^\Pi(x)} = \frac{1}{p_{ij}(x)}- 1.
+	\alpha_{ji}(\boldsymbol{p}^\textrm{multi}) = \frac{p_j^\textrm{multi}(x)}{p_i^\textrm{multi}(x)}
+	=  \frac{d_j(x) P_j}{d_i(x) P_i} = \frac{1}{p^\textrm{binary}_{ij}(x)}- 1.
 	\end{align}
@@
 
-In practice one does not have know true probability distributions and hence cannot construct Bayes classifies.
-However, given a sample from the distribution, we can train binary classifiers to provide approximations $r_{ij}(x)$ to pairwise Bayes classifiers $p_{ij}^\Pi(x)$.
-The goal of probabilistic one-vs-one classification is to deduce for any $x$ in the feature space $X$ an estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\Pi(x)$.
+In practice one does not  know true distributions of samples and hence cannot 
+construct Bayes classifiers. However, given a sample from the distribution, 
+we can train binary classifiers to provide approximations $r_{ij}(x)$ to 
+pairwise Bayes classifiers $p_{ij}^\textrm{multi}(x)$. The goal of probabilistic
+one-vs-one classification is to deduce for any $x$ in the feature space $X$ an 
+estimate $\hat{\boldsymbol{p}}(x)$ for $\boldsymbol{p}^\textrm{multi}(x)$. 
 One does it by finding an approximate solution of the system of equations
@@
  we will describe exact mathematical criteria that one may impose on a coupling method, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
+
+\begin{itemize}
+\item  unique solution(under Assumption \ref{ass:2}),
+\item Bradley-Terry consistency,
+\item canonicity,
+\item symmetry,
+\item Bayes covariance.
+\end{itemize}
 
@@
 \end{align}
-We now say that a method if Bayes covariant if
+We now say that a method is Bayes covariant if
 \begin{align}
@@
 
-\emph{Good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
+\emph{Robustness -- good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
 This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform.

### 2025-07-16 coupling.tex
Notation fixes

@@
 \begin{align*}
-	\hat D_{ij}^\textrm{multi}= \biggl(\frac{\hat{p_i}}{\hat p_i + \hat p_j},\frac{\hat{p_j}}{\hat p_i + \hat p_j}\biggr)	
+	\boldsymbol{d}_{ij}^\textrm{multi}= \biggl(\frac{\hat{p_i}}{\hat p_i + \hat p_j},\frac{\hat{p_j}}{\hat p_i + \hat p_j}\biggr)	
 \end{align*}
@@
 \begin{align*}
-\hat D_{ij}^\textrm{binary} = (\hat r_{ij}, \hat r_{ji}).
+\boldsymbol{d}_{ij}^\textrm{binary} = ( r_{ij},  r_{ji}).
 \end{align*}
@@
 \begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\hat D_{ij}^\textrm{multi}, \hat D_{ij}^\textrm{binary})
+\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\boldsymbol{d}_{ij}^\textrm{multi}, \boldsymbol{d}_{ij}^\textrm{binary})
 \end{align*}
@@
 \begin{align*}
-	\divm\nolimits_\textrm{KL} (\boldsymbol{p}, \boldsymbol{q})= \sum p_i \log (p_i/ q_i)
+	\divm\nolimits_\textrm{KL} (\boldsymbol{d}, \boldsymbol{d'})= \sum d_i \log (d_i/ d'_i)
 \end{align*}
@@
 $$
-Unlike Kullback-Leibler divergence, the penalty for incorrect prediction with arbitrarily low probability is bounded (by one).
-This quadratic score is the basis of the popular Wu-Lin-Weng's method \cite{wu2004probability}.
 
+The quadratic score is the basis of the popular Wu-Lin-Weng's method \cite{wu2004probability}. 
 Their method uses an additional trick, which we term \emph{self-referentiality}.
@@
 An arboreal coupling method ignores all but $K-1$ of the pairwise predictions.
-A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes 1 and 3.
+A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes $C_1$ and $C_3$.
 The two equations form \eqref{eq:bt2} together with the requirement that the prediction probabilities should sum to 1 yield the following system of equations
@@
 
-More generally, to obtain a regular system of equations for  any of $K$ , it is necessary that the tree corresponding to an arboreal method forms a spanning tree.
-Note that any arboreal method is non-canonical, because there is no natural way to choose a tree in a complete graph.
+More generally, to obtain a regular system of equations for  any of $K$ , it is necessary and sufficient that the tree formed by edges for which we include equations from Bradley-Terry system is  a spanning tree.
+Note that any arboreal method is non-canonical, because there is no natural way to choose a spanning tree in a complete graph.
 In fact, a stronger statement is true -- no arboreal method is symmetric.
@@
 Note that here we use the plus symbol to denote the vector addition of vectors representing  probability distributions over $K$ classes.
-This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.
+This is a different classifier from the one given by  \eqref{eq:normal3} , and since it is symmetric, it cannot be Bayes covariant.
 
@@
 We call this coupling method the \emph{normal} coupling method.
-
-\subsection{Properties of coupling methods}
-
-In this section  we summarize properties of coupling methods described earlier in this section.
-Table \ref{tab:summaryCoupling} concisely lists the relevant properties enjoyed by each method.
-Note that we have split the desideratum ``simplicity of computation'' into three different aspects:
-\begin{itemize}
-	\item whether a coupling method amounts to a linear system of equations,
-	\item if the coupling method amounts to a linear system of equations, whether the equations are of a special form (e.g. a Markov matrix) that facilitates their solution,
-	\item whether the authors who published the method provide an iterative method that implements the estimate.
-Iterative methods are often  faster than Gaussian elimination, and less prone to numerical issues.
-\end{itemize}
-
- %interpretation of exact desiderate is unambiguous.
-
-%The following table indicates which properties are enjoyed by each coupling method we described in this section.
-
-\begin{table}[!ht]
-\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
-&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
-\hline 
-\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
-&uniqueness &  yes & yes & yes & yes & yes & yes \\
-&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
-&canonicity & yes & no & yes & yes & no & yes \\
-&symmetry & yes & yes & yes & yes & no & yes \\
-& Bayes covariant & no & no & no & yes & yes & yes \\
-\hline
-\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
-&Hinton's minimality & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
-&robustness & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
-&lack of parameters & yes & yes & yes & yes & yes & yes \\
-& amounts to a linear system & no & yes & yes & yes & yes & yes\\
-& linear system of special form & N/A & no & yes & yes & yes & yes \\
-& iterative method & yes & yes & yes & no & not needed & not needed\\
-\hline
-\end{tabular}
-\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.
-The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu-Lin-Weng \cite{wu2004probability}.}
-\label{tab:summaryCoupling}
-\end{table}

### 2025-07-16 discussion.tex
Add discussion points

@@
 
-In this paper we set out to investigate the curious phenomenon of divergent prediction in one-vs-one probabilistic models. Let us first summarize the new results we have uncovered.
+In this paper we set out to investigate how to handle change of priors n in one-vs-one probabilistic models. Let us first summarize our contributions.
+
+\subsection{Theoretical insights}
 
@@
 
+\subsection{Experimental findings}
+
 The results highlight key findings from the experimental section.
@@
 
-Let us now turn to recommendation to practitioners. Given
+\subsection{Practical recommendation}
 
-One-vs-one classification framework is commonly used by machine learning practitioners, for instance whenever one uses radial basis function SVM implemented in  standard libraries.
+Let us now turn to recommendation to practitioners on how to handle change of priors in one-vs-one probabilistic models. It is possible to choose any of the following approaches
+
+\begin{itemize}
+\item[1.] One can treat the decision on when to apply change of priors -- whether before or after coupling -- as a boolean hyperparameter and use standard machine learning techniques to find the optimal value.
+\item[2.] One can investigate applicability of a Bayes covariant method.
+This may take two forms, either choose a Bayes covariant coupling method, or experiment with changing of algorithm to construct binary classifiers.
+\item[3.] Choose another multi-class probabilistic classification algorithm outside of one-vs-one framework. 
+\end{itemize}
+
+\subsection{Properties of coupling methods}
+
+In this section  we summarize properties of coupling methods discussed in our work.
+Table \ref{tab:summaryCoupling} concisely lists the relevant properties enjoyed by each method.
+Note that we have split the desideratum ``simplicity of computation'' into three different aspects:
+\begin{itemize}
+	\item whether a coupling method amounts to a linear system of equations,
+	\item if the coupling method amounts to a linear system of equations, whether the equations are of a special form (e.g. a Markov matrix) that facilitates their solution,
+	\item whether the authors who published the method provide an iterative method that implements the estimate.
+Iterative methods are often  faster than Gaussian elimination, and less prone to numerical issues.
+\end{itemize}
+
+%interpretation of exact desiderate is unambiguous.
+
+%The following table indicates which properties are enjoyed by each coupling method we described in this section.
+
+\begin{table}[!ht]
+	\begin{tabular}{cm{2.5cm}|m{1.5cm}|m{1.5cm}ccm{1.5cm}|m{1.5cm}}
+		&& less competitive & \multicolumn{4}{c|}{competitive method} & oracle \\
+		\hline 
+		&methods & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
+		\hline 
+		&source & \cite{hastie1998classification} & \cite{wu2004probability} & \cite{vsuch2015new} & \cite{vsuch2016bayes} & this work & this work \\
+		\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
+		&uniqueness &  yes & yes & yes & yes & yes & yes \\
+		&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
+		&canonicity & yes & no & yes & yes & no & yes \\
+		&symmetry & yes & yes & yes & yes & no & yes \\
+		& Bayes covariant & no & no & no & yes & yes & yes \\
+		\hline
+		\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
+		&Hinton's minimality & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
+		&robustness & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
+		&lack of parameters & yes & yes & yes & yes & yes & yes \\
+		& amounts to a linear system & no & yes & yes & yes & yes & yes\\
+		& linear system of special form & N/A & no & yes & yes & yes & yes \\
+		& iterative method & yes & yes & yes & no & not needed & not needed\\
+		\hline
+	\end{tabular}
+	\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.
+The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu-Lin-Weng \cite{wu2004probability}.}
+	\label{tab:summaryCoupling}
+\end{table}
+
+\subsection{Future research}
+
+Based on our findings we see two immediate pathways for future research.
+First, one can study arboreal methods in more detail, since these are Bayes covariant and as shown in Section \ref{sec:exp2} they often provide performance matching that of Wu-Lin-Weng's method.
+Secondly, there is a continuum of Bayes covariant methods which we barely sketched.
+Their properties, parameter selection,  and applicability to practical tasks need to investigated in greater detail.
+
+%
+%One-vs-one classification framework is commonly used by machine learning practitioners, for instance whenever one uses radial basis function SVM implemented in  standard libraries.
 Since those method rely on coupling method of Wu-Lin-Weng, one is faced with the decision how to handle differing predictions when priors change.
-
-Of course, one option is to use other classification models.
+%
+%Of course, one option is to use other classification models.
 For instance, random forests provide a flexible alternative.
 Nevertheless, RBF SVM are still one of the best choices for classification tasks with non-linear boundaries.
-
-We have shown in Experiment 1, that substituting parameterless Bayes covariant method for Wu-Lin-Weng coupling methods incurs penalty in accuracy metric.
-
-In our Experiment 2 we showed that the penalty can be often, but not always, eliminated when one opts for one of the parametric Bayes covariant methods.
-
-Finally, in Experiment 3 we showed that the impact of the
+%
+%We have shown in Experiment 1, that substituting parameterless Bayes covariant method for Wu-Lin-Weng coupling methods incurs penalty in accuracy metric. 
+%
+%In our Experiment 2 we showed that the penalty can be often, but not always, eliminated when one opts for one of the parametric Bayes covariant methods.
+%
+%Finally, in Experiment 3 we showed that the impact of the

### 2025-07-16 experiment.tex
Merge methodology into experiments

@@
-\section{Methodology.}
+\section{Experiments.}
+
+The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
+
+\begin{itemize}
+	\item[a)] Which coupling methods without parameters show good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng (see Section \ref{sec:exp1})? 
+	\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric Bayes covariant method which  matches its performance ((see Section \ref{sec:exp2} and \ref{sec:exp3}))?
+	\item[c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling?
+Additionally, how serious is the impact of the lack of Bayes covariance in practice ((see Section \ref{sec:exp4}))?
+\end{itemize}
+
+These questions will be put to test in Sections \ref{sec:exp1} --\ref{sec:exp4}. The methodology of our experiments is describe in the next two subsections.
 
@@
 %\end{figure}
-
-\section{Experimental results.}
-
-The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
-
-\begin{itemize}
-\item[a)] Which coupling methods without parameters show good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
-\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric Bayes covariant method which  matches its performance?
-\item[c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
-\end{itemize}
-
-These questions will be put to test in Sections \ref{sec:exp1} --\ref{sec:exp4}.
 

### 2025-07-29 coupling.tex
Fixes from proofread (Ondrej)

@@
 $$
-\divm\nolimits_\textrm{quad} (\boldsymbol{p}, \boldsymbol{q})= \sum (p_i - q_i)^2.
+\divm\nolimits_\textrm{quad} (\boldsymbol{d}, \boldsymbol{d'})= \sum (d_i - d'_i)^2.
 $$
@@
 
-For $K=3$, there are three different arboreal coupling methods, which we shall call $\boldsymbol{s}_1$, $\boldsymbol{s}_2$, $\boldsymbol{s}_3$, where the system \eqref{eq:arb1} represents the coupling method $\boldsymbol{s}_2$.
+For $K=3$, there are three different arboreal coupling methods corresponding to three different spanning trees on three vertices.
+We shall call them $\boldsymbol{s}_1$, $\boldsymbol{s}_2$, $\boldsymbol{s}_3$, where the coupling method $\boldsymbol{s}_i$ includes only the equations that involve class $i$.
+In particular, \eqref{eq:arb1} represents the coupling method $\boldsymbol{s}_2$.
 
@@
 In fact, a stronger statement is true -- no arboreal method is symmetric.
+To see that, consider the action of the transposition of a vertex $v$ of degree one and another vertex $v'$ of degree $>1$ in a spanning tree.
+The results of coupling involves different number of equations for classes $C_v$ and $C_v'$ which is a contradiction.
 %However, we will see in Section \ref{sec:bc2} that by ``averaging'' several stars we can obtain a canonical
@@
 %
-The intuition behind \eqref{eq:radial} is that if some component of $\hat{\boldsymbol{p}}$ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${\boldsymbol{s}}_i$.
+The intuition behind \eqref{eq:radial} is that if some component $\hat p_i$ of $\hat{\boldsymbol{p}} =(\hat p_1, \ldots, \hat p_K) $ is close to 1 (and thus the remaining components are close to zero), then the prediction $\hat{\boldsymbol{p}}$ should be close to the prediction of Hinton's oracle which is provided by ${\boldsymbol{s}}_i$.
 
@@
 A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.
-Using earlier notation for odds (see \eqref{eq:alpha}), one has
+Using earlier notation for odds (see \eqref{eq:alpha}), one requires
 \begin{align}
@@
 	%\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant (see Proposition \ref{prop:bcprop}),
-	\item[b)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
+	\item[b)] conversely, if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
 	\item[c)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Lemma \ref{lem:transitivity} in Appendix \ref{app:bc1}).
@@
 
-Now we are ready to prove the our first result.
+Now we are ready to prove the our first key result.
 

### 2025-07-29 intro.tex
Fixes from proofread (Ondrej)

@@
 There is a subtle issue with this approach  when handling probabilistic 
-classifiers arising in one-vs-one classification framework.   
+classifiers arising in \emph{probabilistic} one-vs-one classification framework.   
 One-vs-one classification is a two-step framework to solve 
@@
 obtained after the first step, or after the second step. It is not clear what 
-should be the preferred course of action and this problem motivates our paper.
+should be the preferred course of action and this problem motivates our paper. We note that the dilemma does not appear
+in \emph{non-probabilistic} one-vs-one classification e.g. when voting is used in the second step \cite{galar2011overview}.
 
 Our approach to the problem is to evaluate practical performance of different 
-methods to aggregate binary predictions. Such methods -- called coupling methods
+methods to aggregate probabilistic binary predictions. Such methods -- called coupling methods
 -- first appeared in work of \cite{refregier1991probabilistic} when making 
@@
 We pay special attention to methods that commute with change of priors -- Bayes covariant methods, 
-since such methods provide an unexpected, and elegant solution to our problem. 
+since such methods provide an  elegant solution to our problem. 
 We introduce new coupling methods by forming weighted ensembles. We prove such ensemble of Bayes covariant methods is again Bayes covariant
-when a normalizing condition on weights hold (Proposition \ref{prop:ensemble}).  
+when a normalizing condition on weights holds (Proposition \ref{prop:ensemble}).  
 Our experiments are described in Section 4. In Section 5 we summarize our findings, 

### 2025-07-29 theory.tex
Fixes from proofread (Ondrej)

@@
 	\end{align}
-	Knowing the odds of $C_2$ to $C_1$, $C_3$ to $C_2$ up to $C_{K}$ to $C_{K-1}$ together with the requirement that probabilities sum to one uniquely determines the whole vector $\boldsymbol{p}^\Pi(x)$.
+	Knowing the odds of $C_2$ to $C_1$, $C_3$ to $C_2$ up to $C_{K}$ to $C_{K-1}$ together with the requirement that probabilities sum to one uniquely determines the whole vector $\boldsymbol{p}^\textrm{multi}(x)$.
 \end{proof}
@@
 we can train binary classifiers to provide approximations $r_{ij}(x)$ to 
-pairwise Bayes classifiers $p_{ij}^\textrm{multi}(x)$. The goal of probabilistic
+pairwise Bayes classifiers $p_{ij}^\textrm{binary}(x)$. The goal of probabilistic
 one-vs-one classification is to deduce for any $x$ in the feature space $X$ an 
@@
 A method to solve Bradley-Terry equations is called a \emph{coupling method}.
-Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries being $r_{ij}(x)$.
+Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries representing predicted probabilities $r_{ij}(x)$.
 Schematically, classification using coupling method $\boldsymbol{v}$ proceeds as indicated in Figure \ref{fig:coupling}.
@@
 The system of Bradley-Terry equations is usually inconsistent and additional assumptions are needed to construct an estimator.
-In Sections \ref{sec:des:exact} and \ref{sec:des:inexact} we review various approaches to construct coupling methods.
+In Sections \ref{sec:des:exact} and \ref{sec:des:inexact} we review various desiderata used to construct and compare coupling methods.
 
@@
 
-\emph{Symmetry} We can define two natural actions on permutation group on $K$-elements. Suppose $\sigma$ is a permutation on $K$ elements.
+\emph{Symmetry} refers to transformations of multi-class predictions when permuting classes.
+We can define two natural actions on permutation group on $K$-elements.
+Suppose $\sigma$ is a permutation on $K$ elements.
 
@@
 	 \end{itemize}
-We say that a coupling method $V$ is \emph{symmetric} if 
+We say that a coupling method $\boldsymbol{v}$ is \emph{symmetric} if 
 \begin{align}
@@
 Denote by  $\pi$ the change of priors $\pi:\Pi \rightarrow \Pi'$.
-If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_2^{ij}(D)$ by requiring
+If we have a  binary classifier predicting distribution $D \propto (p, p')$ on two classes $C_i$ and $C_j$, then we define new distribution $\pi_{ij}(D)$ by requiring
 $$
-\pi_2^{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
+\pi_{ij}(D) \propto \biggl(p \frac{P'_i}{P_i},p' \frac{P'_j}{P_j}\biggr).
 $$
-We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_2^{ij}(r_{ij})$.
+We denote by $\boldsymbol{R}^\pi$ the $K\times K$ matrix with entries $\pi_{ij}(r_{ij})$.
 The value $\boldsymbol{v}(\boldsymbol{R}^\pi)$ represents the effect of change of priors if we apply \eqref{eq:changePrior} \emph{before} coupling.
@@
 This issue gains expediency when the underlying binary classification method requires crossvalidation to select some hyperparameters.
-For example, this is the case of support vector machines, where often one opts for RBF kernel, which requires choosing two hyper-parameters.
+For example, this is the case of support vector machines, where often one opts for RBF kernel that requires choosing two hyper-parameters.
 

### 2025-07-30 coupling.tex
Changes for arboreal coupling

@@
 
-System of equations \eqref{eq:bt2} is overdetermined because there are $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.
+System of equations \eqref{eq:bt2} is overdetermined because there are $K$ unknowns and $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.
 Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns.
@@
 
+It is useful to consider the graph on $K$ vertices, where vertices correspond to the classes and edges to the selected equations.
+It cannot have a cycle, otherwise the subsystem of Bradley-Terry equations would be overdetermined for unknowns representing the vertices of the cycle.
+Therefore it has to be a spanning tree.
+
 For $K=3$, there are three different arboreal coupling methods corresponding to three different spanning trees on three vertices.
@@
 
-More generally, to obtain a regular system of equations for  any of $K$ , it is necessary and sufficient that the tree formed by edges for which we include equations from Bradley-Terry system is  a spanning tree.
+%More generally, to obtain a regular system of equations for  any of $K$ , it is necessary and sufficient that the tree formed by edges for which we include equations from Bradley-Terry system is  a spanning tree.
+
 Note that any arboreal method is non-canonical, because there is no natural way to choose a spanning tree in a complete graph. 
-In fact, a stronger statement is true -- no arboreal method is symmetric.
-To see that, consider the action of the transposition of a vertex $v$ of degree one and another vertex $v'$ of degree $>1$ in a spanning tree.
-The results of coupling involves different number of equations for classes $C_v$ and $C_v'$ which is a contradiction.
+%In fact, a stronger statement is true -- no arboreal method is symmetric. 
+In fact, a stronger statement is true.
+\begin{prop}
+No arboreal method is symmetric. 
+\end{prop}
+\begin{proof}
+First note that any spanning tree has a vertex $v$ of degree one and another vertex $v'$ of degree $>1$.
+Now consider the transposition $\sigma$ exchanging  vertices $v$  and $v'$.
+Since coupling involves different number of equations for classes $C_v$ and $C_{v'}$ the required condition \eqref{eq:symmetry} cannot hold for $\sigma$.
+\end{proof}
 %However, we will see in Section \ref{sec:bc2} that by ``averaging'' several stars we can obtain a canonical

### 2025-08-06 intro.tex
Fixes for Peter's proofs

@@
 	\item covariate shift, if $p(X)$ changes, but $p(Y\mid X)$ is unchanged,
-	\item label shift, if $p(Y)$ changes, but $P(X \mid Y)$ remains the same,
+	\item label shift, if $p(Y)$ changes, but $p(X \mid Y)$ remains the same,
 	\item concept shift, if $p(Y \mid X)$ itself changes.
@@
 The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city.
-unlikely to encounter 80mph limit in a city setting. By taking into account 
-the city priors, the system would be more likely to make the proper classification.
+It is very unlikely to encounter 80mph limit in a city setting. By taking 
+the city priors  into account, the system would be more likely to make the proper classification.
 
-Some systems are unable to do incorporate new priors without rebuilding 
-the classifier  e.g. those based 
-on fuzzy logic, or some tree methods. 
+Some systems are unable to incorporate new priors without rebuilding 
+the classifier, e.g., those based 
+on fuzzy logic or some tree methods. 
 However, change of priors can be effectively dealt with in probabilistic 
@@
 One-vs-one classification is a two-step framework to solve 
-multi-class classification problems.
+multiclass classification problems.
 In the first step it reduces the multiclass problem to a series of binary
 classification problems. 
-In the second step it deduces the multi-class decision by aggregating decisions 
+In the second step it deduces the multiclass decision by aggregating decisions 
 for the binary problems. Since the procedure is two-step, there is a possibility 
@@
 should be the preferred course of action and this problem motivates our paper. We note that the dilemma does not appear
-in \emph{non-probabilistic} one-vs-one classification e.g. when voting is used in the second step \cite{galar2011overview}.
+in \emph{non-probabilistic} one-vs-one classification, e.g., when voting is used in the second step \cite{galar2011overview}.
 
 Our approach to the problem is to evaluate practical performance of different 
-methods to aggregate probabilistic binary predictions. Such methods -- called coupling methods
--- first appeared in work of \cite{refregier1991probabilistic} when making 
+methods to aggregate probabilistic binary predictions. Such methods---called coupling methods---first appeared in work of \cite{refregier1991probabilistic} when making 
 multi-class classification using neural networks. 
@@
 We formulate the underlying principles of one-vs-one probabilistic classification in Section 2. In Section 3 we present  different classes of coupling methods. 
-We pay special attention to methods that commute with change of priors -- Bayes covariant methods, 
+We pay special attention to methods that commute with change of priors---Bayes covariant methods, 
 since such methods provide an  elegant solution to our problem. 

### 2025-08-06 theory.tex
Changes for arboreal coupling
Fix changes up to 2.2 per Peter's proof

@@
 
-Knowledge of vector $\boldsymbol{p}^\textrm{multi}(x)$ is equivalent to knowing the functions $p^\textrm{binary}_{ij}(x)$. Indeed under Assumption \ref{ass:1} we have
+Knowledge of vector $\boldsymbol{p}^\textrm{multi}(x)$ is equivalent to knowing the functions $p^\textrm{binary}_{ij}(x)$. Indeed, under Assumption \ref{ass:1} we have
 \begin{align}
@@
 
-Conversely, it is easy to show that  given values of $p_{ij}(x)$ the system of equations \eqref{eq:bt1} has a unique solution.
+Conversely, it is easy to show that  given values of $p_{ij}^\textrm{binary}(x)$, the system of equations \eqref{eq:bt1} has a unique solution.
 This result (Proposition \ref{prop:binary2multi}) can be viewed as the fundamental theorem of one-vs-one classification.
@@
 	 \label{prop:binary2multi}
-	 Knowledge of binary Bayes classifiers $p^\textrm{binary}_{ij}$ determines the multiclass Bayes classifier 
+	 Under Assumption \ref{ass:1}, knowledge of binary Bayes classifiers $p^\textrm{binary}_{ij}$ determines the multiclass Bayes classifier 
 	 $\boldsymbol{p}^\textrm{multi}$.
@@
 \begin{proof}
-	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denote the odds of $C_i$ to $C_j$:
+	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denote the odds of classes $C_i$ to $C_j$:
 	\begin{align}
@@
 
-	From \eqref{eq:bt1} we can deduce the odds of classes $C_j$ to $C_i$ for the Bayes classifier since
+	From \eqref{eq:bt1} we can deduce the odds of  $C_j$ to $C_i$ for the Bayes classifier since
 	\begin{align}
@@
 
-Equations forming system \eqref{eq:bt2} are called Bradley-Terry equations. In parallel to Assumption \ref{ass:1} it is customary to make the following assumption on estimates $r_{ij}$.
+Equations forming system \eqref{eq:bt2} are called Bradley--Terry equations. In parallel to Assumption \ref{ass:1} it is customary to make the following assumption on estimates $r_{ij}$.
 
@@
 
-A method to solve Bradley-Terry equations is called a \emph{coupling method}.
+A method to solve Bradley--Terry equations is called a \emph{coupling method}.
 Its input can be represented by a matrix $\boldsymbol{R}(x)$ with off-diagonal entries representing predicted probabilities $r_{ij}(x)$.
@@
 	\begin{tikzcd}[column sep=3cm]
-		\textrm{sample $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
+		\textrm{observation $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
 		\arrow{d}{coupling} \\
@@
 
-The system of Bradley-Terry equations is usually inconsistent and additional assumptions are needed to construct an estimator.
+The system of Bradley--Terry equations is usually inconsistent and additional assumptions are needed to construct an estimator.
 In Sections \ref{sec:des:exact} and \ref{sec:des:inexact} we review various desiderata used to construct and compare coupling methods.
@@
 \begin{align}
-		\sigma(\boldsymbol{v}(\boldsymbol{R})) = \boldsymbol{v}(\sigma(\boldsymbol{R}))\quad\textrm{for any permutation $\sigma$}.
+		\sigma(\boldsymbol{v}(\boldsymbol{R})) = \boldsymbol{v}(\sigma(\boldsymbol{R}))\quad\textrm{for any permutation $\sigma$}. \label{eq:symmetry}
 \end{align}

### 2025-08-06 coupling.tex
Fix multi-class to multiclass

@@
 
-A multi-class estimate $\hat{\boldsymbol{p}}$ obtained by a coupling method implies via \eqref{eq:bt1} probability distributions on each pair of classes:
+A multiclass estimate $\hat{\boldsymbol{p}}$ obtained by a coupling method implies via \eqref{eq:bt1} probability distributions on each pair of classes:
 \begin{align*}
@@
 
-Suppose first that $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabilistic multi-class classification methods satisfying Assumption \ref{ass:2}.
+Suppose first that $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabilistic multiclass classification methods satisfying Assumption \ref{ass:2}.
 We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies

### 2025-08-06 experiment.tex
Fix multi-class to multiclass

@@
 
-The choice of a coupling method is an important task for practitioners. We aim to help by posing the following interrelated questions
+The choice of a coupling method is an important decision for practitioners. We aim to investigate the following interrelated questions
 
@@
 
-These questions will be put to test in Sections \ref{sec:exp1} --\ref{sec:exp4}. The methodology of our experiments is describe in the next two subsections.
+These questions will be put to test in Sections \ref{sec:exp1} --\ref{sec:exp4}. The methodology of our experiments is described in the next two subsections.
 
@@
 
-It is natural to consider the benchmark datasets used in previous evaluation of coupling methods [\cite{wu2004probability}].
+It is natural to consider the benchmark datasets used in previous evaluation of coupling methods \cite{wu2004probability}.
 The authors considered altogether seven datasets with number of classes ranging from 3 to 26.

### 2025-08-06 theory.tex
Fix multi-class to multiclass

@@
 Suppose we have $K$ classes of objects, each distributed with density $d_i$, $i=1,\ldots, K$ on a feature 
-space $X$. In a multi-class classification problem we are provided with 
+space $X$. In a  classification problem we are provided with 
 the prior probabilities $\Pi = (P_1, \ldots, P_K)$ of each class. Given $x$ in $X$ we aim to find 
@@
 
-Besides the multi-class classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of 
+Besides the multiclass classifier we may also consider the binary Bayes classifiers for any pair $(i,j)$ of 
 classes. Assuming the prior on the two classes is proportional to $(P_i, P_j)$, the binary Bayes classifier 
@@
 	\begin{tikzcd}[column sep=3cm]
-		\textrm{observation $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multi-class~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
+		\textrm{observation $x$}\arrow[r, "binary~classifiers"] \arrow[dr,dotted,swap, "multiclass~ prediction"] & \boldsymbol{R}(x) %\arrow{d}{coupling}[swap]{\boldsymbol{v}} \\
 		\arrow{d}{coupling} \\
@@
 	\end{tikzcd}
-	\caption{Multi-class classification using a coupling method $\boldsymbol{v}$}
+	\caption{Multiclass classification using a coupling method $\boldsymbol{v}$}
 	\label{fig:coupling}
@@
 
-\emph{Unique solution} refers to the fact that the procedure to compute a multi-class probabilistic prediction always converges to a unique solution.
+\emph{Unique solution} refers to the fact that the procedure to compute a multiclass probabilistic prediction always converges to a unique solution.
 One way to satisfy this condition would be that it amounts to a linear system of equations in $K$ variables, and the matrix of the system would be invertible.
@@
 \emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
-The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multi-class Bayes classifier i.e.
+The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multiclass Bayes classifier i.e.
 satisfies \eqref{eq:bt1}.
@@
 
-\emph{Symmetry} refers to transformations of multi-class predictions when permuting classes.
+\emph{Symmetry} refers to transformations of multiclass predictions when permuting classes.
 We can define two natural actions on permutation group on $K$-elements.
@@
 \emph{Bayes covariance} is a notion introduced in  \cite{vsuch2016bayes}.
-It refers to the behavior of a probabilistic multi-class method built in one-vs-one fashion, when the priors change.
+It refers to the behavior of a probabilistic multiclass method built in one-vs-one fashion, when the priors change.
 Any Bayes classifier, whether binary or multiclass changes its prediction when the priors change.
@@
 Let us finally mention \emph{Hinton's minimality}.
-Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multi-class prediction \cite[p.~467]{hastie1998classification}.
+Geoffrey Hinton is reported to object to the underlying principle of one-vs-one classification, where any single classifier influences the multiclass prediction \cite[p.~467]{hastie1998classification}.
 Suppose we are classifying objects from CIFAR-10 dataset.

### 2025-08-10 theory.tex
Proof by Peter

@@
 this section
- we will describe exact mathematical criteria that one may impose on a coupling method, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
+ we will describe the following criteria that one may impose on a coupling method
 
 \begin{itemize}
-\item  unique solution(under Assumption \ref{ass:2}),
-\item Bradley-Terry consistency,
+\item unique solution (under Assumption \ref{ass:2}),
+\item Bradley--Terry consistency,
 \item canonicity,
@@
 
+These criteria are all \emph{exact}, meaning they have a strict mathematical definition, whereas  in section \ref{sec:des:inexact} we shall describe more flexible properties. 
 %\begin{itemize}
@@
 
-\emph{Bradley-Terry consistency} refers to the outcome of a procedure providing a unique solution.
-The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multiclass Bayes classifier i.e.
-satisfies \eqref{eq:bt1}.
+\emph{Bradley--Terry consistency} refers to the outcome of a procedure providing a unique solution.
+The requirement states that should we apply the coupling procedure to binary Bayes classifiers, then the result is the output of multiclass Bayes classifier, i.e., satisfies \eqref{eq:bt1}.
 
 \emph{Canonicity} refers to requirement that the method should be natural.
-Borrowing an example from regression analysis, Gauss-Markov theorem states that ordinary least squares (OLS) estimates is best linear unbiased estimate of the coefficients of a linear model.
+Borrowing an example from regression analysis, Gauss--Markov theorem states that ordinary least squares (OLS) estimate is the best linear unbiased estimate of the coefficients of a linear model.
 Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
@@
 \emph{Symmetry} refers to transformations of multiclass predictions when permuting classes.
-We can define two natural actions on permutation group on $K$-elements.
+We can define two natural actions on permutation group on $K$ elements.
 Suppose $\sigma$ is a permutation on $K$ elements.
@@
 	\end{align}
-	 \item $\sigma$ also acts on the matrix of binary predictions. Namely, the entry of $\sigma(\boldsymbol{R})$ in $i$-th row and $j$-th column is defined to be $r_{\sigma(i), \sigma(j)}$.
+	 \item $\sigma$ also acts on the matrix of binary predictions. Namely, the entry of $\sigma(\boldsymbol{R})$ in the $i$-th row and $j$-th column is defined to be $r_{\sigma(i), \sigma(j)}$.
 	 \end{itemize}
@@
 When we use a coupling method and the prior changes, we  can apply \eqref{eq:changePrior} either before or after coupling.
-If the results are identical, for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.
+If the results are identical for all initial pairwise data $\boldsymbol{R}$, then we say that the coupling method is \emph{Bayes covariant}.
 
@@
 \begin{align}
-D \propto (p_1, \ldots, p_K)
+D \propto (p_1, \ldots, p_K).
 \end{align}
-then we define $D^\pi$ by requiring 
+Then we define $D^\pi$ by requiring 
 \begin{align}
@@
 \end{align}
-for any matrix $\boldsymbol{R}$ with $r_{ij}> 0$.
+for any matrix $\boldsymbol{R}$ satisfying $r_{ij}> 0$ and $r_{ij} = 1 - r_{ji}$.
 
@@
 
-\emph{Robustness -- good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
+\emph{Robustness---good accuracy on benchmark tasks} is  a strong argument to prefer a particular coupling method.
 This criterion is of course subjective, because there is a great variety of datasets in practice and inevitably there will be instances where any coupling method would underperform.

### 2025-08-10 coupling.tex
Coupling methods

@@
 
-A natural way to find  $\hat{\boldsymbol{p}}$ is thus to minimize a functional incorporating divergence measures between these distributions
+A natural way to find  $\hat{\boldsymbol{p}}$ is thus to minimize a functional incorporating divergence measures between these distributions:
 \begin{align*}
-\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\boldsymbol{d}_{ij}^\textrm{multi}, \boldsymbol{d}_{ij}^\textrm{binary})
+\hat{\boldsymbol{p}} \stackrel{def}{=} \argmin_{\boldsymbol{p}} \sum_{ij} w_{ij} \divm (\boldsymbol{d}_{ij}^\textrm{multi}, \boldsymbol{d}_{ij}^\textrm{binary}).
 \end{align*}
 
-A notable example which uses this principle is the coupling method introduced in \cite{hastie1998classification}. Their method uses Kullback-Leibler divergence $\divm_\textrm{KL}$
+A notable example which uses this principle is the coupling method introduced in \cite{hastie1998classification}. Their method uses Kullback--Leibler divergence 
 \begin{align*}
@@
 
-Kullback-Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
-In the context of classification, when we are primarily concerned with accuracy , one could advantageously use other Bregman divergence derived from a proper score \cite{gneiting2007strictly, buja2005loss}.
+Kullback--Leibler divergence strongly penalizes  mispredictions when the true class is predicted to have very low probability.
+In the context of classification, when we are primarily concerned with accuracy, one could advantageously use other Bregman divergence derived from a proper score \cite{gneiting2007strictly, buja2005loss}.
 
@@
 A simple example for 3 classes is the classifier which ignores prediction of the binary classifier distinguishing between classes $C_1$ and $C_3$.
-The two equations form \eqref{eq:bt2} together with the requirement that the prediction probabilities should sum to 1 yield the following system of equations
+The two equations from \eqref{eq:bt2} together with the requirement that the prediction probabilities should sum to 1 yield the following system of equations:
 \begin{equation}
@@
 
-For $K>3$ the three methods can be generalized to corresponds to the trees having the graph structure  of a star centered at class $C_i$ for $i=1, \ldots, K$.
+For $K>3$ the three methods can be generalized to correspond to the trees having the graph structure  of a star centered at class $C_i$ for $i=1, \ldots, K$.
 
@@
 $$
-together the  with total sum equation
+together   with the total sum equation
 $$
@@
 
-For any one sample belonging to class $C_t$, its result is identical to the arboreal method where the underlying tree forms a star with center at $C_t$.
+For any observation belonging to class $C_t$, its result is identical to the arboreal method where the underlying tree forms a star with center at $C_t$.
 This method is clearly the optimal one with respect to Hinton's minimality criterion, because it ignores the output of any classifier not trained on the true class.
@@
 In order to convert Hinton's oracle into a true classification method we can use the principle of self-referentiality.
-Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centred at the class $C_i$.
+Denote by $\boldsymbol{s}_i$ the prediction of the arboreal method, where the underlying tree is a star centered at the class $C_i$.
 The predictions will generally span the vector space $R^K$.
@@
 Let us now define \emph{radial} coupling method.
-The  method requires that for the  weights we could in fact use the components of $\boldsymbol{p}$ i.e.
+The  method requires that for the  weights we could in fact use the components of $\hat\boldsymbol{p}$, i.e.,
 \begin{equation}
 	\begin{split}
-	\hat {\boldsymbol{p}} &= \hat p_1 \boldsymbol{s}_1(x) + \ldots + \hat p_K \boldsymbol{s}_K(x)\\
-	1 &= \hat p_1 + \ldots + \hat p_K
+	\hat {\boldsymbol{p}} &= \hat p_1 \boldsymbol{s}_1(x) + \ldots + \hat p_K \boldsymbol{s}_K(x),\\
+	1 &= \hat p_1 + \ldots + \hat p_K.
 	\end{split}

### 2025-08-10 coupling.tex
From Peter's proof

@@
 Let us now define \emph{radial} coupling method.
-The  method requires that for the  weights we could in fact use the components of $\hat\boldsymbol{p}$, i.e.,
+The  method requires that for the  weights we could in fact use the components of $\hat{\boldsymbol{p}}$, i.e.,
 \begin{equation}
@@
 \begin{align}
-	\alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R}^\pi) \bigr) = \alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R})^\pi \bigr)
+	\alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R}^\pi) \bigr) = \alpha_{ij}\biggl( \bigl(\boldsymbol{v}(\boldsymbol{R}) \bigr)^\pi\biggr)
 \end{align}
@@
 \begin{itemize}
-	\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$ (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
+	\item[(a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$ (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
 	%\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant (see Proposition \ref{prop:bcprop}),
-	\item[b)] conversely, if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
-	\item[c)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Lemma \ref{lem:transitivity} in Appendix \ref{app:bc1}).
+	\item[(b)] conversely, if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
+	\item[(c)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Lemma \ref{lem:transitivity} in Appendix \ref{app:bc1}).
 \end{itemize}
 
-Now we are ready to prove the our first key result.
+Now we are ready to prove  our first key result.
 
@@
 
-Given several Bayes covariant methods one can form  their ``linear combination'' - an ensemble which is also Bayes covariant. Let us make the construction explicit.
+Given several Bayes covariant methods one can form  their ``linear combination''---an ensemble which is also Bayes covariant. Let us make the construction explicit.
 
 Suppose first that $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabilistic multiclass classification methods satisfying Assumption \ref{ass:2}.
-We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
+We define their linear combination $\bigoplus_m a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
 \begin{align*}
@@
 	\label{prop:ensemble}
-Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant.
-If $\sum a_m = 1$, then $\boldsymbol{e} = \bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
+Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\boldsymbol{e} = \bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant.
 \end{prop}
@@
 
-Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$. Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$ i.e.
+Let $\pi$ be a change of priors from $(P_1, \ldots, P_K)$  to $(P'_1, \ldots, P'_K)$. Let $o_m$ denotes the odds of classes $C_i$ and $C_j$ predicted by coupling method $\boldsymbol{v}_m$, i.e.,
 $$
@@
 
-From the definition of linear combination of coupling methods that the odds of $C_i$ to $C_j$ for $\boldsymbol{e}$ are
+From the definition of linear combination of coupling methods the odds of $C_i$ to $C_j$ for $\boldsymbol{e}$ are
 \begin{align}
@@
 As an example, consider the classification problem with three classes.
-We have three arboreal classifiers $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$ which correspond to star graphs centered respectively at classes $C_1, C_2, C_3$.
+We have three arboreal classifiers $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$, which correspond to star graphs centered  at classes $C_1, C_2, C_3$ respectively.
 The classifier
@@
 \begin{thm} \label{thm:K3}
-	There exists a unique symmetric Bayes covariant coupling methods for $K=3$.
+	There exists a unique symmetric Bayes covariant coupling method for $K=3$.
 \end{thm}
@@
 \begin{align}
-	\boldsymbol{R}_s \stackrel{def}{=} \begin{pmatrix} \cdot & s & 1 -s \\  1-s & \cdot & s \\ s & 1-s & \cdot \end{pmatrix}
+	\boldsymbol{R}_s \stackrel{def}{=} \begin{pmatrix} \cdot & s & 1 -s \\  1-s & \cdot & s \\ s & 1-s & \cdot \end{pmatrix}.
 \end{align}
@@
 \end{align}
-Now applying  Proposition \ref{prop:bc3} from Appendix \ref{app:bc1} yields uniqueness. The existence of the method was already shown above using Proposition \ref{prop:ensemble}.
+Applying  Proposition \ref{prop:bc3} from Appendix \ref{app:bc1} yields uniqueness. The existence of the method was already shown above using Proposition \ref{prop:ensemble}.
 \end{proof}
@@
 Note that here we use the plus symbol to denote the vector addition of vectors representing  probability distributions over $K$ classes.
-This is a different classifier from the one given by  \eqref{eq:normal3} , and since it is symmetric, it cannot be Bayes covariant.
+This is a different classifier from the one given by  \eqref{eq:normal3}, and since it is symmetric, it cannot be Bayes covariant.
 
@@
 \begin{align}
-\boldsymbol{e}_K \stackrel{def}{=} \frac1K \boldsymbol{s}_1 \oplus \frac1K \boldsymbol{s}_2 \oplus \ldots \oplus \frac 1K \boldsymbol{s}_K  \label{eq:bc1}
+\boldsymbol{e}_K \stackrel{def}{=} \frac1K \boldsymbol{s}_1 \oplus \frac1K \boldsymbol{s}_2 \oplus \ldots \oplus \frac 1K \boldsymbol{s}_K.  \label{eq:bc1}
 \end{align}

### 2025-08-10 experiment.tex
Fix from Peter's proof

@@
-\section{Experiments.}
+\section{Experiments}
 
-The choice of a coupling method is an important decision for practitioners. We aim to investigate the following interrelated questions
+The choice of a coupling method is an important decision for practitioners. We aim to investigate the following interrelated questions:
 
 \begin{itemize}
-	\item[a)] Which coupling methods without parameters show good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng (see Section \ref{sec:exp1})? 
-	\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric Bayes covariant method which  matches its performance ((see Section \ref{sec:exp2} and \ref{sec:exp3}))?
-	\item[c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling?
-Additionally, how serious is the impact of the lack of Bayes covariance in practice ((see Section \ref{sec:exp4}))?
+	\item[(a)] Which coupling methods without parameters show good performance across diverse data sets?
+Is it the orthodox method of Wu-Lin-Weng?
+An experiment to answer this question is carried out Section \ref{sec:exp1}.
+	\item[(b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric Bayes covariant method which  matches its performance?
+An experiment related to this question is carried out in  Sections \ref{sec:exp2} and \ref{sec:exp3}.
+	\item[(c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling?
+Additionally, how serious is the impact of the lack of Bayes covariance in practice.
+This question is investigated in Section \ref{sec:exp4}.
 \end{itemize}
 
-These questions will be put to test in Sections \ref{sec:exp1} --\ref{sec:exp4}. The methodology of our experiments is described in the next two subsections.
+These questions will be put to test in Sections \ref{sec:exp1}--\ref{sec:exp4}. The methodology of our experiments is described in the next two subsections.
 
@@
 For each dataset they extracted 40 pairs of training and testing datasets.
-Half of these were smaller (300 training samples and 500 testing samples) and the other half was larger (800 training samples and 1000 testing samples).
+Half of these were smaller (300 training samples and 500 testing samples) and the other half were larger (800 training samples and 1000 testing samples).
 In our experiments we use only the larger pairs.
@@
 
-We can infer that except for 'waveform' dataset, majority of binary problems are linearly separable.
+We can infer that except for 'waveform' dataset, majority of binary subproblems are linearly separable.
 
@@
 penalized logistic regression or SVM).
-It usually provides results close to logistic regression [\cite{james2013introduction}].
+It usually provides results close to logistic regression \cite{james2013introduction}.
 
@@
 
-For training LDA we used MASS library in R. We implemented coupling methods in C++ using Eigen library. As arguments to the coupling methods we use log-odds, i.e. instead of $r_{ij}$ they expect
+For training LDA we used MASS library in R. We implemented coupling methods in C++ using Eigen library. As arguments to the coupling methods we use log-odds:
 $$
@@
 Small probabilities generally have very little effect on the implementation of Bayes covariant methods which generally operate using log-odds.
-However small probabilities do affect both the method of Wu-Lin-Weng as well sa radial method, because then Assumption \ref{ass:1} fails to hold.
+However small probabilities do affect both the method of Wu-Lin-Weng as well as radial method, because then Assumption \ref{ass:2} fails to hold.
 
@@
 
-The first experiment compares the performance the following canonical coupling methods
+The first experiment compares the performance of the following canonical coupling methods:
 \begin{itemize}
 \item method of Wu-Lin-Weng, which is widely used in software libraries, and thus can be viewed as an orthodox choice,
-\item normal coupling, which is a Bayes covariant method,
+\item normal coupling, which is Bayes covariant,
 \item radial coupling, which is not Bayes covariant,
@@
 
-Let us define two parameter family of Bayes covariant coupling methods
+Let us define a two-parameter family of Bayes covariant coupling methods
 \begin{align}
@@
 We choose to examine points in the simplex defined by  $a_i\geq 0$, for $i=1,2,3$.
-As Table \ref{tab:step2} shows, this simplex contained in more than half case a Bayes covariant method matching the performance of Wu-Lin-Weng's method.
+As Table \ref{tab:step2} shows, this simplex contained in more than half cases a Bayes covariant method matching the performance of Wu-Lin-Weng's method.
 \end{itemize}

### 2025-08-10 tab-sep.R

@@ -10,11 +10,13 @@ df1 <- df |> group_by(dataset, status, K) |> summarize(count = n() ) |>
               names_from = "status", 
               values_from = "pct", 
               values_fill = 0) |>
-  mutate(separable = optimal) |>
-  select(dataset, K)
+  mutate(separable = optimal)  |>
+ select(dataset, K, optimal)
+
+colnames(df1) <- c("Dataset", "$K$", "Portion linearly separable")
 
 sink("tab-sep.tex")
-print(xtable(df1, label = "tab:sep", digits = 2,
-             caption = "The benchmark datasets with indication of the number of classes $K$ ",
-),  include.rownames = FALSE)
+print(xtable(df1, label = "tab:sep", digits = 3,
+             caption = "The benchmark datasets with indication of the number of classes $K$ and the portion of binary classification problems that are linearly separable",
+),  include.rownames = FALSE, sanitize.colnames.function = identity)
 sink()

### 2025-08-10 tab-step2.R

@@ -5,10 +5,10 @@ library(xtable)
 df <- read.csv("data/triples.csv")
 
 df1 <- df |> mutate(omit = pmax(omit12, omit13, omit23)) |> 
-            summarize(`normal $\\geq$ Wu-Lin-Weng` = mean(normal >= wlw2),
-                      `$\\max(\\boldsymbol{s}_1, \\boldsymbol{s}_2, \\boldsymbol{s}_3) \\geq$ Wu-Lin-Weng` = mean(omit >= wlw2),
-                      `Wu-Lin-Weng > max(normal, $\\boldsymbol{s}_1, \\boldsymbol{s}_2, \\boldsymbol{s}_3$)` = mean(wlw2 > normal & wlw2 > omit)) |>
-      pivot_longer(everything(), names_to = 'outcome', values_to = "percentage")
+            summarize(` $\\boldsymbol{e}_3$ at least as accurate as $\\boldsymbol{wlw}$` = mean(normal >= wlw2),
+                      `one of $\\boldsymbol{s}_1, \\boldsymbol{s}_2, \\boldsymbol{s}_3$ at least as accurate as $\\boldsymbol{wlw}$` = mean(omit >= wlw2),
+                      `$\\boldsymbol{wlw}$ more accurate than $\\boldsymbol{e}_3, \\boldsymbol{s}_1, \\boldsymbol{s}_2, \\boldsymbol{s}_3$` = mean(wlw2 > normal & wlw2 > omit)) |>
+      pivot_longer(everything(), names_to = 'Outcome', values_to = "Portion")
             
                       
                       
@@ -17,7 +17,7 @@ df1 <- df |> mutate(omit = pmax(omit12, omit13, omit23)) |>
 # colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
 sink("tab-step2.tex")
 print(xtable(df1, label = "tab:step2", digits = 2,
-             caption = "Comparison of Wu-Lin-Weng's method and  parameterless coupling methods on three class subset"), 
+             caption = "Comparison of Wu-Lin-Weng's method and  parameterless coupling methods on three class subsets. "), 
     sanitize.text.function = identity,
     include.rownames = FALSE)
 sink()

### 2025-08-13 intro.tex
Explaining wlw abbreviation

@@
 methods to aggregate probabilistic binary predictions. Such methods---called coupling methods---first appeared in work of \cite{refregier1991probabilistic} when making 
-multi-class classification using neural networks. 
+multiclass classification using neural networks. 
 Many authors followed with alternative proposals 

### 2025-08-13 tab-step2.R

@@ -17,7 +17,7 @@ df1 <- df |> mutate(omit = pmax(omit12, omit13, omit23)) |>
 # colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
 sink("tab-step2.tex")
 print(xtable(df1, label = "tab:step2", digits = 2,
-             caption = "Comparison of Wu-Lin-Weng's method and  parameterless coupling methods on three class subsets. "), 
+             caption = "Comparison of Wu-Lin-Weng's method $\\boldsymbol{wlw}$ and  parameterless coupling methods on three class subsets. "), 
     sanitize.text.function = identity,
     include.rownames = FALSE)
 sink()

### 2025-08-13 theory.tex
Proof of Ali

@@
 \emph{Canonicity} refers to requirement that the method should be natural.
-Borrowing an example from regression analysis, Gauss--Markov theorem states that ordinary least squares (OLS) estimate is the best linear unbiased estimate of the coefficients of a linear model.
+Borrowing an example from regression analysis, Gauss--Markov theorem states that ordinary least squares (OLS) estimator is the best linear unbiased estimator of the coefficients of a linear model.
 Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.

### 2025-08-13 discussion.tex
Fix multi-class to multiclass
Peter's proof

@@
 
-In this paper we set out to investigate how to handle change of priors n in one-vs-one probabilistic models. Let us first summarize our contributions.
+In this paper we set out to investigate how to handle change of priors in one-vs-one probabilistic models. Let us first summarize our contributions, both theoretical and experimental.
 
@@
 Important examples of coupling methods has been presented in Section \ref{sec:coupling}.
-We were able to provide a unifying formulation for method of Hastie-Tibshirani and Wu-Lin-Weng.
-We discusses arboreal coupling methods, which are an important example of methods without parameters, albeit noncanonical.
+We were able to provide a unifying formulation for method of Hastie--Tibshirani and Wu--Lin--Weng.
+We introduced arboreal coupling methods, which are an important example of methods without parameters, albeit noncanonical.
 We recast previously known normal coupling method in a new way.
 Although this is a canonical example of Bayes covariant coupling methods,  it is lacking in practical performance, as  we uncovered in the experimental section.
-This creates impetus to study more general Bayes covariant method.
+This creates impetus to study more general Bayes covariant methods.
 The  ensembling approach we proposed in Section \ref{sec:bc2} allows one to build parametric families of Bayes covariant methods.
@@
 \begin{itemize}
-	\item The orthodox method of Wu-Lin-Weng dominates others across diverse classification tasks.
-	\item The only method close to Wu-Lin-Weng is the radial coupling method.
+	\item The orthodox method of Wu--Lin--Weng dominates others across diverse classification tasks.
+	\item The only method close to Wu--Lin--Weng is the radial coupling method.
 	\item The concern of Hinton about one-vs-one classification is unwarranted.
-The method that ignores binary classifiers not trained on a given sample (we call it Hinton's oracle) underperforms the method of Wu-Lin-Weng.
+The method that ignores binary classifiers not trained on a given sample (we call it Hinton's oracle) underperforms the method of Wu--Lin--Weng.
 	\item In more than half of classification problems we were able to find a Bayes covariant coupling method which matches performance of the Wu-Lin-Weng method. 
@@
 \begin{itemize}
-\item[1.] One can treat the decision on when to apply change of priors -- whether before or after coupling -- as a boolean hyperparameter and use standard machine learning techniques to find the optimal value.
+\item[1.] One can treat the decision on when to apply change of priors---whether before or after coupling---as a boolean hyperparameter and use standard machine learning techniques to find the optimal value.
 \item[2.] One can investigate applicability of a Bayes covariant method. 
-This may take two forms, either choose a Bayes covariant coupling method, or experiment with changing of algorithm to construct binary classifiers.
-\item[3.] Choose another multi-class probabilistic classification algorithm outside of one-vs-one framework. 
 \end{itemize}
+%\subsection{Properties of coupling methods}
 
-\subsection{Properties of coupling methods}
-
-In this section  we summarize properties of coupling methods discussed in our work.
+In order to ease the second approach,   we now summarize properties of parameterless coupling methods discussed in our work.
 Table \ref{tab:summaryCoupling} concisely lists the relevant properties enjoyed by each method.
@@
 	\item whether a coupling method amounts to a linear system of equations,
-	\item if the coupling method amounts to a linear system of equations, whether the equations are of a special form (e.g. a Markov matrix) that facilitates their solution,
+	\item if the coupling method amounts to a linear system of equations, whether the equations are of a special form (e.g., a Markov matrix) that facilitates their solution,
 	\item whether the authors who published the method provide an iterative method that implements the estimate.
@@
 \begin{table}[!ht]
-	\begin{tabular}{cm{2.5cm}|m{1.5cm}|m{1.5cm}ccm{1.5cm}|m{1.5cm}}
-		&& less competitive & \multicolumn{4}{c|}{competitive method} & oracle \\
+	\begin{tabular}{cm{2.5cm}|m{1.5cm}ccm{1.5cm}|m{1.5cm}}
+	%	&& less competitive & \multicolumn{4}{c|}{competitive method} & oracle \\
 		\hline 
-		&methods & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
+		&methods % & Hastie-Tibshirani 
+			& Wu--Lin--Weng & radial & normal & arboreal & Hinton's oracle \\
 		\hline 
-		&source & \cite{hastie1998classification} & \cite{wu2004probability} & \cite{vsuch2015new} & \cite{vsuch2016bayes} & this work & this work \\
+		&source % & \cite{hastie1998classification} 
+			& \cite{wu2004probability} & \cite{vsuch2015new} & \cite{vsuch2016bayes} & this work & this work \\
 		\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
-		&uniqueness &  yes & yes & yes & yes & yes & yes \\
-		&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
-		&canonicity & yes & no & yes & yes & no & yes \\
-		&symmetry & yes & yes & yes & yes & no & yes \\
-		& Bayes covariant & no & no & no & yes & yes & yes \\
+		&uniqueness % &  yes 
+			& yes & yes & yes & yes & yes \\
+		&Bradley--Terry consistency %& yes 
+			& yes & yes & yes & yes & yes \\
+		&canonicity %& yes 
+			& no & yes & yes & no & yes \\
+		&symmetry % & yes 
+			& yes & yes & yes & no & yes \\
+		& Bayes covariant %& no 
+			& no & no & yes & yes & yes \\
 		\hline
 		\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
-		&Hinton's minimality & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
-		&robustness & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
-		&lack of parameters & yes & yes & yes & yes & yes & yes \\
-		& amounts to a linear system & no & yes & yes & yes & yes & yes\\
-		& linear system of special form & N/A & no & yes & yes & yes & yes \\
-		& iterative method & yes & yes & yes & no & not needed & not needed\\
+		&Hinton's minimality %& N/A 
+			& \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
+		&robustness %& N/A 
+			& \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
+		&lack of parameters %& yes 
+			& yes & yes & yes & yes & yes \\
+		& amounts to a linear system % & no 
+			& yes & yes & yes & yes & yes\\
+		& linear system of special form % & N/A 
+			& no & yes & yes & yes & yes \\
+		& iterative method %& yes 
+			& yes & yes & no & not needed & not needed\\
 		\hline

### 2025-08-13 experiment.tex
Peter's proof

@@
 	\includegraphics{graphs/exp1-plot1.pdf}
-	\caption{Success rate plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
+	\caption{Accuracy of classification plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
 	\label{fig:exp1-plot1}
@@
 \begin{figure}[!ht]
-\includegraphics{graphs/exp2-summary.pdf}
-\caption{Comparison of success rate for parametric Bayes covariant methods \eqref{eq:family} vs. Wu-Lin-Weng's method}
+\includegraphics{exp2-plot2.pdf}
+\caption{Comparison of accuracy for parametric Bayes covariant methods \eqref{eq:family} vs. Wu-Lin-Weng's method}
 \label{fig:par-bc}

### 2025-08-13 exp2-plot2.R

@@ -1,0 +1,31 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2)
+
+source("theme.R")
+
+
+df1 <- read.csv("data/exp2.csv") |> 
+    mutate(outcome = if_else(cv_acc >= wlw2, "gt", "lt")) |> 
+    group_by(dataset, outcome) |>
+    summarize(count = n())
+
+df1$outcome = as.factor(df1$outcome)
+
+plt1 <- ggplot(df1, aes(x = dataset, y = count, fill = outcome)) + 
+    geom_col() + theme_minimal(base_size = 9) + coord_flip() + pub_theme + 
+    	scale_fill_manual(
+          values = c("gt" = "seagreen", "lt" = "brown"),
+	  labels = c(expression(parametric >= bolditalic(wlw)),
+		     expression(parametric < bolditalic(wlw))),
+	  name = "accuracy comparison"
+	  )
+
+ggsave(
+  filename = "exp2-plot2.pdf",
+    plot = plt1,
+    width = 5.5,   # Width in inches
+    height = 2.5,  # Height in inches
+    units = "in"   # Specify units as inches
+)
+

### 2025-08-13 exp2-summary.R

@@ -6,23 +6,8 @@ source('lda.R')
 source("theme.R")
 
 
+set.seed(123)
 pt <- par_triples(limit = 1000)
-df1 <- pt$df |> 
-    mutate(outcome = if_else(cv_acc >= wlw2, "parametric >= WLW", "parametric < WLW")) |> 
-    group_by(dataset, outcome) |>
-    summarize(count = n())
-
-plt1 <- ggplot(df1, aes(x = dataset, y = count, color = outcome, fill = outcome)) + 
-    geom_col() + theme_minimal(base_size = 9) + coord_flip() + pub_theme
-
 write.csv(pt$df, file = "data/exp2.csv")
 
-
-ggsave(
-  filename = "exp2-summary.pdf",
-    plot = plt1,
-    width = 5.5,   # Width in inches
-    height = 2.5,  # Height in inches
-    units = "in"   # Specify units as inches
-)
 

### 2025-08-13 tab-sep.R
Change to percentages

@@ -10,13 +10,13 @@ df1 <- df |> group_by(dataset, status, K) |> summarize(count = n() ) |>
               names_from = "status", 
               values_from = "pct", 
               values_fill = 0) |>
-  mutate(separable = optimal)  |>
- select(dataset, K, optimal)
+  mutate(separable = sprintf("%.0f %%   ", 100 * optimal))  |>
+  select(dataset, K, separable)
 
-colnames(df1) <- c("Dataset", "$K$", "Portion linearly separable")
+colnames(df1) <- c("Dataset", "$K$", "Percentage linearly separable")
 
 sink("tab-sep.tex")
-print(xtable(df1, label = "tab:sep", digits = 3,
-             caption = "The benchmark datasets with indication of the number of classes $K$ and the portion of binary classification problems that are linearly separable",
+print(xtable(df1, label = "tab:sep", align = c("l", "l", "r", "r"), digits = 3,
+             caption = "The benchmark datasets with indication of the number of classes $K$ and the percentage of binary classification problems that are linearly separable",
 ),  include.rownames = FALSE, sanitize.colnames.function = identity)
 sink()

### 2025-08-13 tab-step2.R

@@ -8,7 +8,8 @@ df1 <- df |> mutate(omit = pmax(omit12, omit13, omit23)) |>
             summarize(` $\\boldsymbol{e}_3$ at least as accurate as $\\boldsymbol{wlw}$` = mean(normal >= wlw2),
                       `one of $\\boldsymbol{s}_1, \\boldsymbol{s}_2, \\boldsymbol{s}_3$ at least as accurate as $\\boldsymbol{wlw}$` = mean(omit >= wlw2),
                       `$\\boldsymbol{wlw}$ more accurate than $\\boldsymbol{e}_3, \\boldsymbol{s}_1, \\boldsymbol{s}_2, \\boldsymbol{s}_3$` = mean(wlw2 > normal & wlw2 > omit)) |>
-      pivot_longer(everything(), names_to = 'Outcome', values_to = "Portion")
+      pivot_longer(everything(), names_to = 'Outcome', values_to = "Portion") |>
+      mutate(Percentage = sprintf("%.0f \\%%  ", 100 * Portion)) |>	select(-Portion)
             
                       
                       
@@ -17,6 +18,7 @@ df1 <- df |> mutate(omit = pmax(omit12, omit13, omit23)) |>
 # colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
 sink("tab-step2.tex")
 print(xtable(df1, label = "tab:step2", digits = 2,
+	     align = c("r", "l", "r"),
              caption = "Comparison of Wu-Lin-Weng's method $\\boldsymbol{wlw}$ and  parameterless coupling methods on three class subsets. "), 
     sanitize.text.function = identity,
     include.rownames = FALSE)

### 2025-08-14 PatRec.tex
Correct hyphenation of Wu-Lin-Weng

--- 2025-06-20 paper.tex
@@
-\documentclass[twoside,11pt]{article}
+%\documentclass[twoside,11pt]{article}
+\documentclass[a4paper,fleqn]{cas-sc}
+
+\usepackage[authoryear,longnamesfirst]{natbib}
 
@@
 \usepackage{amsmath, amsthm, amssymb}
-\usepackage{jmlr2e}
+%\usepackage{jmlr2e}
 
@@
 \usepackage{lastpage}
-\jmlrheading{23}{2025}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
+%\jmlrheading{23}{2025}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
+%
+%% Short headings should be running head and authors last names
+%
+%\ShortHeadings{Probabilistic OVO}{Probabilistic OVO}
+%\firstpageno{1}
 
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Probabilistic OVO}{Probabilistic OVO}
-\firstpageno{1}
+%%%Author macros
+\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
+\tsc{WGM}
+\tsc{QE}
+\tsc{EP}
+\tsc{PMS}
+\tsc{BEC}
+\tsc{DE}
+%%%
 
@@
 
+\let\WriteBookmarks\relax
+\def\floatpagepagefraction{1}
+\def\textpagefraction{.001}
+\shorttitle{Leveraging social media news}
+\shortauthors{J.K. Krishnan et~al.}
+%\begin{frontmatter}
+
+%	\title [mode = title]{This is a specimen $a_b$ title}                      
 \title{New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification }
+\tnotemark[1,2]
 
-\author{\name Ondrej Šuch \email ondrejs@savbb.sk \\
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       \AND
-       \name Peter Novotný \email peter.novotny@fri.uniza.sk \\
-       \addr Fakulta informatiky a riadenia\\
-       Žilinská Univerzita v Žiline\\
-       Žilina, 010 26, Slovakia
-       \AND
-       \name Ali Haidar \email haidar@savbb.sk \\
-       \begin{minipage}[t]{0.45\textwidth}
-       \addr Matematický ústav SAV\\
-       Ďumbierska 1\\
-       Banská Bystrica, 974 01, Slovakia
-       \end{minipage}\hfill
-       \begin{minipage}[t]{0.45\textwidth}
-       \addr Fakulta matematiky, fyziky a informatiky\\
-       Univerzity Komenského \\
-       Mlynská dolina F1 \\
-       Bratislava, 842 48, Slovakia
-       \end{minipage}
-       }
+\tnotetext[1]{This document is the results of the research
+		project funded by the National Science Foundation.}
 
-\editor{My editor}
+\tnotetext[2]{The second title footnote which is a longer text matter
+		to fill through the whole text width and overflow into
+		another line in the footnotes area of the first page.}
 
-\maketitle
+\author[1]{O. Šuch}
+\cormark[1]
+\ead{ondrejs@savbb.sk}
+
+\affiliation[1]{organization={Matematický ústav Slovenskej Akadémie Vied},
+		addressline={Ďumbierska 1},
+		city = {Banská Bystrica},
+		postcode = {97411},
+		country = {Slovakia}}
+
+\author[2]{P. Novotný}
+\cormark[2]
+\ead{peter.novotny@fri.uniza.sk}
+
+\affiliation[2]{organization = {Žilinská Univerzita v Žiline},
+addressline={Univerzitná 8215/1},
+city={Žilina},
+postcode = {01026},
+country = {Slovakia}}
+
+%\author{\name Ondrej Šuch \email ondrejs@savbb.sk \\
+%       \addr Matematický ústav SAV\\
+%       Ďumbierska 1\\
+%       Banská Bystrica, 974 01, Slovakia
+%       \AND
+%       \name Peter Novotný \email peter.novotny@fri.uniza.sk \\
+%       \addr Fakulta informatiky a riadenia\\
+%       Žilinská Univerzita v Žiline\\
+%       Žilina, 010 26, Slovakia
+%       \AND
+%       \name Ali Haidar \email haidar@savbb.sk \\
+%       \begin{minipage}[t]{0.45\textwidth}
+%       \addr Matematický ústav SAV\\
+%       Ďumbierska 1\\
+%       Banská Bystrica, 974 01, Slovakia
+%       \end{minipage}\hfill
+%       \begin{minipage}[t]{0.45\textwidth}
+%       \addr Fakulta matematiky, fyziky a informatiky\\
+%       Univerzity Komenského \\
+%       Mlynská dolina F1 \\
+%       Bratislava, 842 48, Slovakia
+%       \end{minipage}
+%       }
+
+%\editor{My editor}
 
@@
 In majority of cases, it is possible to find a Bayes covariant method matching performance of Wu-Lin-Weng's method.
-
 \end{abstract}
 
+\begin{highlights}
+\item New Bayes covariant coupling methods
+\item New way to create ensembles of multiple Bayes covariant methods
+\item Unification of Hastie-Tibshirani and Wu-Lin-Weng method
+\item Rigorous evaluation of coupling methods
+\end{highlights}
+
 \begin{keywords}
-  distribution shift, label shift, pairwise coupling, one-vs-one classification, Bayes classifier
+  distribution shift \sep label shift \sep pairwise coupling \sep one-vs-one classification \sep Bayes classifier
 \end{keywords}
+
+\maketitle
 
@@
 
-\acks{Research on this paper was partially supported by grant VEGA 2/0172/22 Classification using ensembles of neural networks.  }
+\acks{Research on this paper was partially supported by grant VEGA 2/0172/22 Classification using ensembles of neural networks.
+We thank Muhammad Azeem for helpful discussion during preparation of our paper.
+}
 

### 2025-08-14 coupling.tex
Correct hyphenation of Wu-Lin-Weng

@@
 
-The quadratic score is the basis of the popular Wu-Lin-Weng's method \cite{wu2004probability}. 
+The quadratic score is the basis of the popular Wu--Lin--Weng's method \cite{wu2004probability}. 
 Their method uses an additional trick, which we term \emph{self-referentiality}.
@@
 However the choice of weights $w_{ij}$ to make the method computationally amenable is somewhat arbitrary.
-Thus we do not view Wu-Lin-Weng's method as canonical.
+Thus we do not view Wu--Lin--Weng's method as canonical.
 

### 2025-08-14 discussion.tex
Correct hyphenation of Wu-Lin-Weng

@@
 The method that ignores binary classifiers not trained on a given sample (we call it Hinton's oracle) underperforms the method of Wu--Lin--Weng.
-	\item In more than half of classification problems we were able to find a Bayes covariant coupling method which matches performance of the Wu-Lin-Weng method. 
+	\item In more than half of classification problems we were able to find a Bayes covariant coupling method which matches performance of the Wu--Lin--Weng method. 
 \end{itemize}
@@
 	\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.
-The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu-Lin-Weng \cite{wu2004probability}.}
+The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu--Lin--Weng \cite{wu2004probability}.}
 	\label{tab:summaryCoupling}
@@
 Based on our findings we see two immediate pathways for future research.
-First, one can study arboreal methods in more detail, since these are Bayes covariant and as shown in Section \ref{sec:exp2} they often provide performance matching that of Wu-Lin-Weng's method.
+First, one can study arboreal methods in more detail, since these are Bayes covariant and as shown in Section \ref{sec:exp2} they often provide performance matching that of Wu--Lin--Weng's method.
 Secondly, there is a continuum of Bayes covariant methods which we barely sketched.

### 2025-08-14 experiment.tex
Correct hyphenation of Wu-Lin-Weng

@@
 	\item[(a)] Which coupling methods without parameters show good performance across diverse data sets?
-Is it the orthodox method of Wu-Lin-Weng?
+Is it the orthodox method of Wu--Lin--Weng?
 An experiment to answer this question is carried out Section \ref{sec:exp1}.
@@
 Small probabilities generally have very little effect on the implementation of Bayes covariant methods which generally operate using log-odds.
-However small probabilities do affect both the method of Wu-Lin-Weng as well as radial method, because then Assumption \ref{ass:2} fails to hold.
+However small probabilities do affect both the method of Wu--Lin--Weng as well as radial method, because then Assumption \ref{ass:2} fails to hold.
 
@@
 \begin{itemize}
-\item method of Wu-Lin-Weng, which is widely used in software libraries, and thus can be viewed as an orthodox choice,
+\item method of Wu--Lin--Weng, which is widely used in software libraries, and thus can be viewed as an orthodox choice,
 \item normal coupling, which is Bayes covariant,
@@
 The results are shown in Figure \ref{fig:exp1-plot1}.
-We can clearly see that Wu-Lin-Weng's method has the most robust performance.
+We can clearly see that Wu--Lin--Weng's method has the most robust performance.
 On some datasets it trounces normal coupling method by a wide margin.
 The edge over the radial method is smaller with only mnist and usps datasets showing a significant difference for smaller values of $tol$ hyperparameter.
-However in view of Theorem \ref{thm:K3} the Wu-Lin-Weng's method is not Bayes covariant, therefore we will extend the set of Bayes covariant methods beyond the canonical normal coupling.
+However in view of Theorem \ref{thm:K3} the Wu--Lin--Weng's method is not Bayes covariant, therefore we will extend the set of Bayes covariant methods beyond the canonical normal coupling.
 
@@
 
-In this experiment we compare  Bayes covariant coupling methods \emph{without} parameters that could match the performance of Wu-Lin-Weng's method.
+In this experiment we compare  Bayes covariant coupling methods \emph{without} parameters that could match the performance of Wu--Lin--Weng's method.
 We investigate  the case of three class datasets.
@@
 
-We can see that in slightly less than half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu-Lin-Weng's method.
+We can see that in slightly less than half of the cases none of the four parameterless Bayes covariant methods was able to match the performance of Wu--Lin--Weng's method.
 This leads us to extend evaluation to Bayes covariant methods with parameters.
@@
 
-We start by selecting 1000 three class subsets from all datasets for problems where normal method was outperformed by Wu-Lin-Weng's method.
-For each three-class classification problem we will try to match the performance of Wu-Lin-Weng method with a Bayes covariant method in family \eqref{eq:family}.
+We start by selecting 1000 three class subsets from all datasets for problems where normal method was outperformed by Wu--Lin--Weng's method.
+For each three-class classification problem we will try to match the performance of Wu--Lin--Weng method with a Bayes covariant method in family \eqref{eq:family}.
 
@@
 \item To avoid bias in selection of parameters $a_1, a_2, a_3$ we use a subset of testing dataset to find their optimal values.
-As a result, we will be comparing the accuracy of Wu-Lin-Weng method evaluated with repeated five-fold cross-validation accuracy of a method in family \eqref{eq:family}.
+As a result, we will be comparing the accuracy of Wu--Lin--Weng method evaluated with repeated five-fold cross-validation accuracy of a method in family \eqref{eq:family}.
 We use 20 repetitions.
@@
 We choose to examine points in the simplex defined by  $a_i\geq 0$, for $i=1,2,3$.
-As Table \ref{tab:step2} shows, this simplex contained in more than half cases a Bayes covariant method matching the performance of Wu-Lin-Weng's method.
+As Table \ref{tab:step2} shows, this simplex contained in more than half cases a Bayes covariant method matching the performance of Wu--Lin--Weng's method.
 \end{itemize}
@@
 \includegraphics{exp2-plot2.pdf}
-\caption{Comparison of accuracy for parametric Bayes covariant methods \eqref{eq:family} vs. Wu-Lin-Weng's method}
+\caption{Comparison of accuracy for parametric Bayes covariant methods \eqref{eq:family} vs. Wu--Lin--Weng's method}
 \label{fig:par-bc}
@@
 The summary statistics are shown in Figure \ref{fig:par-bc}.
-We can see that only in minority of cases we found a parametric Bayes covariant coupling method matching the performance of Wu-Lin-Weng's method.
+We can see that only in minority of cases we found a parametric Bayes covariant coupling method matching the performance of Wu--Lin--Weng's method.
 
@@
 %
-%We determined that among the 1000 three-class problems we have examined, the largest gap between Bayes-covariant parametric methods and Wu-Lin-Weng method occurred for mnist dataset and classes 5,6,9.
+%We determined that among the 1000 three-class problems we have examined, the largest gap between Bayes-covariant parametric methods and Wu--Lin--Weng method occurred for mnist dataset and classes 5,6,9.
 Figure
@@
 \subsection{Experiment: Effect of change of priors}  \label{sec:exp4}
-%\subsection{Wu-Lin-Weng's method}
+%\subsection{Wu--Lin--Weng's method}
 
-We have shown that are situations when Wu-Lin-Weng's method outperforms even the best Bayes-covariant parametric methods.
+We have shown that are situations when Wu--Lin--Weng's method outperforms even the best Bayes-covariant parametric methods.
 In this section we thus ponder the question whether some non-Bayes covariant method would be more resilients to change of priors.
@@
 The results, as expected, detect no change between $\boldsymbol{c}_1, \boldsymbol{c}_2$ for normal coupling method.
-However, there is no consistent difference in spread between radial and Wu-Lin-Weng's coupling method.
+However, there is no consistent difference in spread between radial and Wu--Lin--Weng's coupling method.
 Spread for the radial method is lower for 3 datasets (letter, mnist, usps datasets), higher for 3 datasets (dna, satimage, segment) and tied for waveform dataset.
@@
 	\includegraphics{exp4-truth.pdf}
-	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for radial and Wu-Lin-Weng's coupling method.}
+	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for radial and Wu--Lin--Weng's coupling method.}
 	\label{fig:score}

### 2025-08-14 spf.tex
Correct hyphenation of Wu-Lin-Weng

%Version 3.1 December 2024
% See section 11 of the User Manual for version history
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing

%%=======================================================%%
%% to print line numbers in the margin use lineno option %%
%%=======================================================%%

%%\documentclass[lineno,pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%=========================================================================================%%
%% the documentclass is set to pdflatex as default. You can delete it if not appropriate.  %%
%%=========================================================================================%%

%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%Note: the following reference styles support Namedate and Numbered referencing. By default the style follows the most common style. To switch between the options you can add or remove ?Numbered? in the optional parenthesis. 
%%The option is available for: sn-basic.bst, sn-chicago.bst%

%%\documentclass[pdflatex,sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style
%%\documentclass[pdflatex,sn-mathphys-ay]{sn-jnl}% Math and Physical Sciences Author Year Reference Style
%%\documentclass[pdflatex,sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[pdflatex,sn-vancouver-num]{sn-jnl}% Vancouver Numbered Reference Style
%%\documentclass[pdflatex,sn-vancouver-ay]{sn-jnl}% Vancouver Author Year Reference Style
%%\documentclass[pdflatex,sn-apa]{sn-jnl}% APA Reference Style
%%\documentclass[pdflatex,sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style

%%%% Standard Packages
%%<additional latex packages if required can be included here>

\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published 
%%%%  by Springer Nature. The guidance has been prepared in partnership with 
%%%%  production teams to conform to Springer Nature technical requirements. 
%%%%  Editorial and presentation requirements differ among journal portfolios and 
%%%%  research disciplines. You may find sections in this template are irrelevant 
%%%%  to your work and are empowered to omit any such section if allowed by the 
%%%%  journal you intend to submit to. The submission guidelines and policies 
%%%%  of the journal take precedence. A detailed User Manual is available in the 
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

\usepackage{makecell}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{tikz-cd}
\usepackage[utf8]{inputenc} % Enable UTF-8 encoding
\usepackage[T1]{fontenc}
\usepackage{textgreek}
%\undef\orcidlogo

\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{assumption}{Assumption}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
\DeclareMathOperator*{\divm}{div}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

\usepackage{etoolbox}
\let\orcidlogo\relax
\usepackage{orcidlink}

\begin{document}

\title[Change of priors]{New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification}

%%=============================================================%%
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% \author*[1,2]{\fnm{Joergen W.} \spfx{van der} \sur{Ploeg} 
%%  \sfx{IV}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1]{\fnm{Ondrej} \sur{Šuch} \orcidlink{0000-0002-8140-241X}}\email{ondrejs@savbb.sk}
%\equalcont{These authors contributed equally to this work.}

\author[2]{\fnm{Peter} \sur{Novotný}\orcidlink{0000-0002-7949-5215}}\email{peter.novotny@fri.uniza.sk}

\author[1,3]{\fnm{Ali} \sur{Haidar}\orcidlink{0000-0002-7498-4220}}\email{haidar@savbb.sk}
%\equalcont{These authors contributed equally to this work.}

\affil[1]{\orgdiv{Matematický ústav}, \orgname{Slovenská akadémia vied}, 
\orgaddress{\street{Ďumbierska 1}, \city{Banská Bystrica}, \postcode{97411}, \country{Slovakia}}}

\affil*[2]{\orgdiv{Fakulta riadenia a informatiky}, \orgname{Žilinská Univerzita v Žiline}, 
\orgaddress{\street{Univerzitná 8215/1}, \city{Žilina}, \postcode{01026},  \country{Slovakia}}}

\affil[3]{\orgdiv{Fakulta matematiky, fyziky a informatiky}, 
\orgname{Univerzita Komenského}, \orgaddress{\street{Mlynská dolina F1}, \city{Bratislava}, \postcode{84248},  
\country{Slovakia}}}

%%==================================%%
%% Sample for unstructured abstract %%
%%==================================%%

\abstract{Label shift is one kind of distribution shift affecting classification models. Generally, one uses transformation inspired by Bayes classifiers to 
adjust predictions of probabilistic classification models. However, there is an ambiguity how to apply this transformation in the case of  probabilistic models built in one-vs-one (also called pairwise) fashion. One-vs-one classification relies on the choice of a coupling method. Some coupling methods -- called Bayes covariant --  are not affected by the ambiguity. Adopting a Bayes covariant method would be the ideal solution to the ambiguity. However, the most commonly used coupling  method of Wu-Lin-Weng is not Bayes covariant. In our study we present elements of theory of coupling methods and exhibit new Bayes covariant coupling methods. One class is formed by arboreal methods. Still more methods can be formed by the way of ensembling. We compare their performance with that of Wu-Lin-Weng's coupling method. In majority of cases, it is possible to find a Bayes covariant method matching performance of Wu-Lin-Weng's method. }

%%================================%%
%% Sample for structured abstract %%
%%================================%%

% \abstract{\textbf{Purpose:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
% 
% \textbf{Methods:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
% 
% \textbf{Results:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
% 
% \textbf{Conclusion:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}

\keywords{ distribution shift, label shift, pairwise coupling, one-vs-one classification, Bayes classifier}

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

\maketitle

% \input{intro.tex}
% 
% \input{theory.tex}
% 
% \input{coupling.tex}
% 
% \input{experiment.tex}
% 
% \input{discussion.tex}

\backmatter

\bmhead{Supplementary information}

If your article has accompanying supplementary file/s please state so here.

Authors reporting data from electrophoretic gels and blots should supply the full unprocessed scans for key as part of their Supplementary information. This may be requested by the editorial team/s if it is missing.

Please refer to Journal-level guidance for any specific requirements.

\bmhead{Acknowledgements}

Acknowledgements are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.

Please refer to Journal-level guidance for any specific requirements.

\section*{Declarations}

Some journals require declarations to be submitted in a standardised format. Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section. If yes, your manuscript must contain the following sections under the heading `Declarations':

Ondrej Šuch and Ali Haidar were  partially supported by grants VEGA 2/0172/22 Classification using ensembles of neural networks and VEGA 2/0056/25 Cycles and edge colorings of cubic graphs. Peter Novotný did not receive support from any organization for the submitted work.

\begin{itemize}
\item Funding
\item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
\item Ethics approval and consent to participate
\item Consent for publication
\item Data availability 
\item Materials availability
\item Code availability 
\item Author contribution
\end{itemize}

\noindent
If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.

%%===================================================%%
%% For presentation purpose, we have included        %%
%% \bigskip command. Please ignore this.             %%
%%===================================================%%
\bigskip
\begin{flushleft}%
Editorial Policies for:

\bigskip\noindent
Springer journals and proceedings: \url{https://www.springer.com/gp/editorial-policies}

\bigskip\noindent
Nature Portfolio journals: \url{https://www.nature.com/nature-research/editorial-policies}

\bigskip\noindent
\textit{Scientific Reports}: \url{https://www.nature.com/srep/journal-policies/editorial-policies}

\bigskip\noindent
BMC journals: \url{https://www.biomedcentral.com/getpublished/editorial-policies}
\end{flushleft}

%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl

\end{document}

### 2025-08-14 tab-exp4.tex
Correct hyphenation of Wu-Lin-Weng

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Mon Jun 16 08:56:49 2025
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrrr}
  \hline
method & dna & letter & mnist & satimage & segment & usps & waveform \\ 
  \hline
normal & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 \\ 
  radial & 0.022 & 0.039 & 0.020 & 0.014 & 0.009 & 0.014 & 0.002 \\ 
  wlw2 & 0.015 & 0.044 & 0.030 & 0.013 & 0.007 & 0.020 & 0.002 \\ 
   \hline
\end{tabular}
\caption{Comparison of the difference in accuracies between methods $\boldsymbol{c}_1$ and
             $\boldsymbol{c}_2$} 
\label{tab:exp4}
\end{table}

### 2025-08-14 tab-sep.tex
Correct hyphenation of Wu-Lin-Weng

% latex table generated in R 4.5.1 by xtable 1.8-4 package
% Wed Aug 13 15:27:15 2025
\begin{table}[ht]
\centering
\begin{tabular}{lrr}
  \hline
Dataset & $K$ & Percentage linearly separable \\ 
  \hline
dna &    3 & 100 \%    \\ 
  letter &   26 & 99 \%    \\ 
  mnist &   10 & 100 \%    \\ 
  satimage &    6 & 84 \%    \\ 
  segment &    7 & 89 \%    \\ 
  usps &   10 & 100 \%    \\ 
  waveform &    3 & 0 \%    \\ 
   \hline
\end{tabular}
\caption{The benchmark datasets with indication of the number of classes $K$ and the percentage of binary classification problems that are linearly separable} 
\label{tab:sep}
\end{table}

### 2025-08-14 tab-step2.tex
Correct hyphenation of Wu-Lin-Weng

% latex table generated in R 4.5.1 by xtable 1.8-4 package
% Thu Aug 14 09:38:32 2025
\begin{table}[ht]
\centering
\begin{tabular}{lr}
  \hline
Outcome & Percentage \\ 
  \hline
 $\boldsymbol{e}_3$ at least as accurate as $\boldsymbol{wlw}$ & 24 \%   \\ 
  one of $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$ at least as accurate as $\boldsymbol{wlw}$ & 53 \%   \\ 
  $\boldsymbol{wlw}$ more accurate than $\boldsymbol{e}_3, \boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$ & 39 \%   \\ 
   \hline
\end{tabular}
\caption{Comparison of Wu--Lin--Weng's method $\boldsymbol{wlw}$ and  parameterless coupling methods on three class subsets. } 
\label{tab:step2}
\end{table}

### 2025-08-14 tab-multi.R

@@ -7,7 +7,7 @@ df <- read.csv("data/multi-acc.csv")
 df1 <- df |> group_by(dataset) |> summarize(normal = mean(normal)/1000, 
                                             radial = mean(radial)/1000, 
                                             wlw2 = mean(wlw2)/1000)
-colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
+colnames(df1) <- c("dataset", "normal", "radial", "Wu--Lin--Weng")
 sink("tab-multi.tex")
 print(xtable(df1, label = "tab:multi", digits = 2,
              caption = "Comparison of 0-1 score for three parameterless coupling methods"

### 2025-08-14 tab-step2.R

@@ -19,7 +19,7 @@ df1 <- df |> mutate(omit = pmax(omit12, omit13, omit23)) |>
 sink("tab-step2.tex")
 print(xtable(df1, label = "tab:step2", digits = 2,
 	     align = c("r", "l", "r"),
-             caption = "Comparison of Wu-Lin-Weng's method $\\boldsymbol{wlw}$ and  parameterless coupling methods on three class subsets. "), 
+             caption = "Comparison of Wu--Lin--Weng's method $\\boldsymbol{wlw}$ and  parameterless coupling methods on three class subsets. "), 
     sanitize.text.function = identity,
     include.rownames = FALSE)
 sink()

### 2025-08-15 experiment.tex
Fixes in experiments

@@
 
-We have shown that are situations when Wu--Lin--Weng's method outperforms even the best Bayes-covariant parametric methods.
-In this section we thus ponder the question whether some non-Bayes covariant method would be more resilients to change of priors.
+We have shown that there are situations when Wu--Lin--Weng's method outperforms all Bayes covariant parametric methods we considered.
+In this section we thus ponder the question whether some non-Bayes-covariant method would be more resilient to change of priors.
 We consider two facets to this question.
@@
 
-The results, as expected, detect no change between $\boldsymbol{c}_1, \boldsymbol{c}_2$ for normal coupling method.
+The results, as expected, detect no spread between $\boldsymbol{c}_1, \boldsymbol{c}_2$ for normal coupling method.
 However, there is no consistent difference in spread between radial and Wu--Lin--Weng's coupling method.
-Spread for the radial method is lower for 3 datasets (letter, mnist, usps datasets), higher for 3 datasets (dna, satimage, segment) and tied for waveform dataset.
+Spread for the radial method is lower for 3 datasets (letter, mnist, usps), higher for 3 datasets (dna, satimage, segment) and tied for waveform dataset.
 

### 2025-08-15 exp2-plot2.R

@@ -13,7 +13,7 @@ df1 <- read.csv("data/exp2.csv") |>
 df1$outcome = as.factor(df1$outcome)
 
 plt1 <- ggplot(df1, aes(x = dataset, y = count, fill = outcome)) + 
-    geom_col() + theme_minimal(base_size = 9) + coord_flip() + pub_theme + 
+    geom_col(width = 0.5) + theme_minimal(base_size = 9) + coord_flip() + pub_theme + 
     	scale_fill_manual(
           values = c("gt" = "seagreen", "lt" = "brown"),
 	  labels = c(expression(parametric >= bolditalic(wlw)),
@@ -25,7 +25,7 @@ ggsave(
   filename = "exp2-plot2.pdf",
     plot = plt1,
     width = 5.5,   # Width in inches
-    height = 2.5,  # Height in inches
+    height = 2.1,  # Height in inches
     units = "in"   # Specify units as inches
 )
 

### 2025-08-15 msvm.R

@@ -1,7 +1,7 @@
 library(e1071)
 suppressPackageStartupMessages(library(dplyr))
 library(Rcpp)
-library(ParBayesianOptimization)
+# library(ParBayesianOptimization)
 suppressPackageStartupMessages(library(furrr))
 library(future)
 library(magrittr)

### 2025-08-15 tab-exp4.R

@@ -6,13 +6,13 @@ library(xtable)
 
 df <- read.csv("data/exp4.csv")
 
-df1 <- df |> group_by(dataset, method) |> 
+df1 <- df |> group_by(dataset, method) |> mutate(method = ifelse(method == "wlw2", "$\\boldsymbol{wlw}$", method)) |>
     summarize(c2c1 = mean(c2c1)) |> pivot_wider(names_from = "dataset", values_from = c2c1)
 # colnames(df1) <- c("dataset", "normal", "radial", "Wu-Lin-Weng")
 sink("tab-exp4.tex")
 print(xtable(df1, label = "tab:exp4", digits = 3,
-             caption = "Comparison of the difference in accuracies between methods $\\boldsymbol{c}_1$ and
+             caption = "Comparison of the difference in accuracies between models $\\boldsymbol{c}_1$ and
              $\\boldsymbol{c}_2$"
-),  include.rownames = FALSE)
+),  include.rownames = FALSE, sanitize.text.function = identity)
 sink()
 

### 2025-08-20 experiment.tex
Added changes to experiment

@@
 The second question is whether a coupling method would more consistently provide true answers.
-Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large.
-Thus to evaluate this question
+In Figure \ref{fig:score} we show the difference of accuracies of the classification models $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ after ten-fold change of priors.
+Again we can see, that there is no uniform advantage to either method.
+% Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large. Thus to evaluate this question
 
@@
 	\includegraphics{exp4-truth.pdf}
-	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for radial and Wu--Lin--Weng's coupling method.}
+	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for radial and Wu--Lin--Weng's coupling method after change of priors.}
 	\label{fig:score}

### 2025-08-20 experiment.tex
Changes to the last experiment

@@
 
-The second question is whether a coupling method would more consistently provide true answers.
-In Figure \ref{fig:score} we show the difference of accuracies of the classification models $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ after ten-fold change of priors.
-Again we can see, that there is no uniform advantage to either method.
-% Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large. Thus to evaluate this question
-
 \begin{figure}[!ht]
@@
 \end{figure}
+
+The second question is whether a coupling method would more consistently provide true answers.
+In Figure \ref{fig:score} we show the difference of accuracies of the classification models $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ after ten-fold change of priors for 'mnist' dataset.
+Again we can see, that there is no uniform advantage to either method.
+% Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large. Thus to evaluate this question

### 2025-08-20 exp4-truth.R

@@ -1,19 +1,24 @@
 library(ggplot2)
 library(dplyr)
+source("theme.R")
 
-df <- read.csv("data/exp4.csv") |> mutate(diff = multi-binary) |> mutate(step2 = multi) |> mutate(step1 = binary)
+df <- read.csv("data/exp4.csv") |>  mutate(step2 = multi) |> mutate(step1 = binary)
+
 df$class = as.factor(df$changed - 1)
 
-df1 <- df |> filter(dataset ==  "mnist")
+df1 <- df |> filter(dataset ==  "mnist") |> group_by(class) |> mutate(diff = mean(step2 - step1))
 
-plt1 <- ggplot(df1, aes(x = class, y = step2 - step1, color = method)) +  facet_wrap(~ method) + 
-geom_col(data = df1, aes(x = class, y = step2 - step1, color = method), fill = "black", width = 0.7) +
-theme_minimal() + ylab("count")
+plt1 <- ggplot(df1, aes(x = class, y = diff, fill = method, color = method)) +  facet_wrap(~ method) + 
+	geom_col(data = df1, aes(x = class, y = diff, color = method), width = 0.7) +
+	ylab("accuracy difference") + pub_theme +  guides(fill = guide_legend(keyheight = unit(1.2, "lines"))) +
+	theme(legend.position = "none")
+# legend.key.height = unit(1.2, "cm"),       # increase box height in legend
+# legend.spacing.y = unit(0.6, "cm"))
 
 ggsave(
     filename = "exp4-truth.pdf",
     plot = plt1,
     width = 5.5,
-    height  = 2.5,
+    height  = 2.4,
     units = "in"
     )

### 2025-08-26 exp4-truth.R
Fix computation of differences

@@ -6,7 +6,7 @@ df <- read.csv("data/exp4.csv") |>  mutate(step2 = multi) |> mutate(step1 = bina
 
 df$class = as.factor(df$changed - 1)
 
-df1 <- df |> filter(dataset ==  "mnist") |> group_by(class) |> mutate(diff = mean(step2 - step1))
+df1 <- df |> filter(dataset ==  "mnist") |> group_by(class, method) |> mutate(diff = mean(step2 - step1))
 
 plt1 <- ggplot(df1, aes(x = class, y = diff, fill = method, color = method)) +  facet_wrap(~ method) + 
 	geom_col(data = df1, aes(x = class, y = diff, color = method), width = 0.7) +

### 2025-08-26 coupling.tex
Fixes from Peter' proofreading

@@
 \begin{align*}
-	\divm\nolimits_\textrm{KL} (\boldsymbol{d}, \boldsymbol{d'})= \sum d_i \log (d_i/ d'_i)
+	\divm\nolimits_\textrm{KL} (\boldsymbol{d}, \boldsymbol{d'})= \sum d_i \log (d_i/ d'_i).
 \end{align*}
@@
 It is useful to consider the graph on $K$ vertices, where vertices correspond to the classes and edges to the selected equations.
-It cannot have a cycle, otherwise the subsystem of Bradley-Terry equations would be overdetermined for unknowns representing the vertices of the cycle.
+It cannot have a cycle, otherwise the subsystem of Bradley--Terry equations would be overdetermined for unknowns representing the vertices of the cycle.
 Therefore it has to be a spanning tree.
@@
 \begin{align}
-	\alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R}^\pi) \bigr) = \alpha_{ij}\biggl( \bigl(\boldsymbol{v}(\boldsymbol{R}) \bigr)^\pi\biggr)
+	\alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R}^\pi) \bigr) = \alpha_{ij}\biggl( \bigl(\boldsymbol{v}(\boldsymbol{R}) \bigr)^\pi\biggr).
 \end{align}
@@
 	\label{prop:ensemble}
-Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\boldsymbol{e} = \bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant.
+Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\boldsymbol{e} = \bigoplus_m a_m \boldsymbol{v}_m$ is also Bayes covariant.
 \end{prop}

### 2025-08-26 discussion.tex
Fixes from Peter' proofreading

@@
 
-Let us now turn to recommendation to practitioners on how to handle change of priors in one-vs-one probabilistic models. It is possible to choose any of the following approaches
+Let us now turn to recommendation to practitioners on how to handle change of priors in one-vs-one probabilistic models. It is possible to choose any of the following approaches:
 
@@
 	\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.
-The method of Hastie-Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu--Lin--Weng \cite{wu2004probability}.}
+The method of Hastie--Tibshirani is omitted from evaluation in Section \ref{sec:exp1}, because earlier evaluation showed it lacks robustness compared to the method of Wu--Lin--Weng \cite{wu2004probability}.}
 	\label{tab:summaryCoupling}
@@
 Secondly, there is a continuum of Bayes covariant methods which we barely sketched.
-Their properties, parameter selection,  and applicability to practical tasks need to investigated in greater detail.
+Their properties, parameter selection,  and applicability to practical tasks need to be investigated in greater detail.
 

### 2025-08-26 experiment.tex
Fixes from Peter' proofreading

@@
 Is it the orthodox method of Wu--Lin--Weng?
-An experiment to answer this question is carried out Section \ref{sec:exp1}.
+An experiment to answer this question is carried out in Section \ref{sec:exp1}.
 	\item[(b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric Bayes covariant method which  matches its performance?
@@
 	\includegraphics{exp4-truth.pdf}
-	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for radial and Wu--Lin--Weng's coupling method after change of priors.}
+	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for normal, radial and Wu--Lin--Weng's coupling method after change of priors.}
 	\label{fig:score}

### 2025-08-26 exp4-truth.R

@@ -6,7 +6,7 @@ df <- read.csv("data/exp4.csv") |>  mutate(step2 = multi) |> mutate(step1 = bina
 
 df$class = as.factor(df$changed - 1)
 
-df1 <- df |> filter(dataset ==  "mnist") |> group_by(class, method) |> mutate(diff = mean(step2 - step1))
+df1 <- df |> filter(dataset ==  "mnist") |> group_by(class, method) |> mutate(diff = mean(step2 - step1)) |> mutate(method = ifelse(method == "wlw2", "wlw", method))
 
 plt1 <- ggplot(df1, aes(x = class, y = diff, fill = method, color = method)) +  facet_wrap(~ method) + 
 	geom_col(data = df1, aes(x = class, y = diff, color = method), width = 0.7) +

### 2025-09-08 els.tex
New target: els.pdf for Pattern Recognition

%\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style
\documentclass[preprint,12pt]{elsarticle}
%%\documentclass[pdflatex,sn-mathphys-ay]{sn-jnl}% Math and Physical Sciences Author Year Reference Style
%%\documentclass[pdflatex,sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[pdflatex,sn-vancouver-num]{sn-jnl}% Vancouver Numbered Reference Style
%%\documentclass[pdflatex,sn-vancouver-ay]{sn-jnl}% Vancouver Author Year Reference Style
%%\documentclass[pdflatex,sn-apa]{sn-jnl}% APA Reference Style
%%\documentclass[pdflatex,sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style

%%%% Standard Packages
%%<additional latex packages if required can be included here>
\journal{Pattern Recognition}

\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published 
%%%%  by Springer Nature. The guidance has been prepared in partnership with 
%%%%  production teams to conform to Springer Nature technical requirements. 
%%%%  Editorial and presentation requirements differ among journal portfolios and 
%%%%  research disciplines. You may find sections in this template are irrelevant 
%%%%  to your work and are empowered to omit any such section if allowed by the 
%%%%  journal you intend to submit to. The submission guidelines and policies 
%%%%  of the journal take precedence. A detailed User Manual is available in the 
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

\usepackage{makecell}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{tikz-cd}
\usepackage[utf8]{inputenc} % Enable UTF-8 encoding
\usepackage[T1]{fontenc}
\usepackage{textgreek}
\usepackage{ifthen}
%\undef\orcidlogo

\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{assumption}{Assumption}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
\DeclareMathOperator*{\divm}{div}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

\usepackage{etoolbox}
\let\orcidlogo\relax
\usepackage{orcidlink}

\begin{document}

\begin{frontmatter}

\title{New Bayes covariant coupling methods for adapting to change of priors in one-vs-one classification}
%%=============================================================%%
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% \author*[1,2]{\fnm{Joergen W.} \spfx{van der} \sur{Ploeg} 
%%  \sfx{IV}}\email{iauthor@gmail.com}
%%=============================================================%%

%\author{\fnm{Ondrej} \sur{Šuch}\orcidlink{0000-0002-8140-241X}}\email{ondrejs@savbb.sk}
%%\equalcont{These authors contributed equally to this work.}
%
%\author{\fnm{Peter} \sur{Novotný}\orcidlink{0000-0002-7949-5215}}\email{peter.novotny@fri.uniza.sk}
%
%\author{\fnm{Ali} \sur{Haidar}\orcidlink{0000-0002-7498-4220}}\email{haidar@savbb.sk}
%%\equalcont{These authors contributed equally to this work.}
%
%%
%\affil[1]{\orgdiv{Matematický ústav}, \orgname{Slovenská akadémia vied}, 
%\orgaddress{\street{Ďumbierska 1}, \city{Banská Bystrica}, \postcode{97411}, \country{Slovakia}}}
%
%\affil[2]{\orgdiv{Fakulta riadenia a informatiky}, \orgname{Žilinská Univerzita v Žiline}, 
%\orgaddress{\street{Univerzitná 8215/1}, \city{Žilina}, \postcode{01026},  \country{Slovakia}}}
%
%\affil[3]{\orgdiv{Fakulta matematiky, fyziky a informatiky}, 
%\orgname{Univerzita Komenského}, \orgaddress{\street{Mlynská dolina F1}, \city{Bratislava}, \postcode{84248},  
%\country{Slovakia}}}
%\author{hhhh}
%\title{} %% Article title

%% Authors
\author[1]{Ondrej Šuch}
\ead{ondrejs@savbb.sk}

\author[2]{Peter Novotný}
\ead{peter.novotny@fri.uniza.sk}

\author[1,3]{Ali Haidar}
\ead{haidar@savbb.sk}

%% Corresponding author note
\cortext[cor1]{Corresponding author. Email: haidar@savbb.sk}

%% Affiliations
\affiliation[1]{organization={Matematický ústav, Slovenská akadémia vied},%
            addressline={Ďumbierska 1}, 
            city={Banská Bystrica},
            postcode={97411}, 
            country={Slovakia}}

\affiliation[2]{organization={Fakulta riadenia a informatiky, Žilinská Univerzita v Žiline},%
            addressline={Univerzitná 8215/1}, 
            city={Žilina},
            postcode={01026}, 
            country={Slovakia}}

\affiliation[3]{organization={Fakulta matematiky, fyziky a informatiky, Univerzita Komenského},%
            addressline={Mlynská dolina F1}, 
            city={Bratislava},
            postcode={84248}, 
            country={Slovakia}}

%%==================================%%
%% Sample for unstructured abstract %%
%%==================================%%

\begin{abstract}
Label shift is one kind of distribution shift affecting classification models. 
To address label shift one can use transformation inspired by Bayes classifiers to 
adjust predictions of probabilistic classification models. 
However, there is an ambiguity how to apply this transformation in the case of  probabilistic models built 
in one-vs-one (also called pairwise) fashion. One-vs-one classification relies on the choice of a coupling
method. Some coupling methods---called Bayes covariant---are not affected by the ambiguity. 
Adopting a Bayes covariant method would be the ideal solution to the ambiguity. 
However, the most commonly used coupling  method of Wu--Lin--Weng is not Bayes covariant. 
In our study we present elements of theory of coupling methods and exhibit new Bayes covariant coupling methods.
One class is formed by arboreal methods. 
Additional methods can be formed by the way of ensembling. We compare their performance with that of Wu--Lin--Weng's coupling method. In majority of cases, it is possible to find a Bayes covariant method matching performance of Wu--Lin--Weng's method. 
\end{abstract}

\begin{keyword}
 distribution shift\sep label shift\sep pairwise coupling\sep one-vs-one classification\sep Bayes classifier.
\end{keyword}

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

\end{frontmatter}
%\maketitle

% \ifthenelse{\not\equal{\mysecret}{1}}{
\input{intro.tex}

\input{theory.tex}

\input{coupling.tex}

\input{experiment.tex}

\input{discussion.tex}

% }{
% }

%\backmatter
%\bmhead{Acknowledgements}

%Acknowledgements are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.

%Please refer to Journal-level guidance for any specific requirements.

%\ifthenelse{\not\equal{\mysecret}{2}}{

\section*{Declarations}

%Some journals require declarations to be submitted in a standardised format. Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section. If yes, your manuscript must contain the following sections under the heading `Declarations':

\begin{itemize}
\item Funding Ondrej Šuch and Ali Haidar were  partially supported by grants VEGA 2/0172/22 Classification using ensembles of neural networks and VEGA 2/0056/25 Cycles and edge colorings of cubic graphs. Peter Novotný did not receive support from any organization for the submitted work.
\item Conflict of interest/Competing interests: Authors declare no competing interests.
\item Ethics approval and consent to participate: Not applicable.
\item Consent for publication: Not applicable.
\item Data availability: All data is available from https://www.csie.ntu.edu.tw/~cjlin/papers/svmprob/data/, and also upon request from the authors.
\item Materials availability: Not applicable.
\item Code availability: Code is available upon request.
\item Author contribution: All authors contributed equally to preparation of manuscript.
\item Acknowledgement: We thank to Muhammad Azeem for help with proof reading this paper
\end{itemize}

\noindent
%If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.

%%===================================================%%
%% For presentation purpose, we have included        %%
%% \bigskip command. Please ignore this.             %%
%%===================================================%%
%\bigskip
%\begin{flushleft}%
%Editorial Policies for:

%\bigskip\noindent
%Springer journals and proceedings: \url{https://www.springer.com/gp/editorial-policies}

%\bigskip\noindent
%Nature Portfolio journals: \url{https://www.nature.com/nature-research/editorial-policies}

%\bigskip\noindent
%\textit{Scientific Reports}: \url{https://www.nature.com/srep/journal-policies/editorial-policies}

%\bigskip\noindent
%BMC journals: \url{https://www.biomedcentral.com/getpublished/editorial-policies}
%\end{flushleft}
%
%}{
%}

%\ifthenelse{\not\equal{\mysecret}{1}}{

\begin{appendices}

\input{appendix.tex}
%\section{Section title of first appendix}\label{secA1}
%
%An appendix contains supplementary information that is not an essential part of the text itself but which may be helpful in providing a more comprehensive understanding of the research problem or it is information that is too cumbersome to be included in the body of the paper.

%%=============================================%%
%% For submissions to Nature Portfolio Journals %%
%% please use the heading ``Extended Data''.   %%
%%=============================================%%

%%=============================================================%%
%% Sample for another appendix section			       %%
%%=============================================================%%

%% \section{Example of another appendix section}\label{secA2}%
%% Appendices may be used for helpful, supporting or essential material that would otherwise 
%% clutter, break up or be distracting to the text. Appendices can consist of sections, figures, 
%% tables and equations etc.
% }{}

\end{appendices}

%%===========================================================================================%%
%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
%% system, please include the references within the manuscript file itself. You may do this  %%
%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
%% file, and delete the associated \verb+\bibliography+ commands.                            %%
%%===========================================================================================%%

%\bibliography{sn-bibliography}% common bib file
%\nocite{*}
%\bibliographystyle{elsarticle-num} % or elsarticle-harv
%\bibliography{paper}% common bib file
%}{
%}
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl

\begin{thebibliography}{00}

\bibitem{chow:68}
C.~K. Chow and C.~N. Liu.
Approximating discrete probability distributions with dependence trees.
\emph{IEEE Transactions on Information Theory}, 14(3):462--467, 1968.

\bibitem{pearl:88}
J.~Pearl.
\emph{Probabilistic Reasoning in Intelligent Systems: Networks of Plausible Inference}.
Morgan Kaufman Publishers, San Mateo, CA, 1988.

\bibitem{shannon1948mathematical}
C.~E. Shannon.
A mathematical theory of communication.
\emph{The Bell System Technical Journal}, 27(3):379--423, 1948.

\bibitem{wu2004probability}
T.-F. Wu, C.-J. Lin, and R.~C. Weng.
Probability estimates for multi-class classification by pairwise coupling.
\emph{Journal of Machine Learning Research}, 5:975--1005, 2004.

\bibitem{hastie1998classification}
T.~Hastie and R.~Tibshirani.
Classification by pairwise coupling.
\emph{Annals of Statistics}, 26(3):451--471, 1998.

\bibitem{brier1950verification}
G.~W. Brier.
Verification of forecasts expressed in terms of probability.
\emph{Monthly Weather Review}, 78(1):1--3, 1950.

\bibitem{selten1998axiomatic}
R.~Selten.
Axiomatic characterization of the quadratic scoring rule.
\emph{Experimental Economics}, 1:43--61, 1998.

\bibitem{vsuch2016bayes}
O.~{\v{S}}uch and S.~Barreda.
Bayes covariant multi-class classification.
\emph{Pattern Recognition Letters}, 84:99--106, 2016.

\bibitem{james2013introduction}
G.~James, D.~Witten, T.~Hastie, R.~Tibshirani, et al.
\emph{An Introduction to Statistical Learning}.
Springer, New York, 2013.

\bibitem{buja2005loss}
A.~Buja, W.~Stuetzle, and Y.~Shen.
Loss functions for binary class probability estimation and classification: Structure and applications.
\emph{Working draft}, 3:13, 2005.

\bibitem{gneiting2007strictly}
T.~Gneiting and A.~E. Raftery.
Strictly proper scoring rules, prediction, and estimation.
\emph{Journal of the American Statistical Association}, 102(477):359--378, 2007.

\bibitem{vsuch2015new}
O.~{\v{S}}uch, {\v{S}}. Benu{\v{s}}, and A.~Tinajov{\'a}.
A new method to combine probability estimates from pairwise binary classifiers.
\emph{RMJ}, 1:12, 2015.

\bibitem{garg2020unified}
S.~Garg, Y.~Wu, S.~Balakrishnan, and Z.~Lipton.
A unified view of label shift estimation.
\emph{Advances in Neural Information Processing Systems}, 33:3290--3300, 2020.

\bibitem{tasche2017fisher}
D.~Tasche.
Fisher consistency for prior probability shift.
\emph{Journal of Machine Learning Research}, 18(95):1--32, 2017.

\bibitem{kressel19991999}
U.~Kressel.
1999 Pairwise Classification and Support Vector Machines.
In \emph{Advances in Kernel Methods: Support Vector Learning}. MIT Press, 1999.

\bibitem{barnard1935secular}
M.~M. Barnard.
The secular variations of skull characters in four series of Egyptian skulls.
\emph{Annals of Eugenics}, 6(4):352--371, 1935.

\bibitem{martin1936study}
E.~S. Martin.
A study of an Egyptian series of mandibles, with special reference to mathematical methods of sexing.
\emph{Biometrika}, 28(1/2):149--178, 1936.

\bibitem{galar2011overview}
M.~Galar, A.~Fern{\'a}ndez, E.~Barrenechea, H.~Bustince, and F.~Herrera.
An overview of ensemble methods for binary classifiers in multi-class problems: Experimental study on one-vs-one and one-vs-all schemes.
\emph{Pattern Recognition}, 44(8):1761--1776, 2011.

\bibitem{vsipka2022hitchhiker}
T.~{\v{S}}ipka, M.~{\v{S}}ulc, and J.~Matas.
The hitchhiker's guide to prior-shift adaptation.
In \emph{Proceedings of the IEEE/CVF Winter Conference on Applications of Computer Vision}, pages 1516--1524, 2022.

\bibitem{lipton2018detecting}
Z.~Lipton, Y.-X. Wang, and A.~Smola.
Detecting and correcting for label shift with black box predictors.
In \emph{International Conference on Machine Learning}, pages 3122--3130. PMLR, 2018.

\bibitem{zhang2023dive}
A.~Zhang, Z.~C. Lipton, M.~Li, and A.~J. Smola.
\emph{Dive into Deep Learning}.
Cambridge University Press, Cambridge, 2023.

\bibitem{sugiyama2007covariate}
M.~Sugiyama, M.~Krauledat, and K.-R. M{\"u}ller.
Covariate shift adaptation by importance weighted cross validation.
\emph{Journal of Machine Learning Research}, 8(5), 2007.

\bibitem{refregier1991probabilistic}
P.~Refregier and F.~Vallet.
Probabilistic approach for multiclass classification with neural networks.
In \emph{Artificial Neural Networks}, pages 1003--1006. Elsevier, Amsterdam, 1991.

\bibitem{price1994pairwise}
D.~Price, S.~Knerr, L.~Personnaz, and G.~Dreyfus.
Pairwise neural network classifiers with probabilistic outputs.
In \emph{Advances in Neural Information Processing Systems}, 7, 1994.

\bibitem{zahorian1999partitioned}
S.~A. Zahorian and Z.~B. Nossair.
A partitioned neural network approach for vowel classification using smoothed time/frequency features.
\emph{IEEE Transactions on Speech and Audio Processing}, 7(4):414--425, 1999.

\end{thebibliography}

\end{document}
